### 2022-06-24 Notes_3dH3.tex
initial commit with small intro and first step for IIB

%!TEX output_directory = aux

\documentclass[11pt]{article}

\usepackage[english]{babel}

% ---- FONT & MICROTYPOGRAPHY ----
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{moresize}

% ---- FORMATTING ----
\usepackage{csquotes,textcase,xspace}

% ---- PAGE LAYOUT ----
\usepackage{geometry}
\geometry{top=2.5cm,bottom=2cm,inner=2cm,outer=2cm,footnotesep=7mm plus 4pt minus 4pt}
\usepackage{setspace}
\setstretch{1.1}

% ---- GRAPHIQUE ----
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[font=small,labelfont=bf,labelsep=space]{caption}
\usepackage{subfigure}
\captionsetup{width=0.9\textwidth,font={small,stretch=1.1}}
\addto\captionsenglish{\renewcommand{\figurename}{Fig.}}
\addto\captionsenglish{\renewcommand{\tablename}{Tab.}}
\definecolor{JoliBleu}{rgb}{0,0.55,0.55}
\definecolor{JoliVert}{rgb}{0.15,0.6,0}
\definecolor{JoliRouge}{rgb}{0.86,0.08,0}
\definecolor{JoliJaune}{rgb}{1,0.75,0}
\definecolor{JoliGris}{rgb}{0.52,0.52,0.51}
\definecolor{myblue}{RGB}{26, 77, 116}
\definecolor{myorange}{RGB}{181, 116, 30}
\definecolor{mydarkorange}{RGB}{166, 88, 0}
\definecolor{mygreen}{RGB}{21, 124, 80}
\definecolor{myblack}{RGB}{43, 65, 82}
\definecolor{myred}{rgb}{0.5, 0.0, 0.13}

% ---- SECTIONING ----
\usepackage{titlesec}
\titleformat{\section}[block]{\Large\boldmath\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}[block]{\large\boldmath\bfseries}{\thesubsection}{0.5em}{}
\usepackage{appendix}
\renewcommand{\setthesection}{\Alph{section}}
\renewcommand{\restoreapp}{}
\makeatletter
\renewcommand{\theequation}{\thesection.\arabic{equation}}
\@addtoreset{equation}{section}
\makeatother

% ---- FOOTERS HEADERS ----
\usepackage[bottom]{footmisc}
\usepackage{fancyhdr}

% ---- TABLE OF CONTENTS ----
\usepackage{titletoc}
\setcounter{tocdepth}{3}

% ---- BIBLIOGRAPHY ----
\usepackage[nosort]{cite}
\bibliographystyle{utphys}
\newcommand{\eprint}[1]{{\href{http://arxiv.org/abs/#1}{\texttt{[#1]}}}}
\newcommand{\eprintN}[1]{{\href{http://arxiv.org/abs/#1}{\texttt{#1 [hep-th]}}}}
\newcommand{\doi}[2]{\href{http://dx.doi.org/#2}{#1}}

% ---- HYPER REF ----
\usepackage{hyperref}
\hypersetup{colorlinks=true,
        pdfstartview=FitV,
        linkcolor= mydarkorange,
        citecolor= mydarkorange,
        urlcolor= JoliGris!60!black,
        hypertexnames=false,
        linktoc=page}

% ---- TIKZ ----
\usepackage{tikz}
\usetikzlibrary{calc}

% ---- MATHS ----
\usepackage{amsmath,amssymb,amsfonts,dsfont}
\usepackage{mathrsfs}
\usepackage{physics}
\usepackage{ytableau}
\ytableausetup{boxsize=1.1em,centertableaux}
\usepackage{stmaryrd}
\usepackage{nicefrac}
\allowdisplaybreaks[1]
% \usepackage{bbold}
\usepackage{cases}
\usepackage{bm}

% ---- TABLES ----
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{pdflscape}
\usepackage{array}

% ---- ENUMERATION ----
\usepackage[shortlabels]{enumitem}

% ---- MATHS COMMANDS ----
\newcommand{\A}{\ensuremath{\mathcal{A}}\xspace}
\newcommand{\F}{\ensuremath{\mathcal{F}}\xspace}
\renewcommand{\H}{\ensuremath{\mathcal{H}}\xspace}
\newcommand{\M}{\ensuremath{\mathcal{M}}\xspace}
\renewcommand{\P}{\ensuremath{\mathcal{P}}\xspace}
\newcommand{\J}{\ensuremath{\mathcal{J}}\xspace}
\renewcommand{\d}{\ensuremath{\mathrm{d}}\xspace}
\renewcommand{\H}{\ensuremath{\mathcal{H}}\xspace}
\newcommand{\SO}{\ensuremath{\mathrm{SO}}\xspace}
\renewcommand{\O}{\ensuremath{\mathrm{O}}\xspace}
\newcommand{\SL}{\ensuremath{\mathrm{SL}}\xspace}
\newcommand{\E}{\ensuremath{\mathrm{E}}\xspace}
\newcommand{\R}{\ensuremath{\mathbb{R}}\xspace}
\newcommand{\Odd}{\ensuremath{\mathrm{O}(d,d)}\xspace}
\newcommand{\odd}{\ensuremath{\mathfrak{o}(d,d)}\xspace}
\renewcommand{\Tr}[1]{\ensuremath{\mathrm{Tr}\left(#1\right)}\xspace}

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}

% ---- COMMENTS ----
\newcommand{\ce}[1]{\marginpar{\parbox{\marginparwidth}{\boldmath $\Longleftarrow$}}
{\boldmath\bfseries #1}}

% ---- TITLE PAGE ----
\usepackage[affil-it]{authblk}
\def\preprint{}

\makeatletter
\def\@maketitle{%
  \newpage
  \null\hfill\texttt{\preprint}
  \vskip 4em%
  \begin{center}%
  \let \footnote \thanks
    {\LARGE\bfseries\boldmath \@title \par}%
    \vskip 2.5em%
    % {\large
    %   \lineskip .5em%
    %   \begin{center}
    %     \begin{minipage}{0.95\textwidth}
    %         \begin{tabular}[t]{c}%
    %         \@author
    %         \end{tabular}
    %     \end{minipage}    
    %   \end{center}\par}%
    % \vskip 1em%
   {\large \@date}%
  \end{center}%
  \par
  \vskip 1.5em}
\makeatother

\renewcommand\Authands{ and }

\title{Notes: New gaugings in 3d from three-form}
\author{}

\begin{document}

\maketitle

Three-form field-strengths are auxiliary in three dimensions and can be integrated out, giving rise to additional gaugings and contributions to the scalar potential, or equivalently leading to new terms in the embedding tensor (see ref.~\cite{Deger:2014ofa,Eloy:2021fhc} for explicit realisations in half-maximal supergravity). We want to generalize this to maximal supergravity. For a given $\E_{8(8)}$ consistent truncations of gauge group $G_{0}$, we ask the question whether it is possible to turn on additional components in the embedding tensor (corresponding to three-form degrees of freedom). If so, the new consistent truncation has gauging $G\supset G_{0}$. We first need to identify which components of the embedding tensor correspond to these degrees of freedom, and to count the number of singlets under $G_{0}$ within them. There will be at least one singlet, corresponding to the gauging of $G_{0}$ in the initial truncation. Any additional singlet would indicate additional parameters to play with, possibly leading to new vacua.

\section{Truncations within \texorpdfstring{$\SL(8)_{\rm IIB}\subset\E_{8(8)}$}{SL(8)IIB in E8(8)}}

\paragraph{10d origin of the three-forms} Both the 10d two-forms $\hat{C}_{\hat\mu\hat\nu}^{\alpha}$ ($\alpha\in{1,2}$ for $\SL(2)$ doublet) and the 10d four-form $\hat{C}_{\hat\mu\hat\nu\hat\rho\hat\sigma}$ give two-form potentials $C^{\alpha}_{\mu\nu}$ and $C_{\mu\nu mn}$ in 3d ($m,n\in\llbracket1,7\rrbracket$ are $\SL(7)$ indices). Their three-form field-strengths are dual to purely internal seven-form and five-form field-strengths $H_{(7)}^{\alpha}$ and $H_{(5)}$, respectively. We note $C_{(6)}^{\alpha}$ and $C_{(4)}$ the six-form and four-form potentials from which they derive.

\paragraph{\boldmath $C_{(6)}^{\alpha}$ and $C_{(4)}$ in $\SL(8)_{\rm IIB}\times\R_{+}$} In the $\E_{8(8)}\rightarrow\SL(7)\times\SL(2)\times\R_{+}$ decomposition
\begin{equation}
  \begin{aligned}
    \bm{248} \longrightarrow & \ (\bm{7},\bm{1})_{12} \oplus (\bm{\bar{7}},\bm{2})_{6} \oplus (\bm{\bar{35}},\bm{1})_{6} \oplus (\bm{21},\bm{2})_{3} \oplus (\bm{1},\bm{1})_{0} \oplus (\bm{1},\bm{3})_{0} \oplus (\bm{48},\bm{1})_{0} \\
    & \oplus (\bm{\bar{21}},\bm{2})_{-3} \oplus (\bm{35},\bm{1})_{-6} \oplus (\bm{7},\bm{2})_{-9} \oplus (\bm{\bar{7}},\bm{1})_{-12}
  \end{aligned} 
\end{equation}
of the $\E_{8(8)}$ coordinates $X^{M}$, $C_{(6)}^{\alpha}$ and $C_{(4)}$ sit in the representations $(\bm{7},\bm{2})_{-9}$ and $(\bm{35},\bm{1})_{-6}$, respectively.\footnote{The internal coordinates $y^{m}$ are in the representation $(\bm{7},\bm{1})_{12}$, and $\bm{\bar{7}}^{\wedge 4}=\bm{35}$ and $\bm{\bar{7}}^{\wedge 6}=\bm{7}$.} They originate from the representations $\bm{8}_{3}\oplus\bm{63}_{0}$ and $\bm{56}_{1}$ in $\E_{8(8)}\rightarrow\SL(9)\rightarrow\SL(8)_{\rm IIB}\times\R_{+}$ decomposition
\begin{equation}
  \bm{248} \longrightarrow \bm{80} \oplus \bm{84} \oplus \bm{\bar{84}} \longrightarrow \left[\bm{8}_{3} \oplus \bm{1}_{0} \oplus \bm{63}_{0} \oplus \bm{\bar{8}}_{-3}\right] \oplus \left[\bm{56}_{1} \oplus \bm{28}_{-2}\right] \oplus \left[\bm{\bar{28}}_{2} \oplus \bm{\bar{56}}_{-1}\right],
\end{equation}
whereas the internal coordinates are in the representation $\bm{\bar{28}}_{2}$.

\ce{Give further details?}

\paragraph{\boldmath $H_{(7)}^{\alpha}$ and $H_{(5)}$ in $\SL(8)_{\rm IIB}$} Now that we know what are the $\SL(8)_{\rm IIB}\times\R_{+}$ representation corresponding to the internal coordinates, $C_{(6)}^{\alpha}$ and $C_{(4)}$, we can infer those of $H_{(7)}^{\alpha}$ and $H_{(5)}$:
\begin{equation}
  \begin{aligned}
    H_{(7)}^{\alpha} & \subset \bm{\bar{28}}_{2} \otimes \left(\bm{8}_{3}\oplus\bm{63}_{0}\right) = \bm{\bar{8}}_{5} \oplus \bm{\bar{216}}_{5} \oplus \bm{\bar{28}}_{2} \oplus \bm{\bar{36}}_{2} \oplus \bm{\bar{420}}_{2} \oplus \bm{\bar{1280}}_{2}, \\
    H_{(5)} & \subset \bm{\bar{28}}_{2} \otimes \bm{56}_{1} = \bm{8}_{3} \oplus \bm{216}_{3} \oplus \bm{1344}_{3}.
  \end{aligned}
\end{equation}

\paragraph{\boldmath $H_{(7)}^{\alpha}$ and $H_{(5)}$ in the embedding tensor}

\ce{Give decomposition of the embedding tensor to identify components, and count singlets.}

\bibliography{ref}

\end{document}

### 2022-06-24 Notes_3dH3.tex
full IIB and beginning of 6d

@@
 
+\section{\texorpdfstring{${\rm AdS}_{3}\times S^{3}$}{AdS3xS3}: a proof of concept}
+We start by reproducing the analysis of ref.~\cite{Eloy:2021fhc} to prove the validity of our method.
+We consider reductions within the minimal ${\cal N}=(1,0)$ six-dimensional supergravity, leading to duality group $\SO(4,4)$ in three dimensions, from which the half-maximal cases ${\cal N}=(1,1)$ and ${\cal N}=(2,0)$ can be deduced (in those cases the duality group in three dimensions in $\SO(8,4)$).
+
+The coordinates $X^{[MN]}$ of the $\SO(p,q)$ exceptional field theory of ref.~\cite{Hohm:2017wtr} sit in the adjoint $\bm{28}$ of $\SO(4,4)$.
+Under $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}$, it decomposes into
+\begin{equation}
+  \begin{aligned}
+    \bm{28} &\longrightarrow \bm{6}_{2} \oplus \bm{1}_{0} \oplus \bm{15}_{0} \oplus \bm{6}_{-2},\\
+    X^{MN} &\longrightarrow \{Y^{A0},Y^{0}{}_{0},Y^{[AB]},Y^{A}{}_{0}\}.
+  \end{aligned}
+\end{equation}
+Further decomposing $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}\rightarrow\SL(3)\times\R_{+}\times\R_{+}$, we get
+\begin{equation}
+  \bm{28} \longrightarrow \left[\bm{\bar{3}}_{2,2} \oplus \bm{3}_{-2,2}\right] \oplus \bm{1}_{0,0} \oplus \left[\bm{3}_{4,0} \oplus \bm{1}_{0,0} \oplus \bm{8}_{0,0} \oplus \bm{\bar{3}}_{-4,0}\right] \oplus \left[\bm{\bar{3}}_{2,-2} \oplus \bm{3}_{-2,-2}\right].
+\end{equation}
+They are two physically different possibilities to embed the internal coordinates in $X^{MN}$, corresponding to the two different half-maximal supergravities in six dimensions:\footnote{The choices are equivalent in $\SO(4,4)$ (through triality), but different once embedded in $\SO(8,4)$.}
+\begin{equation}
+  \begin{aligned}
+    {\cal N}=(1,1):&\qquad y^{m}=Y^{m0}\quad {\rm in}\quad  \bm{\bar{3}}_{2,2} \subset \bm{6}_{2},\\
+    {\cal N}=(2,0):&\qquad \tilde{y}_{m}=\varepsilon_{mnp}Y^{np}\quad {\rm in}\quad  \bm{3}_{4,0} \subset \bm{15}_{0}.
+  \end{aligned}
+\end{equation}
+
 \section{Truncations within \texorpdfstring{$\SL(8)_{\rm IIB}\subset\E_{8(8)}$}{SL(8)IIB in E8(8)}}
+We analyse here whether the type IIB $S^{7}$ truncation of ref.~\cite{Galli:2022idq} admit additional gaugings.
 
@@
 
-\paragraph{\boldmath $H_{(7)}^{\alpha}$ and $H_{(5)}$ in $\SL(8)_{\rm IIB}$} Now that we know what are the $\SL(8)_{\rm IIB}\times\R_{+}$ representation corresponding to the internal coordinates, $C_{(6)}^{\alpha}$ and $C_{(4)}$, we can infer those of $H_{(7)}^{\alpha}$ and $H_{(5)}$:
-\begin{equation}
+\paragraph{\boldmath $H_{(7)}^{\alpha}$ and $H_{(5)}$ in $\SL(8)_{\rm IIB}$} Now that we know what are the $\SL(8)_{\rm IIB}\times\R_{+}$ representations corresponding to the internal coordinates, $C_{(6)}^{\alpha}$ and $C_{(4)}$, we can infer those of $H_{(7)}^{\alpha}$ and $H_{(5)}$:
+\begin{equation}  \label{eq:H7H5inIIB}
   \begin{aligned}
@@
 
-\paragraph{\boldmath $H_{(7)}^{\alpha}$ and $H_{(5)}$ in the embedding tensor}
-
-\ce{Give decomposition of the embedding tensor to identify components, and count singlets.}
+\paragraph{\boldmath $H_{(7)}^{\alpha}$ and $H_{(5)}$ in the embedding tensor} Under $\E_{8(8)}\rightarrow\SL(9)\rightarrow\SL(8)_{\rm IIB}\times\R_{+}$, the $\E_{8(8)}$ embedding tensor decomposes as
+\begin{equation}
+  \begin{aligned}
+    \bm{3875} &\longrightarrow {\color{mydarkorange}\bm{80}} \oplus \bm{240} \oplus {\color{mydarkorange}\bm{\bar{240}}} \oplus \bm{1050} \oplus {\color{mydarkorange}\bm{\bar{1050}}} \oplus {\color{mydarkorange}\bm{1215}} \\
+    &\longrightarrow \left[{\color{mydarkorange}\bm{8}_{3}} \oplus \bm{1}_{0} \oplus \bm{63}_{0} \oplus \bm{\bar{8}}_{-3}\right] \oplus \left[\bm{168}_{1} \oplus \bm{28}_{-2} \oplus \bm{36}_{-2} \oplus \bm{8}_{-5}\right] \oplus \left[{\color{mydarkorange}\bm{\bar{8}}_{5}} \oplus {\color{mydarkorange}\bm{\bar{28}}_{2}} \oplus {\color{mydarkorange}\bm{\bar{36}}_{2}} \oplus \bm{\bar{168}}_{-1} \right] \\
+    &\quad \oplus \left[\bm{70}_{4} \oplus \bm{56}_{1} \oplus \bm{504}_{1} \oplus \bm{420}_{-2}\right] \oplus \left[{\color{mydarkorange}\bm{\bar{420}}_{2}} \oplus \bm{\bar{56}}_{-1} \oplus \bm{\bar{504}}_{-2}\oplus \bm{\bar{70}}_{-4} \right] \oplus \left[{\color{mydarkorange}\bm{216}_{3}} \oplus \bm{63}_{0} \oplus \bm{720}_{0} \oplus \bm{\bar{216}}_{-3}\right].
+  \end{aligned}
+\end{equation}
+The coloured representations are those that can originate from $H_{(7)}^{\alpha}$ and $H_{(5)}$, \textit{i.e.} those in common with eq.~\eqref{eq:H7H5inIIB}.
+Among them, only the $\bm{\bar{36}}_{2}$ features a singlet under $\SO(8)_{\rm IIB}$.
+This is the singlet used in ref.~\cite{Galli:2022idq} to support the $S^{7}$ truncation, which thus do not admit further gaugings.
 

### 2022-06-24 Notes_3dH3.tex
Sections on 6d (1,0), (2,0) and (1,1), and schematic results for IIA.

@@
 We start by reproducing the analysis of ref.~\cite{Eloy:2021fhc} to prove the validity of our method.
-We consider reductions within the minimal ${\cal N}=(1,0)$ six-dimensional supergravity, leading to duality group $\SO(4,4)$ in three dimensions, from which the half-maximal cases ${\cal N}=(1,1)$ and ${\cal N}=(2,0)$ can be deduced (in those cases the duality group in three dimensions in $\SO(8,4)$).
+They are two different half-maximal supergravities in six dimensions, with ${\cal N}=(2,0)$ and ${\cal N}=(1,1)$.
+They both admit consistent truncation on $S^{3}$~\cite{Hohm:2017wtr,Samtleben:2019zrh}, leading to half-maximal gauged supergravity in three dimensions with duality group $\SO(8,4)$.
+These truncations have isometry group $\SO(4)\times\SO(4)$ and are constructed in terms of two different $\SO(3,3)$ subgroups of $\SO(8,4)$:
+\begin{subequations}
+  \begin{align}
+    {\cal N}=(2,0):&\qquad \SO(8,4)\longrightarrow\SO(3,3)_{(2,0)}\times \SO(5,1)\longrightarrow\SO(3,3)_{(2,0)}\times \SO(5), \label{eq:SO84decomp20}\\
+    {\cal N}=(1,1):&\qquad \SO(8,4)\longrightarrow\SO(4,4)\times \SO(4)\longrightarrow\SO(3,3)_{(1,1)}\times\R_{+}\times\SO(4). \label{eq:SO84decomp11}
+  \end{align}
+\end{subequations}
 
-The coordinates $X^{[MN]}$ of the $\SO(p,q)$ exceptional field theory of ref.~\cite{Hohm:2017wtr} sit in the adjoint $\bm{28}$ of $\SO(4,4)$.
-Under $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}$, it decomposes into
+  \subsection{\texorpdfstring{${\cal N}=(2,0)$}{N=(2,0)} six-dimensional supergravity}
+
+  \paragraph{6d origin of the three-forms} The ${\cal N}=(2,0)$ supergravity features 5 self-dual two-forms $\hat{B}_{\hat\mu\hat\nu}^{i}$ ($i\in\llbracket1,5\rrbracket$ is the $\SO(5)$ vector index).
+They lead to two-form potentials $B_{(2)}^{i}$ in 3d, with three-form field strengths dual to purely internal three-form field-strengths $H_{(3)}^{i}$.
+
+  \ce{Should we consider the anti-self dual two-form also?}
+
+  \paragraph{\boldmath $B_{(2)}^{i}$ in $\SO(3,3)_{(2,0)}\times\SO(5)$}
+  The coordinates $X^{[MN]}$ of the $\SO(8,4)$ exceptional field theory of ref.~\cite{Hohm:2017wtr} sit in the adjoint $\bm{66}$ of $\SO(8,4)$. Under eq.~\eqref{eq:SO84decomp20}, it decomposes into
+  \begin{equation}  
+    \bm{66} \longrightarrow (\bm{6},\bm{1}) \oplus (\bm{6},\bm{5}) \oplus (\bm{15},\bm{1}) \oplus (\bm{1},\bm{5}) \oplus (\bm{1},\bm{10}).
+  \end{equation}
+  Further decomposing $\SO(3,3)_{(2,0)}\times\SO(5)\rightarrow\SL(3)\times\R_{+}\times\SO(5)$, we get
   \begin{equation}
     \begin{aligned}
-    \bm{28} &\longrightarrow \bm{6}_{2} \oplus \bm{1}_{0} \oplus \bm{15}_{0} \oplus \bm{6}_{-2},\\
-    X^{MN} &\longrightarrow \{Y^{A0},Y^{0}{}_{0},Y^{[AB]},Y^{A}{}_{0}\}.
+      \bm{66} &\longrightarrow [(\bm{\bar{3}}_{2},\bm{1})\oplus(\bm{3}_{-2},\bm{1})] \oplus [(\bm{3}_{-2},\bm{5})\oplus(\bm{\bar{3}}_{2},\bm{5})] \oplus [(\bm{3}_{4},\bm{1})\oplus(\bm{1}_{0},\bm{1})\oplus(\bm{8}_{0},\bm{1})\oplus(\bm{\bar{3}}_{-4},\bm{1})] \\
+      & \qquad \oplus (\bm{1}_{0},\bm{5}) \oplus (\bm{1}_{0},\bm{10}).
     \end{aligned}
   \end{equation}
-Further decomposing $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}\rightarrow\SL(3)\times\R_{+}\times\R_{+}$, we get
+  The internal coordinates $y^{m}$ then sit in the representation $(\bm{3}_{4},\bm{1})$ and the two-form potentials $B_{(2)}^{i}$ in $(\bm{3}_{-2},\bm{5})$, they thus originate from the $\SO(3,3)_{(2,0)}\times\SO(5)$ representations $(\bm{15},\bm{1})$ and $(\bm{6},\bm{5})$, respectively.
+
+  \paragraph{\boldmath $H_{(3)}^{i}$ in $\SO(3,3)_{(2,0)}\times\SO(5)$}
   \begin{equation}
-  \bm{28} \longrightarrow \left[\bm{\bar{3}}_{2,2} \oplus \bm{3}_{-2,2}\right] \oplus \bm{1}_{0,0} \oplus \left[\bm{3}_{4,0} \oplus \bm{1}_{0,0} \oplus \bm{8}_{0,0} \oplus \bm{\bar{3}}_{-4,0}\right] \oplus \left[\bm{\bar{3}}_{2,-2} \oplus \bm{3}_{-2,-2}\right].
+    H_{(3)}^{i} \subset(\bm{15},\bm{1})\otimes(\bm{6},\bm{5})=(\bm{6},\bm{5})\oplus(\bm{10},\bm{5})\oplus(\bm{\bar{10}},\bm{5})\oplus(\bm{64},\bm{5}).
   \end{equation}
-They are two physically different possibilities to embed the internal coordinates in $X^{MN}$, corresponding to the two different half-maximal supergravities in six dimensions:\footnote{The choices are equivalent in $\SO(4,4)$ (through triality), but different once embedded in $\SO(8,4)$.}
+
+  \paragraph{\boldmath $H_{(3)}^{i}$ in the embedding tensor}
+  The embedding tensor of the $\SO(8,4)$ exceptional theory has two different components: $\theta_{(MN)}\subset\bm{77}$ and $\theta_{[MNPQ]}\subset\bm{495}$.
+It decomposes as follows under $\SO(8,4)\rightarrow\SO(3,3)_{(2,0)}\times \SO(5)$:
   \begin{equation}
     \begin{aligned}
-    {\cal N}=(1,1):&\qquad y^{m}=Y^{m0}\quad {\rm in}\quad  \bm{\bar{3}}_{2,2} \subset \bm{6}_{2},\\
-    {\cal N}=(2,0):&\qquad \tilde{y}_{m}=\varepsilon_{mnp}Y^{np}\quad {\rm in}\quad  \bm{3}_{4,0} \subset \bm{15}_{0}.
+      \bm{77} &\longrightarrow 2\times(\bm{1},\bm{1}) \oplus (\bm{6},\bm{1}) \oplus {\color{mydarkorange}(\bm{6},\bm{5})} \oplus (\bm{20'},\bm{1}) \oplus (\bm{1},\bm{5}) \oplus (\bm{1},\bm{14}),\\
+      \bm{495} &\longrightarrow (\bm{10},\bm{1}) \oplus {\color{mydarkorange}(\bm{10},\bm{5})} \oplus (\bm{\bar{10}},\bm{1}) \oplus {\color{mydarkorange}(\bm{\bar{10}},\bm{5})} \oplus (\bm{15},\bm{1}) \oplus (\bm{1},\bm{5}) \oplus (\bm{1},\bm{10}) \\
+      &\qquad\oplus (\bm{6},\bm{10}) \oplus (\bm{6},\bm{\bar{10}}) \oplus (\bm{15},\bm{5}) \oplus (\bm{15},\bm{10}),
     \end{aligned}
   \end{equation}
+  where the colored representations are those coming from the three-forms.
+Only $(\bm{10},\bm{5})$ and $(\bm{\bar{10}},\bm{5})$ feature singlets under the isometry group $\SO(4)\times\SO(4)$.
+One of these support the $S^{3}$ reduction, while the other can be turned on, leading to new solutions as first demonstrated in ref.~\cite{Hohm:2017wtr,Samtleben:2019zrh}.
+All singlets sit in $\theta_{MNPQ}$.
+
+ \subsection{\texorpdfstring{${\cal N}=(1,1)$}{N=(1,1)} six-dimensional supergravity}
+
+  \paragraph{6d origin of the three-forms} The ${\cal N}=(1,1)$ supergravity features a two-form $\hat{B}_{\hat\mu\hat\nu}$ Both $\hat{B}_{\hat\mu\hat\nu}$ and its dual lead to two-form potentials in 3d.
+Their three-form field strengths are dual to purely internal three-form field-strengths $H_{(3)}$ and $*H_{(3)}$, of two-form potentials $C_{(2)}^{1}$ and $C_{(2)}^{2}$.
+
+  \paragraph{\boldmath $C_{(2)}^{1}$ and $C_{(2)}^{2}$in $\SO(4,4)\times\SO(4)$}
+  Under $\SO(8,4)\longrightarrow\SO(4,4)\times \SO(4)$, the coordinates $X^{[MN]}$ decompose into
+  \begin{equation}  
+    \bm{66} \longrightarrow \bm{1}^{(\bm{3},\bm{1})} \oplus \bm{1}^{(\bm{1},\bm{3})} \oplus \bm{8_{\rm v}}^{(\bm{2},\bm{2})} \oplus \bm{28}^{(\bm{1},\bm{1})}.
+  \end{equation}
+  The internal coordinates and the two-form potentials are singlets under the $\SO(4)$ factor, which is related the 6d vectors only.
+They thus all belong to the representation $\bm{28}^{(\bm{1},\bm{1})}$.
+
+  \paragraph{\boldmath $H_{(3)}$ and $*H_{(3)}$ in $\SO(4,4)\times\SO(4)$}
+  \begin{equation}
+    H_{(3)}, *H_{3}\subset\bm{28}^{(\bm{1},\bm{1})}\otimes\bm{28}^{(\bm{1},\bm{1})}=\bm{1}^{(\bm{1},\bm{1})}\oplus\bm{28}^{(\bm{1},\bm{1})}\oplus\bm{35_{\rm v}}^{(\bm{1},\bm{1})}\oplus\bm{35_{\rm s}}^{(\bm{1},\bm{1})}\oplus\bm{35_{\rm c}}^{(\bm{1},\bm{1})}\oplus\bm{300}^{(\bm{1},\bm{1})}\oplus\bm{350}^{(\bm{1},\bm{1})}.
+  \end{equation}
+
+  \paragraph{\boldmath $H_{(3)}$ and $*H_{(3)}$ in the embedding tensor}
+  \begin{equation}
+    \begin{aligned}
+      \bm{77} &\longrightarrow {\color{mydarkorange}\bm{1}^{(\bm{1},\bm{1})}} \oplus \bm{1}^{(\bm{3},\bm{3})} \oplus \bm{8_{\rm v}}^{(\bm{2},\bm{2})} \oplus {\color{mydarkorange}\bm{35_{\rm v}}^{(\bm{1},\bm{1})}},\\
+      \bm{495} &\longrightarrow {\color{mydarkorange}\bm{1}^{(\bm{1},\bm{1})}} \oplus \bm{8_{\rm v}}^{(\bm{2},\bm{2})} \oplus \bm{28}^{(\bm{1},\bm{3})} \oplus \bm{28}^{(\bm{3},\bm{1})} \oplus {\color{mydarkorange}\bm{35_{\rm s}}^{(\bm{1},\bm{1})}} \oplus {\color{mydarkorange}\bm{35_{\rm c}}^{(\bm{1},\bm{1})}} \oplus \bm{56_{\rm v}}^{(\bm{2},\bm{2})}.
+    \end{aligned}
+  \end{equation}
+  The singlets certainly gauge the trombone symmetry.
+Each $\bm{35}$ feature $\SO(4)\times\SO(4)$ singlets, but \ce{less clear how to precisely relate to ref.~\cite{Eloy:2021fhc}.
+Need to consider quadratic constraint?}
 
@@
 
-\paragraph{\boldmath $H_{(7)}^{\alpha}$ and $H_{(5)}$ in $\SL(8)_{\rm IIB}$} Now that we know what are the $\SL(8)_{\rm IIB}\times\R_{+}$ representations corresponding to the internal coordinates, $C_{(6)}^{\alpha}$ and $C_{(4)}$, we can infer those of $H_{(7)}^{\alpha}$ and $H_{(5)}$:
+\paragraph{\boldmath $H_{(7)}^{\alpha}$ and $H_{(5)}$ in $\SL(8)_{\rm IIB}\times\R_{+}$} Now that we know what are the $\SL(8)_{\rm IIB}\times\R_{+}$ representations corresponding to the internal coordinates, $C_{(6)}^{\alpha}$ and $C_{(4)}$, we can infer those of $H_{(7)}^{\alpha}$ and $H_{(5)}$:
 \begin{equation}  \label{eq:H7H5inIIB}
@@
 
+\section{Truncations within \texorpdfstring{$\SL(8)_{\rm IIA}\subset\E_{8(8)}$}{SL(8)IIA in E8(8)}}
+
+Can be seen as further reduction of four dimensional $\E_{7(7)}$ solutions on a circle. Under $\E_{8(8)}\rightarrow\E_{7(7)}\times\SL(2)\rightarrow\E_{7(7)}\times\R_{+}$,
+\begin{equation}
+  \bm{248} \longrightarrow (\bm{1},\bm{3}) \oplus (\bm{56},\bm{2}) \oplus (\bm{133},\bm{3})\longrightarrow \bm{1}_{2} \oplus \bm{56}_{1} \oplus \bm{1}_{0} \oplus \bm{133}_{0} \oplus \bm{56}_{-1} \oplus \bm{1}_{-2}.
+\end{equation}
+The $\E_{7(7)}$ coordinates are in the $\bm{56}_{1}$, and $C_{(6)}$ in $\bm{56}_{-1}$ (11d $\hat{C}_{\hat\mu\hat\nu\hat\rho}$ leads to $C_{\mu\nu\,m}$ in 3d, $H_{\mu\nu\rho\,m}$ dual to purely internal $H_{(7)}$ of potential $C_{(6)}$).
+Then,
+\begin{equation}
+    H_{(7)} \subset \bm{56}_{1} \otimes \bm{56}_{-1} = \bm{1}_{0} \oplus \bm{133}_{0} \oplus \bm{1463}_{0} \oplus \bm{1539}_{0}.
+\end{equation}
+Under $\E_{8(8)}\rightarrow\E_{7(7)}\times\SL(2)\rightarrow\E_{7(7)}\times\R_{+}$, the $\E_{8(8)}$ embedding tensor decomposes as
+\begin{equation}
+    \bm{3875} \longrightarrow \bm{133}_{2} \oplus \bm{56}_{1} \oplus \bm{912}_{1} \oplus {\color{mydarkorange}\bm{1}_{0}} \oplus {\color{mydarkorange}\bm{133}_{0}} \oplus {\color{mydarkorange}\bm{1539}_{0}} \oplus \bm{56}_{-1} \oplus \bm{912}_{-1} \oplus \bm{133}_{-2}.
+\end{equation}
+
+\paragraph{\boldmath $\SO(8)_{\rm IIA}$ singlets}
+Under $\E_{7(7)}\rightarrow\SL(8)_{\rm IIA}$:
+\begin{equation}
+  \begin{aligned}
+    \bm{133} & \longrightarrow \bm{63} \oplus \bm{70},\\
+    \bm{1539} & \longrightarrow \bm{63} \oplus \bm{378} \oplus \bm{\bar{378}} \oplus \bm{720}.
+  \end{aligned}
+\end{equation}
+No singlet other that $\bm{1}$.
+
+\paragraph{\boldmath $\SO(7)$ singlets}
+Under $\E_{7(7)}\rightarrow\SL(7)\times\R_{+}$:
+\begin{equation}
+  \begin{aligned}
+    \bm{133} & \longrightarrow \bm{1}_{0} \oplus \ldots,\\
+    \bm{1539} & \longrightarrow \bm{1}_{0} \oplus \ldots
+  \end{aligned}
+\end{equation}
+where only representations featuring $\SO(7)$ singlets have been specified.
+
+\paragraph{\boldmath $\SO(6)\times\R_{+}$ singlets}
+Under $\E_{7(7)}\rightarrow\SL(6)\times\SL(2)\times\R_{+}$:
+\begin{equation}
+  \begin{aligned}
+    \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus \ldots,\\
+    \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
+  \end{aligned}
+\end{equation}
+where only representations featuring $\SO(6)\times\R_{+}$ singlets have been specified.
+
+\paragraph{\boldmath $\SO(5)\times\SO(3)$ singlets}
+Under $\E_{7(7)}\rightarrow\SL(5)\times\SL(3)\times\R_{+}$:
+\begin{equation}
+  \begin{aligned}
+    \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus \ldots,\\
+    \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
+  \end{aligned}
+\end{equation}
+where only representations featuring $\SO(5)\times\SO(3)$ singlets have been specified.
+
+\paragraph{\boldmath $\SO(4)\times\SO(4)$ singlets}
+Under $\E_{7(7)}\rightarrow\SL(4)\times\SL(4)\times\R_{+}$:
+\begin{equation}
+  \begin{aligned}
+    \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus (\bm{1},\bm{1})_{4} \oplus (\bm{1},\bm{1})_{-4} \oplus \ldots,\\
+    \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
+  \end{aligned}
+\end{equation}
+where only representations featuring $\SO(4)\times\SO(4)$ singlets have been specified.
+
+\paragraph*{} The singlets always come from the $\bm{63}$ and $\bm{720}$ of $\SL(8)_{\rm IIB}$ (and $\bm{70}$ for $\SL(4)\times\SL(4)\times\R_{+}$).
+
+\appendix
+
+\section{Miniminal ${\cal N}=(1,0)$ six-dimensional supergravity}
+We consider reductions within the minimal ${\cal N}=(1,0)$ six-dimensional supergravity, leading to duality group $\SO(4,4)$ in three dimensions, from which the half-maximal cases ${\cal N}=(1,1)$ and ${\cal N}=(2,0)$ can be deduced (in those cases the duality group in three dimensions in $\SO(8,4)$).
+
+The coordinates $X^{[MN]}$ of the $\SO(p,q)$ exceptional field theory of ref.~\cite{Hohm:2017wtr} sit in the adjoint $\bm{28}$ of $\SO(4,4)$.
+Under $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}$, it decomposes into
+\begin{equation}  
+  \begin{aligned}
+    \bm{28} &\longrightarrow \bm{6}_{2} \oplus \bm{1}_{0} \oplus \bm{15}_{0} \oplus \bm{6}_{-2},\\
+    X^{MN} &\longrightarrow \{Y^{A0},Y^{0}{}_{0},Y^{[AB]},Y^{A}{}_{0}\}.
+  \end{aligned}
+\end{equation}
+Further decomposing $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}\rightarrow\SL(3)\times\R_{+}\times\R_{+}$, we get
+\begin{equation}  \label{eq:decomp28SO8}
+  \bm{28} \longrightarrow \left[\bm{\bar{3}}_{2,2} \oplus \bm{3}_{-2,2}\right] \oplus \bm{1}_{0,0} \oplus \left[\bm{3}_{4,0} \oplus \bm{1}_{0,0} \oplus \bm{8}_{0,0} \oplus \bm{\bar{3}}_{-4,0}\right] \oplus \left[\bm{\bar{3}}_{2,-2} \oplus \bm{3}_{-2,-2}\right].
+\end{equation}
+They are two physically different possibilities to embed the internal coordinates in $X^{MN}$, corresponding to the two different half-maximal supergravities in six dimensions:\footnote{The choices are equivalent in $\SO(4,4)$ (through triality), but different once embedded in $\SO(8,4)$.}
+\begin{equation}  \label{eq:coordSO8}
+  \begin{aligned}
+    {\cal N}=(1,1):&\qquad y^{m}=Y^{m0}\subset\bm{\bar{3}}_{2,2} \longleftarrow \bm{6}_{2},\\
+    {\cal N}=(2,0):&\qquad \tilde{y}_{m}=\varepsilon_{mnp}Y^{np}\subset\bm{3}_{4,0}\longleftarrow\bm{15}_{0}.
+  \end{aligned}
+\end{equation}
+
+\paragraph{6d origin of the three-forms} The ${\cal N}=(1,0)$ supergravity features a two-form $\hat{B}_{\hat\mu\hat\nu}$.
+Both $\hat{B}_{\hat\mu\hat\nu}$ and its dual lead to two-form potentials in 3d.
+Their three-form field strengths are dual to purely internal three-form field-strengths $H_{(3)}$ and $*H_{(3)}$, of two-form potentials $C_{(2)}^{1}$ and $C_{(2)}^{2}$.
+
+\paragraph{\boldmath $C_{(2)}^{1}$ and $C_{(2)}^{2}$ in $\SO(3,3)\times\R_{+}$} Given the decomposition~\eqref{eq:decomp28SO8} and the coordinates~\eqref{eq:coordSO8}, the two forms sit in the following representations:
+\begin{equation}
+  \begin{aligned}
+    {\cal N}=(1,1):&\qquad C^{1}_{(2)}\subset\bm{\bar{3}}_{-4,0} \longleftarrow\bm{15}_{0}\quad{\rm and}\quad C^{2}_{(2)}\subset\bm{3}_{4,0} \longleftarrow\bm{15}_{0},\\
+    {\cal N}=(2,0):&\qquad C^{1}_{(2)}\subset\bm{3}_{-2,2} \longleftarrow\bm{6}_{2}\quad{\rm and}\quad C^{2}_{(2)}\subset\bm{\bar{3}}_{2,2} \longleftarrow\bm{6}_{2}.
+  \end{aligned}
+\end{equation}
+
+\paragraph{\boldmath $H_{(3)}$ and $*H_{(3)}$ in $\SO(3,3)\times\R_{+}$}
+\begin{equation}
+  \begin{aligned}
+    {\cal N}=(1,1):&\qquad H_{(3)},*H_{(3)} \subset\bm{6}_{2}\otimes\bm{15}_{0}=\bm{6}_{2}\oplus\bm{10}_{2}\oplus\bm{\bar{10}}_{2}\oplus\bm{64}_{2},\\
+    {\cal N}=(2,0):&\qquad H_{(7)},*H_{(7)} \subset\bm{10}_{0}\otimes\bm{6}_{2}=\bm{6}_{2}\oplus\bm{10}_{2}\oplus\bm{\bar{10}}_{2}\oplus\bm{64}_{2},
+  \end{aligned}
+\end{equation}
+
+\paragraph{\boldmath $H_{(3)}$ and $*H_{(3)}$ in the embedding tensor} The embedding tensor of the $\SO(4,4)$ exceptional theory has two different components: $\theta_{[MNPQ]}\subset\bm{35_{\rm s}}\oplus\bm{35_{\rm c}}$ and $\theta_{(MN)}\subset\bm{35_{\rm v}}$.
+It decomposes as follows under $\SO(4,4)\rightarrow\SO(3,3)\times\R_{+}$:
+\begin{equation}
+  \begin{aligned}
+    \bm{35_{\rm v}} &\longrightarrow \bm{1}_{4} \oplus {\color{mydarkorange}\bm{6}_{2}} \oplus \bm{1}_{0} \oplus \bm{20'}_{0} \oplus \bm{6}_{-2} \oplus \bm{1}_{-4},\\
+    \bm{35_{\rm s}} &\longrightarrow {\color{mydarkorange}\bm{10}_{2}} \oplus \bm{15}_{0}  \oplus \bm{\bar{10}}_{-2},\\
+    \bm{35_{\rm c}} &\longrightarrow {\color{mydarkorange}\bm{\bar{10}}_{2}} \oplus \bm{15}_{0}  \oplus \bm{10}_{-2},
+  \end{aligned}
+\end{equation}
+where the colored representations are those coming from the three-forms.
+Only $\bm{10}_{2}$ and $\bm{\bar{10}}_{2}$ feature $\SO(4)$ singlets.
+\ce{So no distinction between (1,1) and (2,0)?
+Because triality, or I made errors?}
+
 \bibliography{ref}

### 2022-07-01 Notes_3dH3.tex
Typos corrected and comments added.

@@
 There will be at least one singlet, corresponding to the gauging of $G_{0}$ in the initial truncation.
-Any additional singlet would indicate additional parameters to play with, possibly leading to new vacua.
+(\ce{What if the original truncation uses components of the embedding tensor not related to three-forms?}) Any additional singlet would indicate additional parameters to play with, possibly leading to new vacua.
 
@@
   \begin{aligned}
-    \bm{248} \longrightarrow & \ (\bm{7},\bm{1})_{12} \oplus (\bm{\bar{7}},\bm{2})_{6} \oplus (\bm{\bar{35}},\bm{1})_{6} \oplus (\bm{21},\bm{2})_{3} \oplus (\bm{1},\bm{1})_{0} \oplus (\bm{1},\bm{3})_{0} \oplus (\bm{48},\bm{1})_{0} \\
+    \bm{248} \longrightarrow & \ (\bm{7},\bm{1})_{12} \oplus (\bm{\bar{7}},\bm{2})_{9} \oplus (\bm{\bar{35}},\bm{1})_{6} \oplus (\bm{21},\bm{2})_{3} \oplus (\bm{1},\bm{1})_{0} \oplus (\bm{1},\bm{3})_{0} \oplus (\bm{48},\bm{1})_{0} \\
     & \oplus (\bm{\bar{21}},\bm{2})_{-3} \oplus (\bm{35},\bm{1})_{-6} \oplus (\bm{7},\bm{2})_{-9} \oplus (\bm{\bar{7}},\bm{1})_{-12}
@@
 \end{equation}
+\ce{A priori the $\bm{912}_{1}$ is the 4d embedding tensor, which should support the 4d gaugings, so we need only one singlet in three-form.}
 

### 2022-07-22 Notes_3dH3.tex
New section 4 with notes on S3xS3xS1.

@@
 \usepackage{bm}
+\usepackage{extarrows}
 
@@
 \newcommand{\ce}[1]{\marginpar{\parbox{\marginparwidth}{\boldmath $\Longleftarrow$}}
-{\boldmath\bfseries #1}}
+{\boldmath\bfseries (ce: #1)}}
 
@@
 
-\paragraph{\boldmath $\SO(8)_{\rm IIA}$ singlets}
+% \paragraph{\boldmath $\SO(8)_{\rm IIA}$ singlets}
 Under $\E_{7(7)}\rightarrow\SL(8)_{\rm IIA}$:
@@
 \end{equation}
-No singlet other that $\bm{1}$.
+No $\SO(8)_{\rm IIA}$ singlet other that $\bm{1}$.
 
-\paragraph{\boldmath $\SO(7)$ singlets}
-Under $\E_{7(7)}\rightarrow\SL(7)\times\R_{+}$:
+% \paragraph{\boldmath $\SO(7)$ singlets}
+% Under $\E_{7(7)}\rightarrow\SL(7)\times\R_{+}$:
+% \begin{equation}
+%   \begin{aligned}
+%     \bm{133} & \longrightarrow \bm{1}_{0} \oplus \ldots,\\
+%     \bm{1539} & \longrightarrow \bm{1}_{0} \oplus \ldots
+%   \end{aligned}
+% \end{equation}
+% where only representations featuring $\SO(7)$ singlets have been specified.
+
+% \paragraph{\boldmath $\SO(6)\times\R_{+}$ singlets}
+% Under $\E_{7(7)}\rightarrow\SL(6)\times\SL(2)\times\R_{+}$:
+% \begin{equation}
+%   \begin{aligned}
+%     \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus \ldots,\\
+%     \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
+%   \end{aligned}
+% \end{equation}
+% where only representations featuring $\SO(6)\times\R_{+}$ singlets have been specified.
+
+% \paragraph{\boldmath $\SO(5)\times\SO(3)$ singlets}
+% Under $\E_{7(7)}\rightarrow\SL(5)\times\SL(3)\times\R_{+}$:
+% \begin{equation}
+%   \begin{aligned}
+%     \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus \ldots,\\
+%     \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
+%   \end{aligned}
+% \end{equation}
+% where only representations featuring $\SO(5)\times\SO(3)$ singlets have been specified.
+
+% \paragraph{\boldmath $\SO(4)\times\SO(4)$ singlets}
+% Under $\E_{7(7)}\rightarrow\SL(4)\times\SL(4)\times\R_{+}$:
+% \begin{equation}
+%   \begin{aligned}
+%     \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus (\bm{1},\bm{1})_{4} \oplus (\bm{1},\bm{1})_{-4} \oplus \ldots,\\
+%     \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
+%   \end{aligned}
+% \end{equation}
+% where only representations featuring $\SO(4)\times\SO(4)$ singlets have been specified.
+
+% \paragraph*{} The singlets always come from the $\bm{63}$ and $\bm{720}$ of $\SL(8)_{\rm IIB}$ (and $\bm{70}$ for $\SL(4)\times\SL(4)\times\R_{+}$).
+
+\section{\texorpdfstring{$S^{1}$}{S1} reductions of 4d dyonic gaugings}
+Dyonic truncations from type II supergravities to four-dimensional gauged supergravity have been constructed in ref.~\cite{Inverso:2016eet} with $\E_{7(7)}$ exceptional field theory.
+Here, we further compactify on a circle and study whether it is possible to turn on additional gauging in three dimensions.
+Schematically:
+% \begin{equation}
+%   \text{Type IIA/B sugra} \xlongrightarrow[\SL(8-p)\times\SL(p)]{S^{7-p}\times S^{p-1}} \text{4d gauged sugra} \xlongrightarrow[\SL(2)]{S^{1}} \text{3d gauged sugra}.
+% \end{equation}
 \begin{equation}
   \begin{aligned}
-    \bm{133} & \longrightarrow \bm{1}_{0} \oplus \ldots,\\
-    \bm{1539} & \longrightarrow \bm{1}_{0} \oplus \ldots
+    \begin{tikzpicture}
+    \draw (0,0) node (10d) [align=center] {Type IIA/B \\ supergravity};
+    \draw ($(10d)+(6,0)$) node (4d) [align=center] {4d gauged \\ supergravity};
+    \draw ($(4d)+(4,0)$) node (3d) [align=center] {3d gauged \\ supergravity};
+
+    \draw [thick, -stealth] (10d) -- (4d) node [midway, above] {\small $S^{7-p}\times S^{p-1}$} node [midway, below] {\small $\SL(8-p)\times \SL(p)$};
+    \draw [thick, -stealth] (4d) -- (3d) node [midway, above] {\small $S^{1}$} node [midway, below] {\small $\SL(2)$};
+    \draw [thick, -stealth] ($(10d)-(0,0.6)$) arc [start angle=-160,end angle=-20,x radius=5.3,y radius=1.25] node [midway, above] {\small $S^{7-p}\times S^{p-1}\times S^{1}$} node [midway, below] {\small $\SL(8-p)\times \SL(p)\times \SL(2)$};
+    \end{tikzpicture}
   \end{aligned}
 \end{equation}
-where only representations featuring $\SO(7)$ singlets have been specified.
+The truncation from 10d to 3d is constructed using $\E_{8(8)}$ exceptional field theory, with isometries embedded as $\SL(8-p)\times\SL(p)\times\SL(2) \subset \E_{7(7)} \times \SL(2) \subset \E_{8(8)}$.
+Under $\E_{8(8)}\rightarrow\E_{7(7)}\times\SL(2)$, the ExFT coordinates decompose as
+\begin{equation}
+  \bm{248} \longrightarrow (\bm{1},\bm{3}) \oplus (\bm{56},\bm{2}) \oplus (\bm{133},\bm{3}).
+\end{equation}
+The $\E_{7(7)}$ coordinates sit in $(\bm{56},\bm{2})$. \ce{Further review ref.~\cite{Inverso:2016eet}? At least coordinates and cie. Details of IIA and IIB embeddings of forms?}
 
-\paragraph{\boldmath $\SO(6)\times\R_{+}$ singlets}
-Under $\E_{7(7)}\rightarrow\SL(6)\times\SL(2)\times\R_{+}$:
+  \subsection{\texorpdfstring{$S^{3}\times S^{3}\times S^{1}$}{S3xS3xS1}}
+  In ref.~\cite{Inverso:2016eet}, a truncation from type IIB to 4d on $S^{3}\times S^{3}\times S^{1}$ has been constructed.
+The type IIB two-forms $\hat{C}^{\alpha}_{\hat{\mu}\hat{\nu}}$ ($\alpha$ denotes a $\SL(2)_{\rm IIB}$ doublet) lead to seven-form field-strengths $H_{(7)}^{\alpha}=\d C_{(6)}^{\alpha}$.
+We search for singlets within $H_{(7)}^{\alpha}$ on $S^{3}\times S^{3}\times S^{1}$.
+Coordinates $\{y^{m}\}$ on $S^{3}\times S^{3}$, $z$ on $S^{1}$.
+Choice of gauge such that $H_{(7)}^{\alpha}$ given by
+  \begin{equation}
+    \partial_{z}C_{mnpqrs}^{\alpha}.
+  \end{equation}
+  Thus, we have to search for singlets in $C_{(6)}^{\alpha}$, built on $S^{3}\times S^{3}$ only. \ce{Is the choice of gauge always possible?}
+
+  We first have to identify how $\SL(2)_{\rm IIB}$ is embedded in $\E_{7(7)}$ (which will help us to identify $\SL(2)_{\rm IIB}$ doublets like $C_{(6)}^{\alpha}$).
+To do so, we first follow ref.~\cite{Inverso:2016eet}, where the internal coordinates $\{y^{m}\}$ are embedded into $\E_{7(7)}$ following the decomposition $\E_{7(7)}\longrightarrow\SL(6)\times\SL(2)_{\rm IIB}\times\R^{+}_{\rm IIB}$:
+  \begin{equation}
+    \bm{56} \rightarrow (\bm{6'},\bm{1})_{-4} \oplus (\bm{6},\bm{2})_{-2} \oplus (\bm{20},\bm{1})_{0} \oplus (\bm{6'},\bm{2})_{2} \oplus (\bm{6},\bm{1})_{4},
+  \end{equation}
+  with coordinates in $(\bm{6'},\bm{1})_{-4}$.
+To build the truncation on $S^{3}\times S^{3}$, we are rather interested in the decomposition under $\E_{7(7)}\longrightarrow\SL(4)_{1}\times\SL(4)_{2}\times\R^{+}_{\SL(8)}$ (through $\SL(8)$):
+  \begin{equation}
+    \bm{56} \rightarrow \left[(\bm{6},\bm{1})_{2} \oplus (\bm{4},\bm{4})_{0} \oplus (\bm{1},\bm{6})_{-2}\right] \oplus \left[(\bm{1},\bm{6})_{2} \oplus (\bm{\bar{4}},\bm{\bar{4}})_{0} \oplus (\bm{6},\bm{1})_{-2}\right].
+  \end{equation}
+  We compare these two decompositions by further decomposing under
   \begin{equation}
     \begin{aligned}
-    \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus \ldots,\\
-    \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
+     (i):&\qquad \E_{7(7)}\longrightarrow\SL(6)\times\SL(2)_{\rm IIB}\times\R^{+}_{\rm IIB} \longrightarrow \SL(3)_{1}\times\SL(3)_{2}\times\R^{+}_{\SL(6)}\times\R^{+}_{\SL(2)_{\rm IIB}}\times\R^{+}_{\rm IIB},\\
+     (ii):&\qquad \E_{7(7)}\longrightarrow\SL(4)_{1}\times\SL(4)_{2}\times\R^{+}_{\SL(8)} \longrightarrow \SL(3)_{1}\times\SL(3)_{2}\times\R^{+}_{1}\times\R^{+}_{2}\times\R^{+}_{\SL(8)}.
     \end{aligned}
   \end{equation}
-where only representations featuring $\SO(6)\times\R_{+}$ singlets have been specified.
-
-\paragraph{\boldmath $\SO(5)\times\SO(3)$ singlets}
-Under $\E_{7(7)}\rightarrow\SL(5)\times\SL(3)\times\R_{+}$:
+  We get the following:
   \begin{equation}
     \begin{aligned}
-    \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus \ldots,\\
-    \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
+    \bm{56} &\overset{(i)}{\longrightarrow} \Big[(\bm{\bar{3}},\bm{1})_{-1,0,-4} \oplus (\bm{1},\bm{\bar{3}})_{1,0,-4}\Big] \oplus \Big[(\bm{3},\bm{1})_{1,1,-2} \oplus (\bm{3},\bm{1})_{1,-1,-2} \oplus (\bm{1},\bm{3})_{-1,1,-2} \oplus (\bm{1},\bm{3})_{-1,-1,-2}\Big] \\
+    &\qquad \oplus \Big[(\bm{1},\bm{1})_{3,0,0} \oplus (\bm{1},\bm{1})_{-3,0,0} \oplus (\bm{3},\bm{\bar{3}})_{-1,0,0} \oplus (\bm{\bar{3}},\bm{3})_{1,0,0}\Big] \\
+    &\qquad \oplus \Big[(\bm{\bar{3}},\bm{1})_{-1,1,2} \oplus (\bm{\bar{3}},\bm{1})_{-1,-1,2} \oplus (\bm{1},\bm{\bar{3}})_{1,1,2} \oplus (\bm{1},\bm{\bar{3}})_{1,-1,2}\Big] \oplus \Big[(\bm{3},\bm{1})_{1,0,4} \oplus (\bm{1},\bm{3})_{-1,0,4}\Big],\\[10pt]
+    \bm{56} &\overset{(ii)}{\longrightarrow} \Big[(\bm{\bar{3}},\bm{1})_{2,0,2} \oplus (\bm{3},\bm{1})_{-2,0,2} \oplus (\bm{1},\bm{1})_{-3,-3,0} \oplus (\bm{1},\bm{3})_{-3,1,0}\oplus (\bm{3},\bm{1})_{1,-3,0} \oplus (\bm{3},\bm{3})_{1,1,0}\\
+      &\quad\qquad \oplus (\bm{1},\bm{\bar{3}})_{0,2,-2} \oplus (\bm{1},\bm{3})_{0,-2,-2}\Big] \oplus \Big[(\bm{1},\bm{\bar{3}})_{0,2,2} \oplus (\bm{1},\bm{3})_{0,-2,2} \oplus (\bm{1},\bm{1})_{3,3,0} \oplus (\bm{1},\bm{\bar{3}})_{3,-1,0}\\
+      &\quad\qquad \oplus (\bm{\bar{3}},\bm{1})_{-1,3,0} \oplus (\bm{\bar{3}},\bm{\bar{3}})_{-1,-1,0} \oplus (\bm{\bar{3}},\bm{1})_{2,0,-2} \oplus (\bm{3},\bm{1})_{-2,0,-2}\Big].
     \end{aligned}
   \end{equation}
-where only representations featuring $\SO(5)\times\SO(3)$ singlets have been specified.
 
-\paragraph{\boldmath $\SO(4)\times\SO(4)$ singlets}
-Under $\E_{7(7)}\rightarrow\SL(4)\times\SL(4)\times\R_{+}$:
+  From these decompositions we extract the relations between the charges:
+  \begin{equation}
+    \begin{cases}
+    q_{\SL(6)} = -\dfrac{1}{2}(q_{\SL(3)_{1}}+q_{\SL(3)_{2}}), \\[7pt]
+    q_{\SL(2)_{\rm IIB}} = \dfrac{1}{4}\,\left(q_{\SL(3)_{1}}-q_{\SL(3)_{2}}+q_{\SL(8)}\right), \\[7pt]
+    q_{\rm IIB} = \dfrac{1}{2}\,\left(-q_{\SL(3)_{1}}+q_{\SL(3)_{2}}+3\,q_{\SL(8)}\right).
+    \end{cases}
+  \end{equation}
+  So the coordinates are inside $(\bm{6},\bm{1})_{-2}\oplus(\bm{1},\bm{6})_{2}$ of $\SL(4)_{1}\times\SL(4)_{2}\times\R^{+}_{\SL(8)}$.
+\ce{Problem with $3, \bar{3}$?
+Comes from identification $\bm{6'}=\bm{\bar{6}}$?}
+
+  We now turn to the six-form potential $C_{(6)}^{\alpha}$, which sits in the representation $\bm{133}$ of $\E_{7(7)}$.
+Under $\E_{7(7)} \rightarrow \SL(8)$, it decomposes as $\bm{133} \rightarrow \bm{63} \oplus \bm{70}$, and
   \begin{equation}
     \begin{aligned}
-    \bm{133} & \longrightarrow (\bm{1},\bm{1})_{0} \oplus (\bm{1},\bm{1})_{4} \oplus (\bm{1},\bm{1})_{-4} \oplus \ldots,\\
-    \bm{1539} & \longrightarrow 2\times(\bm{1},\bm{1})_{0} \oplus \ldots\\
+    \SL(8) & \longrightarrow \SL(4) \times \SL(4) \times \R^{+} \\
+    \bm{63} & \longrightarrow (\bm{4},\bm{\bar{4}})_{2} \oplus (\bm{1},\bm{1})_{0} \oplus (\bm{1},\bm{15})_{0} \oplus (\bm{15},\bm{1})_{0} \oplus (\bm{\bar{4}},\bm{4})_{-2} \\
+    \bm{70} & \longrightarrow (\bm{1},\bm{1})_{4} \oplus (\bm{\bar{4}},\bm{4})_{2} \oplus (\bm{6},\bm{6})_{0} \oplus (\bm{4},\bm{\bar{4}})_{-2} \oplus (\bm{1},\bm{1})_{-4}.
     \end{aligned}
   \end{equation}
-where only representations featuring $\SO(4)\times\SO(4)$ singlets have been specified.
+  Given that $C_{(6)}^{\alpha}$ is a $\SL(2)_{\rm IIB}$ doublet of fixed $R_{\rm IIB}^{+}$ charge, let us spell out the charges explicitly. In $\bm{63}$:
+  \begin{equation}
+    \begin{aligned}
+    \SL(4) \times \SL(4) \times \R^{+} & \longrightarrow \SL(3) \times \SL(3) \times \R^{+}_{\SL(2)_{\rm IIB}} \times \R^{+}_{\rm IIB} \\
+    (\bm{4},\bm{\bar{4}})_{2} & \longrightarrow (\bm{1},\bm{1})_{-1,6} \oplus (\bm{1},\bm{\bar{3}})_{0,4} \oplus (\bm{3},\bm{1})_{0,4} \oplus (\bm{3},\bm{\bar{3}})_{1,2}\\
+    (\bm{1},\bm{1})_{0} & \longrightarrow (\bm{1},\bm{1})_{0,0} \\
+    (\bm{1},\bm{15})_{0} & \longrightarrow (\bm{1},\bm{1})_{0,0} \oplus (\bm{1},\bm{3})_{-1,2} \oplus (\bm{1},\bm{\bar{3}})_{1,-2} \oplus (\bm{1},\bm{8})_{0,0}\\
+    (\bm{15},\bm{1})_{0} & \longrightarrow (\bm{1},\bm{1})_{0,0} \oplus (\bm{3},\bm{1})_{1,-2} \oplus (\bm{\bar{3}},\bm{1})_{-1,2} \oplus (\bm{8},\bm{1})_{0,0} \\
+    (\bm{\bar{4}},\bm{4})_{-2} & \longrightarrow (\bm{1},\bm{1})_{1,-6} \oplus (\bm{1},\bm{3})_{0,-4} \oplus (\bm{\bar{3}},\bm{1})_{0,-4} \oplus (\bm{\bar{3}},\bm{3})_{-1,-2}.
+    \end{aligned}
+  \end{equation}
+  In $\bm{70}$:
+  \begin{equation}
+    \begin{aligned}
+    \SL(4) \times \SL(4) \times \R^{+} & \longrightarrow \SL(3) \times \SL(3) \times \R^{+}_{\SL(2)_{\rm IIB}} \times \R^{+}_{\rm IIB} \\
+    (\bm{1},\bm{1})_{4} & \longrightarrow (\bm{1},\bm{1})_{1,6}\\
+    (\bm{\bar{4}},\bm{4})_{2} & \longrightarrow (\bm{1},\bm{1})_{2,0} \oplus (\bm{1},\bm{3})_{1,2} \oplus (\bm{\bar{3}},\bm{1})_{1,2} \oplus (\bm{\bar{3}},\bm{3})_{0,4} \\
+    (\bm{6},\bm{6})_{0} & \longrightarrow (\bm{3},\bm{3})_{0,0} \oplus (\bm{3},\bm{\bar{3}})_{-1,2} \oplus (\bm{\bar{3}},\bm{3})_{1,-2} \oplus (\bm{\bar{3}},\bm{\bar{3}})_{0,0} \\
+    (\bm{4},\bm{\bar{4}})_{-2} & \longrightarrow (\bm{1},\bm{1})_{-2,0} \oplus (\bm{1},\bm{\bar{3}})_{-1,-2} \oplus (\bm{3},\bm{1})_{-1,-2} \oplus (\bm{3},\bm{\bar{3}})_{0,-4} \\
+    (\bm{1},\bm{1})_{-4} & \longrightarrow (\bm{1},\bm{1})_{-1,-6}
+    \end{aligned}
+  \end{equation}
+  $\SO(3)\times\SO(3)$ singlets $\SL(2)_{\rm IIB}$ doublets and of given $R_{\rm IIB}^{+}$ charge are given by
+  \begin{equation}
+    (\bm{1},\bm{1})_{1,6} \oplus (\bm{1},\bm{1})_{-1,6} \subset (\bm{1},\bm{1})_{4} \oplus (\bm{4}, \bm{\bar{4}})_{2} \quad {\rm and} \quad (\bm{1},\bm{1})_{1,-6} \oplus (\bm{1},\bm{1})_{-1,-6} \subset (\bm{1},\bm{1})_{-4} \oplus (\bm{\bar{4}}, \bm{4})_{-2},
+  \end{equation}
+  where we wrote embeddings of $\SL(3) \times \SL(3) \times \R^{+}_{\SL(2)_{\rm IIB}} \times \R^{+}_{\rm IIB}$ in $\SL(4) \times \SL(4) \times \R^{+}$.
+These doublets correspond to $C_{(6)}^{\alpha}$ and the analogous $C^{(6)\,\alpha}$.
+So
+  \begin{equation}
+    C_{(6)}^{\alpha} \subset (\bm{1},\bm{1})_{4} \oplus (\bm{4},\bm{\bar{4}})_{2}.
+  \end{equation}
+  \ce{But no $(\bm{4},\bm{\bar{4}})$ in $\left((\bm{6},\bm{1})_{2}\oplus(\bm{1},\bm{6})_{-2}\right)^{\wedge 6}$...}
 
-\paragraph*{} The singlets always come from the $\bm{63}$ and $\bm{720}$ of $\SL(8)_{\rm IIB}$ (and $\bm{70}$ for $\SL(4)\times\SL(4)\times\R_{+}$).
+  \subsection{\texorpdfstring{$S^{7-p}\times S^{p-1}$}{S7-pxSp-1}}
+  ...
 

### 2022-10-25 Notes_3dH3.tex
Draft of the 4-param deformation of S3S3S1.

@@
 \begin{equation}
-  \bm{248} \longrightarrow (\bm{1},\bm{3}) \oplus (\bm{56},\bm{2}) \oplus (\bm{133},\bm{3})\longrightarrow \bm{1}_{2} \oplus \bm{56}_{1} \oplus \bm{1}_{0} \oplus \bm{133}_{0} \oplus \bm{56}_{-1} \oplus \bm{1}_{-2}.
+  \bm{248} \longrightarrow (\bm{1},\bm{3}) \oplus (\bm{56},\bm{2}) \oplus (\bm{133},\bm{1})\longrightarrow \bm{1}_{2} \oplus \bm{56}_{1} \oplus \bm{1}_{0} \oplus \bm{133}_{0} \oplus \bm{56}_{-1} \oplus \bm{1}_{-2}.
 \end{equation}
@@
 
+\section{\texorpdfstring{${\rm AdS}_{3}\times S^{3}\times S^{3}\times S^{1}$}{AdS3xS3xS3xS1}}
+Ten-dimensional maximal supergravity features a solution on ${\rm AdS}_{3}\times S^{3}_{+}\times S^{3}_{-}\times S^{1}$, whose vacuum preserves ${\cal N}=(4,4)$ supersymmetries.
+The superisometries are given by
+\begin{equation}
+  D^{1}(2,1;\alpha)_{\rm L}\times D^{1}(2,1;\alpha)_{\rm R},   
+\end{equation}
+with $\alpha$ the ratio of the spheres $S^{3}$ radii.
+The even part of $D^{1}(2,1;\alpha)$ is isomorphic to $\SL(2,\mathbb{R})\times\SO(3)^{+}\times\SO(3)^{-}$~\cite{Gunaydin:1986fe}, so that the bosonic symmetries at the vacuum are given by
+\begin{equation}
+  \underbrace{\SL(2,\mathbb{R})_{\rm L}\times\SL(2,\mathbb{R})_{\rm R}}_{\textstyle {\rm AdS}_{3}}\underbrace{\times\SO(3)^{+}_{\rm L}\times\SO(3)^{+}_{\rm R}}_{\textstyle S^{3}_{+}}\times\underbrace{\SO(3)^{-}_{\rm L}\times\SO(3)^{-}_{\rm R}}_{\textstyle S^{3}_{-}}.
+\end{equation}
+
+This vacuum has been described with an $\SO(8,8)$ embedding tensor $\theta_{IJ\vert KL}$ in ref.~\cite{Eloy:2020uix}.
+Possible to build an $\E_{8(8)}$ embedding tensor using $\theta_{IJ\vert KL}$~\cite{Deger:2019tem}: the maximal theory can be truncated to a half-maximal subsector upon truncating the coset space
+\begin{equation} \label{eq:E8SO88}
+{\rm E}_{8(8)}/{\rm SO}(16) \longrightarrow \SO(8,8)/(\SO(8)\times\SO(8)).
+\end{equation}
+Specifically, splitting the ${\rm E}_{8(8)}$ generators according to
+\begin{equation}
+  \left\{L^{[IJ]}, Y^{A}\right\},\quad I\in\llbracket1,16\rrbracket,\;\; A\in\llbracket1,128\rrbracket,
+\end{equation}
+into $\SO(8,8)$ and its orthogonal complement (transforming in the spinor representation ${\bf 128}_{\rm s}$ of $\SO(8,8)$), an embedding tensor of the maximal theory takes the form
+\begin{equation} \label{eq:embmax}
+  \begin{cases}
+  \Theta_{IJ|KL} = \theta_{IJ|KL},\medskip\\
+  \Theta_{A|B} =-\dfrac{1}{2}\theta\,\eta_{AB}+\dfrac{1}{96}\,\Gamma^{IJKL}_{AB}\,\theta_{IJ\vert KL},
+  \end{cases}
+\end{equation}
+where $\Gamma^{IJKL}_{AB}$ denotes the four-fold product of $\SO(8,8)$ $\Gamma$ matrices.
+Spectrum computed in ref.~\cite{Eberhardt:2017fsi}, organized into long multiplets $\left[\ell^{+}_{R},\ell^{-}_{R},\ell^{+}_{L},\ell^{-}_{L}\right]$ of $D^{1}(2,1;\alpha)_{\rm L}\times D^{1}(2,1;\alpha)_{\rm R}$.
+
+  \subsection{Deformations from \texorpdfstring{${\rm AdS}_{3}\times S^{3}$}{AdS3xS3}}
+  In ref.~\cite{Eloy:2021fhc}, deformation of ${\rm AdS}_{3}\times S^{3}$ built from a $\SO(8,4)$ coset-representative $v(\omega,\zeta)$. For generic $(\omega,\zeta)$, ${\cal N}=0$, but along
+  \begin{equation}
+    \zeta^{2}=1-e^{-2\omega},
+  \end{equation}
+  ${\cal N}=(4,0)$.
+
+  From this deformation, we can generate of deformation of ${\rm AdS}_{3}\times S^{3}_{+}\times S^{3}_{-}\times S^{1}$: first embed $v$ in ${\cal V}\in\SO(8,8)$, then deform embedding tensor $T={\cal V}^{-1}\cdot\theta$, and embed $T$ in $\E_{8(8)}$.
+Two different ways of embedding $v$ in $\SO(8,8)$ $\implies$ ${\cal V}^{(+)}(\omega_{+},\zeta_{+})$ and ${\cal V}^{(-)}(\omega_{-},\zeta_{-})$.
+Then, four-parameter deformation from
+  \begin{equation}
+    {\cal V}(\omega_{+},\zeta_{+},\omega_{-},\zeta_{-})={\cal V}^{(+)}{\cal V}^{(-)}.
+  \end{equation}
+  \ce{More possibilities?}
+
+  Symmetries:
+  \begin{equation}
+   \begin{tikzpicture}
+      \draw (0,0) node (round) {${\rm SO}(4)_{+} \times{\rm SO}(4)_{-} $};
+      \draw ($(round)+(-4,0)$) node {\small Round spheres};
+      \draw ($(round)+(5,0)$) node (susy) {\small ${\cal N}=(4,4)$};
+      \draw [thick,-stealth] (round) -- +(-2.5,-2.5) node (defp) [below] {${\rm U}(1)\times{\rm U}(1) \times{\rm SO}(4)_{-}$} node [midway,above left] {$(\omega_{+},\zeta_ {+})$};
+      \draw [thick,-stealth] (round) -- +(2.5,-2.5) node (defm) [below] {${\rm SO}(4)_{+} \times{\rm U}(1)\times{\rm U}(1)$} node [midway,above right] {$(\omega_{-},\zeta_ {-})$};
+      \draw ($(susy)+(0,-2.5)$) node [below] {\small ${\cal N}=0$};
+      \draw [thick,-stealth] (defm) -- +(-2.5,-2.5) node (defpm) [below] {${\rm U}(1)\times{\rm U}(1) \times{\rm U}(1)\times{\rm U}(1)$} node [above=1.2cm] {$(\omega_{+},\zeta_ {+},\omega_{-},\zeta_ {-})$};
+      \draw [thick,-stealth] (defp) -- +(2.5,-2.5);
+      \draw ($(susy)+(0,-5.5)$) node {\small ${\cal N}=0$};
+    \end{tikzpicture}
+  \end{equation}
+  Two lines along which ${\cal N}=(4,0)$;
+  \begin{equation}
+    \begin{cases}
+      \zeta^{2}_{+}=1-e^{-2\omega_{+}},\\
+      \omega_{-}=\zeta_{-}=0,
+    \end{cases}
+    \quad 
+    \begin{cases}
+      \omega_{+}=\zeta_{+}=0,\\
+      \zeta^{2}_{-}=1-e^{-2\omega_{-}}.
+    \end{cases}
+  \end{equation}
+  \ce{More?}
+
+  \subsubsection{Deformation \texorpdfstring{${\cal V}^{(+)}$}{V+}}
+  Study of deformation with ${\cal V}^{(+)}$ with half-maximal theory (access to full spectrum). For $\zeta^{2}_{+}=1-e^{-2\omega_{+}}$, $D^{1}(2,1;\alpha)_{\rm L}$ broken, for even part:
+  \begin{equation}
+    \SL(2,\mathbb{R})_{\rm L}\times\SO(3)^{+}_{\rm L}\times\SO(3)^{-}_{\rm L} \longrightarrow \SL(2,\mathbb{R})_{\rm L}\times\SO(2)^{+}_{\rm L}\times\SO(3)^{-}_{\rm L}
+  \end{equation}
+  Then spectrum organized in terms of lon multiplet of $D^{1}(2,1;\alpha)_{\rm R}$, charge $q_{\rm L}^{+}$ and spin $j_{\rm L}^{+}$:
+  \begin{equation}
+    \left[\ell^{+}_{R},\ell^{-}_{R}\right]^{j_{\rm L}^{+}}_{_{\rm L}^{+}},
+  \end{equation}
+  with conformal weight:
+  \begin{equation}
+    \Delta_{q}^{\ell^{+},\ell^{-}} = -\frac{1}{2} + \frac{1}{2}\sqrt{1+\frac{4\ell^{+}(\ell^{+}+1)+q^{2}(e^{2\omega}-1)+4\alpha^{2}\ell^{-}(\ell^{-}+1)}{1+\alpha^{2}}}.
+  \end{equation}
+  For ${\cal V}^{(-)}$, $\alpha\rightarrow\alpha^{-1}$.
+
 \appendix
@@
 \ce{So no distinction between (1,1) and (2,0)?
-Because triality, or I made errors?}
+Because triality, or I made errors?} $\leq$
 

### 2023-05-08 Draft_3dH3.tex
Draft created by Emanuel.

\documentclass[a4paper, 11pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsfonts,slashed}
%\usepackage{arydshln}
%\usepackage[greek,english]{babel}
%\usepackage{cancel}
%\usepackage{upgreek}
\usepackage{float}
\usepackage{cite}
%\usepackage{url}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{epsfig}
%\usepackage{isomath}
\usepackage{latexsym,amssymb}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
%\usepackage{fontenc}
\usepackage{graphicx,tikz}
\usepackage{multirow}
\setcounter{MaxMatrixCols}{13}
%\usepackage{xfrac}
%\usepackage[T1]{fontenc}
\usepackage{textcomp}
%\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{stmaryrd}
%%%%%%%%% Packages to show breakings %%%%%%%%%
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}

%  PDF specials
%\newif\ifpdf
\usepackage{ifpdf}
\ifx\pdfoutput\undefined
\pdffalse
\usepackage{cite}
\else
\pdfoutput=1
\pdftrue
%\usepackage[pdftex]{hyperref}
\pdfcompresslevel=9
\fi
\DeclareFontFamily{OMS}{rsfs}{\skewchar\font'60}
\DeclareFontShape{OMS}{rsfs}{m}{n}{<-5>rsfs5 <5-7>rsfs7 <7->rsfs10 }{}
\DeclareSymbolFont{rsfs}{OMS}{rsfs}{m}{n}
\DeclareSymbolFontAlphabet{\Scr}{rsfs}
\newcommand{\RRB}[2]{\makebox[#1]{$\left.\rule{0pt}{#2}\right)$}}
\newcommand{\LRB}[2]{\makebox[#1]{$\left(\rule{0pt}{#2}\right.$}}
\newcommand{\RSB}[2]{\makebox[#1]{$\left.\rule{0pt}{#2}\right]$}}
\newcommand{\LSB}[2]{\makebox[#1]{$\left[\rule{0pt}{#2}\right.$}}
\newcommand{\gr}[1]{\begin{greek}#1\end{greek}}
\setlength{\parskip}{0pt} \setlength{\parindent}{0.5cm}
\setcounter{footnote}{0}
\renewcommand{\theequation}{\thesection.\arabic{equation}}
\numberwithin{equation}{section}
\def\be{\begin{equation}}
	\def\ee{\end{equation}}
\def\ba{\begin{array}}
	\def\ea{\end{array}}
\newcommand{\ho}[1]{$\, ^{#1}$}
\newcommand{\hoch}[1]{$\, ^{#1}$}
\newcommand{\bea}{\begin{eqnarray}}
	\newcommand{\eea}{\end{eqnarray}}
\newcommand{\ds}{\displaystyle}
\newcommand{\BNA}{\makebox[0.8em]{\tiny$b\neq a$}}
\newcommand{\notEq}[2]{\makebox[0.8em]{\tiny$#1\neq #2$}}
\newcommand{\ph}{\alpha}
\newcommand{\scal}{z}
\newcommand{\bscal}{\bar\scal}
\newcommand{\scalC}{\pi}
%%%%%%%%%%%%%%%%% formatting
\textwidth 165mm \textheight 220mm \topmargin 0pt \oddsidemargin 2mm
%%% macros
\newcommand{\rmg}[1]{\mbox{{\small \textgreek{#1}}}}
\newcommand{\rmgg}[1]{\mathrm{#1}}
\newcommand{\ft}[2]{{\textstyle\frac{#1}{#2}}}

\newcommand{\uA}{{\underline{A}}}
\newcommand{\uB}{{\underline{B}}}
\newcommand{\uC}{{\underline{C}}}
\newcommand{\uD}{{\underline{D}}}
\newcommand{\uE}{{\underline{E}}}
\newcommand{\uF}{{\underline{F}}}
\newcommand{\uG}{{\underline{G}}}
\newcommand{\uM}{{\underline{M}}}
\newcommand{\uN}{{\underline{N}}}
\newcommand{\uP}{{\underline{P}}}
\newcommand{\dom}{{\dot{m}}}
\newcommand{\don}{{\dot{n}}}
\newcommand{\dop}{{\dot{p}}}
\newcommand{\doq}{{\dot{q}}}
\newcommand{\dor}{{\dot{r}}}
\newcommand{\ua}{{\overline{\alpha}}}
\newcommand{\ub}{{\overline{\beta}}}
\newcommand{\uc}{{\overline{\gamma}}}
\newcommand{\ude}{{\overline{\delta}}}
\newcommand{\AI}{\left(A^{-1}(\eta)\right)}
\newcommand{\ff}[1]{\mathfrak{#1}}
\newcommand{\fA}{\ff{A}}
\newcommand{\fB}{\ff{B}}
\newcommand{\FF}{{\cal F}}
\newcommand{\FG}{{\cal G}}
\newcommand{\ov}[1]{\overline{#1}}

%
%\newcommand{\hc}{{\rm h.c.}}
%\newcommand{\bbox}{\lower.2ex\hbox{$\Box$}}
%% Formatting of group names
\newcommand{\un}[1]{\mathrm{SU}( #1 )}
\newcommand{\ON}[1]{\mathrm{O}( #1 )}
\newcommand{\SU}[1]{\mathrm{SU}( #1 )}
\newcommand{\SL}[1]{\mathrm{SL}( #1 )}
\newcommand{\GL}[1]{\mathrm{GL}( #1 )}
\newcommand{\SO}[1]{\mathrm{SO}( #1 )}
\newcommand{\UO}{\mathrm{U}(1)}
\newcommand{\U}[1]{\mathrm{U}(#1)}
\newcommand{\Spin}[1]{\mathrm{Spin}(#1)}
\newcommand{\EE}{E_{8(8)}}
\newcommand{\USp}[1]{\mathrm{USp}(#1)}
\newcommand{\Un}[1]{\mathrm{U}(#1)}
\newcommand{\Gt}{\mathrm{G}_{2(2)}}
\newcommand{\Ff}{\mathrm{F}_{4(4)}}
\newcommand{\En}[1]{E_{#1(#1)}}
\newcommand{\Gst}{G_S}
\newcommand{\Msc}{{\cal M}_{\rm scalar}}
\newcommand{\SUc}[2]{\mathrm{S}(\U{#1}\times\U{#2})}

\newcommand{\Com}[2]{\mathrm{Com}_{#1}(#2)}
\newcommand{\SLA}{\SL{8}_{\rm IIA}}
\newcommand{\SLB}{\SL{8}_{\rm IIB}}

%% Formatting Lie algebra names
\newcommand{\su}[1]{\mathfrak{su}(#1)}
\newcommand{\so}[1]{\mathfrak{so}(#1)}
\newcommand{\usp}[1]{\mathfrak{usp}(#1)}
\newcommand{\gt}{\mathfrak{G}_2}
\newcommand{\fF}{\mathfrak{F}_4}
\newcommand{\uu}{\mathfrak{u}(1)}

\newcommand{\ud}[1]{\underline{#1}}

%% Group theory stuff
\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\mbfb}[1]{\mathbf{\left(#1\right)}}
%\newcommand{\obf}[1]{\overline{\mathbf{#1}}}
\newcommand{\obf}[1]{\mbf{\overline{\mathbf{#1}}}}
\newcommand{\trep}[1]{(\mbf{#1})}
\newcommand{\PR}[1]{(\mathbb{P}_{#1})}

\newcommand{\Leib}[2]{\llbracket #1,#2 \rrbracket}

%\newcommand{}
\newcommand{\+}{\oplus}
\newcommand{\cc}{\text{c.c.}}

%%%%%%%% generalised stuff
\newcommand{\gL}{\mathcal{L}}
\newcommand{\gM}{\mathcal{M}}
\newcommand{\tw}{{\cal U}}
\newcommand{\kr}[2]{\delta^{#1}_{#2}}
\newcommand{\cU}{{\cal U}}
\newcommand{\UI}{\left(U^{-1}\right)}
\newcommand{\flt}[1]{\underline{#1}}
\newcommand{\fl}[1]{\ov{#1}}
\newcommand{\cY}{{\cal Y}}
\newcommand{\vg}{\mathring{g}}
\newcommand{\cP}{{\cal P}}
\newcommand{\cV}{{\cal V}}
\newcommand{\cVI}{\left(\cV^{-1}\right)}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}

%%%%%%%% math operators
\DeclareMathOperator{\tr}{Tr}
%% Comments
\newcommand{\EM}[1]{\textcolor{red}{#1}}
\newcommand{\MG}[1]{\textcolor{blue}{#1}}
\newcommand{\CE}[1]{\textcolor{green}{#1}}
\newcommand{\CG}{\Com{G}{\EE}}
\newcommand{\cJ}{{\cal J}}

%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{titlepage}
	\vfill
	\begin{flushright}
		HU-EP-23/XX
	\end{flushright}

	\vfill

	\begin{center}
		\baselineskip=16pt
		{\Large \bf Adding fluxes to consistent truncations: \\ IIB supergravity on ${\rm AdS}_3 \times S^3 \times S^3 \times S^1$}
		\vskip 2cm
		{\large \bf Camille Eloy$^a$\footnote{\tt camille.eloy@vub.be}, Michele Galli$^b$\footnote{\tt michele.galli@physik.hu-berlin.de},  Emanuel Malek$^b$\footnote{\tt emanuel.malek@physik.hu-berlin.de}}
		\vskip .6cm
		{\it $^a$ Theoretische Natuurkunde, Vrije Universiteit Brussel, and the Interational Solvay, \\
			Institutes, Pleinlaan 2, B-1050 Brussels, Belgium}
		\\ \ \\
		{\it $^b$ Institut f\"ur Physik, Humboldt-Universit\"at zu Berlin, \\IRIS Geb\"aude, Zum Gro\ss en Windkanal 2, 12489 Berlin, Germany \\ \ \\}
		\vskip 1cm
	\end{center}
	\vfill

	\begin{abstract}
		We use $\EE$ Exceptional Field Theory to construct the consistent truncation of IIB supergravity on $S^3 \times S^3 \times S^1$ to maximal 3-dimensional ${\cal N}=16$ gauged supergravity containing the ${\cal N}=(4,4)$ AdS$_3$ vacuum. We explain how to achieve this by adding a 7-form flux to the $S^1$ reduction of the dyonic $\En{7}$ truncation on $S^3 \times S^3$ previously constructed in the literature. Our truncation Ansatz includes, in addition to the ${\cal N}=(4,4)$ vacuum, a host of moduli breaking some or all of the supersymmetries. We explicitly construct the uplift of a subset of these to construct new supersymmetric and non-supersymmetric AdS$_3$ vacua of IIB string theory, and show how the moduli space of AdS$_3$ vacua of six-dimensional gauged supergravity studied in \cite{Eloy:2021fhc} is compactified upon lifting to 10 dimensions. Along the way, we also derive the form of 3-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor.
	\end{abstract}
	\vskip 0cm

	\vfill

	\setcounter{footnote}{0}

\end{titlepage}

\tableofcontents

\newpage

\EM{To do:
\begin{itemize}
	\item Think about title - mention new AdS$_3$ vacua? Lifting AdS$_3$ vacua?
	\item Move 3-d gauged SUGRA to somewhere else??
	\item Discuss IIA (and IIB -- Jerome's story) T-duals
\end{itemize}
}

\section{Introduction}

\section{Review of $\EE$ ExFT and consistent truncations} \label{s:Review}
Review relevant bits of \cite{Hohm:2014fxa} and \cite{Galli:2022idq}.

A consistent truncation requires that the objects
\begin{equation} \label{eq:DoubleU}
	\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}}) \,, \qquad \Sigma_{\fl{M}\,M} = \frac{1}{60} \rho^{-1} f_{\fl{M}}{}^{\fl{N}\fl{P}}\, U_{\fl{N}\,P} \partial_M U_{\fl{P}}{}^{P} \,, \qquad \cU_{\fl{M}}{}^M = \rho^{-1} U_{\fl{M}}{}^M \,,
\end{equation}
satisfy the differential condition
\begin{equation} \label{eq:GenLeibniz}
	\gL_{\ff{U}_{\fl{M}}} {\cU}_{\fl{N}}{}^M = X_{\fl{M}\fl{N}}{}^{\fl{P}}\, \cU_{\fl{P}}{}^M \,,
\end{equation}
with $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ constant.

\section{3-dimensional ${\cal N}=16$ gauged supergravity} \label{s:3dSUGRA}

\section{Adding fluxes to consistent truncations} \label{s:AddFlux}
In order to construct the consistent truncation around the ${\cal N}=(4,4)$ AdS$_3 \times S^3 \times S^3 \times S^1$ vacuum of IIB supergravity, a promising starting point is the dyonic $S^3 \times S^3$ truncation of IIB supergravity constructed in \cite{Inverso:2016eet}, and further reducing this on $S^1$. However, this will not give the correct AdS$_3$ vacuum since the truncation is missing the 7-form flux on $S^3 \times S^3 \times S^1$ that is required. Indeed, the 3-dimensional gauged supergravity that would be obtained as discussed way does not have any AdS$_3$ vacua. We can remedy this situation by defining a new consistent truncation by adding a 7-form flux to the one obtained from the $S^3 \times S^3$ reduction constructed in $\En{7}$ ExFT.

This motivates the following question, given a consistent truncation, i.e. $\cU_{\fl{M}}{}^M$, satisfying \eqref{eq:GenLeibniz}, when can we add a new flux component of string theory to the compactification to obtain a new consistent truncation? Adding a new flux component to the truncation is equivalent to twisting the generalised frame as follows
\begin{equation} \label{eq:Twisting}
	\cU_{\fl{M}}{}^M \longrightarrow \cU'_{\fl{M}}{}^M = \cU_{\fl{M}}{}^N \exp(C)_N{}^M \,,
\end{equation}
where $C$ denotes the $\EE$ generator corresponding to the potential we want to add to the compactification. The effect of the twist \eqref{eq:Twisting} is that the generalised Lie derivative of $\cU'$ satisfies
\begin{equation}
	\gL_{\ff{U}'_{\fl{M}}} \cU'_{\fl{N}}{}^M = \left( \gL_{\ff{U}_{\fl{M}}} \cU_{\fl{N}}{}^N + F_{PQ}{}^N\, \cU_{\fl{M}}{}^P\, \cU_{\fl{N}}{}^Q \right) \exp(C)_N{}^M \,,
\end{equation}
where $F_{MN}{}^P$ is a tensor in the $\mathbf{1} \oplus \mathbf{248} \oplus \mathbf{3875}$ of $\EE$, i.e. the same representation as the embedding tensor, corresponding to the field strength of the potential $C$ in \eqref{eq:Twisting}. Using \eqref{eq:GenLeibniz}, we now have
\begin{equation}
	\gL_{\ff{U}'_{\fl{M}}} \cU'_{\fl{N}}{}^M = \left( X_{\fl{M}\fl{N}}{}^{\fl{P}} + \rho^{-1}\, F_{\fl{M}\fl{N}}{}^{\fl{P}} \right) \cU'_{\fl{P}}{}^M \,,
\end{equation}
where we defined
\begin{equation} \label{eq:FlatF}
	F_{\fl{M}\fl{N}}{}^{\fl{P}} \equiv \UI_{\fl{M}}{}^M\, \UI_{\fl{N}}{}^N\, U_P{}^{\fl{P}}\, F_{MN}{}^P \,,
\end{equation}
and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ is already constant. Therefore, we have a consistent truncation if and only iff $\rho^{-1}\, F_{\fl{M}\fl{N}}{}^{\fl{P}}$ is constant.

A particularly simple way of having constant $\rho^{-1}\, F_{\fl{M}\fl{N}}{}^{\fl{P}}$ is to consider fluxes which are stabilised by the twist matrix $U_M{}^{\fl{M}}$. The twist matrix typically only lives in a subgroup $G \subset \EE$. Therefore, in this case, we can simply tune the $G$-singlet components of the flux $F_{MN}{}^P$ to be proportional to $\rho$ to obtain a new consistent truncation.

\subsection{Adding fluxes to the $S^3$ truncation of 6-dimensional supergravity} \label{s:S3Flux}
Before dealing with the $S^3 \times S^3 \times S^1$ truncation, let us demonstrate this methdology for the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity on $S^3$, which was constructed in \cite{Eloy:2021fhc}. As discussed in \cite{Eloy:2021fhc}, the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity to 3-dimensional half-maximal gauged supergravity can be described using the $\SO{8,4}$ ExFT \cite{Hohm:2017wtr,Samtleben:2019zrh}. On the other hand, the consistent truncation on $S^3$ is conveniently described by twist matrices living in $\SL{4} \simeq \SO{3,3}$ \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou} \EM{I think the twist matrix of \cite{Baguet:2015iou,Lee:2014mla,Hohm:2014qga} coincide in the $\SL{4}$ case, right? Camille, do you agree?} with the embedding $\SO{3,3} \subset \SO{4,4} \subset \SO{8,4}$. However, the twist matrix in \cite{Eloy:2021fhc} differs from this $\SO{3,3}$ twist matrix \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou} by an additional parameter, $\lambda$, which gives rise to an external 3-form flux or, equivalently, a new internal 3-form flux.

\subsubsection{The $S^3$ twist matrix}
Since it will play a role throughout this paper, we will begin by giving the $\SL{4} \simeq \SO{3,3}$ twist matrix that describes the consistent truncation on $S^3$. Here, we give a slightly different, but equivalent, form of the twist matrix constructed in \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou} for the consistent truncation on $S^n$.

\EM{Maybe even move this $\SL{n+1}$ ExFT to the review section?}
We use an $\SL{n+1}$ ExFT, like in \cite{Lee:2014mla}, which encodes an $n$-dimensional metric and volume-form flux, i.e. Freund-Rubin compactifications, and is thus a natural description of $S^n$ compactifications. The $\SL{n+1}$ ExFT formally has coordinates in the antisymmetric representation of $\SL{n+1}$, $y^{IJ} = - y^{JI}$, with $I = 1, \ldots, n+1$, and similarly, generalised vector fields transform in the antisymmetric representation of $\SL{n+1}$. The generalised Lie derivative on a generalised tensor in the fundamental $V^I$ of weight $\lambda$ is given by
\begin{equation} \label{eq:SLnGenLie}
	\gL_\Lambda V^I = \frac12 \Lambda^{JK} \partial_{JK} V^{I} - V^J \partial_{JK} \Lambda^{IK} + \left( \frac{\lambda}{2} + \frac{1}{n+1} \right) V^I \partial_{JK} \Lambda^{JK} \,,
\end{equation}
and similarly for other generalised tensors. Closure of the generalised Lie derivative \eqref{eq:SLnGenLie} requires the section condition
\begin{equation} \label{eq:SLnSC}
	\partial_{[IJ} \otimes \partial_{KL]} = 0 \,,
\end{equation}
which restricts the dependence of all fields to a subset of physical coordinates.

We are interested in the maximal solutions of the section condition \eqref{eq:SLnSC} which preserve a $\SL{n} \subset \SL{n+1}$ subgroup. Under this decomposition $\SL{n+1} \rightarrow \SL{n}$ with $V^I = \left( V^i,\, V^0 \right)$, where $i = 1, \ldots, n$, we solve the section condition by having physical coordinates $y^{i0}$ on the $n$-dimensional manifold $M$, i.e. $\partial_{ij} = 0$ for all fields with only $\partial_{i0} \neq 0$. Correspondingly, the generalised tangent bundle, whose sections are in the antisymmetric representation of $\SL{n+1}$ and carry weight $\frac{n-3}{n+1}$, decomposes as
\begin{equation} \label{eq:SLnE}
	E = TM \oplus \Lambda^{n-2} T^*M \,,
\end{equation}
Note that for the case of interest to us, $n=3$, \eqref{eq:SLnE} reduces to
\begin{equation}
	E = TM \oplus T^*M \,,
\end{equation}
and its fibres transform in the $\mathbf{6}$ of $\SL{4} \simeq \SO{3,3}$. It is convenient to also introduce the generalised bundle with fibres in the anti-fundamental of $\SL{n+1}$, which is, similarly, given by
\begin{equation}
	N = T^*M \oplus \Lambda^{n} T^*M \,.
\end{equation}
Sections of $N$ are generalised tensors transforming in the anti-fundamental of $\SL{n+1}$ and carrying weight $\frac{2}{n+1}$. For $V, V' \in \Gamma(E)$ and $W \in \Gamma(N)$, the generalised Lie derivative \eqref{eq:SLnGenLie} reduces to
\begin{equation}
	\begin{split}
		\gL_{V} V' &= [v, v'] + L_{v} \omega'_{(n-2)} - \imath_{v'} \omega_{(n-2)} \,, \\
		\gL_{V} W &= L_v \omega_{(1)} + L_v \omega_{(n)} - \EM{\alpha} \omega_{(1)} \wedge \omega_{(n-2)} \,,
	\end{split}
\end{equation}
\EM{(I think $\alpha = 1$ but not 100\% sure)}
where we write $V = v + \omega_{(n-2)}$, $V' = v' + \omega'_{(n-2)}$ and $W = \omega_{(1)} + \omega_{(n)}$ as a formal of vectors and $p$-forms, and $L$ denotes the ordinary Lie derivative and $[v,v']$ the ordinary Lie bracket between vector fields $v$ and $v'$.

We can now describe the $S^n$ consistent truncation using the $\SL{n+1}$ ExFT above. Let $Y^I$, $I = 1, \ldots, n+1$ be the embedding coordinates of $S^{n} \subset \mathbb{R}^{n+1}$, such that $Y^I\, Y_I = 1$. On $S^n$, we can define a parallelisation of $N$ using the generalised frame \EM{Check sign of A! Although I'm pretty confident about it.}
\begin{equation}\label{eq:SnFrame}
	\cU^{\fl{I}} = dY^{\fl{I}} + Y^{\fl{I}}\, vol_{S^n} - A \wedge dY^{\fl{I}} \,,
\end{equation}
where $A$ is an $(n-1)$-potential with field strength $dA = (n-1) vol_{S^n}$, and
\begin{equation}
	vol_{S^n} = \epsilon_{I_1 I_2 \ldots I_{n+1}} Y^{I_1}\, dY^{I_2} \wedge \ldots \wedge dY^{I_{n+1}} \,,
\end{equation}
is the volume form on $S^n$. The frame in \eqref{eq:SnFrame} has the important property that the $n+1$ generalised tensors are nowhere vanishing since $dY^I = 0$ only when $Y^I = 1$.

In a local basis, \eqref{eq:SnFrame} gives us a $\GL{n+1}$ matrix, $\cU_I{}^{\fl{I}}$, whose determinant allows us to define the scalar density
\begin{equation} \label{eq:rho}
	\rho = \left(\det \cU_I{}^{\fl{I}}\right)^{-1/2} = \left(\det \mathring{g}\right)^{-1/2} \,,
\end{equation}
with $\mathring{g}$ the round metric on $S^n$. Using \eqref{eq:SnFrame} and \eqref{eq:rho} we can define the $\SL{n}$ twist matrix
\begin{equation} \label{eq:SLnFrame}
	U_I{}^{\fl{I}} = \rho^{2/(n+1)}\, \cU_I{}^{\fl{I}} \,.
\end{equation}
and hence a generalised frame for $E$ or a generalised bundle in any other rep of $\SL{n+1}$.

Evaluating \eqref{eq:SLnFrame} and \eqref{eq:rho} on the northern hemisphere $Y^I = \left( y^i,\, \sqrt{1-y^i y_i}\right)$, $i = 1, \ldots, n$ and using the gauge choice for the potential $A$
\begin{equation}
	A_{ij} = \epsilon_{ijk}\, y^k (1 + K(v)) \,,
\end{equation}
with $v = y^i\, y^i$ and $\epsilon_{ijk}$ the volume form on $S^3$, we precisely recover the $\SL{4}$ twist matrix of \cite{Hohm:2014qga}, i.e.
\begin{equation} \label{eq:SLnTwist}
	\UI_{\fl{I}}{}^I = \begin{pmatrix}
		\left(1-v\right)^{-1/4} \left( \delta_i{}^j + y_i\, y^j K(v) \right) & y_i \left(1-v\right)^{1/4} \\
		y^j \left(1-v\right)^{1/4} K(v) & \left(1-v\right)^{3/4}
	\end{pmatrix} \,.
\end{equation}
Moreover, the generalised frame for $E$ precisely coincides with the twist matrix in \cite{Lee:2014mla,Baguet:2015iou}. \EM{Give it explicitly?}

\EM{To do: Should mention Leibniz parallelisability somewhere and the embedding tensor that arises}

\subsubsection{Adding flux}
To demonstrate our methodology, we will now show how the parameter $\lambda$ introduced in \cite{Eloy:2021fhc} can be obtained by the twisting procedure outlined in \ref{s:AddFlux}. Let us decompose $\SO{4,4} \rightarrow \SO{3,3} \times \SO{1,1}$, such that
\begin{equation}
	\begin{split}
		\mathbf{8} &\rightarrow \mathbf{6_0} \oplus \mathbf{1_2} \oplus \mathbf{1_{-2}} \,, \\
		\mathbf{28} &\rightarrow \mathbf{15_0} \oplus \mathbf{6_2} \oplus \mathbf{6_{-2}} \oplus \mathbf{1_0} \,.
	\end{split}
\end{equation}
Correspondingly, we write a $\SO{4,4}$ vector $V^M$ as
\begin{equation}
	V^M = \left( V^A,\, V^z,\, V^{\bar{z}} \right) \,,
\end{equation}
where $A = 1, \ldots, 6$ labels the vector of $\SO{3,3}$ and $z$, $\bar{z}$ label the $\mathbf{1_2}$ and $\mathbf{1_{-2}}$, respectively.

We denote by $U_A{}^{\ov{A}}$ the $\SO{3,3}$ twist matrix corresponding to the $S^3$ truncation constructed in \cite{Lee:2014mla,Baguet:2015iou} and obtained from \eqref{eq:SLnFrame}, \eqref{eq:rho}, \eqref{eq:SLnTwist}. Then, we can add a 3-form potential by twisting with the $\SO{4,4}$ generator
\begin{equation} \label{eq:C2S3example}
	(e^C)^{MN} = C_A \left( t^A \right)^{MN} \,,
\end{equation}
with $C_A$ an element of the $\mathbf{6_{2}}$, and $\left( t^A \right)^{MN}$ the corresponding to $\SO{4,4}$ generator whose only non-zero component is
\begin{equation}
	\left(t^A\right)^{Bz} = \eta^{AB} \,.
\end{equation}
Here $\eta_{MN}$ and $\eta_{AB}$ are the $\SO{4,4}$ and $\SO{3,3}$ invariant metrics, respectively, and are used to raise/lower the corresponding vector indices. Decomposing with respect to the geometric $\SL{3} \times \mathbb{R}^+$ of the $S^3$,  the coordinates on $S^3$ live in the $Y^A = \left( y^i,\, y_i \right)$, $i = 1, 2, 3$, while $C_A = \left( C_i,\, C^i \right)$ naturally contains a 2-form $C^i$. The field strength $H_3 = \partial^A C_A = \partial_i C^i$ is a singlet of $\SO{3,3}$ and thus we see that $F_{AB}{}^C$ in \eqref{eq:FlatF} is constant and we obtain a consistent truncation with a new 3-form flux. Evaluating the twist matrix
\begin{equation}
	U'_M{}^{\ov{M}} = (e^C)_M{}^N  U_N{}^{\ov{M}} \,,
\end{equation}
explicitly using \eqref{eq:C2S3example} and setting $C^i = \lambda\, \xi^i$ in the notatin of \cite{Eloy:2021fhc}, we obtain precisely the twist matrix used in \cite{Eloy:2021fhc} for the consistent truncation of 6-dimensional ${\cal N}=(1,1)$ supergravity on $S^3$ with $H_3$ flux. \EM{Give precise form of $C^i$ such that we recover $\lambda$?}

%\EM{Spell out this as an example of the method}\\
%In fact, the consistent truncation of AdS$_3 \times S^3$ constructed in \cite{Eloy:2021fhc} can be understood exactly as arising in this way: it utilises the generalised parallelisability of $S^3$ with $U_M{}^A \in \SL{4} \simeq \SO{3,3}$ twist matrices but then adds a volume flux to the $S^3$ which is a singlet of $\SL{4}$ to obtain a new twist matrix via \eqref{eq:Twisting} which lives in $\SO{4,4}$. \EM{Should mention that this is a subsector of the $\SO{4,8}$ setup there?}
We will now follow this same procedure in the next section to obtain the consistent truncation of IIB supergravity on $S^3 \times S^3 \times S^1$ with 7-form flux.

\subsection{Adding flux to the $S^3 \times S^3 \times S^1$ truncation of IIB supergravity}
Our strategy for constructing the consistent truncation on $S^3 \times S^3 \times S^1$ with 7-form flux is to embed the $S^3 \times S^3$ truncation of $\En{7}$ ExFT \cite{Inverso:2017lrz} into $\EE \rightarrow \En{7} \times \SL{2}$, as described in \cite{Galli:2022idq} to generate the consistent truncation on $S^3 \times S^3 \times S^1$ without 7-form flux. We then add a 7-form flux to this truncation as outlined above.

\subsubsection{The $S^3 \times S^3$ truncation} \label{s:S3S3}
Let us first review the dyonic $S^3 \times S^3$ truncation of IIB supergravity \cite{Inverso:2017lrz}, which forms the starting point of our construction. The key step in the construction of \cite{Inverso:2017lrz} is that we can use the $\SL{4}$ generalised frame \eqref{eq:SLnFrame} to form a generalised Leibniz parallelisation of $\En{7}$ via the embedding
\begin{equation}
	\En{7} \rightarrow \SL{8} \rightarrow \SL{4} \times \SL{4} \times \mathbb{R}^+ \,.
\end{equation}
The fundamental of $\En{7}$ then decomposes as
\begin{equation}
	\mathbf{56} \rightarrow \mathbf{28} \oplus \overline{\mathbf{28}} \rightarrow \left[ \mathbf{\left(6,1\right)_2} \oplus \mathbf{\left(1,6\right)_{-2}} \oplus \mathbf{\left(4,4\right)_0} \right] \oplus \left[ \mathbf{\left(6,1\right)_{-2}} \oplus \mathbf{\left(1,6\right)_{2}} \oplus \mathbf{\left(\overline{4},\overline{4}\right)_0} \right] \,,
\end{equation}
where the first square brackets denote the branching of the $\mathbf{28}$ under $\SL{4} \times \SL{4} \times \mathbb{R}^+$ and the second square brackets that of the $\mathbf{\overline{28}}$. Crucially, for the generalised Leibniz condition \eqref{eq:GenLeibniz} to hold, the coordinates and generalised vector fields corresponding to the two $\SL{4}$'s must be embedded within the $\mathbf{28}$ and $\mathbf{\overline{28}}$, respectively, which we will call ``electric'' and ``magnetic'' coordinates, following \cite{Inverso:2017lrz}. Thus, we write the 56 $\En{7}$ coordinates as
\begin{equation}
	Y^M = \left( Y^{\cA\cB} ,\, Y_{\cA\cB} \right) \,,
\end{equation}
with $\cA, \cB = 1, \ldots, 8$ labelling the fundamental of $\SL{8}$, corresponding to the decomposition $\En{7} \rightarrow \SL{8}$. Following the conventions of \cite{Inverso:2017lrz}, the coordinates of the two $\SL{4}$ ExFTs are embedded as $Y^{IJ} \subset Y^{\cA\cB}$, with $I, J = 1, 2, 3, 8$, and $Y_{AB} \subset Y_{\cA\cB}$, with $A, B = 4, 5, 6, 7$. Solving the $\SL{4}$ ExFT section condition for $Y^{IJ}$ and $Y_{AB}$ guarantees a solution to the $\En{7}$ ExFT, and we choose the solution where the six physical coordinates of IIB are
\begin{equation} \label{eq:PhysicalCoords}
	y^i = Y^{i8},\, \qquad \tilde{y}_a = Y_{a7} \,, \qquad i = 1, 2, 3 \,, \qquad a = 4, 5, 6 \,.
\end{equation}

We can now use one copy of the $\SL{4}$ frame \eqref{eq:SLnFrame} for each $\SL{4}$ subgroup to construct a generalised parallelisation for the full $\En{7}$ ExFT, with an embedding tensor via \eqref{eq:GenLeibniz} \EM{given by \ldots}.

\EM{Include breaking of adjoint here?}\\
\EM{Should mention the geometric $\SL{3}$ subgroups here???}

\subsubsection{The $S^3 \times S^3 \times S^1$ truncation} \label{s:S3S3S1}
We now construct the consistent truncation on $S^3 \times S^3 \times S^1$ by embedding the $\En{7}$ twist matrix corresponding to the $S^3 \times S^3$ truncation reviewed above \ref{s:S3S3} in $\EE$ via the branching $\EE \rightarrow \En{7} \times \SL{2}$, such that $\mathbf{248} \rightarrow \mathbf{\left(133,1\right)} \oplus \mathbf{\left(56,2\right)} \oplus \mathbf{\left(1,3\right)}$. As explained in \cite{Galli:2022idq}, we can construct a consistent truncation on $M \times S^1$ to 3-dimensional gauged supergravity by embedding a consistent truncation on $M$ to 4-dimensional supergravity, characterised by a $\En{7}$ twist matrix, as follows. The $\EE$ twist matrix is parameterised by the $\En{7}$ twist matrix describing the consistent truncation on $M$ and the $\SL{2}$ twist matrix given by
\begin{equation}
	v_{\ov{i}}{}^i = \begin{pmatrix}
		\sigma & 0 \\ 0 & \sigma^{-1}
	\end{pmatrix} \,,
\end{equation}
where $\sigma$ is the $\En{7}$ scalar density used to construct the $\En{7}$ truncation on $M$. Finally, the $\EE$ scalar density satisfies $\rho = \sigma^2$ to ensure a consistent truncation on $S^3 \times S^3 \times S^1$. However, we still need to add the 7-form flux to obtain the ${\cal N}=(4,4)$ AdS$_3$ vacuum we are looking for. To do this, let us first review the group theory of the $S^3 \times S^3$ truncation, since this will allow us to determine whether the 7-form flux is stabilised by the twist matrix.

\subsubsection{Adding flux}
%We now wish to add a 7-form flux to the $S^3 \times S^3 \times S^1$ truncation constructed above.
To add a 7-form flux to the above truncation, we will follow the logic laid out in section \ref{s:AddFlux}, i.e. we will investigate whether the 7-form flux is stabilised by the twist matrix on $S^3 \times S^3 \times S^1$ constructed in section \ref{s:S3S3S1}. Thus, we need to understand 
%the group theory underlying the consistent truncation on $S^3 \times S^3$ \cite{Inverso:2016eet}. The $\En{7}$ twist matrix describing this truncation is constructed from two $\SL{4}$ twist matrices, one for each $S^3$ similar to \ref{s:S3Flux}, via the decomposition
%\begin{equation}
%	\En{7} \rightarrow \SL{8} \rightarrow \SL{4} \times \SL{4} \times \mathbb{R}^+ \,,
%\end{equation}
%under which the fundamental of $\En{7}$ branches as
%\begin{equation}
%	\mathbf{56} \rightarrow \mathbf{28} \oplus \overline{\mathbf{28}} \rightarrow \left[ \mathbf{\left(6,1\right)_2} \oplus \mathbf{\left(1,6\right)_{-2}} \oplus \mathbf{\left(4,4\right)_0} \right] \oplus \left[ \mathbf{\left(6,1\right)_{-2}} \oplus \mathbf{\left(1,6\right)_{2}} \oplus \mathbf{\left(\overline{4},\overline{4}\right)_0} \right] \,,
%\end{equation}
%where the first square brackets denote the branching of the $\mathbf{28}$ under $\SL{4} \times \SL{4} \times \mathbb{R}^+$ and the second square brackets that of the $\mathbf{\overline{28}}$.
%We want to see if 
whether IIB supergravity admits a 7-form field strength that is a singlet under these two $\SL{4}$ groups. To answer this question, we pick a gauge where the 6-form potential lives entirely in $S^3 \times S^3$ but depends on the $S^1$ coordinate, $z$. Therefore, in this gauge choice, the 6-form potential correspond sto an adjoint generator of $\En{7}$, and since the $S^1$ coordinate is an $\En{7}$ singlet, this adjoint generator must be a singlet under $\SL{4} \times \SL{4} \subset \SL{8} \subset \En{7}$ in order for us to have a consistent truncation.

IIB supergravity contains an S-duality doublet of 6-forms, which we can easily identify using the decomposition $\En{7} \rightarrow \SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB}$, under which the $\En{7}$ adjoint decomposes as
\begin{equation} \label{eq:AdjointSL6}
	\begin{split}
		\mathbf{133} &\rightarrow \mathbf{\left(35,1\right)_0} \oplus \mathbf{\left(1,3\right)_0} \oplus \mathbf{\left(1,1\right)_0} \oplus \mathbf{\left(1,2\right)_{\pm 6}} \\
		& \quad \oplus \mathbf{\left(\overline{15},2\right)_2} \oplus \mathbf{\left(\overline{15},1\right)_{-4}} \oplus \mathbf{\left(15,2\right)_{-2}} \oplus \mathbf{\left(15,1\right)_4} \,.
	\end{split}
\end{equation}
The 6-form doublet corresponds to the $\mathbf{\left(1,2\right)}_{6}$. To understand if one of the 6-forms in the doublet are singlets under $\SL{4} \times \SL{4} \subset \En{7}$, we must decompose $\En{7}$ with respect to the common subgroup of $\SL{4} \times \SL{4}$ and $\SL{6} \times \SL{2}$, which is $\SL{3}_1 \times \SL{3}_2 \times \mathbb{R}^+ \times \mathbb{R}^+$. The two $\SL{3}$ subgroups are defined by the embedding of the physical coordinates \eqref{eq:PhysicalCoords} into $\SL{4} \times \SL{4} \subset \SL{8} \subset \En{7}$. An important for us is to correctly identify the $\mathbb{R}^+$ charges in both decompositions. We have, on the one hand,
\begin{equation} \label{eq:SL4SL4}
	\begin{split}
		\En{7} &\rightarrow \SL{8} \rightarrow \SL{4} \times \SL{4} \times \mathbb{R}^+_{\SL{8}} \\
		&\rightarrow \SL{3}_1 \times \SL{3}_2 \times \mathbb{R}^+_1 \times \mathbb{R}^+_2 \times \mathbb{R}^+_{\SL{8}} \,,
	\end{split}
\end{equation}
and, on the other,
\begin{equation} \label{eq:SL6SL2}
	\begin{split}
		\En{7} &\rightarrow \SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB} \\
		&\rightarrow \SL{3}_1 \times \SL{3}_2 \times \mathbb{R}^+_{\SL{2}} \times \mathbb{R}^+_{\SL{6}} \times \mathbb{R}^+_{\rm IIB} \,.
	\end{split}
\end{equation}
Here, we label the $\mathbb{R}^+$'s with a subscript that refers to the the groups they belong belong to. The $\mathbb{R}^+$ generators of the two decompositions are related as
\begin{equation} \label{eq:R+charges}
	\begin{split}
		\mathbb{R}^+_{\SL{6}} &= - \frac12 \left( \mathbb{R}^+_{\SL{3}_1} + \mathbb{R}^+_{\SL{3}_2} \right) \,, \\
		\mathbb{R}^+_{\SL{2}} &= \frac14 \left( \mathbb{R}^+_{\SL{3}_1} - \mathbb{R}^+_{\SL{3}_2} + \mathbb{R}^+_{\SL{8}} \right) \,, \\
		\mathbb{R}^+_{\rm IIB} &= \frac12 \left( \mathbb{R}^+_{\SL{3}_1} - \mathbb{R}^+_{\SL{3}_2} - 3\, \mathbb{R}^+_{\SL{8}} \right) \,.
	\end{split}
\end{equation}

The branching of the adjoint \eqref{eq:AdjointSL6} under $\SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB}$ in \eqref{eq:SL6SL2} needs to now be compared with that via $\SL{4} \times \SL{4} \times \mathbb{R}^+_{\SL{8}}$, given by
\begin{equation}
	\begin{split}
		\mathbf{133} &\rightarrow \mathbf{63} \oplus \mathbf{70} \\
		&\rightarrow \mathbf{\left(15,1\right)_0} \oplus \mathbf{\left(1,15\right)_0} \oplus \mathbf{\left(1,1\right)_0} \oplus \mathbf{\left(4,\overline{4}\right)_2} \oplus \mathbf{\left(\overline{4},4\right)_{-2}} \\
		& \quad \oplus \mathbf{\left(1,1\right)_{-4}} \oplus \mathbf{\left(1,1\right)_{4}} \oplus \mathbf{\left(4,\overline{4}\right)_{-2}} \oplus \mathbf{\left(\overline{4},4\right)_{2}} \oplus \mathbf{\left(6,6\right)_0} \,.
	\end{split}
\end{equation}
Using \eqref{eq:R+charges}, we can now identify each of the singlet generators $\left(1,1\right)_{\pm4}$ with one of the $\SL{2}$ doublet generators of charge $\mp 6$. Therefore, we find exactly one singlet $\SL{4} \times \SL{4}$ generator, which we can write as $t_{1238}$, corresponding to a 6-form potential. The other $\SL{4} \times \SL{4}$ singlet generator, $t_{4567}$, only differs by a compact generator and thus does not corresponding to a different physical field. Finally, the other elements of the $\SL{2}$ doublet of 6-form potential can be mapped to the $\mathbf{\left(4,\overline{4}\right)_{2}} \oplus \mathbf{\left(\overline{4},4\right)_{-2}}$ generators, specifically $t_7{}^8$ and $t_8{}^7$ and are clearly not $\SL{4}$ singlets.
\EM{Is this sufficiently clear? I am not so sure...}

Therefore, we can add a 7-form flux to the twist matrix using
\begin{equation}
	\cU_{\fl{M}}{}^M \longrightarrow \cU'_{\fl{M}}{}^M = \cU_{\fl{M}}{}^N \exp(C)_N{}^M \,,
\end{equation}
with $C_M{}^N = \lambda\, z\, t_{1238\,M}{}^N$ and $\lambda$ a numerical parameter corresponding to the amount of 7-form flux. \EM{Is there a density factor that needs to be added?} \EM{The resulting embedding tensor is \ldots}

%, which transform under the subgroup $\SL{6} \times \SL{2} \times \mathbb{R}^+_{IIB} \subset \En{7}$ as $\mathbf{\left(1,2\right)_{6}} \subset \mathbf{133}$

%\EM{Describe how $C_6{}^\alpha$ sits in here}

\section{Moduli of AdS$_3 \times S^3 \times S^3 \times S^1$}

\subsection{Moduli in gauged supergravity}

\subsection{Moduli in 10 dimensions}

\paragraph{SUSY deformation}
\begin{equation}
	\begin{split}
		ds^2 &= \alpha^2 \left[ ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
		d\sigma &= vol_{\mathbb{CP}^1} \,.
	\end{split}
\end{equation}

\paragraph{Non-SUSY deformation}
\begin{equation}
\begin{split}
ds^2 &= \alpha^2 \left[ d\alpha_1^2 +  ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
d\sigma &= vol_{\mathbb{CP}^1} \,.
\end{split}
\end{equation}

\subsection{Compactification of the moduli space}

\section{Conclusions}

\section*{Acknowledgements}
We are grateful to XXX for useful discussions and correspondence. CE is supported by the FWO-Vlaanderen through the project G006119N and by the Vrije Universiteit Brussel through the Strategic Research Program ``High-Energy Physics''. MG and EM are supported by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) via the Emmy Noether program ``Exploring the landscape of string theory flux vacua using exceptional field theory'' (project number 426510644).

\bibliographystyle{JHEP}
\bibliography{NewBib}

\end{document}

### 2023-05-08 Notes_3dH3.tex
Draft created by Emanuel.

@@
   \end{equation}
-  So the coordinates are inside $(\bm{6},\bm{1})_{-2}\oplus(\bm{1},\bm{6})_{2}$ of $\SL(4)_{1}\times\SL(4)_{2}\times\R^{+}_{\SL(8)}$.
+  So the coordinates are inside $(\bm{6},\bm{1})_{-2}\oplus(\bm{1},\bm{6})_{-2}$ of $\SL(4)_{1}\times\SL(4)_{2}\times\R^{+}_{\SL(8)}$.
 \ce{Problem with $3, \bar{3}$?
@@
   \begin{equation}
-    \left[\ell^{+}_{R},\ell^{-}_{R}\right]^{j_{\rm L}^{+}}_{_{\rm L}^{+}},
+    \left[\ell^{+}_{R},\ell^{-}_{R}\right]^{j_{\rm L}^{+}}_{q_{\rm L}^{+}},
   \end{equation}
@@
 \ce{So no distinction between (1,1) and (2,0)?
-Because triality, or I made errors?} $\leq$
+Because triality, or I made errors?}
+
+\section{\texorpdfstring{$\E_{8(8)}$}{E8(8)} identities}
+
+\begin{gather}
+  \eta^{MN} = \frac{1}{60}\,f^{MK}{}_{L}f^{NL}{}_{K}, \\
+  \M^{PM}\M^{QN}f_{PQ}{}^{K} = - f^{MN}{}_{L}\M^{LK}, \\
+  J_{\bar M\bar N}{}^{\bar P} = U_{\bar M}{}^{M}\partial_{M}U_{\bar N}{}^{P}U^{\bar P}{}_{P}, \\
+  f^{K}{}_{MR}f^{RL}{}_{N}\,J_{KP}{}^{Q}J_{LU}{}^{V} = J_{MP}{}^{Q}J_{NU}{}^{V}+J_{NP}{}^{Q}J_{MU}{}^{V},\\
+  f^{MN}{}_{P}J_{KL}{}^{P} = -2\,J_{KP}{}^{[M}f^{N]P}{}_{L}, \\
+  J_{MN}{}^{P} = \frac{1}{60} \,f_{N}{}^{PR}f_{RK}{}^{L}J_{ML}{}^{K}, \\
+  J_{MN}{}^{P} = -\frac{1}{30} \,f_{N}{}^{KR}f_{R}{}^{P}{}_{L}J_{MK}{}^{L},\\
+  f_{M}{}^{KL}J_{KL}{}^{R}J_{RP}{}^{Q} = f_{M}{}^{KL}J_{RQ}{}^{P}J_{KL}{}^{K},\\
+  2\,J_{L[M}{}^{K}f_{N]K}{}^{L} = -f_{MN}{}^{K}J_{LK}{}^{L}.
+\end{gather}
+
+Section constraint (one of them):
+\begin{equation}
+  f^{K}{}_{MR}f^{RL}{}_{N} \,\partial_{K}\otimes\partial_{L} = 2\,\partial_{(M}\otimes\partial_{N)}.
+\end{equation}
 

### 2023-05-09 Draft_3dH3.tex
Update of section 2 with a review of ExFT and consistent truncations. Upadate of section 4 with the 10d metric of the 3-parameter solution.

@@
+%!TEX output_directory = aux
+
 \documentclass[a4paper, 11pt]{article}
@@
 \usepackage[shortlabels]{enumitem}
+
+\usepackage{xspace}
+\usepackage{mathrsfs}
 
@@
 \newcommand{\Spin}[1]{\mathrm{Spin}(#1)}
-\newcommand{\EE}{E_{8(8)}}
+\newcommand{\EE}{\ensuremath{E_{8(8)}}\xspace}
 \newcommand{\USp}[1]{\mathrm{USp}(#1)}
@@
 \DeclareMathOperator{\tr}{Tr}
+
+% ---- MATHS COMMANDS ----
+\newcommand{\M}{\ensuremath{\mathcal{M}}\xspace}
+\newcommand{\A}{\ensuremath{\mathcal{A}}\xspace}
+\renewcommand{\d}{\ensuremath{\mathrm{d}}\xspace}
+
 %% Comments
@@
 \newcommand{\MG}[1]{\textcolor{blue}{#1}}
-\newcommand{\CE}[1]{\textcolor{green}{#1}}
+\definecolor{darkorange}{RGB}{166, 88, 0}
+\newcommand{\CE}[1]{\textcolor{darkorange}{#1}}
 \newcommand{\CG}{\Com{G}{\EE}}
@@
 
-\section{Review of $\EE$ ExFT and consistent truncations} \label{s:Review}
-Review relevant bits of \cite{Hohm:2014fxa} and \cite{Galli:2022idq}.
+\section{\texorpdfstring{\EE}{E8(8)} ExFT and consistent truncations} \label{s:Review}
 
-A consistent truncation requires that the objects
-\begin{equation} \label{eq:DoubleU}
-	\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}}) \,, \qquad \Sigma_{\fl{M}\,M} = \frac{1}{60} \rho^{-1} f_{\fl{M}}{}^{\fl{N}\fl{P}}\, U_{\fl{N}\,P} \partial_M U_{\fl{P}}{}^{P} \,, \qquad \cU_{\fl{M}}{}^M = \rho^{-1} U_{\fl{M}}{}^M \,,
+\subsection{Review of \texorpdfstring{\EE}{E8(8)} exceptional field theory}
+The \EE exceptional field theory, first constructed in ref.~\cite{Hohm:2014fxa}, is an \EE duality-covariant formulation of type II and 11d supergravities.
+It is defined on a set of $3+248$ coordinates made of three-dimensonal external coordinates $\{x^{\mu}\}$ and internal coordinates $\{Y^{M}\}$ in the 248-dimensional adjoint representation of \EE.
+The dependance of the fields on these coordinates is constrained by the ``section constraints''\footnote{We use the notation $\otimes$ to indicate that both derivatives may act on different functions.}
+\begin{equation} \label{eq:sectionconstraints}
+	\begin{cases}
+		\eta^{MN}\partial_{M}\otimes\partial_{N} = 0,\\
+		f^{MN}{}_{P}\,\partial_{M}\otimes\partial_{N} = 0,\\
+		(\mathbb{P}_{3875})_{MN}{}^{KL}\partial_{K}\otimes\partial_{L} = 0,
+	\end{cases}
 \end{equation}
-satisfy the differential condition
+where $f_{MN}{}^{P}$ are the structure constants of \EE, $\eta_{MN} = (1/60)\,f_{MK}{}^{L}f_{NL}{}^{K}$ its Cartan-Killing metric and $(\mathbb{P}_{3875})_{MN}{}^{KL}$ is the projector on the representation $\mathbf{3875}$:
+\begin{equation}
+	(\mathbb{P}_{3875})_{MN}{}^{KL} = \frac{1}{7}\, \delta_{(M}{}^{K}\delta_{N)}{}^{L}-\frac{1}{56}\,\eta_{MN}\eta^{KL}-\frac{1}{14}\,f^{P}{}_{M}{}^{(K}f_{PN}{}^{L)}.
+\end{equation}
+Here and in the following, \EE indices are raised and lowered by the Cartan-Killing metric $\eta_{MN}$.
+The section constraints~\eqref{eq:sectionconstraints} ensure that the fields depends only on the 7- or 8-dimensional physical internal coordinates embeded in $Y^{M}$.
+
+The theory describes the dynamics of the following bosonic fields:
+\begin{equation}
+	\left\{g_{\mu\nu}, \M_{MN}, A_{\mu}{}^{M}, B_{\mu\,M}\right\},
+\end{equation}
+with $g_{\mu\nu}$ the 3-dimensinal external metric, $\M_{MN}$ the generalized metric parametrizing the coset space $\EE/\SO{16}$ and the gauge fields $A_{\mu}{}^{M}$ and $B_{\mu\,M}$.
+It is a gauge theory, invariant under the generalized Lie derivative of parameters $\Upsilon=(\Lambda^{M},\Sigma_{M})$, whose action on a vector $V^{M}$ of weight $\lambda$ is given by
+\begin{equation} \label{eq:genlie}
+	{\cal L}_{\Upsilon} V^{M} = \Lambda^{N}\partial_{N}V^{M}-60\,(\mathbb{P}_{248})^{M}{}_{N}{}^{K}{}_{L}\,V^{N}\partial_{K}\Lambda^{L} + \lambda\, V^{M}\partial_{N}\Lambda^{N}+f^{MN}{}_{K}\Sigma_{N}V^{K},
+\end{equation}
+with $(\mathbb{P}_{248})^{M}{}_{N}{}^{K}{}_{L}=(1/60)\,f^{M}{}_{NP}f^{PK}{}_{L}$ the projector on the adjoint representation.
+These transformations are well-defined (in particular, they close into an algebra) only if the parameters $\Sigma_{M}$ and the fields $B_{\mu\, M}$ are covariantly constrained: they have to satisfy algebraic constraints similar to eq.~\eqref{eq:sectionconstraints} and be compatibile with the partial derivatives.
+We require that
+\begin{equation} \label{eq:sectionconstraint2}
+	\begin{cases}
+		\eta^{MN}C_{M}\otimes C'_{N} = 0,\\
+		f^{MN}{}_{P}\,C_{M}\otimes C'_{N} = 0,\\
+		(\mathbb{P}_{3875})_{MN}{}^{KL}C_{K}\otimes C'_{L} = 0,
+	\end{cases}
+	\forall\  C_{M}, C'_{M} \in \{\partial_{M}, \Sigma_{M}, B_{\mu\,M}\}.
+\end{equation}
+
+\paragraph{}
+The bosonic action of \EE exceptional field theory is invariant under the transformations~\eqref{eq:genlie} and has the expression
+\begin{equation} \label{eq:ExFTaction}
+	S_{\rm ExFT} = \int d^{3}x\,d^{248}Y\,\sqrt{\vert g\vert} \bigg(\widehat{R}+\frac{1}{240}\,D_{\mu}\M_{MN}D^{\mu}\M^{MN}+\mathscr{L}_{\rm int}+\frac{1}{\sqrt{\vert g\vert}}\,\mathscr{L}_{\rm CS}\bigg).
+\end{equation}
+$\widehat{R}$ is the \EE-covariantised Ricci scalar and the covariant derivative is defined as
+\begin{equation}
+	D_{\mu} = \partial_{\mu} - {\cal L}_{(A_{\mu}, B_{\mu})}.
+\end{equation}
+$\mathscr{L}_{\rm int}$ is a potential term depending only on internal derivatives:
+\begin{equation}
+	\begin{aligned}
+		\mathscr{L}_{\rm int} &= \frac{1}{240}\,\M^{MN}\partial_{M}\M^{KL}\partial_{N}\M_{KL} - \frac{1}{2}\,\M^{MN}\partial_{M}\M^{KL}\partial_{L}\M_{NK} \\
+		&\quad -\frac{1}{7200}\,f^{NQ}{}_{P}f^{MS}{}_{R}\,\M^{PK}\partial_{M}\M_{QK}\,\M^{RL}\partial_{N}\M_{SL}\\
+		&\quad +\frac{1}{2}\,g^{-1}\partial_{M}g\,\partial_{N}\M^{MN} + \frac{1}{4}\,\M^{MN}\,g^{-2}\partial_{M}g\,\partial_{N}g + \frac{1}{4}\,\M^{MN}\,\partial_{M}g_{\mu\nu}\,\partial_{N}g^{\mu\nu}.
+	\end{aligned}
+\end{equation}
+Finally, $\mathscr{L}_{\rm CS}$ is a Chern-Simons term required to impose the on-shell duality between scalar and vector fields:
+\begin{equation}
+	\begin{aligned}
+		\mathscr{L}_{\rm CS} &= \frac{1}{2}\,\varepsilon^{\mu\nu\rho}\,\bigg(F_{\mu\nu}{}^{M}B_{\rho\,M}-f_{KL}{}^{N}\,\partial_{\mu}A_{\nu}{}^{K}\partial_{N}A_{\rho}{}^{L}-\frac{2}{3}\,f^{N}{}_{KL}\,\partial_{M}\partial_{N}A_{\mu}{}^{K}A_{\nu}{}^{M}A_{\rho}{}^{L}\\
+		&\quad -\frac{1}{3}\,f_{MKL}\,f^{KP}{}_{Q}\,f^{LR}{}_{S}\,A_{\mu}{}^{M}\partial_{P}A_{\nu}{}^{Q}\partial_{R}A_{\rho}{}^{S}\bigg),
+	\end{aligned}
+\end{equation}
+where $F_{\mu\nu}{}^{M}$ is the covariant field strength of $A_{\mu}{}^{M}$ (see eq. (2.26) of ref.~\cite{Hohm:2014fxa}).
+
+\subsection{Generalized Scherk-Schwarz ansatz and consistent truncations}
+The \EE exceptional field theory is well suited to the construction of consistent truncation of type~II and 11d supergravities to three-dimensional maximal supergravity.
+These truncations arise as generalised Scherk-Schwarz reduction, described by an \EE-valued twist matrix $U_{\fl{M}}{}^{M}$ and a scale factor $\rho$.
+The compactification Ansätze are as follows~\cite{Galli:2022idq}:
+\begin{equation} \label{eq:GSSansatz}
+	\begin{aligned}
+		g_{\mu\nu}(x,Y)&=\rho(Y)^{-2}\,\mathring{g}_{\mu\nu}(x),\\
+		\M_{MN}(x,Y)&=U^{\fl{M}}{}_{M}(Y)\,U^{\fl{N}}{}_{N}(Y)\,\M_{\fl{MN}}(x),\\
+		A_{\mu}{}^{M}(x,Y)=&\rho(Y)^{-1}\,U_{\fl{M}}{}^{M}(Y)\,\A_{\mu}{}^{\fl{M}}(x),\\
+		B_{\mu\,M}(x,Y)&=\Sigma_{\fl{M}\,M}(Y)\,\A_{\mu}{}^{\fl{M}}(x),
+	\end{aligned}
+\end{equation}
+with
+\begin{equation}
+	\Sigma_{\fl{M}\,M}=\frac{\rho^{-1}}{60}\,f_{\fl{M}}{}^{\fl{PQ}}\,U_{\fl{P}P}\,\partial_{M}U_{\fl{Q}}{}^{P}.
+\end{equation}
+The fields with flat indices $\fl{M}$ (in the $\mathbf{248}$ representation of \EE) describe the three-dimensional theory; all the dependence on the internal manifold is factored out in $U_{\fl{M}}{}^{M}$ and $\rho$.
+Note that with the definition of $\Sigma_{\fl{M}\,M}$ the condition~\eqref{eq:sectionconstraint2} is automatically satisfied.
+
+The Ansätze~\eqref{eq:GSSansatz} describe a consistent truncation if the following condition is satisfied:
 \begin{equation} \label{eq:GenLeibniz}
-	\gL_{\ff{U}_{\fl{M}}} {\cU}_{\fl{N}}{}^M = X_{\fl{M}\fl{N}}{}^{\fl{P}}\, \cU_{\fl{P}}{}^M \,,
+	\gL_{\ff{U}_{\fl{M}}} {\cU}_{\fl{N}}{}^M = X_{\fl{M}\fl{N}}{}^{\fl{P}}\, \cU_{\fl{P}}{}^M,
 \end{equation}
-with $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ constant.
+with $\cU_{\fl{M}}{}^M = \rho^{-1} U_{\fl{M}}{}^M$, $\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}})$ and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ a constant tensor.
+This condition ensures that the factorised form of the Ansätze~\eqref{eq:GSSansatz} is preserved by the generalized Lie derivative, \textit{e.g.}
+\begin{equation}
+	\begin{aligned}
+		D_{\mu}\M(x,Y) &= U^{\fl{M}}{}_{M}(Y)\,U^{\fl{N}}{}_{N}(Y)\,{\cal D}_{\mu}\M_{\fl{MN}}(x),\\
+		{\cal L}_{(A_{\mu},B_{\nu})}A_{\mu}(x,Y) &= \rho(Y)^{-1}\,U_{\fl{M}}{}^{M}(Y)\,\llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}(x),
+	\end{aligned}
+\end{equation}
+where
+\begin{equation}
+	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}}-2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M})}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}} \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}}.
+\end{equation}
 
-\section{3-dimensional ${\cal N}=16$ gauged supergravity} \label{s:3dSUGRA}
+The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity. It has the following expression:
+\begin{equation}
+	\begin{aligned}
+		X_{\bar M\bar N}{}^{\bar P}&=-\rho^{-1}\,\Gamma_{\bar M\bar N}{}^{\bar P} + \rho^{-1}\,f^{\bar P}{}_{\bar N\bar Q}f^{\bar Q\bar K}{}_{\bar L}\,\Gamma_{\bar K\bar M}{}^{\bar L}-\frac{1}{60}\,\rho^{-1}\,f^{\bar P\bar K}{}_{\bar N}f_{\bar M\bar L}{}^{\bar Q}\,\Gamma_{\bar K\bar Q}{}^{\bar L}\\
+		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\bar P}{}_{\bar N\bar Q}f^{\bar Q\bar K}{}_{\bar M}\,\Gamma_{\bar R\bar K}{}^{\bar R}+\left(\delta_{\bar M}{}^{\bar K}\delta_{\bar N}{}^{\bar P}-\frac{1}{2}\,f_{\bar M}{}^{\bar L\bar K}f_{\bar N\bar L}{}^{\bar P}\right)\,\xi_{\bar K}.
+	\end{aligned}
+\end{equation}
+Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\bar M\bar N}{}^{\bar P}=U_{\bar M}{}^{K}U_{\bar N}{}^{L}\partial_{K}U^{\bar P}{}_{L}$ and the trombone gauging
+\begin{equation}
+	\xi_{\bar M} = 2\,U_{\bar M}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\bar M}{}^{N}.
+\end{equation}
+In the following, we consider $\xi_{\bar M}=0$. The embedding tensor is most nicely expressed once projected on the adjoint representation
+\begin{equation}
+	X_{\bar M\bar N} = -\frac{1}{60}\,X_{\bar M\bar P}{}^{\bar Q}\,f_{\bar N\bar Q}{}^{\bar P} = 2\,\rho^{-1}\,\Gamma_{(\bar M\bar N)} - \rho^{-1}\,\Gamma_{\bar K(\bar M}{}^{\bar L}\,f_{\bar N)\bar L}{}^{\bar K},
+\end{equation}
+with the projection of the current $\Gamma_{\bar M\bar N} = (1/60)\,\Gamma_{\bar M\bar P}{}^{\bar Q}\,f_{\bar N\bar Q}{}^{\bar P}$.
+
+% Consider a twist matrix $U_{\bar M}{}^{M}$ and a scale factor $\rho$. A consistent truncation requires that the objects
+% \begin{equation} \label{eq:DoubleU}
+% 	\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}}) \,, \qquad \Sigma_{\fl{M}\,M} = \frac{1}{60} \rho^{-1} f_{\fl{M}}{}^{\fl{N}\fl{P}}\, U_{\fl{N}\,P} \partial_M U_{\fl{P}}{}^{P} \,, \qquad \cU_{\fl{M}}{}^M = \rho^{-1} U_{\fl{M}}{}^M \,,
+% \end{equation}
+% satisfy the differential condition
+% \begin{equation} \label{eq:GenLeibniz}
+% 	\gL_{\ff{U}_{\fl{M}}} {\cU}_{\fl{N}}{}^M = X_{\fl{M}\fl{N}}{}^{\fl{P}}\, \cU_{\fl{P}}{}^M \,,
+% \end{equation}
+
+With the generalized Scherk-Schwarz Ansätze~\eqref{eq:GSSansatz}, the action~\eqref{eq:ExFTaction} becomes
+\begin{equation}
+	\begin{aligned}
+		S_{\rm ExFT} \underset{\rm gSS}{=} \int\d^{248}Y\,\rho^{-1}\int \d^{3}x & \bigg[\sqrt{\vert\mathring{g}\vert}\bigg(\mathring{R}+\frac{1}{240}\,{\cal D}_{\mu}\M_{\bar M\bar N}{\cal D}^{\mu}\M^{\bar M\bar N}-V\bigg) \\
+		&-\varepsilon^{\mu\nu\rho}\,X_{\bar M\bar N}\,\A_{\mu}{}^{\bar M} \left(\partial_{\nu}\A_{\rho}{}^{\bar N}-\frac{1}{3}\,\llbracket\A_{\nu},\A_{\rho}\rrbracket^{\bar N}\right)\bigg],
+	\end{aligned}
+\end{equation}
+with the potential\footnote{To obtain this potential, one has to add the total derivative $-\partial_{M}\left(\sqrt{\vert g\vert}\,\partial_{N}\M^{MN}+(4/3)\,\M^{MN}\partial_{N}\sqrt{\vert g\vert}\right)$ to $\sqrt{\vert g\vert}\,\mathscr{L}_{\rm int}$.}
+\begin{equation}
+	V = X_{\bar M\bar N}\,X_{\bar P\bar Q}\left(\frac{1}{28}\,\M^{\bar M\bar P}\M^{\bar N\bar Q}+\frac{1}{2}\,\M^{\bar M\bar P}\eta^{\bar N\bar Q}+\frac{13}{28}\,\eta^{\bar M\bar P}\eta^{\bar N\bar Q}\right).
+\end{equation}
 
@@
 However, this will not give the correct AdS$_3$ vacuum since the truncation is missing the 7-form flux on $S^3 \times S^3 \times S^1$ that is required.
-Indeed, the 3-dimensional gauged supergravity that would be obtained as discussed way does not have any AdS$_3$ vacua.
+Indeed, the 3-dimensional gauged supergravity that would be obtained as discussed way \CE{(?)} does not have any AdS$_3$ vacua.
 We can remedy this situation by defining a new consistent truncation by adding a 7-form flux to the one obtained from the $S^3 \times S^3$ reduction constructed in $\En{7}$ ExFT.
@@
 \subsection{Adding fluxes to the $S^3$ truncation of 6-dimensional supergravity} \label{s:S3Flux}
-Before dealing with the $S^3 \times S^3 \times S^1$ truncation, let us demonstrate this methdology for the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity on $S^3$, which was constructed in \cite{Eloy:2021fhc}.
+Before dealing with the $S^3 \times S^3 \times S^1$ truncation, let us demonstrate this methodology for the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity on $S^3$, which was constructed in \cite{Eloy:2021fhc}.
 As discussed in \cite{Eloy:2021fhc}, the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity to 3-dimensional half-maximal gauged supergravity can be described using the $\SO{8,4}$ ExFT \cite{Hohm:2017wtr,Samtleben:2019zrh}.
@@
 \end{equation}
-explicitly using \eqref{eq:C2S3example} and setting $C^i = \lambda\, \xi^i$ in the notatin of \cite{Eloy:2021fhc}, we obtain precisely the twist matrix used in \cite{Eloy:2021fhc} for the consistent truncation of 6-dimensional ${\cal N}=(1,1)$ supergravity on $S^3$ with $H_3$ flux.
+explicitly using \eqref{eq:C2S3example} and setting $C^i = \lambda\, \xi^i$ in the notation of \cite{Eloy:2021fhc}, we obtain precisely the twist matrix used in \cite{Eloy:2021fhc} for the consistent truncation of 6-dimensional ${\cal N}=(1,1)$ supergravity on $S^3$ with $H_3$ flux.
 \EM{Give precise form of $C^i$ such that we recover $\lambda$?}
@@
 To answer this question, we pick a gauge where the 6-form potential lives entirely in $S^3 \times S^3$ but depends on the $S^1$ coordinate, $z$.
-Therefore, in this gauge choice, the 6-form potential correspond sto an adjoint generator of $\En{7}$, and since the $S^1$ coordinate is an $\En{7}$ singlet, this adjoint generator must be a singlet under $\SL{4} \times \SL{4} \subset \SL{8} \subset \En{7}$ in order for us to have a consistent truncation.
+Therefore, in this gauge choice, the 6-form potential corresponds to an adjoint generator of $\En{7}$, and since the $S^1$ coordinate is an $\En{7}$ singlet, this adjoint generator must be a singlet under $\SL{4} \times \SL{4} \subset \SL{8} \subset \En{7}$ in order for us to have a consistent truncation.
 
@@
 \end{equation}
-Here, we label the $\mathbb{R}^+$'s with a subscript that refers to the the groups they belong belong to. The $\mathbb{R}^+$ generators of the two decompositions are related as
+Here, we label the $\mathbb{R}^+$'s with a subscript that refers to the the groups they belong to. The $\mathbb{R}^+$ generators of the two decompositions are related as
 \begin{equation} \label{eq:R+charges}
@@
 with $C_M{}^N = \lambda\, z\, t_{1238\,M}{}^N$ and $\lambda$ a numerical parameter corresponding to the amount of 7-form flux.
-\EM{Is there a density factor that needs to be added?} \EM{The resulting embedding tensor is \ldots}
+\EM{Is there a density factor that needs to be added?} \CE{Yes.} \EM{The resulting embedding tensor is \ldots}
 
@@
 \paragraph{SUSY deformation}
+In Hopf coordinates:
 \begin{equation}
@@
 		ds^2 &= \alpha^2 \left[ ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
-		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
+		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{\CE{-}(1-e^{2\omega})} d\psi \,, \\
 		d\sigma &= vol_{\mathbb{CP}^1} \,.
@@
 
+In spherical coordinates:
+\begin{equation}
+	\begin{aligned}
+		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+\alpha^{2}\,\d s^2\left(S^{3}_{-}\right) +e^{-2\omega}\,\d\psi^{2}\\
+		&\quad+2\,\alpha\,e^{-2\omega}\,\sqrt{-1+e^{2\omega}}\left(-\cos^{2}(\theta)\,\d\varphi_{1}+\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi\\[5pt]
+		&= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+e^{-4\omega}\,\d\psi^{2}\\
+		&\quad+\alpha^{2}\bigg[\d \theta^2+\cos^{2}(\theta)\left(\d\varphi_{1}-\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}+\sin^{2}(\theta)\left(\d\varphi_{2}+\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}\bigg] ,\\[5pt]
+		\d s^2\left(S^{3}_{-}\right) &= \d\theta^{2}+\cos^{2}(\theta)\,\d\varphi_{1}^{2}+\sin^{2}(\theta)\,\d\varphi_{2}^{2}.
+	\end{aligned}
+\end{equation}
+
 \paragraph{Non-SUSY deformation}
+In spherical coordinates:
 \begin{equation}
-\begin{split}
-ds^2 &= \alpha^2 \left[ d\alpha_1^2 +  ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
-\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
-d\sigma &= vol_{\mathbb{CP}^1} \,.
-\end{split}
+	\begin{aligned}
+		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
+		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
+		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2},\\[5pt]
+		\Delta^{-1} &= 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
+	\end{aligned}
+\end{equation}
+
+In Hopf coordinates:
+% \begin{equation}
+% \begin{split}
+% ds^2 &= \alpha^2 \left[ d\alpha_1^2 +  ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
+% \kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
+% d\sigma &= vol_{\mathbb{CP}^1} \,.
+% \end{split}
+% \end{equation}
+% \begin{equation}
+% 	\begin{aligned}
+% 		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+% 		&\quad + \Delta\,\alpha^{2}\bigg[\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm I}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm R}^{2}\Big)\,\d z_{\rm R}^{2}\\
+% 		&\qquad\ \  + \frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm R}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm I}^{2}\Big)\,\d z_{\rm I}^{2}\\
+% 		&\qquad\ \  + 2\,\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(-\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(2+\vert z\vert^{2}\right)+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d z_{\rm R}\d z_{\rm I}\\
+% 		&\qquad\ \  +2\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\,\vert z\vert^{2}+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d\theta^{2}\bigg]\\
+% 		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
+% 		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
+% 		\Delta^{-1} &= 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
+% 	\end{aligned}
+% \end{equation}
+\begin{equation}
+	\begin{aligned}
+		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+		&\quad + \frac{\alpha^{2}}{1+\gamma\,\vert z\vert^{2}}\bigg[\Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm I}^{2}\right)+\left(\gamma-1\right)\,z_{\rm R}^{2}\Big)\,\frac{\d z_{\rm R}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
+		&\qquad + \Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm R}^{2}\right)+\left(\gamma-1\right)\,z_{\rm I}^{2}\Big)\,\frac{\d z_{\rm I}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}} - 2\,\Big(1+\vert z\vert^{2}-\left(\gamma-1\right)\Big)\,\frac{\d z_{\rm R}\d z_{\rm I}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
+		&\qquad+2\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\left(\gamma+\vert z\vert^{2}\right)\d\theta^{2}\bigg]\\
+		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
+		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
+		\gamma &= \frac{2\,e^{2\Omega}+\zeta_{2,3}^{2}}{2+e^{2\Omega}\zeta_{1,8}^{2}},\qquad \Delta^{-1} = 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
+	\end{aligned}
 \end{equation}

### 2023-05-15 Draft_3dH3.tex
Change of notation for barred indices.

@@
 
-\section{\texorpdfstring{\EE}{E8(8)} ExFT and consistent truncations} \label{s:Review}
+% \section{\texorpdfstring{\EE}{E8(8)} ExFT and consistent truncations}
 
-\subsection{Review of \texorpdfstring{\EE}{E8(8)} exceptional field theory}
+\section{Review of \texorpdfstring{\EE}{E8(8)} exceptional field theory} \label{s:Review}
+
 The \EE exceptional field theory, first constructed in ref.~\cite{Hohm:2014fxa}, is an \EE duality-covariant formulation of type II and 11d supergravities.
@@
 
-\subsection{Generalized Scherk-Schwarz ansatz and consistent truncations}
+\section{Consistent truncations to 3-dimensional \texorpdfstring{${\cal N}=16$}{N=16} gauged supergravity}
 The \EE exceptional field theory is well suited to the construction of consistent truncation of type~II and 11d supergravities to three-dimensional maximal supergravity.
-These truncations arise as generalised Scherk-Schwarz reduction, described by an \EE-valued twist matrix $U_{\fl{M}}{}^{M}$ and a scale factor $\rho$.
+These truncations arise as generalised Scherk-Schwarz reductions, described by an \EE-valued twist matrix $U_{\fl{M}}{}^{M}$ and a scale factor $\rho$.
 The compactification Ansätze are as follows~\cite{Galli:2022idq}:
@@
 	\begin{aligned}
-		X_{\bar M\bar N}{}^{\bar P}&=-\rho^{-1}\,\Gamma_{\bar M\bar N}{}^{\bar P} + \rho^{-1}\,f^{\bar P}{}_{\bar N\bar Q}f^{\bar Q\bar K}{}_{\bar L}\,\Gamma_{\bar K\bar M}{}^{\bar L}-\frac{1}{60}\,\rho^{-1}\,f^{\bar P\bar K}{}_{\bar N}f_{\bar M\bar L}{}^{\bar Q}\,\Gamma_{\bar K\bar Q}{}^{\bar L}\\
-		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\bar P}{}_{\bar N\bar Q}f^{\bar Q\bar K}{}_{\bar M}\,\Gamma_{\bar R\bar K}{}^{\bar R}+\left(\delta_{\bar M}{}^{\bar K}\delta_{\bar N}{}^{\bar P}-\frac{1}{2}\,f_{\bar M}{}^{\bar L\bar K}f_{\bar N\bar L}{}^{\bar P}\right)\,\xi_{\bar K}.
+		X_{\fl{MN}}{}^{\fl{P}}&=-\rho^{-1}\,\Gamma_{\fl{MN}}{}^{\fl{P}} + \rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}f^{\fl{QK}}{}_{\fl{L}}\,\Gamma_{\fl{KM}}{}^{\fl{L}}-\frac{1}{60}\,\rho^{-1}\,f^{\fl{PK}}{}_{\fl{N}}f_{\fl{ML}}{}^{\fl{Q}}\,\Gamma_{\fl{KQ}}{}^{\fl{L}}\\
+		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}f^{\fl{QK}}{}_{\fl{M}}\,\Gamma_{\fl{RK}}{}^{\fl{R}}+\left(\delta_{\fl{M}}{}^{\fl{K}}\delta_{\fl{N}}{}^{\fl{P}}-\frac{1}{2}\,f_{\fl{M}}{}^{\fl{LK}}f_{\fl{NL}}{}^{\fl{P}}\right)\,\xi_{\fl{K}}.
 	\end{aligned}
 \end{equation}
-Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\bar M\bar N}{}^{\bar P}=U_{\bar M}{}^{K}U_{\bar N}{}^{L}\partial_{K}U^{\bar P}{}_{L}$ and the trombone gauging
+Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=U_{\fl{M}}{}^{K}U_{\fl{N}}{}^{L}\partial_{K}U^{\fl{P}}{}_{L}$ and the trombone gauging
 \begin{equation}
-	\xi_{\bar M} = 2\,U_{\bar M}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\bar M}{}^{N}.
+	\xi_{\fl{M}} = 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\fl{M}}{}^{N}.
 \end{equation}
-In the following, we consider $\xi_{\bar M}=0$. The embedding tensor is most nicely expressed once projected on the adjoint representation
+In the following, we consider $\xi_{\fl{M}}=0$. The embedding tensor is most nicely expressed once projected on the adjoint representation
 \begin{equation}
-	X_{\bar M\bar N} = -\frac{1}{60}\,X_{\bar M\bar P}{}^{\bar Q}\,f_{\bar N\bar Q}{}^{\bar P} = 2\,\rho^{-1}\,\Gamma_{(\bar M\bar N)} - \rho^{-1}\,\Gamma_{\bar K(\bar M}{}^{\bar L}\,f_{\bar N)\bar L}{}^{\bar K},
+	X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} = 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{K}(\fl{M}}{}^{\fl{L}}\,f_{\fl{N})\fl{L}}{}^{\fl{K}},
 \end{equation}
-with the projection of the current $\Gamma_{\bar M\bar N} = (1/60)\,\Gamma_{\bar M\bar P}{}^{\bar Q}\,f_{\bar N\bar Q}{}^{\bar P}$.
+with the projection of the current $\Gamma_{\fl{MN}} = (1/60)\,\Gamma_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}}$.
 
@@
 	\begin{aligned}
-		S_{\rm ExFT} \underset{\rm gSS}{=} \int\d^{248}Y\,\rho^{-1}\int \d^{3}x & \bigg[\sqrt{\vert\mathring{g}\vert}\bigg(\mathring{R}+\frac{1}{240}\,{\cal D}_{\mu}\M_{\bar M\bar N}{\cal D}^{\mu}\M^{\bar M\bar N}-V\bigg) \\
-		&-\varepsilon^{\mu\nu\rho}\,X_{\bar M\bar N}\,\A_{\mu}{}^{\bar M} \left(\partial_{\nu}\A_{\rho}{}^{\bar N}-\frac{1}{3}\,\llbracket\A_{\nu},\A_{\rho}\rrbracket^{\bar N}\right)\bigg],
+		S_{\rm ExFT} \underset{\rm gSS}{=} \int\d^{248}Y\,\rho^{-1}\int \d^{3}x & \bigg[\sqrt{\vert\mathring{g}\vert}\bigg(\mathring{R}+\frac{1}{240}\,{\cal D}_{\mu}\M_{\fl{MN}}{\cal D}^{\mu}\M^{\fl{MN}}-V\bigg) \\
+		&-\varepsilon^{\mu\nu\rho}\,X_{\fl{MN}}\,\A_{\mu}{}^{\fl{M}} \left(\partial_{\nu}\A_{\rho}{}^{\fl{N}}-\frac{1}{3}\,\llbracket\A_{\nu},\A_{\rho}\rrbracket^{\fl{N}}\right)\bigg],
 	\end{aligned}
@@
 \begin{equation}
-	V = X_{\bar M\bar N}\,X_{\bar P\bar Q}\left(\frac{1}{28}\,\M^{\bar M\bar P}\M^{\bar N\bar Q}+\frac{1}{2}\,\M^{\bar M\bar P}\eta^{\bar N\bar Q}+\frac{13}{28}\,\eta^{\bar M\bar P}\eta^{\bar N\bar Q}\right).
+	V = X_{\fl{MN}}\,X_{\fl{PQ}}\left(\frac{1}{28}\,\M^{\fl{MP}}\M^{\fl{NQ}}+\frac{1}{2}\,\M^{\fl{MP}}\eta^{\fl{NQ}}+\frac{13}{28}\,\eta^{\fl{MP}}\eta^{\fl{NQ}}\right).
 \end{equation}

### 2023-05-15 Draft_3dH3.tex
First draft for the full computation of the 3d potential.

@@
 $\mathscr{L}_{\rm int}$ is a potential term depending only on internal derivatives:
-\begin{equation}
+\begin{equation} \label{eq:ExFTLint}
 	\begin{aligned}
@@
 This condition ensures that the factorised form of the Ansätze~\eqref{eq:GSSansatz} is preserved by the generalized Lie derivative, \textit{e.g.}
-\begin{equation}
+\begin{equation} \label{eq:GSSexample}
 	\begin{aligned}
@@
 
-The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity. It has the following expression:
+For a given twist matrix $U_{\fl{M}}{}^{M}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity.
+The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity.
+From eq.~~\eqref{eq:GenLeibniz}, it has the following expression:
 \begin{equation}
@@
 \end{equation}
-In the following, we consider $\xi_{\fl{M}}=0$. The embedding tensor is most nicely expressed once projected on the adjoint representation
-\begin{equation}
+In the following, we consider $\xi_{\fl{M}}=0$. The embedding tensor is then most nicely expressed once projected on the adjoint representation \CE{(Give expression with projector on 3875?)}
+\begin{equation} \label{eq:symembeddingtensor}
 	X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} = 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{K}(\fl{M}}{}^{\fl{L}}\,f_{\fl{N})\fl{L}}{}^{\fl{K}},
@@
 with the projection of the current $\Gamma_{\fl{MN}} = (1/60)\,\Gamma_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}}$.
+
+The three-dimensional action follows from inserting the Ansätze~\eqref{eq:GSSansatz} in the ExFT action~\eqref{eq:ExFTaction}.
+The expressions of the kinetic and Chern-Simons terms result from eq.~\eqref{eq:GSSexample}: \CE{(A work on the Ricci scalar?)}
+\begin{equation}
+	\begin{aligned}
+		\mathscr{L}_{\rm kin} &= \frac{1}{240}\,D_{\mu}\M_{MN}D^{\mu}\M^{MN} \underset{\rm gSS}{=} \frac{\rho^{2}}{240}\,{\cal D}_{\mu}\M_{\fl{MN}}{\cal D}^{\mu}\M^{\fl{MN}}, \\
+		\mathscr{L}_{\rm CS} &\underset{\rm gSS}{=} -\rho^{-1}\,\varepsilon^{\mu\nu\rho}\,X_{\fl{MN}}\,\A_{\mu}{}^{\fl{M}} \left(\partial_{\nu}\A_{\rho}{}^{\fl{N}}-\frac{1}{3}\,\llbracket\A_{\nu},\A_{\rho}\rrbracket^{\fl{N}}\right).
+	\end{aligned}
+\end{equation}
+
+The case of the potential term $\mathscr{L}_{\rm int}$, leading to a potential $V$ for the three-dimensional scalars $\M_{\fl{MN}}$, is more subtle.
+We expect $V$ to be quadratic in the embedding tensor, which makes the identification of $X_{\fl{MN}}$ more complicated.
+We adopt the following strategy.
+First, we insert the generalized Sherk-Schwarz Ansätze~\eqref{eq:GSSansatz} into the expression of $\mathscr{L}_{\rm int}$~\eqref{eq:ExFTLint} with an additional total derivative: \CE{(Fill in with the eq.
+of 08/02, global $-1$ and  $a \rightarrow a/3$.
+Need to motivate the total derivative?
+Need to give some formula?
+As MMf=-fM?
+Ad invariance?
+Mention use of section constraint?
+Factor $\sqrt{\vert g\vert}$ to avoid carrying $\rho$ in $V$?)}
+\begin{equation} \label{eq:Lintexpansion}
+	\begin{aligned}
+		\mathscr{L}_{\rm int} + \frac{a}{\sqrt{\vert g\vert}}\,\partial_{M}\Big(&\sqrt{\vert g\vert}\,\partial_{N}\M^{MN}+\frac{4}{3}\,\M^{MN}\partial_{N}\sqrt{\vert g\vert}\Big)\\
+		&\underset{\rm gSS}{=} -\frac{1}{2}\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma_{\fl{N}}{}^{\fl{K}} + \ldots
+	\end{aligned}
+\end{equation}
+Then, we consider the most general exactly quadratic function in $X_{\fl{MN}}$ and develop it in \EE currents using eq.~\eqref{eq:symembeddingtensor}: \CE{(Sign convention between $V$ and ${\mathscr{L}}_{\rm int}$.)}
+\begin{equation} \label{eq:Vexpansion}
+	\begin{aligned}
+		V &= X_{\fl{MN}}X_{\fl{PQ}}\left(\alpha\,\M^{\fl{MP}}\M^{\fl{NQ}}+\beta\,\M^{\fl{MP}}\eta^{\fl{NQ}}+\delta\,\eta^{\fl{MP}}\eta^{\fl{NQ}}+\gamma\,\eta^{\fl{MN}}\eta^{\fl{PQ}}\right) \\
+		&\underset{\rm gSS}{=} \rho^{-2}\bigg(14\,\alpha\,\Gamma_{\fl{MN}}\Gamma_{\fl{PQ}}\,\M^{\fl{MP}}\M^{\fl{NQ}}+\ldots\bigg).
+	\end{aligned}
+\end{equation}
+\CE{Finally, comparing eq.~\eqref{eq:Lintexpansion} and~\eqref{eq:Vexpansion}, the parameters are fixed to...}
 
@@
 \end{equation}
+\CE{(A word on the 3d linear and quadratic constraints?)}
 

### 2023-05-15 Draft_3dH3.tex
Change of convention for U in sec. 3, completed expressions and added formula in sec. 3. Sent to Emanuel and Michele.

--- 2023-05-15 Draft_3dH3.tex
@@
 The \EE exceptional field theory is well suited to the construction of consistent truncation of type~II and 11d supergravities to three-dimensional maximal supergravity.
-These truncations arise as generalised Scherk-Schwarz reductions, described by an \EE-valued twist matrix $U_{\fl{M}}{}^{M}$ and a scale factor $\rho$.
+These truncations arise as generalised Scherk-Schwarz reductions, described by an \EE-valued twist matrix $U_{M}{}^{\fl{M}}$ and a scale factor $\rho$.
 The compactification Ansätze are as follows~\cite{Galli:2022idq}:
@@
 		g_{\mu\nu}(x,Y)&=\rho(Y)^{-2}\,\mathring{g}_{\mu\nu}(x),\\
-		\M_{MN}(x,Y)&=U^{\fl{M}}{}_{M}(Y)\,U^{\fl{N}}{}_{N}(Y)\,\M_{\fl{MN}}(x),\\
-		A_{\mu}{}^{M}(x,Y)=&\rho(Y)^{-1}\,U_{\fl{M}}{}^{M}(Y)\,\A_{\mu}{}^{\fl{M}}(x),\\
+		\M_{MN}(x,Y)&=U_{M}{}^{\fl{M}}(Y)\,U_{N}{}^{\fl{N}}(Y)\,\M_{\fl{MN}}(x),\\
+		A_{\mu}{}^{M}(x,Y)=&\rho(Y)^{-1}\,\UI_{\fl{M}}{}^{M}(Y)\,\A_{\mu}{}^{\fl{M}}(x),\\
 		B_{\mu\,M}(x,Y)&=\Sigma_{\fl{M}\,M}(Y)\,\A_{\mu}{}^{\fl{M}}(x),
@@
 \begin{equation}
-	\Sigma_{\fl{M}\,M}=\frac{\rho^{-1}}{60}\,f_{\fl{M}}{}^{\fl{PQ}}\,U_{\fl{P}P}\,\partial_{M}U_{\fl{Q}}{}^{P}.
+	\Sigma_{\fl{M}\,M}=\frac{\rho^{-1}}{60}\,f_{\fl{M}}{}^{\fl{PQ}}\,\UI_{\fl{P}P}\,\partial_{M}\UI_{\fl{Q}}{}^{P}.
 \end{equation}
@@
 \end{equation}
-with $\cU_{\fl{M}}{}^M = \rho^{-1} U_{\fl{M}}{}^M$, $\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}})$ and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ a constant tensor.
+with $\cU_{\fl{M}}{}^M = \rho^{-1} \UI_{\fl{M}}{}^M$, $\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}})$ and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ a constant tensor.
 This condition ensures that the factorised form of the Ansätze~\eqref{eq:GSSansatz} is preserved by the generalized Lie derivative, \textit{e.g.}
-\begin{equation}
+\begin{equation} \label{eq:GSSexample}
 	\begin{aligned}
-		D_{\mu}\M(x,Y) &= U^{\fl{M}}{}_{M}(Y)\,U^{\fl{N}}{}_{N}(Y)\,{\cal D}_{\mu}\M_{\fl{MN}}(x),\\
-		{\cal L}_{(A_{\mu},B_{\nu})}A_{\mu}(x,Y) &= \rho(Y)^{-1}\,U_{\fl{M}}{}^{M}(Y)\,\llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}(x),
+		D_{\mu}\M(x,Y) &= U_{M}{}^{\fl{M}}(Y)\,U_{N}{}^{\fl{N}}(Y)\,{\cal D}_{\mu}\M_{\fl{MN}}(x),\\
+		{\cal L}_{(A_{\mu},B_{\nu})}A_{\mu}(x,Y) &= \rho(Y)^{-1}\,\UI_{\fl{M}}{}^{M}(Y)\,\llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}(x),
 	\end{aligned}
@@
 
-The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity. It has the following expression:
+For a given twist matrix $U_{M}{}^{\fl{M}}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity.
+The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity.
+From eq.~~\eqref{eq:GenLeibniz}, it has the following expression:
 \begin{equation}
@@
 \end{equation}
-In the following, we consider $\xi_{\fl{M}}=0$. The embedding tensor is most nicely expressed once projected on the adjoint representation
-\begin{equation}
-	X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} = 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{K}(\fl{M}}{}^{\fl{L}}\,f_{\fl{N})\fl{L}}{}^{\fl{K}},
+In the following, we consider $\xi_{\fl{M}}=0$. The embedding tensor is then most nicely expressed once projected on the adjoint representation \CE{(Keep expression with projector on 3875?)}
+\begin{equation} \label{eq:symembeddingtensor}
+	\begin{aligned}
+		X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} &= 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{P}(\fl{M}}{}^{\fl{Q}}\,f_{\fl{N})\fl{Q}}{}^{\fl{P}}\\
+		&=14\,\rho^{-1}\,(\mathbb{P}_{3875})_{\fl{MN}}{}^{\fl{PQ}}\,\Gamma_{\fl{PQ}}+\frac{1}{4}\,\rho^{-1}\,\eta_{\fl{MN}}\,\Gamma_{\fl{P}}{}^{\fl{P}},
+	\end{aligned}
 \end{equation}
 with the projection of the current $\Gamma_{\fl{MN}} = (1/60)\,\Gamma_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}}$.
+
+The three-dimensional action follows from inserting the Ansätze~\eqref{eq:GSSansatz} in the ExFT action~\eqref{eq:ExFTaction}.
+The expressions of the kinetic and Chern-Simons terms result from eq.~\eqref{eq:GSSexample}: \CE{(A word on the Ricci scalar?)}
+\begin{equation}
+	\begin{aligned}
+		\mathscr{L}_{\rm kin} &= \frac{1}{240}\,D_{\mu}\M_{MN}D^{\mu}\M^{MN} \underset{\rm gSS}{=} \frac{\rho^{2}}{240}\,{\cal D}_{\mu}\M_{\fl{MN}}{\cal D}^{\mu}\M^{\fl{MN}}, \\
+		\mathscr{L}_{\rm CS} &\underset{\rm gSS}{=} -\rho^{-1}\,\varepsilon^{\mu\nu\rho}\,X_{\fl{MN}}\,\A_{\mu}{}^{\fl{M}} \left(\partial_{\nu}\A_{\rho}{}^{\fl{N}}-\frac{1}{3}\,\llbracket\A_{\nu},\A_{\rho}\rrbracket^{\fl{N}}\right).
+	\end{aligned}
+\end{equation}
+
+The case of the potential term $\mathscr{L}_{\rm int}$, leading to a potential $V$ for the three-dimensional scalars $\M_{\fl{MN}}$, is more subtle.
+We expect $V$ to be quadratic in the embedding tensor, which makes the identification of $X_{\fl{MN}}$ more complicated.
+We adopt the following strategy.
+First, we insert the generalized Sherk-Schwarz Ansätze~\eqref{eq:GSSansatz} into the expression of $\mathscr{L}_{\rm int}$~\eqref{eq:ExFTLint} with an additional total derivative: \CE{(Need to motivate the total derivative?
+Mention the need for section constraint?
+Factor $\sqrt{\vert g\vert}$ to avoid carrying $\rho$ in $V$?)}
+\begin{equation} \label{eq:Lintexpansion}
+	\begin{aligned}
+		\mathscr{L}_{\rm int} &+ \frac{a}{\sqrt{\vert g\vert}}\,\partial_{M}\Big(\sqrt{\vert g\vert}\,\partial_{N}\M^{MN}+\frac{4}{3}\,\M^{MN}\partial_{N}\sqrt{\vert g\vert}\Big)\\
+		&\underset{\rm gSS}{=} -\frac{1}{2}\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma_{\fl{N}}{}^{\fl{K}} -\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma^{\fl{K}}{}_{\fl{N}} -\frac{1}{2}\,\Gamma_{\fl{MN}}\Gamma^{\fl{NM}} - \frac{1}{2}\,\M^{\fl{MN}}\M^{\fl{KL}}\,\Gamma_{\fl{MK}}\Gamma_{\fl{NL}} \\
+		&\ \quad - \frac{1}{2}\,\M^{\fl{MN}}\M^{\fl{KL}}\,\Gamma_{\fl{MK}}\Gamma_{\fl{LN}} +\frac{3}{2}\left(a-1\right)\,\M^{\fl{MN}}\Gamma_{\fl{MN}}{}^{\fl{K}}\Gamma_{\fl{LK}}{}^{\fl{L}}-\frac{a}{2}\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{K}}\Gamma_{\fl{LN}}{}^{\fl{L}}\\
+		&\ \quad + \left(\frac{1}{2}-a\right)\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{L}}\Gamma_{\fl{LN}}{}^{\fl{K}}+\,\M^{\fl{MN}}\Gamma_{\fl{MK}}{}^{\fl{L}}\Gamma_{\fl{LN}}{}^{\fl{K}}-\frac{1}{2}\,\M^{\fl{MN}}\M^{\fl{KL}}f_{\fl{QL}}{}^{\fl{P}}\Gamma_{\fl{PN}}{}^{\fl{Q}}\Gamma_{\fl{MK}}.
+	\end{aligned}
+\end{equation}
+Then, we consider the most general exactly quadratic function in $X_{\fl{MN}}$ and develop it in \EE currents using eq.~\eqref{eq:symembeddingtensor}: \CE{(Sign convention between $V$ and ${\mathscr{L}}_{\rm int}$?
+$+{\mathscr{L}}_{\rm int}$ in eq.~\eqref{eq:ExFTaction} but $-V$ in eq.~\eqref{eq:ExFTactiongSS}.)}
+\begin{equation} \label{eq:Vexpansion}
+	\begin{aligned}
+		-V &= X_{\fl{MN}}X_{\fl{PQ}}\left(\alpha\,\M^{\fl{MP}}\M^{\fl{NQ}}+\beta\,\M^{\fl{MP}}\eta^{\fl{NQ}}+\delta\,\eta^{\fl{MP}}\eta^{\fl{NQ}}+\gamma\,\eta^{\fl{MN}}\eta^{\fl{PQ}}\right) \\
+		&\underset{\rm gSS}{=} \rho^{-2}\bigg(14\,\alpha\,\Gamma_{\fl{MN}}\Gamma_{\fl{PQ}}\,\M^{\fl{MP}}\M^{\fl{NQ}}+14\,\alpha\,\Gamma_{\fl{MN}}\Gamma_{\fl{PQ}}\,\M^{\fl{MQ}}\M^{\fl{NP}}\\
+		&\ \quad +2\,\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma^{\fl{K}}{}_{\fl{N}}+\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma_{\fl{N}}{}^{\fl{K}}+\left(-12\,\alpha+2\,\delta-(62)^2\,\gamma\right)\,\Gamma_{\fl{MN}}\Gamma^{\fl{MN}}\\
+		&\ \quad -2\,\beta\,\M^{\fl{MN}}\Gamma_{\fl{MK}}{}^{\fl{L}}\Gamma_{\fl{LN}}{}^{\fl{K}}+\beta\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{L}}\Gamma_{\fl{LN}}{}^{\fl{K}}+\left(7\,\alpha+\frac{\beta}{2}\right)\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{K}}\Gamma_{\fl{LN}}{}^{\fl{L}}\\
+		&\ \quad +14\,\alpha\,\M^{\fl{MN}}\M^{\fl{KL}}f_{\fl{QL}}{}^{\fl{P}}\Gamma_{\fl{PN}}{}^{\fl{Q}}\Gamma_{\fl{MK}}\bigg).
+	\end{aligned}
+\end{equation}
+Finally, comparing eq.~\eqref{eq:Lintexpansion} and~\eqref{eq:Vexpansion}, the parameters are fixed to
+\begin{equation}
+	\alpha = \frac{\rho^{2}}{28},\quad \beta = \frac{\rho^{2}}{2},\quad a=1,\quad \delta=\frac{13}{28}\,\rho^{2}, \quad \gamma=0.
+\end{equation}
+\CE{Freedom for $\delta$ and $\gamma$: $2\delta-(62)^2\gamma=\rho^{2}(1/2+3/7)$.}
+
+\CE{Some formula used to derive the previous equations:
+\begin{equation}
+	\begin{aligned}
+		\M^{\fl{MP}}\M^{\fl{NQ}}f_{\fl{PQ}}{}^{\fl{K}}&=-f^{\fl{MN}}{}_{\fl{L}}\,\M^{\fl{LK}},\\
+		{\rm Ad\ invariance:}\quad 2\,\Gamma_{\fl{K}[\fl{M}}{}^{\fl{L}}\,f_{\fl{N}]\fl{L}}{}^{\fl{P}}&= -f_{\fl{MN}}{}^{\fl{L}}\,\Gamma_{\fl{KL}}{}^{\fl{P}},\\
+		{\rm No\ trombone:}\quad \UI_{\fl{M}}{}^{M}\partial_{M}\ln(\rho)&= -\frac{1}{2}\,\Gamma_{\fl{KM}}{}^{\fl{K}},\\
+		{\rm Eq.~\eqref{eq:sectionconstraints}}\ \implies \ f^{\fl{K}}{}_{\fl{MP}}f^{\fl{PL}}{}_{\fl{N}}\,\partial_{\fl{K}}\otimes\partial_{\fl{L}} &= 2\,\partial_{(\fl{M}}\otimes\partial_{\fl{N})}.
+	\end{aligned}
+\end{equation}
+}
 
@@
 With the generalized Scherk-Schwarz Ansätze~\eqref{eq:GSSansatz}, the action~\eqref{eq:ExFTaction} becomes
-\begin{equation}
+\begin{equation} \label{eq:ExFTactiongSS}
 	\begin{aligned}

### 2023-05-30 Draft_3dH3.tex
Small changes before pulling Emanuel's updates.

@@
 \end{equation}
-The fields with flat indices $\fl{M}$ (in the $\mathbf{248}$ representation of \EE) describe the three-dimensional theory; all the dependence on the internal manifold is factored out in $U_{\fl{M}}{}^{M}$ and $\rho$.
+The fields with flat indices $\fl{M}$ (in the $\mathbf{248}$ representation of \EE) describe the three-dimensional theory; all the dependence on the internal manifold is factored out in $U_{M}{}^{\fl{M}}$ and $\rho$.
 Note that with the definition of $\Sigma_{\fl{M}\,M}$ the condition~\eqref{eq:sectionconstraint2} is automatically satisfied.
@@
 \begin{equation}
-	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}}-2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M})}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}} \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}}.
+	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}}-2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M}}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}} \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}}.
 \end{equation}
 
-For a given twist matrix $U_{M}{}^{\fl{M}}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity.
+For a given twist matrix $U_{M}{}^{\fl{M}}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity~\cite{Nicolai:2000sc,Nicolai:2001sv}.
 The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity.
@@
 		X_{\fl{MN}}{}^{\fl{P}}&=-\rho^{-1}\,\Gamma_{\fl{MN}}{}^{\fl{P}} + \rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}f^{\fl{QK}}{}_{\fl{L}}\,\Gamma_{\fl{KM}}{}^{\fl{L}}-\frac{1}{60}\,\rho^{-1}\,f^{\fl{PK}}{}_{\fl{N}}f_{\fl{ML}}{}^{\fl{Q}}\,\Gamma_{\fl{KQ}}{}^{\fl{L}}\\
-		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}f^{\fl{QK}}{}_{\fl{M}}\,\Gamma_{\fl{RK}}{}^{\fl{R}}+\left(\delta_{\fl{M}}{}^{\fl{K}}\delta_{\fl{N}}{}^{\fl{P}}-\frac{1}{2}\,f_{\fl{M}}{}^{\fl{LK}}f_{\fl{NL}}{}^{\fl{P}}\right)\,\xi_{\fl{K}}.
+		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}f^{\fl{QK}}{}_{\fl{M}}\,\Gamma_{\fl{LK}}{}^{\fl{L}}+\left(\delta_{\fl{M}}{}^{\fl{K}}\delta_{\fl{N}}{}^{\fl{P}}-\frac{1}{2}\,f_{\fl{M}}{}^{\fl{LK}}f_{\fl{NL}}{}^{\fl{P}}\right)\,\xi_{\fl{K}}.
 	\end{aligned}
 \end{equation}
-Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=U_{\fl{M}}{}^{K}U_{\fl{N}}{}^{L}\partial_{K}U^{\fl{P}}{}_{L}$ and the trombone gauging
+Here, we defined the \EE current $\Gamma_{\fl{MN}}{}^{\fl{P}}=\UI_{\fl{M}}{}^{K}\UI_{\fl{N}}{}^{L}\partial_{K}U_{L}{}^{\fl{P}}$ and the trombone gauging
 \begin{equation}
-	\xi_{\fl{M}} = 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\fl{M}}{}^{N}.
+	\xi_{\fl{M}} = 2\,\UI_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}\UI_{\fl{M}}{}^{N}.
 \end{equation}
@@
 		&\underset{\rm gSS}{=} \rho^{-2}\bigg(14\,\alpha\,\Gamma_{\fl{MN}}\Gamma_{\fl{PQ}}\,\M^{\fl{MP}}\M^{\fl{NQ}}+14\,\alpha\,\Gamma_{\fl{MN}}\Gamma_{\fl{PQ}}\,\M^{\fl{MQ}}\M^{\fl{NP}}\\
-		&\ \quad +2\,\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma^{\fl{K}}{}_{\fl{N}}+\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma_{\fl{N}}{}^{\fl{K}}+\left(-12\,\alpha+2\,\delta-(62)^2\,\gamma\right)\,\Gamma_{\fl{MN}}\Gamma^{\fl{MN}}\\
+		&\ \quad +2\,\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma^{\fl{K}}{}_{\fl{N}}+\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma_{\fl{N}}{}^{\fl{K}}+\left(-12\,\alpha+2\,\delta-(62)^2\,\gamma\right)\,\Gamma_{\fl{MN}}\Gamma^{\fl{NM}}\\
 		&\ \quad -2\,\beta\,\M^{\fl{MN}}\Gamma_{\fl{MK}}{}^{\fl{L}}\Gamma_{\fl{LN}}{}^{\fl{K}}+\beta\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{L}}\Gamma_{\fl{LN}}{}^{\fl{K}}+\left(7\,\alpha+\frac{\beta}{2}\right)\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{K}}\Gamma_{\fl{LN}}{}^{\fl{L}}\\
@@
 \end{equation}
-and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ is already constant. Therefore, we have a consistent truncation if and only iff $\rho^{-1}\, F_{\fl{M}\fl{N}}{}^{\fl{P}}$ is constant.
+and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ is already constant. Therefore, we have a consistent truncation if and only if $\rho^{-1}\, F_{\fl{M}\fl{N}}{}^{\fl{P}}$ is constant.
 
@@
 \subsection{Adding fluxes to the $S^3$ truncation of 6-dimensional supergravity} \label{s:S3Flux}
-Before dealing with the $S^3 \times S^3 \times S^1$ truncation, let us demonstrate this methodology for the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity on $S^3$, which was constructed in \cite{Eloy:2021fhc}.
+Before dealing with the $S^3 \times S^3 \times S^1$ truncation, let us demonstrate this methodology for the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity on $S^3$, which was constructed in~\cite{Eloy:2021fhc}.
 As discussed in \cite{Eloy:2021fhc}, the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity to 3-dimensional half-maximal gauged supergravity can be described using the $\SO{8,4}$ ExFT \cite{Hohm:2017wtr,Samtleben:2019zrh}.
@@
 Decomposing with respect to the geometric $\SL{3} \times \mathbb{R}^+$ of the $S^3$,  the coordinates on $S^3$ live in the $Y^A = \left( y^i,\, y_i \right)$, $i = 1, 2, 3$, while $C_A = \left( C_i,\, C^i \right)$ naturally contains a 2-form $C^i$.
-The field strength $H_3 = \partial^A C_A = \partial_i C^i$ is a singlet of $\SO{3,3}$ and thus we see that $F_{AB}{}^C$ in \eqref{eq:FlatF} is constant and we obtain a consistent truncation with a new 3-form flux.
+The field strength $H_3 = \partial^A C_A = \partial_i C^i$ is a singlet of $\SO{3,3}$ and thus we see that $F_{AB}{}^C$ in \eqref{eq:FlatF} is constant \CE{(what about the $\rho$ factor?)} and we obtain a consistent truncation with a new 3-form flux.
 Evaluating the twist matrix
@@
 \EM{Should mention the geometric $\SL{3}$ subgroups here???}
+
+\CE{(Add $\alpha$ here?)}
 

### 2023-05-30 Notes_3dH3.tex
Small changes before pulling Emanuel's updates.

@@
 
+\section{Mass matrices}
+\subsection{Vector fields}
+\begin{equation}
+  M_{(1)}{}^{\bar M}{}_{\bar N} = X^{\bar M\bar P}\left(\eta_{\bar P\bar N} + \M_{\bar P\bar N}\right).
+\end{equation}
+
+\subsection{Scalar fields}
+We define the scalars using coset representative ${\cal V}_{\bar M}{}^{\bar N}\in\E_{8(8)}/\SO(16)$:
+\begin{equation}
+  {\cal V} = \exp\left(\Phi^{\bar A}\,T_{\bar A}\right),
+\end{equation}
+with $\left(T_{\bar A}\right)_{\bar M}{}^{\bar K}$ the non-compact generators of $\E_{8(8)}$. Let $\Delta_{\bar M\bar N}$ be a matrix such that these generators satisfy
+\begin{equation}
+  \left(T_{\bar A}\right)_{[\bar M}{}^{\bar K}\Delta_{\bar N]\bar K} = 0.
+\end{equation}
+We then construct the scalar matrix from coset representatives:
+\begin{equation}
+  \M_{\bar M\bar N} = {\cal V}_{\bar M}{}^{\bar P}{\cal V}_{\bar N}{}^{\bar Q}\,\Delta_{\bar P\bar Q}.
+\end{equation}
+
+Then, the scalar fields mass matrix (at the scalar origin) is
+\begin{equation}
+  M_{(0)\,\bar A\bar B}^{2} = {\cal P}_{\bar A}{}^{\bar M\bar N}{\cal P}_{\bar B}{}^{\bar P\bar Q}\left(\frac{1}{7}\,X_{\bar M\bar P}X_{\bar N\bar Q}+X_{\bar M\bar K}\left(\frac{1}{7}\,\Delta^{\bar K\bar L}+\eta^{\bar K\bar L}\,X_{\bar L\bar P}\,\Delta_{\bar N\bar Q}\right)\right).
+\end{equation}
+The mass matrix for a vacuum away from the scalar origin is given by the same formula, where all occurences of embedding tensor should be modified to the ``dressed'' embedding tensor.
+
 \appendix

### 2023-05-30 Draft_3dH3.tex
Pulling Emanuel's updates.

--- 2023-05-15 Draft_3dH3.tex
@@
 \newcommand{\cC}{\mathcal{C}}
+\newcommand{\dg}{\vert g \vert}
 
@@
 We explicitly construct the uplift of a subset of these to construct new supersymmetric and non-supersymmetric AdS$_3$ vacua of IIB string theory, and show how the moduli space of AdS$_3$ vacua of six-dimensional gauged supergravity studied in \cite{Eloy:2021fhc} is compactified upon lifting to 10 dimensions.
-Along the way, we also derive the form of 3-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor.
+Along the way, we also derive the form of 3-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor and rule out a 10-/11-dimensional origin of some 3-dimensional gauged supergravities.
 	\end{abstract}
@@
 	\item Think about title - mention new AdS$_3$ vacua? Lifting AdS$_3$ vacua?
+	\item Check the $\SL{n}$ equations
 	\item Move 3-d gauged SUGRA to somewhere else??
-	\item Discuss IIA (and IIB -- Jerome's story) T-duals
+	\item Construct 10-parameter uplift
+	\item Complex geometry of moduli space?
+	\item Compare with classification known in literature, e.g. in IIA (and IIB -- Jerome's story)
 \end{itemize}
@@
 \section{Introduction}
+Consistent truncations are a powerful technique that simplifies the dynamics of 10-/11-dimensional supergravity by focusing on a restricted subset of fields.
+The key principle behind a consistent truncation is to truncate to a subsector of fields, such that all solutions of the truncated theory correspond to solutions of the original 10-/11-dimensional supergravity theory.
+By considering only a, typically finite, subset of fields, consistent truncations provide a powerful tool to find complicated new 10-/11-dimensional supergravity solutions and to study their deformations.
+Consistent truncations have proven particularly powerful in the AdS/CFT correspondence, since all well-understood AdS vacua of string theory do not admit scale-separation and, thus, cannot be studied using the usual tools of lower-dimensional effective theories.
 
-% \section{\texorpdfstring{\EE}{E8(8)} ExFT and consistent truncations}
+Exceptional Field Theory (ExFT) is a reformulation of 10-/11-dimensional supergravity that unifies the metric and flux degrees of freedom and thereby makes manifest an exceptional symmetry group\footnote{For the purposes of this paper, we do not draw a distinction between ExFT and Exceptional Generalised Geometry, since these agree when the ``section condition'' is solved, which we will always assume here.}.
+Over the last decade, this has proven an extremely useful tool for constructing consistent truncations, leading to a number of new examples preserving various amounts of supersymmetry \cite{Hohm:2014qga,Lee:2014mla,Malek:2015hma,Baguet:2015sma,Baguet:2015iou,Lee:2015xga,Malek:2016bpu,Ciceri:2016dmd,Cassani:2016ncu,Inverso:2016eet,Malek:2017cle,Malek:2017njj,Malek:2018zcz,Malek:2019ucd,Cassani:2019vcl,Malek:2020jsa,Cassani:2020cod}.
+However, consistent truncations to three dimensions have, until recently \cite{Galli:2022idq}, remained largely unexplored.
+One reason is that the $\EE$ ExFT requires modifications for its local symmetry structure, i.e.
+the generalised Lie derivative, to close into an algebra \cite{Hohm:2014fxa,Cederwall:2015ica}.
+Another is that there are no maximally supersymmetric AdS$_3$ vacua, i.e.
+preserving 32 supercharges, of string theory, leaving no natural candidate for constructing a consistent truncation with vacua.
+Indeed, while the consistent truncations of 11-dimensional supergravity on $S^7$ and $S^4$ and of 10-dimensional supergravity on $S^5$ contain maximally supersymmetric AdS vacua and are captured by a universal Ansatz in ExFT \cite{Hohm:2014qga,Lee:2014mla}, the analogous $S^8$ truncation of 11-dimensional supergravity does not exist, while there are two $S^7$ truncations of 10-dimensional supergravity but neither contains a maximally symmetric vacuum\cite{Fischbacher:2003yw,Galli:2022idq}.
+
+Nonetheless, there are half-maximal, i.e.
+${\cal N}=(4,4)$, supersymmetric AdS$_3$ vacua of string theory that are extremely intriguing.
+These are the AdS$_3 \times S^3 \times S^3 \times S^1$ and AdS$_3 \times S^3 \times T^4$ of IIB string theory (realising the ``small'' and ``large'' ${\cal N}=(4,4)$ superconformal symmetries), and, unlike in higher dimensions, can be supported by pure NS-NS flux.
+Not only does this mean that there are also heterotic versions of these vacua (preserving ${\cal N}=(4,0)$ supersymmetry), but also that they can be readily studied via the string worldsheet CFT \cite{Maldacena:2000hw,Eberhardt:2018ouy,Eberhardt:2019niq,Eberhardt:2019ywk}.
+Moreover, the string sigma model in these vacua is also integrable \cite{}.
+Finally, the AdS$_3$/CFT$_2$ correspondence has seen much progress recently, with many new holographic duals being established \cite{}.
+
+Here we will focus on the ${\cal N}=(4,4)$ AdS$_3 \times S^3 \times S^3 \times S^1$ vacuum of IIB string theory and show that it admits a consistent truncation to a maximal gauged supergravity, which was first studied in \cite{Hohm:2005ui}.
+All vacua of this theory break at least half the supersymmetries, reflecting the absence of a maximally supersymmetric AdS$_3$ vacuum in string theory.
+Key to constructing this consistent truncation is to add new fluxes to the $S^1$ reduction of the consistent truncation of IIB supergravity on $S^3 \times S^3$ \cite{Inverso:2016eet}.
+
+Using our consistent truncation, we will show that the AdS$_3 \times S^3 \times S^3 \times S^1$ has a rich moduli space of symmetry- and supersymmetry-breaking deformations, including some that are analogous to the ``flat deformations'' studied for AdS$_4 \times S^5 \times S^1$ \cite{Guarino:2020gfe,Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}.
+While some of these deformations preserve some amounts of supersymmetry, others break all supersymmetries, yet, surprisingly, at least a subset of vacua continue to be perturbatively stable within IIB supergravity, similar to \cite{Giambrone:2021wsm}.
+Our work also provides an uplift of 6-dimensional supergravity on $S^3$ studied in \cite{Eloy:2021fhc} to IIB string theory.
+As we will show, some deformations that appear non-compact in 6-dimensional supergravity \cite{Eloy:2021fhc} are compactified within the full 10-dimensional supergravity theory.
+
+Another technical result of our work is the derivation of the potential of 3-dimensional gauged supergravity in terms of the embedding tensor, which was previously only expressed in terms of fermion shift matrices.
+As a by-product, we find that a constraint that must be obeyed by the embedding tensor of any 3-dimensional gauged supergravity that can be uplifted to 10-/11-dimensional supergravity.
+As we show, this allows us to prove a higher-dimensional origin of some 3-dimensional gaugings.
+
+The outline of our paper is as follows.
+We begin with a review of $\EE$ ExFT in section \ref{s:Review} and how to derive consistent truncations in this formalism in \ref{s:TruncationReview}.
+In section \ref{s:Potential} we derive the potential of 3-dimensional gauged supergravity in terms of the embedding tensor and prove the lack of higher-dimensional origin of some 3-dimensional theories.
+Then, we show how to add fluxes to consistent truncations in \ref{s:AddFlux}, allowing us to construct the consistent truncation of IIB supergravity on $S^3 \times S^3 \times S^1$.
+Using this truncation, we study the moduli space of the AdS$_3$ vacua in section \ref{s:Moduli}, before concluding in section \ref{s:Conclusions}.
 
@@
 	\begin{cases}
-		\eta^{MN}\partial_{M}\otimes\partial_{N} = 0,\\
-		f^{MN}{}_{P}\,\partial_{M}\otimes\partial_{N} = 0,\\
-		(\mathbb{P}_{3875})_{MN}{}^{KL}\partial_{K}\otimes\partial_{L} = 0,
+		\eta^{MN}\partial_{M}\otimes\partial_{N} = 0\,,\\
+		f^{MN}{}_{P}\,\partial_{M}\otimes\partial_{N} = 0\,,\\
+		(\mathbb{P}_{3875})_{MN}{}^{KL}\partial_{K}\otimes\partial_{L} = 0\,,
 	\end{cases}
 \end{equation}
-where $f_{MN}{}^{P}$ are the structure constants of \EE, $\eta_{MN} = (1/60)\,f_{MK}{}^{L}f_{NL}{}^{K}$ its Cartan-Killing metric and $(\mathbb{P}_{3875})_{MN}{}^{KL}$ is the projector on the representation $\mathbf{3875}$:
+where $f_{MN}{}^{P}$ are the structure constants of \EE, $\eta_{MN} = \tfrac{1}{60}\,f_{MK}{}^{L}f_{NL}{}^{K}$ its Cartan-Killing metric and $(\mathbb{P}_{3875})_{MN}{}^{KL}$ is the projector on the representation $\mathbf{3875}$:
 \begin{equation}
-	(\mathbb{P}_{3875})_{MN}{}^{KL} = \frac{1}{7}\, \delta_{(M}{}^{K}\delta_{N)}{}^{L}-\frac{1}{56}\,\eta_{MN}\eta^{KL}-\frac{1}{14}\,f^{P}{}_{M}{}^{(K}f_{PN}{}^{L)}.
+	(\mathbb{P}_{3875})_{MN}{}^{KL} = \frac{1}{7}\, \delta_{(M}{}^{K}\delta_{N)}{}^{L}-\frac{1}{56}\,\eta_{MN}\eta^{KL}-\frac{1}{14}\,f^{P}{}_{M}{}^{(K}f_{PN}{}^{L)}\,.
 \end{equation}
@@
 \begin{equation}
-	\left\{g_{\mu\nu}, \M_{MN}, A_{\mu}{}^{M}, B_{\mu\,M}\right\},
+	\left\{g_{\mu\nu}, \M_{MN}, A_{\mu}{}^{M}, B_{\mu\,M}\right\}\,,
 \end{equation}
@@
 \begin{equation} \label{eq:genlie}
-	{\cal L}_{\Upsilon} V^{M} = \Lambda^{N}\partial_{N}V^{M}-60\,(\mathbb{P}_{248})^{M}{}_{N}{}^{K}{}_{L}\,V^{N}\partial_{K}\Lambda^{L} + \lambda\, V^{M}\partial_{N}\Lambda^{N}+f^{MN}{}_{K}\Sigma_{N}V^{K},
+	{\cal L}_{\Upsilon} V^{M} = \Lambda^{N}\partial_{N}V^{M}-60\,(\mathbb{P}_{248})^{M}{}_{N}{}^{K}{}_{L}\,V^{N}\partial_{K}\Lambda^{L} + \lambda\, V^{M}\partial_{N}\Lambda^{N}+f^{MN}{}_{K}\Sigma_{N}V^{K}\,,
 \end{equation}
@@
 	\begin{cases}
-		\eta^{MN}C_{M}\otimes C'_{N} = 0,\\
-		f^{MN}{}_{P}\,C_{M}\otimes C'_{N} = 0,\\
-		(\mathbb{P}_{3875})_{MN}{}^{KL}C_{K}\otimes C'_{L} = 0,
+		\eta^{MN}C_{M}\otimes C'_{N} = 0\,,\\
+		f^{MN}{}_{P}\,C_{M}\otimes C'_{N} = 0\,,\\
+		(\mathbb{P}_{3875})_{MN}{}^{KL}C_{K}\otimes C'_{L} = 0\,,
 	\end{cases}
-	\forall\  C_{M}, C'_{M} \in \{\partial_{M}, \Sigma_{M}, B_{\mu\,M}\}.
+	\forall\  C_{M}, C'_{M} \in \{\partial_{M}, \Sigma_{M}, B_{\mu\,M}\}\,.
 \end{equation}
@@
 \begin{equation} \label{eq:ExFTaction}
-	S_{\rm ExFT} = \int d^{3}x\,d^{248}Y\,\sqrt{\vert g\vert} \bigg(\widehat{R}+\frac{1}{240}\,D_{\mu}\M_{MN}D^{\mu}\M^{MN}+\mathscr{L}_{\rm int}+\frac{1}{\sqrt{\vert g\vert}}\,\mathscr{L}_{\rm CS}\bigg).
+	S_{\rm ExFT} = \int d^{3}x\,d^{248}Y\,\sqrt{\vert g\vert} \bigg(\widehat{R}+\frac{1}{240}\,D_{\mu}\M_{MN}D^{\mu}\M^{MN}+\mathscr{L}_{\rm int}+\frac{1}{\sqrt{\vert g\vert}}\,\mathscr{L}_{\rm CS}\bigg)\,.
 \end{equation}
@@
 \begin{equation}
-	D_{\mu} = \partial_{\mu} - {\cal L}_{(A_{\mu}, B_{\mu})}.
+	D_{\mu} = \partial_{\mu} - {\cal L}_{(A_{\mu}, B_{\mu})}\,.
 \end{equation}
-$\mathscr{L}_{\rm int}$ is a potential term depending only on internal derivatives:
+$\mathscr{L}_{\rm int}$ is a potential term depending only on internal derivatives, explicitly
 \begin{equation} \label{eq:ExFTLint}
@@
 		&\quad -\frac{1}{7200}\,f^{NQ}{}_{P}f^{MS}{}_{R}\,\M^{PK}\partial_{M}\M_{QK}\,\M^{RL}\partial_{N}\M_{SL}\\
-		&\quad +\frac{1}{2}\,g^{-1}\partial_{M}g\,\partial_{N}\M^{MN} + \frac{1}{4}\,\M^{MN}\,g^{-2}\partial_{M}g\,\partial_{N}g + \frac{1}{4}\,\M^{MN}\,\partial_{M}g_{\mu\nu}\,\partial_{N}g^{\mu\nu}.
+		&\quad +\frac{1}{2}\,g^{-1}\partial_{M}g\,\partial_{N}\M^{MN} + \frac{1}{4}\,\M^{MN}\,g^{-2}\partial_{M}g\,\partial_{N}g + \frac{1}{4}\,\M^{MN}\,\partial_{M}g_{\mu\nu}\,\partial_{N}g^{\mu\nu}\,.
 	\end{aligned}
 \end{equation}
-Finally, $\mathscr{L}_{\rm CS}$ is a Chern-Simons term required to impose the on-shell duality between scalar and vector fields:
+Finally, $\mathscr{L}_{\rm CS}$ is a Chern-Simons term required to impose the on-shell duality between scalar and vector fields, given by
 \begin{equation}
@@
 
-\section{Consistent truncations to 3-dimensional \texorpdfstring{${\cal N}=16$}{N=16} gauged supergravity}
+\section{Consistent truncations to 3-dimensional \texorpdfstring{${\cal N}=16$}{N=16} gauged supergravity} \label{s:TruncationReview}
 The \EE exceptional field theory is well suited to the construction of consistent truncation of type~II and 11d supergravities to three-dimensional maximal supergravity.
-These truncations arise as generalised Scherk-Schwarz reductions, described by an \EE-valued twist matrix $U_{\fl{M}}{}^{M}$ and a scale factor $\rho$.
-The compactification Ansätze are as follows~\cite{Galli:2022idq}:
+These truncations arise as generalised Scherk-Schwarz reductions, described by an \EE-valued twist matrix $U_{M}{}^{\fl{M}}$ and a scale factor $\rho$.
+The truncation Ansätze are as follows~\cite{Galli:2022idq}:
 \begin{equation} \label{eq:GSSansatz}
 	\begin{aligned}
-		g_{\mu\nu}(x,Y)&=\rho(Y)^{-2}\,\mathring{g}_{\mu\nu}(x),\\
-		\M_{MN}(x,Y)&=U^{\fl{M}}{}_{M}(Y)\,U^{\fl{N}}{}_{N}(Y)\,\M_{\fl{MN}}(x),\\
-		A_{\mu}{}^{M}(x,Y)=&\rho(Y)^{-1}\,U_{\fl{M}}{}^{M}(Y)\,\A_{\mu}{}^{\fl{M}}(x),\\
-		B_{\mu\,M}(x,Y)&=\Sigma_{\fl{M}\,M}(Y)\,\A_{\mu}{}^{\fl{M}}(x),
+		g_{\mu\nu}(x,Y)&=\rho(Y)^{-2}\,\mathring{g}_{\mu\nu}(x)\,,\\
+		\M_{MN}(x,Y)&=U_{M}{}^{\fl{M}}(Y)\,U_{N}{}^{\fl{N}}(Y)\,\M_{\fl{MN}}(x)\,,\\
+		A_{\mu}{}^{M}(x,Y)=&\rho(Y)^{-1}\,\UI_{\fl{M}}{}^{M}(Y)\,\A_{\mu}{}^{\fl{M}}(x)\,,\\
+		B_{\mu\,M}(x,Y)&=\Sigma_{\fl{M}\,M}(Y)\,\A_{\mu}{}^{\fl{M}}(x)\,,
 	\end{aligned}
@@
 \begin{equation}
-	\Sigma_{\fl{M}\,M}=\frac{\rho^{-1}}{60}\,f_{\fl{M}}{}^{\fl{PQ}}\,U_{\fl{P}P}\,\partial_{M}U_{\fl{Q}}{}^{P}.
+	\Sigma_{\fl{M}\,M}=\frac{\rho^{-1}}{60}\,f_{\fl{M}}{}^{\fl{PQ}}\,\UI_{\fl{P}P}\,\partial_{M}\UI_{\fl{Q}}{}^{P}\,.
 \end{equation}
-The fields with flat indices $\fl{M}$ (in the $\mathbf{248}$ representation of \EE) describe the three-dimensional theory; all the dependence on the internal manifold is factored out in $U_{\fl{M}}{}^{M}$ and $\rho$.
+The fields with flat indices $\fl{M}$ (in the $\mathbf{248}$ representation of \EE) belong to the three-dimensional theory; all the dependence on the internal manifold is factored out in $U_{\fl{M}}{}^{M}$ and $\rho$.
 Note that with the definition of $\Sigma_{\fl{M}\,M}$ the condition~\eqref{eq:sectionconstraint2} is automatically satisfied.
 
-The Ansätze~\eqref{eq:GSSansatz} describe a consistent truncation if the following condition is satisfied:
+The Ansätze~\eqref{eq:GSSansatz} describe a \textit{consistent} truncation if the following condition is satisfied:
 \begin{equation} \label{eq:GenLeibniz}
-	\gL_{\ff{U}_{\fl{M}}} {\cU}_{\fl{N}}{}^M = X_{\fl{M}\fl{N}}{}^{\fl{P}}\, \cU_{\fl{P}}{}^M,
+	\gL_{\ff{U}_{\fl{M}}} {\cU}_{\fl{N}}{}^M = X_{\fl{M}\fl{N}}{}^{\fl{P}}\, \cU_{\fl{P}}{}^M\,,
 \end{equation}
-with $\cU_{\fl{M}}{}^M = \rho^{-1} U_{\fl{M}}{}^M$, $\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}})$ and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ a constant tensor.
+with $\cU_{\fl{M}}{}^M = \rho^{-1} \UI_{\fl{M}}{}^M$, $\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}})$ and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ a constant tensor.
 This condition ensures that the factorised form of the Ansätze~\eqref{eq:GSSansatz} is preserved by the generalized Lie derivative, \textit{e.g.}
@@
 	\begin{aligned}
-		D_{\mu}\M(x,Y) &= U^{\fl{M}}{}_{M}(Y)\,U^{\fl{N}}{}_{N}(Y)\,{\cal D}_{\mu}\M_{\fl{MN}}(x),\\
-		{\cal L}_{(A_{\mu},B_{\nu})}A_{\mu}(x,Y) &= \rho(Y)^{-1}\,U_{\fl{M}}{}^{M}(Y)\,\llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}(x),
+		D_{\mu}\M(x,Y) &= U_{M}{}^{\fl{M}}(Y)\,U_{N}{}^{\fl{N}}(Y)\,{\cal D}_{\mu}\M_{\fl{MN}}(x)\,,\\
+		{\cal L}_{(A_{\mu},B_{\nu})}A_{\mu}(x,Y) &= \rho(Y)^{-1}\,\UI_{\fl{M}}{}^{M}(Y)\,\llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}(x)\,,
 	\end{aligned}
@@
 where
-\begin{equation}
-	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}}-2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M})}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}} \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}}.
+\begin{equation} \label{eq:3dCovDeriv}
+	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}}-2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M})}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}}\,, \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}} \,.
 \end{equation}
 
-For a given twist matrix $U_{\fl{M}}{}^{M}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity.
-The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity.
-From eq.~~\eqref{eq:GenLeibniz}, it has the following expression:
+Thus, for a given twist matrix $U_{M}{}^{\fl{M}}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity.
+The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity, as is clear from its appearance in \eqref{eq:3dCovDeriv} in the gauge-covariant derivative and the gauge algebra of the vector fields.
+From eq.
+\eqref{eq:GenLeibniz}, it has the following expression in terms of the twist matrix and $\rho$
 \begin{equation}
 	\begin{aligned}
-		X_{\fl{MN}}{}^{\fl{P}}&=-\rho^{-1}\,\Gamma_{\fl{MN}}{}^{\fl{P}} + \rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}f^{\fl{QK}}{}_{\fl{L}}\,\Gamma_{\fl{KM}}{}^{\fl{L}}-\frac{1}{60}\,\rho^{-1}\,f^{\fl{PK}}{}_{\fl{N}}f_{\fl{ML}}{}^{\fl{Q}}\,\Gamma_{\fl{KQ}}{}^{\fl{L}}\\
-		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}f^{\fl{QK}}{}_{\fl{M}}\,\Gamma_{\fl{RK}}{}^{\fl{R}}+\left(\delta_{\fl{M}}{}^{\fl{K}}\delta_{\fl{N}}{}^{\fl{P}}-\frac{1}{2}\,f_{\fl{M}}{}^{\fl{LK}}f_{\fl{NL}}{}^{\fl{P}}\right)\,\xi_{\fl{K}}.
+		X_{\fl{MN}}{}^{\fl{P}}&=-\rho^{-1}\,\Gamma_{\fl{MN}}{}^{\fl{P}} + \rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{L}}\,\Gamma_{\fl{KM}}{}^{\fl{L}}-\frac{1}{60}\,\rho^{-1}\,f^{\fl{PK}}{}_{\fl{N}}\,f_{\fl{ML}}{}^{\fl{Q}}\,\Gamma_{\fl{KQ}}{}^{\fl{L}}\\
+		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{M}}\,\Gamma_{\fl{RK}}{}^{\fl{R}}+\left(\delta_{\fl{M}}{}^{\fl{K}}\delta_{\fl{N}}{}^{\fl{P}}-\frac{1}{2}\,f_{\fl{M}}{}^{\fl{LK}}f_{\fl{NL}}{}^{\fl{P}}\right)\,\xi_{\fl{K}}\,.
 	\end{aligned}
 \end{equation}
-Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=U_{\fl{M}}{}^{K}U_{\fl{N}}{}^{L}\partial_{K}U^{\fl{P}}{}_{L}$ and the trombone gauging
-\begin{equation}
-	\xi_{\fl{M}} = 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\fl{M}}{}^{N}.
+Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=U_{\fl{M}}{}^{K}U_{\fl{N}}{}^{L}\partial_{K}U^{\fl{P}}{}_{L}$ and the trombone gauging \EM{Give this in terms of $\Gamma_{\fl{M}\fl{N}}$ for later use?}
+\begin{equation} \label{eq:Trombone}
+	\xi_{\fl{M}} = 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\fl{M}}{}^{N} \,.
 \end{equation}
-In the following, we consider $\xi_{\fl{M}}=0$. The embedding tensor is then most nicely expressed once projected on the adjoint representation \CE{(Give expression with projector on 3875?)}
+In the following, we consider only gaugings with $\xi_{\fl{M}}=0$.
+The embedding tensor is then most nicely expressed once projected on the adjoint representation \CE{(Keep expression with projector on 3875?)} \EM{I think it's useful}
 \begin{equation} \label{eq:symembeddingtensor}
-	X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} = 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{K}(\fl{M}}{}^{\fl{L}}\,f_{\fl{N})\fl{L}}{}^{\fl{K}},
+	\begin{aligned}
+		X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} &= 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{P}(\fl{M}}{}^{\fl{Q}}\,f_{\fl{N})\fl{Q}}{}^{\fl{P}}\\
+		&=14\,\rho^{-1}\,(\mathbb{P}_{3875})_{\fl{MN}}{}^{\fl{PQ}}\,\Gamma_{\fl{PQ}}+\frac{1}{4}\,\rho^{-1}\,\eta_{\fl{MN}}\,\Gamma_{\fl{P}}{}^{\fl{P}} \,,
+	\end{aligned}
 \end{equation}
-with the projection of the current $\Gamma_{\fl{MN}} = (1/60)\,\Gamma_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}}$.
+with the projection of the current $\Gamma_{\fl{MN}} = \tfrac{1}{60}\,\Gamma_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}}$.
 
 The three-dimensional action follows from inserting the Ansätze~\eqref{eq:GSSansatz} in the ExFT action~\eqref{eq:ExFTaction}.
-The expressions of the kinetic and Chern-Simons terms result from eq.~\eqref{eq:GSSexample}: \CE{(A work on the Ricci scalar?)}
+The expressions of the kinetic and Chern-Simons terms result immediately from eq.~\eqref{eq:GSSexample} \CE{(A word on the Ricci scalar?)} \EM{Yes, should briefly mention what happens}
 \begin{equation}
@@
 		\mathscr{L}_{\rm kin} &= \frac{1}{240}\,D_{\mu}\M_{MN}D^{\mu}\M^{MN} \underset{\rm gSS}{=} \frac{\rho^{2}}{240}\,{\cal D}_{\mu}\M_{\fl{MN}}{\cal D}^{\mu}\M^{\fl{MN}}, \\
-		\mathscr{L}_{\rm CS} &\underset{\rm gSS}{=} -\rho^{-1}\,\varepsilon^{\mu\nu\rho}\,X_{\fl{MN}}\,\A_{\mu}{}^{\fl{M}} \left(\partial_{\nu}\A_{\rho}{}^{\fl{N}}-\frac{1}{3}\,\llbracket\A_{\nu},\A_{\rho}\rrbracket^{\fl{N}}\right).
+		\mathscr{L}_{\rm CS} &\underset{\rm gSS}{=} -\rho^{-1}\,\varepsilon^{\mu\nu\rho}\,X_{\fl{MN}}\,\A_{\mu}{}^{\fl{M}} \left(\partial_{\nu}\A_{\rho}{}^{\fl{N}}-\frac{1}{3}\,\llbracket\A_{\nu},\A_{\rho}\rrbracket^{\fl{N}}\right)\,.
 	\end{aligned}
@@
 
-The case of the potential term $\mathscr{L}_{\rm int}$, leading to a potential $V$ for the three-dimensional scalars $\M_{\fl{MN}}$, is more subtle.
+However, the case of the potential term $\mathscr{L}_{\rm int}$, leading to a potential $V$ for the three-dimensional scalars $\M_{\fl{MN}}$, is more subtle.
 We expect $V$ to be quadratic in the embedding tensor, which makes the identification of $X_{\fl{MN}}$ more complicated.
-We adopt the following strategy.
-First, we insert the generalized Sherk-Schwarz Ansätze~\eqref{eq:GSSansatz} into the expression of $\mathscr{L}_{\rm int}$~\eqref{eq:ExFTLint} with an additional total derivative: \CE{(Fill in with the eq.
-of 08/02, global $-1$ and  $a \rightarrow a/3$.
-Need to motivate the total derivative?
-Need to give some formula?
-As MMf=-fM?
-Ad invariance?
-Mention use of section constraint?
+Moreover, the potential of three-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor is unknown, with currently the potential only expressed in terms of the fermion shift matrices of the gauged supergravity.
+Thus, in the following, we will follow the truncation procedure carefully and thereby construct the potential of the three-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor.
+
+\section{Deriving the potential of ${\cal N}=16$ gauged supergravity} \label{s:Potential}
+Here we will use the $\EE$ ExFT Lagrangian and the consistent truncation Ansatz \eqref{eq:GSSansatz} to derive the potential of three-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor.
+Not only is this an interesting application of ExFT, relying on purely bosonic considerations and bypassing the usual construction of the gauged supergravity potential using supersymmetry\footnote{Note that the same strategy was recently used to impressively derive the potential of maximal two-dimensional gauged supergravity \cite{Bossard:2022wvi}, where fermions are extremely poorly understood.
+As a result, in that case, the bosonic $\En{9}$ ExFT \cite{Bossard:2018utw,Bossard:2021jix} provides the only currently accessible route for computing the gauged supergravity potential.}, but the potential is crucial for finding vacua of the three-dimensional theory and uplifting these in the later parts of this paper.
+
+In order to derive the potential, we adopt the following strategy.
+We want $\mathscr{L}_{\rm int}$ \eqref{eq:ExFTLint} to reduce to the embedding tensor squared upon inserting the generalised Scherk-Schwarz Ans\"{a}tze \eqref{eq:GSSansatz}.
+However, as in higher dimensions, e.g.
+\cite{Berman:2012uy,Musaev:2013rq,Blair:2014zba}, this does not have to match identically, but only up to total derivative terms and terms which violate the section condition.
+The possible boundary terms are
+\begin{equation} \label{eq:BoundaryTerms}
+	\frac{1}{\sqrt{\dg}} \partial_M \left(\sqrt{\dg} \partial_N \gM^{MN} \right) \quad \text{and} \quad \frac{1}{\sqrt{\dg}} \partial_M \left( \gM^{MN} \partial_N \sqrt{\dg}\right) \,.
+\end{equation}
+However, since the ${\cal N}=16$ supergravity potential will be given by terms quadratic in $X_{\fl{MN}}{}^{\fl{P}}$, we do not want the boundary terms to involve any double derivative terms.
+Therefore, the two boundary terms \eqref{eq:BoundaryTerms} can only appear via the combination
+\begin{equation} \label{eq:BoundaryTermCombination}
+	\frac{1}{\sqrt{\dg}}\,\partial_{M}\Big(\sqrt{\dg}\,\partial_{N}\M^{MN}+\frac{4}{3}\,\M^{MN}\partial_{N}\sqrt{\dg}\Big) \,.
+\end{equation}
+
+Now, we first insert the generalized Sherk-Schwarz Ansätze \eqref{eq:GSSansatz} into the expression of $\mathscr{L}_{\rm int}$ \eqref{eq:ExFTLint} with the additional total derivative \eqref{eq:BoundaryTermCombination} \CE{(Need to motivate the total derivative?
+Mention the need for section constraint?
 Factor $\sqrt{\vert g\vert}$ to avoid carrying $\rho$ in $V$?)}
@@
 	\begin{aligned}
-		\mathscr{L}_{\rm int} + \frac{a}{\sqrt{\vert g\vert}}\,\partial_{M}\Big(&\sqrt{\vert g\vert}\,\partial_{N}\M^{MN}+\frac{4}{3}\,\M^{MN}\partial_{N}\sqrt{\vert g\vert}\Big)\\
-		&\underset{\rm gSS}{=} -\frac{1}{2}\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma_{\fl{N}}{}^{\fl{K}} + \ldots
+		\mathscr{L}_{\rm int} &+ \frac{a}{\sqrt{\vert g\vert}}\,\partial_{M}\Big(\sqrt{\vert g\vert}\,\partial_{N}\M^{MN}+\frac{4}{3}\,\M^{MN}\partial_{N}\sqrt{\vert g\vert}\Big)\\
+		&\underset{\rm gSS}{=} -\frac{1}{2}\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma_{\fl{N}}{}^{\fl{K}} -\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma^{\fl{K}}{}_{\fl{N}} -\frac{1}{2}\,\Gamma_{\fl{MN}}\Gamma^{\fl{NM}} - \frac{1}{2}\,\M^{\fl{MN}}\M^{\fl{KL}}\,\Gamma_{\fl{MK}}\Gamma_{\fl{NL}} \\
+		&\ \quad - \frac{1}{2}\,\M^{\fl{MN}}\M^{\fl{KL}}\,\Gamma_{\fl{MK}}\Gamma_{\fl{LN}} +\frac{3}{2}\left(a-1\right)\,\M^{\fl{MN}}\Gamma_{\fl{MN}}{}^{\fl{K}}\Gamma_{\fl{LK}}{}^{\fl{L}}-\frac{a}{2}\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{K}}\Gamma_{\fl{LN}}{}^{\fl{L}}\\
+		&\ \quad + \left(\frac{1}{2}-a\right)\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{L}}\Gamma_{\fl{LN}}{}^{\fl{K}}+\,\M^{\fl{MN}}\Gamma_{\fl{MK}}{}^{\fl{L}}\Gamma_{\fl{LN}}{}^{\fl{K}}-\frac{1}{2}\,\M^{\fl{MN}}\M^{\fl{KL}}f_{\fl{QL}}{}^{\fl{P}}\Gamma_{\fl{PN}}{}^{\fl{Q}}\Gamma_{\fl{MK}}\,.
 	\end{aligned}
 \end{equation}
-Then, we consider the most general exactly quadratic function in $X_{\fl{MN}}$ and develop it in \EE currents using eq.~\eqref{eq:symembeddingtensor}: \CE{(Sign convention between $V$ and ${\mathscr{L}}_{\rm int}$.)}
+
+Secondly, knowing that the ${\cal N}=16$ potential must be quadratic in $X_{\fl{MN}}$, we consider the most general quadratic function in $X_{\fl{MN}}$ and develop it in \EE currents using eq.~\eqref{eq:symembeddingtensor}.
+\CE{(Sign convention between $V$ and ${\mathscr{L}}_{\rm int}$?
+$+{\mathscr{L}}_{\rm int}$ in eq.~\eqref{eq:ExFTaction} but $-V$ in eq.~\eqref{eq:ExFTactiongSS}.)} Note that in higher dimensions, there exist only two quadratic combinations of the embedding tensor
+\begin{equation}
+	X_{\fl{M}\fl{N}}{}^{\fl{P}} X_{\fl{Q}\fl{P}}{}^{\fl{N}} \gM^{\fl{MQ}} \qquad \text{and} \qquad X_{\fl{M}\fl{N}}{}^{\fl{P}} X_{\fl{Q}\fl{R}}{}^{\fl{S}} \gM^{\fl{MQ}} \gM^{\fl{N}\fl{R}} \gM_{\fl{P}\fl{S}} \,.
+\end{equation}
+However, in three dimensions, because the vector fields transform in the adjoint representation of $\EE$, we can write two additional terms
+\begin{equation} \label{eq:ExtraX2Terms}
+	X_{\fl{MN}} X_{\fl{PQ}}\, \eta^{\fl{MP}} \eta^{\fl{NQ}} \qquad \text{and} \qquad X_{\fl{MN}} X_{\fl{PQ}}\, \eta^{\fl{MN}} \eta^{\fl{PQ}} \,,
+\end{equation}
+where the second term corresponds to the square of the singlet part of the embedding tensor.
+
+It turns out that for gaugings that arise from consistent truncations, these two terms \eqref{eq:ExtraX2Terms} can be related to the square of the trombone tensor.
+We can square eq.~\eqref{eq:symembeddingtensor} to derive an expression for $X_{\ov{MN}}X^{\ov{MN}}$ in terms of the current $\Gamma$.
+We find
+\begin{equation}\label{eq:XXwitheta}
+	X_{\ov{MN}}X^{\ov{MN}} = 21 \rho^{-2}\, \Gamma_{\ov{MN}}\, \Gamma^{\ov{NM}} + 19 \rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\right)^2\,.
+\end{equation}
+Similarly, squaring the trombone tensor $\xi$ gives \EM{Should we give \eqref{eq:Trombone} in terms of $\Gamma$?}, we find
+\begin{equation}\label{eq:xixiwitheta}
+	\xi_{\ov M}\,\xi^{\ov M}=\rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\Gamma_{\ov N}{}^{\ov N}+\Gamma_{\ov{MN}}\Gamma^{\ov{NM}}\right) \,.
+\end{equation}
+We can now deduce
+\begin{equation}
+	X_{\ov{MN}} \,X^{\ov{MN}}=21	\xi_{\ov M} \, \xi^{\ov M} - 2 \rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\right)^2 \,,
+\end{equation}
+which can be expressed entirely in terms of $X_{\fl{M}\fl{N}}$ after tracing eq.~\eqref{eq:symembeddingtensor}
+\begin{equation}\label{eq:reltrX}
+	X_{\ov{MN}}\,X^{\ov{MN}} = 21\, \xi_{\ov M}\, \xi^{\ov M} - \frac1{1922}\left(X_{\ov M}{}^{\ov M}\right)^2 \,. 
+\end{equation}
+Thus, \eqref{eq:reltrX} is a constraint on the embedding tensor of three-dimensional supergravity which must be satisfied in order for it to have an uplift to 10-/11-dimensional supergravity.
+Note that this constraint is not implied by the quadratic constraint.
+To see this, simply observe that the theory with $\En{8}$ gauging has $X_{\ov{MN}}=\eta_{\ov{MN}}$ and $\xi_{\fl{M}} = 0$, violating \eqref{eq:reltrX}.
+
+Since we are focusing on gaugings with vanishing trombone $\xi_{\fl{M}} = 0$, \eqref{eq:reltrX} implies that the two terms in \eqref{eq:ExtraX2Terms} are proportional and we only need to consider one of these terms in the gauged supergravity potential.
+Thus, the most general Ansatz for the supergravity potential, for gaugings that have an uplift to 10-/11-dimensional supergravity\footnote{If we do not require the three-dimensional gauged supergravity to arise from a consistent truncation, \eqref{eq:reltrX} may be violated and we need to include both terms of \eqref{eq:ExtraX2Terms}.
+However, here we are not interested in such gaugings.}, is
 \begin{equation} \label{eq:Vexpansion}
 	\begin{aligned}
-		V &= X_{\fl{MN}}X_{\fl{PQ}}\left(\alpha\,\M^{\fl{MP}}\M^{\fl{NQ}}+\beta\,\M^{\fl{MP}}\eta^{\fl{NQ}}+\delta\,\eta^{\fl{MP}}\eta^{\fl{NQ}}+\gamma\,\eta^{\fl{MN}}\eta^{\fl{PQ}}\right) \\
-		&\underset{\rm gSS}{=} \rho^{-2}\bigg(14\,\alpha\,\Gamma_{\fl{MN}}\Gamma_{\fl{PQ}}\,\M^{\fl{MP}}\M^{\fl{NQ}}+\ldots\bigg).
+		-V &= X_{\fl{MN}}X_{\fl{PQ}}\left(\alpha\,\M^{\fl{MP}}\M^{\fl{NQ}}+\beta\,\M^{\fl{MP}}\eta^{\fl{NQ}}+\delta\,\eta^{\fl{MP}}\eta^{\fl{NQ}}
+		%+\gamma\,\eta^{\fl{MN}}\eta^{\fl{PQ}}
+		\right) \\
+		&\underset{\rm gSS}{=} \rho^{-2}\bigg(14\,\alpha\,\Gamma_{\fl{MN}}\,\Gamma_{\fl{PQ}}\,\M^{\fl{MP}}\M^{\fl{NQ}}+14\,\alpha\,\Gamma_{\fl{MN}}\,\Gamma_{\fl{PQ}}\,\M^{\fl{MQ}}\M^{\fl{NP}}\\
+		&\ \quad +2\,\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma^{\fl{K}}{}_{\fl{N}}+\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\,\Gamma_{\fl{N}}{}^{\fl{K}}+\left(-12\,\alpha+2\,\delta
+		%-(62)^2\,\gamma
+		\right)\,\Gamma_{\fl{MN}}\,\Gamma^{\fl{MN}}\\
+		&\ \quad -2\,\beta\,\M^{\fl{MN}}\Gamma_{\fl{MK}}{}^{\fl{L}}\,\Gamma_{\fl{LN}}{}^{\fl{K}}+\beta\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{L}}\,\Gamma_{\fl{LN}}{}^{\fl{K}}+\left(7\,\alpha+\frac{\beta}{2}\right)\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{K}}\,\Gamma_{\fl{LN}}{}^{\fl{L}}\\
+		&\ \quad +14\,\alpha\,\M^{\fl{MN}}\M^{\fl{KL}}f_{\fl{QL}}{}^{\fl{P}}\Gamma_{\fl{PN}}{}^{\fl{Q}}\,\Gamma_{\fl{MK}}\bigg)\,.
 	\end{aligned}
 \end{equation}
-\CE{Finally, comparing eq.~\eqref{eq:Lintexpansion} and~\eqref{eq:Vexpansion}, the parameters are fixed to...}
+Finally, comparing eq.~\eqref{eq:Lintexpansion} and~\eqref{eq:Vexpansion}, the parameters are fixed to
+\begin{equation}
+	\alpha = \frac{\rho^{2}}{28}\,,\quad \beta = \frac{\rho^{2}}{2}\,,\quad a=1\,,\quad \delta=\frac{13}{28}\,\rho^{2}\,. %, \quad \gamma=0.
+\end{equation}
+%\CE{Freedom for $\delta$ and $\gamma$: $2\delta-(62)^2\gamma=\rho^{2}(1/2+3/7)$.}
+%\EM{MG and EM are confused about this -- we need to chat all together}
+
+\CE{Some formula used to derive the previous equations:
+\begin{equation}
+	\begin{aligned}
+		\M^{\fl{MP}}\M^{\fl{NQ}}f_{\fl{PQ}}{}^{\fl{K}}&=-f^{\fl{MN}}{}_{\fl{L}}\,\M^{\fl{LK}},\\
+		{\rm Ad\ invariance:}\quad 2\,\Gamma_{\fl{K}[\fl{M}}{}^{\fl{L}}\,f_{\fl{N}]\fl{L}}{}^{\fl{P}}&= -f_{\fl{MN}}{}^{\fl{L}}\,\Gamma_{\fl{KL}}{}^{\fl{P}}\,,\\
+		{\rm No\ trombone:}\quad \UI_{\fl{M}}{}^{M}\partial_{M}\ln(\rho)&= -\frac{1}{2}\,\Gamma_{\fl{KM}}{}^{\fl{K}},\\
+		{\rm Eq.~\eqref{eq:sectionconstraints}}\ \implies \ f^{\fl{K}}{}_{\fl{MP}}f^{\fl{PL}}{}_{\fl{N}}\,\partial_{\fl{K}}\otimes\partial_{\fl{L}} &= 2\,\partial_{(\fl{M}}\otimes\partial_{\fl{N})}\,.
+	\end{aligned}
+\end{equation}
+}
 
@@
 \end{equation}
-with the potential\footnote{To obtain this potential, one has to add the total derivative $-\partial_{M}\left(\sqrt{\vert g\vert}\,\partial_{N}\M^{MN}+(4/3)\,\M^{MN}\partial_{N}\sqrt{\vert g\vert}\right)$ to $\sqrt{\vert g\vert}\,\mathscr{L}_{\rm int}$.}
+with the potential%\footnote{To obtain this potential, one has to add the total derivative $-\partial_{M}\left(\sqrt{\vert g\vert}\,\partial_{N}\M^{MN}+(4/3)\,\M^{MN}\partial_{N}\sqrt{\vert g\vert}\right)$ to $\sqrt{\vert g\vert}\,\mathscr{L}_{\rm int}$.}
 \begin{equation}
@@
 \CE{(A word on the 3d linear and quadratic constraints?)}
+
+%\subsection{Relating $\tr( X^2)$ and $(\tr X) ^2$ using $\xi$}
+%One can square eq.~\eqref{eq:symembeddingtensor} to derive an expression for $X_{\ov{MN}}X^{\ov{MN}}$ in terms of the current $\Gamma$, we find 
+%\begin{equation}\label{eq:XXwitheta}
+%	X_{\ov{MN}}X^{\ov{MN}}=21\rho^{-2}\Gamma_{\ov{MN}}\Gamma^{\ov{NM}}+19\rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\right)^2.
+%\end{equation}
+%Similarly, squaring the trombone tensor $\xi$ gives 
+%\begin{equation}\label{eq:xixiwitheta}
+%	\xi_{\ov M}\xi^{\ov M}=\rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\Gamma_{\ov N}{}^{\ov N}+\Gamma_{\ov{MN}}\Gamma^{\ov{NM}}\right),
+%\end{equation}
+%we can then deduce
+%\begin{equation}
+%	X_{\ov{MN}}X^{\ov{MN}}=21	\xi_{\ov M}\xi^{\ov M}-2\rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\right)^2
+%\end{equation}
+%which can be expressed entirely in terms of $X$ after tracing eq.~\eqref{eq:symembeddingtensor}:
+%\begin{equation}\label{eq:reltrX}
+%		X_{\ov{MN}}X^{\ov{MN}}=21	\xi_{\ov M}\xi^{\ov M}-\frac1{1922}\left(X_{\ov M}{}^{\ov M}\right)^2. 
+%\end{equation}
+%Whenever $\xi=0$, eq.~\eqref{eq:reltrX} is a constraint on the embedding tensor of the resulting three dimensional supergravity which does not arise from the quadratic constraint.
+To see this, simply observe that the theory with $\En{8}$ gauging constructed in \MG{REFERENCE}, has $X_{\ov{MN}}=\eta_{\ov{MN}}$, violating~\eqref{eq:reltrX}.
+\\
+%Since we used the Scherk-Schwarz Ansatz in the calculation, we deduce that this must in fact be a condition satisfied by any theory that comes from type II or 11 dimensional supergravity.
+For example \MG{$\SO{4}\times \SO{4}$ gauging ...}
+
+\subsection{Ruling out gaugings}
 
@@
 	\begin{split}
-		\gL_{V} V' &= [v, v'] + L_{v} \omega'_{(n-2)} - \imath_{v'} \omega_{(n-2)} \,, \\
-		\gL_{V} W &= L_v \omega_{(1)} + L_v \omega_{(n)} - \EM{\alpha} \omega_{(1)} \wedge \omega_{(n-2)} \,,
+		\gL_{V} V' &= [v, v'] + L_{v} \omega'_{(n-2)} - \imath_{v'} d\omega_{(n-2)} \,, \\
+		\gL_{V} W &= L_v \omega_{(1)} + L_v \omega_{(n)} - \EM{\alpha} \omega_{(1)} \wedge d\omega_{(n-2)} \,,
 	\end{split}
@@
 \begin{equation}
-	vol_{S^n} = \epsilon_{I_1 I_2 \ldots I_{n+1}} Y^{I_1}\, dY^{I_2} \wedge \ldots \wedge dY^{I_{n+1}} \,,
+	vol_{S^n} = \frac{1}{n!}\epsilon_{I_1 I_2 \ldots I_{n+1}} Y^{I_1}\, dY^{I_2} \wedge \ldots \wedge dY^{I_{n+1}} \,,
 \end{equation}
@@
 
+\EM{I think the sign conventions are:
+	\begin{equation}
+		\begin{split}
+			\cU^{\fl{I}} &= dY^{\fl{I}} + Y^{\fl{I}}\, vol_{S^n} + dY^{\fl{I}} \wedge A \,, \\
+			\gL_{V} W &= L_v \omega_{(1)} + L_v \omega_{(n)} + \omega_{(1)} \wedge d\omega_{(n-2)} \,, \\
+			\gL_{\cU_{\fl{I}\fl{J}}} \cU^{\fl{K}} &= - X_{\fl{I}\fl{J},\fl{L}}{}^{\fl{K}}\, \cU^{\fl{L}} \,, \\
+			X_{\fl{I}\fl{J},\fl{L}}{}^{\fl{K}} &= 2\, \delta_{\fl{L}[\fl{I}} \delta_{\fl{J}]}^{\fl{K}} \,.
+		\end{split}
+	\end{equation}
+For the twist matrix in the antisymmetric rep, I find
+\begin{equation}
+	\cU_{[\fl{I}} \cU_{\fl{J}]} = v_{\fl{J}\fl{I}} + \star \left( dY_{\fl{I}} \wedge dY_{\fl{J}} \right) + \left(-1\right)^{n-1} \imath_{v_{\fl{J}\fl{I}}} A \,,
+\end{equation}
+where the vector part is $V^{i\,0}$, the $(n-2)$-form part is $V^{ij} = \frac{1}{(n-2)!} \epsilon^{k_1 \ldots k_{n-2} ij} \lambda_{k_{1} \ldots k_{n-2}}$ and the coordinates are identified as $Y^{i\,0} = y^i$.
+We can probably match the sign of the vector part of \cite{Baguet:2015iou} by taking the vector part to be $V^{0\,i}$ and also changing the coordinates to be $Y^{0\,i} = y^i$.
+We should probably check this carefully since it's useful to write up properly.
+}
+
 \subsubsection{Adding flux}
@@
 
-\section{Moduli of AdS$_3 \times S^3 \times S^3 \times S^1$}
+\section{Moduli of AdS$_3 \times S^3 \times S^3 \times S^1$} \label{s:Moduli}
 
@@
 \subsection{Moduli in 10 dimensions}
+\MG{Maybe we recall what the vacuum at the origin is here and reference somebody?}
+The seven form flux is unaffected by the deformations.
 
 \paragraph{SUSY deformation}
-In Hopf coordinates:
+
+%In Hopf coordinates:
+%\begin{equation}
+%	\begin{split}
+%		ds^2 &= \alpha^2 \left[ ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
+%		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{\CE{-}(1-e^{2\omega})} d\psi \,, \\
+%		d\sigma &= vol_{\mathbb{CP}^1} \,.
+%	\end{split}
+%\end{equation}
+
+It is convenient to use the Hopf fibration to describe this, we denote by $\phi$ the coordinate on the $S^1$ fibre and by $\xi$ the homogeneous coordinate on $\mathbb{CP}^1$.
+The round metric on $S^3$ then reads
+\begin{equation}
+	g= \mathrm{d}s^2_{\mathbb{CP}^1} + (\sigma + \mathrm{d}\phi)^2
+\end{equation}
+where 
 \begin{equation}
 	\begin{split}
-		ds^2 &= \alpha^2 \left[ ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
-		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{\CE{-}(1-e^{2\omega})} d\psi \,, \\
-		d\sigma &= vol_{\mathbb{CP}^1} \,.
+		\mathrm{d}s^2_{\mathbb{CP}^1} &= \frac1{(1+|\xi|^2)^2}\mathrm{d}\xi\,\mathrm{ d}\ov{\xi}\\
+		\sigma&=\frac{i}{2(1+|\xi|^2)}(\xi \mathrm{d} \ov{\xi}-\ov{\xi}\mathrm{d}\xi)\\ 
+		vol_{S^3}&=vol_{\mathbb{CP}^1}\wedge \mathrm{d}\psi .
 	\end{split}
 \end{equation}
-
-In spherical coordinates:
+The deformation does not affect $S_+^3$, but it mixes the $S^1$ factor in the internal space with the Hopf fibre of $S_-^3$. It is parametrised by a real number $\Omega$, such that the metric reads
 \begin{equation}
-	\begin{aligned}
-		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+\alpha^{2}\,\d s^2\left(S^{3}_{-}\right) +e^{-2\omega}\,\d\psi^{2}\\
-		&\quad+2\,\alpha\,e^{-2\omega}\,\sqrt{-1+e^{2\omega}}\left(-\cos^{2}(\theta)\,\d\varphi_{1}+\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi\\[5pt]
-		&= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+e^{-4\omega}\,\d\psi^{2}\\
-		&\quad+\alpha^{2}\bigg[\d \theta^2+\cos^{2}(\theta)\left(\d\varphi_{1}-\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}+\sin^{2}(\theta)\left(\d\varphi_{2}+\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}\bigg] ,\\[5pt]
-		\d s^2\left(S^{3}_{-}\right) &= \d\theta^{2}+\cos^{2}(\theta)\,\d\varphi_{1}^{2}+\sin^{2}(\theta)\,\d\varphi_{2}^{2}.
-	\end{aligned}
+	\begin{split}
+		\mathrm{d}s^2 &= \alpha^2(\mathrm{d}s^2_{\mathbb{CP}^1}+\kappa^2) + \mathrm{d}s^2_{S_+^3} + e^{-4\Omega}\mathrm{d}\psi^2\\
+		\kappa &= \mathrm{d}\phi + \sigma - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi.
+	\end{split}
+\end{equation}
+ The three form flux gets changed according to the prescription $\d\phi \rightarrow \d\phi -  \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d \psi$ and we find:
+\begin{equation}
+	H_{(3)}=\alpha^2vol_{\mathbb{CP}^1}\wedge (\d\phi - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi) + vol_{S_+^3}.
 \end{equation}
 
+%
+%In spherical coordinates:
+%\begin{equation}
+%	\begin{aligned}
+%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+\alpha^{2}\,\d s^2\left(S^{3}_{-}\right) +e^{-2\omega}\,\d\psi^{2}\\
+%		&\quad+2\,\alpha\,e^{-2\omega}\,\sqrt{-1+e^{2\omega}}\left(-\cos^{2}(\theta)\,\d\varphi_{1}+\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi\\[5pt]
+%		&= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+e^{-4\omega}\,\d\psi^{2}\\
+%		&\quad+\alpha^{2}\bigg[\d \theta^2+\cos^{2}(\theta)\left(\d\varphi_{1}-\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}+\sin^{2}(\theta)\left(\d\varphi_{2}+\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}\bigg] ,\\[5pt]
+%		\d s^2\left(S^{3}_{-}\right) &= \d\theta^{2}+\cos^{2}(\theta)\,\d\varphi_{1}^{2}+\sin^{2}(\theta)\,\d\varphi_{2}^{2}.
+%	\end{aligned}
+%\end{equation}
+
 \paragraph{Non-SUSY deformation}
-In spherical coordinates:
+Here we study a more general deformation depending on three parameters $\Omega$, $\zeta_{1,8}$ and $\zeta_{2,3}$.
+It is convenient to write down the uplift in terms of spherical coordinates on $S_-^3$, while again $S_+^3$ is not deformed.\\
+\noindent For the metric we find
+%\begin{equation}
+%	\begin{aligned}
+%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+%		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
+%		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
+%		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2}.\\[5pt]
+%		\Delta^{-1} &= 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
+%	\end{aligned}
+%\end{equation}
 \begin{equation}
@@
 		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
-		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2},\\[5pt]
-		\Delta^{-1} &= 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
+		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2},
 	\end{aligned}
 \end{equation}
-
-In Hopf coordinates:
+where $\Delta$ is the warp factor
+\begin{equation}
+		\Delta^{-1} = 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
+\end{equation}
+The three-form flux is 
+\begin{equation}
+	H_{(3)}=vol_{S_-^3}+\alpha ^2\sin(\theta)\cos (\theta)(2+e^{2\Omega}\zeta^2_{1,8})(2e^{2\Omega}+\zeta_{2,3}^2)\Delta^2\mathrm{d}\theta\wedge\kappa_1\wedge\kappa_2,
+\end{equation}
+with the two one forms $\kappa_{1,2}$ defined by 
+\begin{equation}
+\begin{split}
+		\kappa_1&=\mathrm{d}\phi_1-\frac{\zeta_{2,3}}{\alpha(2e^{2\Omega}+\zeta_{2,3}^2)}\mathrm{d}\psi \\
+	\kappa_2&=\mathrm{d}\phi_2+ \frac{\zeta_{1,8}}{\alpha(2+e^{2\Omega}\zeta_{1,8}^2)}\mathrm{d}\psi.
+\end{split}
+\end{equation}
+Note that setting $...$ recovers the supersymmetric deformation described earlier.
+%In Hopf coordinates:
 % \begin{equation}
@@
 % \end{equation}
-\begin{equation}
-	\begin{aligned}
-		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-		&\quad + \frac{\alpha^{2}}{1+\gamma\,\vert z\vert^{2}}\bigg[\Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm I}^{2}\right)+\left(\gamma-1\right)\,z_{\rm R}^{2}\Big)\,\frac{\d z_{\rm R}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
-		&\qquad + \Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm R}^{2}\right)+\left(\gamma-1\right)\,z_{\rm I}^{2}\Big)\,\frac{\d z_{\rm I}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}} - 2\,\Big(1+\vert z\vert^{2}-\left(\gamma-1\right)\Big)\,\frac{\d z_{\rm R}\d z_{\rm I}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
-		&\qquad+2\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\left(\gamma+\vert z\vert^{2}\right)\d\theta^{2}\bigg]\\
-		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
-		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
-		\gamma &= \frac{2\,e^{2\Omega}+\zeta_{2,3}^{2}}{2+e^{2\Omega}\zeta_{1,8}^{2}},\qquad \Delta^{-1} = 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
-	\end{aligned}
-\end{equation}
+
+%%%%
+
+%\begin{equation}
+%	\begin{aligned}
+%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+%		&\quad + \frac{\alpha^{2}}{1+\gamma\,\vert z\vert^{2}}\bigg[\Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm I}^{2}\right)+\left(\gamma-1\right)\,z_{\rm R}^{2}\Big)\,\frac{\d z_{\rm R}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
+%		&\qquad + \Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm R}^{2}\right)+\left(\gamma-1\right)\,z_{\rm I}^{2}\Big)\,\frac{\d z_{\rm I}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}} - 2\,\Big(1+\vert z\vert^{2}-\left(\gamma-1\right)\Big)\,\frac{\d z_{\rm R}\d z_{\rm I}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
+%		&\qquad+2\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\left(\gamma+\vert z\vert^{2}\right)\d\theta^{2}\bigg]\\
+%		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
+%		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
+%		\gamma &= \frac{2\,e^{2\Omega}+\zeta_{2,3}^{2}}{2+e^{2\Omega}\zeta_{1,8}^{2}},\qquad \Delta^{-1} = 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
+%	\end{aligned}
+%\end{equation}
 
@@
 
-\section{Conclusions}
+\section{Conclusions} \label{s:Conclusions}
 

### 2023-06-05 Draft_3dH3.tex
Update sec. 6. Commit before merging with Emanuel changes.

@@
 
-\section{Moduli of AdS$_3 \times S^3 \times S^3 \times S^1$} \label{s:Moduli}
+\section{Moduli of \texorpdfstring{AdS$_3 \times S^3 \times S^3 \times S^1$}{AdS3xS3xS3xS1}} \label{s:Moduli}
+
+\paragraph{10d solution}
+Pure NSNS solution, after ref.~\cite{Dei:2018yth} (but that's not the original ref):
+\begin{equation}
+	\begin{aligned}
+		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) + \alpha^{2}\,\d s^{2}\left(S^{3}\right)+\d s^{2}\big(\widetilde{S}^{3}\big)+\d\psi^{2},\\
+		H_{(3)} &= 2\left(\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})+\alpha^{2}\,{\rm Vol}\big(S^{3}\big)+{\rm Vol}\big(\widetilde{S}^{3}\big)\right),
+	\end{aligned}
+\end{equation}
+with $H_{(3)} = \d B_{(2)}$ and
+\begin{equation}
+	\ell_{\rm AdS}^{2} = \frac{\alpha^{2}}{1+\alpha^{2}}.
+\end{equation}
+
+The three-dimensional solution preserves ${\cal N}=(4,4)$ supercharges.
+The isometry group is ${\cal G}=D^{1}(2,1;\alpha)_{\rm L}\times D^{1}(2,1;\alpha)_{\rm R}$, with two copies of the large ${\cal N}=4$ supergroup.
+The parameter $\alpha$ is given by the ratio of the $S^{3}$ spheres radii.
+The even part of $D^{1}(2,1;\alpha)$ is isomorphic to ${\rm SL}(2,\mathbb{R})\times{\rm SO}(3)\times\widetilde{{\rm SO}(3)}$ and the bosonic isometries of the ${\rm AdS}_{3}\times S^{3}\times\widetilde{S}^{3}$ background are built from the even part of ${\cal G}$.
+The ${\rm AdS}_{3}$ isometry group is ${\rm SO}(2,2)\simeq{\rm SL}(2,\mathbb{R})_{\rm L}\times{\rm SL}(2,\mathbb{R})_{\rm R}$, and the factors ${\rm SO}(3)_{\rm L}\times{\rm SO}(3)_{\rm R}\times\widetilde{{\rm SO}(3)}_{\rm L}\times\widetilde{{\rm SO}(3)}_{\rm R}\simeq{\rm SO}(4)\times\widetilde{SO(4)}$ combine into the isometry groups of the two spheres.
+
+The spectrum organizes into long representations of ${\cal G}$~\cite{Eberhardt:2017fsi}. The spectrum at the consistent truncation is the one of ref.~\cite{Hohm:2005ui}. \CE{What details do we need?}
 
 \subsection{Moduli in gauged supergravity}
+\paragraph{S-fold like deformations} Scalar spectrum:
+\begin{equation}
+	\begin{aligned}
+		(m_{(0)}\ell_{\rm AdS})^2:	\quad 
+		&8\ [1],\quad \frac{4\,\chi_{1}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{4\,\chi_{2}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{(\chi_{1}+\chi_{2})^{2}}{1+\alpha^{2}}\ [4], \quad \frac{(\chi_{1}-\chi_{2})^{2}}{1+\alpha^{2}}\ [4],	\\
+		&\frac{4\,\alpha^{2}\widetilde{\chi}_{1}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{4\,\alpha^{2}\widetilde{\chi}_{2}^{2}}{1+\alpha^{2}}\ [2], \quad \alpha^{2} \frac{(\widetilde{\chi}_{1}+\widetilde{\chi}_{2})^{2}}{1+\alpha^{2}}\ [4], \quad \alpha^{2} \frac{(\widetilde{\chi}_{1}-\widetilde{\chi}_{2})^{2}}{1+\alpha^{2}}\ [4],	\\
+		& \frac{\left(\chi_{1} + \chi_{2} \pm \alpha\,(\widetilde{\chi}_{1}+\widetilde{\chi}_{2})\right)^{2}}{1+\alpha^{2}}\ [2+2], \quad \frac{\left(\chi_{1} - \chi_{2} \pm \alpha\,(\widetilde{\chi}_{1}-\widetilde{\chi}_{2})\right)^{2}}{1+\alpha^{2}}\ [2+2],\\
+		&1+\frac{\left(\chi_{1}-\alpha\,\widetilde{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}-\alpha\,\widetilde{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{1}+\alpha\,\widetilde{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}+\alpha\,\widetilde{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{1}-\alpha\,\widetilde{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}-\alpha\,\widetilde{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{1}+\alpha\,\widetilde{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}+\alpha\,\widetilde{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{2}-\alpha\,\widetilde{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}-\alpha\,\widetilde{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{2}+\alpha\,\widetilde{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}+\alpha\,\widetilde{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{2}-\alpha\,\widetilde{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}-\alpha\,\widetilde{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{2}+\alpha\,\widetilde{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}+\alpha\,\widetilde{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2].
+	\end{aligned}
+\end{equation}
 
@@
 The seven form flux is unaffected by the deformations.
+
+\paragraph{S-fold like deformations}
+Using spherical coordinates for both spheres:
+\begin{equation}
+	\begin{aligned}
+		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^{2}({\rm AdS}_{3}) +\alpha^{2}\left(\d\theta^{2} + \cos^{2}(\theta)\,\d\phi'_{1}{}^{2} + \sin^{2}(\theta)\,\d\phi'_{2}{}^{2} \right) \\
+		&\quad +\d\widetilde{\theta}^{2} + \cos^{2}(\widetilde{\theta})\,\widetilde{\d\phi'}_{1}^{2} + \sin^{2}(\widetilde{\theta})\,\widetilde{\d\phi'}_{2}^{2} + \d\psi^{2}, \\[5pt]
+		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) + 2\,\alpha^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge\d\phi'_{1}\wedge\d\phi'_{2}+ 2\cos(\widetilde{\theta})\sin(\widetilde{\theta})\,\d\widetilde{\theta}\wedge\widetilde{\d\phi'}_{1}\wedge\widetilde{\d\phi'}_{2},
+	\end{aligned}
+\end{equation}
+where
+\begin{equation}
+	\begin{aligned}
+		\d\phi'_{1} &= \d\phi_{1} + \chi_{1}\,\d\psi,\\
+		\d\phi'_{2} &= \d\phi_{2} - \chi_{2}\,\d\psi,\\
+		\widetilde{\d\phi'}_{1} &= \d\widetilde{\phi}_{1} + \widetilde{\chi}_{1}\,\d\widetilde{\psi},\\
+		\widetilde{\d\phi'}_{2} &= \d\widetilde{\phi}_{2} - \widetilde{\chi}_{2}\,\d\widetilde{\psi}.
+	\end{aligned}
+\end{equation}
 
@@
 	\begin{aligned}
-		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
 		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\

### 2023-06-05 Draft_3dH3.tex
Merging with Emanuel updates.

--- 2023-05-30 Draft_3dH3.tex
@@
 \newcommand{\ft}[2]{{\textstyle\frac{#1}{#2}}}
+\newcommand{\ts}[1]{\widetilde{#1}}
 
@@
 	\item Compare with classification known in literature, e.g. in IIA (and IIB -- Jerome's story)
+	\item Email DW and MP to ask who we should cite for \eqref{eq:Twisting}
 \end{itemize}
@@
 ${\cal N}=(4,4)$, supersymmetric AdS$_3$ vacua of string theory that are extremely intriguing.
-These are the AdS$_3 \times S^3 \times S^3 \times S^1$ and AdS$_3 \times S^3 \times T^4$ of IIB string theory (realising the ``small'' and ``large'' ${\cal N}=(4,4)$ superconformal symmetries), and, unlike in higher dimensions, can be supported by pure NS-NS flux.
+These are the AdS$_3 \times S^3 \times S^3 \times S^1$ and AdS$_3 \times S^3 \times T^4$ of IIB string theory (realising the ``large'' and ``small'' ${\cal N}=(4,4)$ superconformal symmetries), and, unlike in higher dimensions, can be supported by pure NS-NS flux.
 Not only does this mean that there are also heterotic versions of these vacua (preserving ${\cal N}=(4,0)$ supersymmetry), but also that they can be readily studied via the string worldsheet CFT \cite{Maldacena:2000hw,Eberhardt:2018ouy,Eberhardt:2019niq,Eberhardt:2019ywk}.
@@
 
-Another technical result of our work is the derivation of the potential of 3-dimensional gauged supergravity in terms of the embedding tensor, which was previously only expressed in terms of fermion shift matrices.
+Another technical result of our work is the derivation of the potential of 3-dimensional gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv} in terms of the embedding tensor, which was previously only expressed in terms of fermion shift matrices.
 As a by-product, we find that a constraint that must be obeyed by the embedding tensor of any 3-dimensional gauged supergravity that can be uplifted to 10-/11-dimensional supergravity.
@@
 
-Thus, for a given twist matrix $U_{M}{}^{\fl{M}}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity.
+Thus, for a given twist matrix $U_{M}{}^{\fl{M}}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv}.
 The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity, as is clear from its appearance in \eqref{eq:3dCovDeriv} in the gauge-covariant derivative and the gauge algebra of the vector fields.
@@
 \end{equation}
-Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=U_{\fl{M}}{}^{K}U_{\fl{N}}{}^{L}\partial_{K}U^{\fl{P}}{}_{L}$ and the trombone gauging \EM{Give this in terms of $\Gamma_{\fl{M}\fl{N}}$ for later use?}
+Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=U_{\fl{M}}{}^{K}U_{\fl{N}}{}^{L}\partial_{K}U^{\fl{P}}{}_{L}$ and the trombone gauging
 \begin{equation} \label{eq:Trombone}
-	\xi_{\fl{M}} = 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\fl{M}}{}^{N} \,.
-\end{equation}
-In the following, we consider only gaugings with $\xi_{\fl{M}}=0$.
-The embedding tensor is then most nicely expressed once projected on the adjoint representation \CE{(Keep expression with projector on 3875?)} \EM{I think it's useful}
+	\begin{split}
+		\xi_{\fl{M}} %&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\fl{M}}{}^{N} \\
+		&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1} - \rho^{-1}\, \Gamma_{\ov{N}\ov{M}}{}^{\ov{N}} \,.
+	\end{split}
+\end{equation}
+The embedding tensor is most nicely expressed once projected on the adjoint representation
 \begin{equation} \label{eq:symembeddingtensor}
 	\begin{aligned}
-		X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} &= 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{P}(\fl{M}}{}^{\fl{Q}}\,f_{\fl{N})\fl{Q}}{}^{\fl{P}}\\
-		&=14\,\rho^{-1}\,(\mathbb{P}_{3875})_{\fl{MN}}{}^{\fl{PQ}}\,\Gamma_{\fl{PQ}}+\frac{1}{4}\,\rho^{-1}\,\eta_{\fl{MN}}\,\Gamma_{\fl{P}}{}^{\fl{P}} \,,
-	\end{aligned}
-\end{equation}
-with the projection of the current $\Gamma_{\fl{MN}} = \tfrac{1}{60}\,\Gamma_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}}$.
+		X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} &= - 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{P}(\fl{M}}{}^{\fl{Q}}\,f_{\fl{N})\fl{Q}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \\
+		&= - 14\,\rho^{-1}\,(\mathbb{P}_{3875})_{\fl{MN}}{}^{\fl{PQ}}\,\Gamma_{\fl{PQ}} - \frac{1}{4}\,\rho^{-1}\,\eta_{\fl{MN}}\,\Gamma_{\fl{P}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \,,
+	\end{aligned}
+\end{equation}
+with the projection of the current $\Gamma_{\fl{MN}} = - \tfrac{1}{60}\,\Gamma_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}}$. In the following, we will focus on gaugings with $\xi_{\fl{M}}=0$.
 
 The three-dimensional action follows from inserting the Ansätze~\eqref{eq:GSSansatz} in the ExFT action~\eqref{eq:ExFTaction}.
-The expressions of the kinetic and Chern-Simons terms result immediately from eq.~\eqref{eq:GSSexample} \CE{(A word on the Ricci scalar?)} \EM{Yes, should briefly mention what happens}
+The expressions of the kinetic and Chern-Simons terms result immediately from eq.~\eqref{eq:GSSexample}
 \begin{equation}
@@
 We expect $V$ to be quadratic in the embedding tensor, which makes the identification of $X_{\fl{MN}}$ more complicated.
-Moreover, the potential of three-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor is unknown, with currently the potential only expressed in terms of the fermion shift matrices of the gauged supergravity.
+Moreover, the potential of three-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor is unknown, with currently the potential only expressed in terms of the fermion shift matrices of the gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv}.
 Thus, in the following, we will follow the truncation procedure carefully and thereby construct the potential of the three-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor.
@@
 \section{Deriving the potential of ${\cal N}=16$ gauged supergravity} \label{s:Potential}
-Here we will use the $\EE$ ExFT Lagrangian and the consistent truncation Ansatz \eqref{eq:GSSansatz} to derive the potential of three-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor.
+Here we will use the $\EE$ ExFT Lagrangian and the consistent truncation Ansatz \eqref{eq:GSSansatz} to derive the potential of three-dimensional ${\cal N}=16$ gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv} in terms of the embedding tensor.
 Not only is this an interesting application of ExFT, relying on purely bosonic considerations and bypassing the usual construction of the gauged supergravity potential using supersymmetry\footnote{Note that the same strategy was recently used to impressively derive the potential of maximal two-dimensional gauged supergravity \cite{Bossard:2022wvi}, where fermions are extremely poorly understood.
@@
 
-Now, we first insert the generalized Sherk-Schwarz Ansätze \eqref{eq:GSSansatz} into the expression of $\mathscr{L}_{\rm int}$ \eqref{eq:ExFTLint} with the additional total derivative \eqref{eq:BoundaryTermCombination} \CE{(Need to motivate the total derivative?
-Mention the need for section constraint?
-Factor $\sqrt{\vert g\vert}$ to avoid carrying $\rho$ in $V$?)}
+Now, we first insert the generalized Sherk-Schwarz Ansätze \eqref{eq:GSSansatz} into the expression of $\mathscr{L}_{\rm int}$ \eqref{eq:ExFTLint} with the additional total derivative \eqref{eq:BoundaryTermCombination}
 \begin{equation} \label{eq:Lintexpansion}
@@
 Secondly, knowing that the ${\cal N}=16$ potential must be quadratic in $X_{\fl{MN}}$, we consider the most general quadratic function in $X_{\fl{MN}}$ and develop it in \EE currents using eq.~\eqref{eq:symembeddingtensor}.
-\CE{(Sign convention between $V$ and ${\mathscr{L}}_{\rm int}$?
-$+{\mathscr{L}}_{\rm int}$ in eq.~\eqref{eq:ExFTaction} but $-V$ in eq.~\eqref{eq:ExFTactiongSS}.)} Note that in higher dimensions, there exist only two quadratic combinations of the embedding tensor
+Note that in higher dimensions, there exist only two quadratic combinations of the embedding tensor
 \begin{equation}
@@
 We can square eq.~\eqref{eq:symembeddingtensor} to derive an expression for $X_{\ov{MN}}X^{\ov{MN}}$ in terms of the current $\Gamma$.
-We find
+We find \EM{check coefficient of last term}
 \begin{equation}\label{eq:XXwitheta}
-	X_{\ov{MN}}X^{\ov{MN}} = 21 \rho^{-2}\, \Gamma_{\ov{MN}}\, \Gamma^{\ov{NM}} + 19 \rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\right)^2\,.
-\end{equation}
-Similarly, squaring the trombone tensor $\xi$ gives \EM{Should we give \eqref{eq:Trombone} in terms of $\Gamma$?}, we find
+	X_{\ov{MN}}X^{\ov{MN}} = 21 \rho^{-2}\, \Gamma_{\ov{MN}}\, \Gamma^{\ov{NM}} + 19 \rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\right)^2 - 15\, \xi_{\ov{M}}\, \xi^{\ov{M}} \,.
+\end{equation}
+Similarly, squaring the trombone tensor $\xi$ gives
 \begin{equation}\label{eq:xixiwitheta}
@@
 \begin{equation}
-	X_{\ov{MN}} \,X^{\ov{MN}}=21	\xi_{\ov M} \, \xi^{\ov M} - 2 \rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\right)^2 \,,
+	X_{\ov{MN}} \,X^{\ov{MN}}= 6\, \xi_{\ov M} \, \xi^{\ov M} - 2\, \rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\right)^2 \,,
 \end{equation}
@@
 \begin{equation}\label{eq:reltrX}
-	X_{\ov{MN}}\,X^{\ov{MN}} = 21\, \xi_{\ov M}\, \xi^{\ov M} - \frac1{1922}\left(X_{\ov M}{}^{\ov M}\right)^2 \,. 
+	X_{\ov{MN}}\,X^{\ov{MN}} = 6\, \xi_{\ov M}\, \xi^{\ov M} - \frac1{1922}\left(X_{\ov M}{}^{\ov M}\right)^2 \,. 
 \end{equation}
@@
 Note that this constraint is not implied by the quadratic constraint.
-To see this, simply observe that the theory with $\En{8}$ gauging has $X_{\ov{MN}}=\eta_{\ov{MN}}$ and $\xi_{\fl{M}} = 0$, violating \eqref{eq:reltrX}.
+To see this, simply observe that the theory with $\En{8}$ gauging has $X_{\ov{MN}}=\eta_{\ov{MN}}$ and $\xi_{\fl{M}} = 0$ \cite{Nicolai:2000sc,Nicolai:2001sv}, violating \eqref{eq:reltrX}.
 
@@
 \end{equation}
-Finally, comparing eq.~\eqref{eq:Lintexpansion} and~\eqref{eq:Vexpansion}, the parameters are fixed to
-\begin{equation}
-	\alpha = \frac{\rho^{2}}{28}\,,\quad \beta = \frac{\rho^{2}}{2}\,,\quad a=1\,,\quad \delta=\frac{13}{28}\,\rho^{2}\,. %, \quad \gamma=0.
+Finally, by requiring
+\begin{equation}
+	\sqrt{|g|} \mathscr{L}_{\rm int} \underset{\rm gSS}{=} - \sqrt{|\mathring{g}|} V \,,
+\end{equation}
+the parameters in \eqref{eq:Lintexpansion} and \eqref{eq:Vexpansion} are fixed to
+\begin{equation}
+	\alpha = \frac{1}{28}\,,\quad \beta = \frac{1}{2}\,,\quad a=1\,,\quad \delta=\frac{13}{28} \,. %, \quad \gamma=0.
 \end{equation}
@@
 
-\CE{Some formula used to derive the previous equations:
-\begin{equation}
-	\begin{aligned}
-		\M^{\fl{MP}}\M^{\fl{NQ}}f_{\fl{PQ}}{}^{\fl{K}}&=-f^{\fl{MN}}{}_{\fl{L}}\,\M^{\fl{LK}},\\
-		{\rm Ad\ invariance:}\quad 2\,\Gamma_{\fl{K}[\fl{M}}{}^{\fl{L}}\,f_{\fl{N}]\fl{L}}{}^{\fl{P}}&= -f_{\fl{MN}}{}^{\fl{L}}\,\Gamma_{\fl{KL}}{}^{\fl{P}}\,,\\
-		{\rm No\ trombone:}\quad \UI_{\fl{M}}{}^{M}\partial_{M}\ln(\rho)&= -\frac{1}{2}\,\Gamma_{\fl{KM}}{}^{\fl{K}},\\
-		{\rm Eq.~\eqref{eq:sectionconstraints}}\ \implies \ f^{\fl{K}}{}_{\fl{MP}}f^{\fl{PL}}{}_{\fl{N}}\,\partial_{\fl{K}}\otimes\partial_{\fl{L}} &= 2\,\partial_{(\fl{M}}\otimes\partial_{\fl{N})}\,.
-	\end{aligned}
-\end{equation}
-}
+%\CE{Some formula used to derive the previous equations:
+%\begin{equation}
+%	\begin{aligned}
+%		\M^{\fl{MP}}\M^{\fl{NQ}}f_{\fl{PQ}}{}^{\fl{K}}&=-f^{\fl{MN}}{}_{\fl{L}}\,\M^{\fl{LK}},\\
+%		{\rm Ad\ invariance:}\quad 2\,\Gamma_{\fl{K}[\fl{M}}{}^{\fl{L}}\,f_{\fl{N}]\fl{L}}{}^{\fl{P}}&= -f_{\fl{MN}}{}^{\fl{L}}\,\Gamma_{\fl{KL}}{}^{\fl{P}}\,,\\
+%		{\rm No\ trombone:}\quad \UI_{\fl{M}}{}^{M}\partial_{M}\ln(\rho)&= -\frac{1}{2}\,\Gamma_{\fl{KM}}{}^{\fl{K}},\\
+%		{\rm Eq.~\eqref{eq:sectionconstraints}}\ \implies \ f^{\fl{K}}{}_{\fl{MP}}f^{\fl{PL}}{}_{\fl{N}}\,\partial_{\fl{K}}\otimes\partial_{\fl{L}} &= 2\,\partial_{(\fl{M}}\otimes\partial_{\fl{N})}\,.
+%	\end{aligned}
+%\end{equation}
+%}
 
@@
 \end{equation}
-\CE{(A word on the 3d linear and quadratic constraints?)}
+As in higher dimensions, $X_{\ov{M}\ov{N}}$ obtained from \eqref{eq:GenLeibniz} automatically satisfies the linear constraint of the 3-dimensional maximal gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv}, and the section condition implies the quadratic constraints for $X_{\ov{M}\ov{N}}$.
 
@@
 \subsection{Ruling out gaugings}
+\EM{Let's check the $\GL{6} \times \SO{2,2}$ gauging (half-maximal embedded in maximal)....}
 
@@
 In order to construct the consistent truncation around the ${\cal N}=(4,4)$ AdS$_3 \times S^3 \times S^3 \times S^1$ vacuum of IIB supergravity, a promising starting point is the dyonic $S^3 \times S^3$ truncation of IIB supergravity constructed in \cite{Inverso:2016eet}, and further reducing this on $S^1$.
-However, this will not give the correct AdS$_3$ vacuum since the truncation is missing the 7-form flux on $S^3 \times S^3 \times S^1$ that is required.
-Indeed, the 3-dimensional gauged supergravity that would be obtained as discussed way \CE{(?)} does not have any AdS$_3$ vacua.
+However, this will not give the correct AdS$_3$ vacuum since the truncation is missing the required 7-form flux on $S^3 \times S^3 \times S^1$.
+Indeed, the 3-dimensional gauged supergravity that would be obtained this way does not have any AdS$_3$ vacua.
 We can remedy this situation by defining a new consistent truncation by adding a 7-form flux to the one obtained from the $S^3 \times S^3$ reduction constructed in $\En{7}$ ExFT.
 
-This motivates the following question, given a consistent truncation, i.e.
+This motivates the following question: Given a consistent truncation, i.e.
 $\cU_{\fl{M}}{}^M$, satisfying \eqref{eq:GenLeibniz}, when can we add a new flux component of string theory to the compactification to obtain a new consistent truncation?
-Adding a new flux component to the truncation is equivalent to twisting the generalised frame as follows
+Adding a new flux component to the truncation is equivalent to twisting the generalised frame as follows \EM{Email DW and MP to ask who we should cite for this?}
 \begin{equation} \label{eq:Twisting}
@@
 \end{equation}
-and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ is already constant. Therefore, we have a consistent truncation if and only iff $\rho^{-1}\, F_{\fl{M}\fl{N}}{}^{\fl{P}}$ is constant.
-
-A particularly simple way of having constant $\rho^{-1}\, F_{\fl{M}\fl{N}}{}^{\fl{P}}$ is to consider fluxes which are stabilised by the twist matrix $U_M{}^{\fl{M}}$.
-The twist matrix typically only lives in a subgroup $G \subset \EE$.
+and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ is already constant. Therefore, we have a consistent truncation if and only if $\rho^{-1}\, F_{\fl{M}\fl{N}}{}^{\fl{P}}$ is constant.
+
+A particularly simple way of having constant $\rho^{-1}\, F_{\fl{M}\fl{N}}{}^{\fl{P}}$ is to switch on fluxes which are stabilised by the twist matrix $U_M{}^{\fl{M}}$, which typically only lives in a subgroup $G \subset \EE$.
 Therefore, in this case, we can simply tune the $G$-singlet components of the flux $F_{MN}{}^P$ to be proportional to $\rho$ to obtain a new consistent truncation.
@@
 \subsection{Adding fluxes to the $S^3$ truncation of 6-dimensional supergravity} \label{s:S3Flux}
-Before dealing with the $S^3 \times S^3 \times S^1$ truncation, let us demonstrate this methodology for the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity on $S^3$, which was constructed in \cite{Eloy:2021fhc}.
+As a warm-up for the $S^3 \times S^3 \times S^1$ truncation, let us demonstrate this methodology for the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity on $S^3$, which was constructed in \cite{Eloy:2021fhc}.
 As discussed in \cite{Eloy:2021fhc}, the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity to 3-dimensional half-maximal gauged supergravity can be described using the $\SO{8,4}$ ExFT \cite{Hohm:2017wtr,Samtleben:2019zrh}.
@@
 \subsubsection{The $S^3$ twist matrix}
-Since it will play a role throughout this paper, we will begin by giving the $\SL{4} \simeq \SO{3,3}$ twist matrix that describes the consistent truncation on $S^3$.
-Here, we give a slightly different, but equivalent, form of the twist matrix constructed in \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou} for the consistent truncation on $S^n$.
-
-\EM{Maybe even move this $\SL{n+1}$ ExFT to the review section?}
+\EM{Move to appendix?!?!}\\
+Since we will use it throughout this paper, let us construct the $\SL{4} \simeq \SO{3,3}$ twist matrix that describes the consistent truncation on $S^3$.
+This can be viewed as a special case of a family of consistent truncations on $S^n$ \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou}.
+Here, we give a slightly different, but equivalent, form of this construction.
+
 We use an $\SL{n+1}$ ExFT, like in \cite{Lee:2014mla}, which encodes an $n$-dimensional metric and volume-form flux, i.e.
-Freund-Rubin compactifications, and is thus a natural description of $S^n$ compactifications.
+Freund-Rubin compactifications, and thus gives a natural description of $S^n$ compactifications.
 The $\SL{n+1}$ ExFT formally has coordinates in the antisymmetric representation of $\SL{n+1}$, $y^{IJ} = - y^{JI}$, with $I = 1, \ldots, n+1$, and similarly, generalised vector fields transform in the antisymmetric representation of $\SL{n+1}$.
@@
 \end{equation}
-is the volume form on $S^n$. The frame in \eqref{eq:SnFrame} has the important property that the $n+1$ generalised tensors are nowhere vanishing since $dY^I = 0$ only when $Y^I = 1$.
+is the volume form on $S^n$.
+The frame in \eqref{eq:SnFrame} has the important property that the $n+1$ generalised tensors are nowhere vanishing since $dY^I = 0$ only when $Y^I = 1$.
+Therefore, \eqref{eq:SnFrame} provides a generalised parallelisation of $S^n$ in the $\SL{n+1}$ ExFT.
 
@@
 \begin{equation} \label{eq:SLnFrame}
-	U_I{}^{\fl{I}} = \rho^{2/(n+1)}\, \cU_I{}^{\fl{I}} \,.
+	U_I{}^{\fl{I}} = \rho^{2/(n+1)}\, \cU_I{}^{\fl{I}} \,,
 \end{equation}
@@
 \subsubsection{Adding flux}
-To demonstrate our methodology, we will now show how the parameter $\lambda$ introduced in \cite{Eloy:2021fhc} can be obtained by the twisting procedure outlined in \ref{s:AddFlux}.
-Let us decompose $\SO{4,4} \rightarrow \SO{3,3} \times \SO{1,1}$, such that
+To demonstrate our methodology, we will now show how the parameter $\lambda$ introduced in \cite{Eloy:2021fhc} can be obtained by the twisting procedure described above.
+Thus, we want to consider the $\SO{3,3} \subset \SO{4,4}$ twist matrix corresponding to $S^3$ \eqref{eq:SLnTwist} and add a 3-form flux via a $\SO{4,4}$ twist.
+We begin by decomposing $\SO{4,4} \rightarrow \SO{3,3} \times \SO{1,1}$, such that
 \begin{equation}
@@
 Decomposing with respect to the geometric $\SL{3} \times \mathbb{R}^+$ of the $S^3$,  the coordinates on $S^3$ live in the $Y^A = \left( y^i,\, y_i \right)$, $i = 1, 2, 3$, while $C_A = \left( C_i,\, C^i \right)$ naturally contains a 2-form $C^i$.
-The field strength $H_3 = \partial^A C_A = \partial_i C^i$ is a singlet of $\SO{3,3}$ and thus we see that $F_{AB}{}^C$ in \eqref{eq:FlatF} is constant \CE{(what about the $\rho$ factor?)} and we obtain a consistent truncation with a new 3-form flux.
+The field strength $H_3 = \partial^A C_A = \partial_i C^i$ is a singlet of $\SO{3,3}$ and thus we see that $\rho^{-1} F_{\ov{M}\ov{N}}{}^{\ov{P}}$ in \eqref{eq:FlatF} is constant and we obtain a consistent truncation with a new 3-form flux.
 Evaluating the twist matrix
@@
 \end{equation}
-explicitly using \eqref{eq:C2S3example} and setting $C^i = \lambda\, \xi^i$ in the notation of \cite{Eloy:2021fhc}, we obtain precisely the twist matrix used in \cite{Eloy:2021fhc} for the consistent truncation of 6-dimensional ${\cal N}=(1,1)$ supergravity on $S^3$ with $H_3$ flux.
-\EM{Give precise form of $C^i$ such that we recover $\lambda$?}
+explicitly using \eqref{eq:C2S3example} and setting $C^i = \lambda\, \xi^i$, with $\nabla_i \xi^i = 1$, in the notation of \cite{Eloy:2021fhc}, we obtain precisely the twist matrix used in \cite{Eloy:2021fhc} for the consistent truncation of 6-dimensional ${\cal N}=(1,1)$ supergravity on $S^3$ with $H_3$ flux.
+%\EM{Give precise form of $C^i$ such that we recover $\lambda$?}
 
@@
 \subsection{Adding flux to the $S^3 \times S^3 \times S^1$ truncation of IIB supergravity}
-Our strategy for constructing the consistent truncation on $S^3 \times S^3 \times S^1$ with 7-form flux is to embed the $S^3 \times S^3$ truncation of $\En{7}$ ExFT \cite{Inverso:2017lrz} into $\EE \rightarrow \En{7} \times \SL{2}$, as described in \cite{Galli:2022idq} to generate the consistent truncation on $S^3 \times S^3 \times S^1$ without 7-form flux.
-We then add a 7-form flux to this truncation as outlined above.
+Our strategy for constructing the consistent truncation on $S^3 \times S^3 \times S^1$ with 7-form flux is to embed the $S^3 \times S^3$ truncation of $\En{7}$ ExFT \cite{Inverso:2016eet} into $\EE \rightarrow \En{7} \times \SL{2}$, as described in \cite{Galli:2022idq}.
+This will give us the consistent truncation on $S^3 \times S^3 \times S^1$ without 7-form flux.
+Then we add a 7-form flux to this truncation as outlined above.
 
 \subsubsection{The $S^3 \times S^3$ truncation} \label{s:S3S3}
-Let us first review the dyonic $S^3 \times S^3$ truncation of IIB supergravity \cite{Inverso:2017lrz}, which forms the starting point of our construction.
-The key step in the construction of \cite{Inverso:2017lrz} is that we can use the $\SL{4}$ generalised frame \eqref{eq:SLnFrame} to form a generalised Leibniz parallelisation of $\En{7}$ via the embedding
-\begin{equation}
-	\En{7} \rightarrow \SL{8} \rightarrow \SL{4} \times \SL{4} \times \mathbb{R}^+ \,.
+Let us first review the dyonic $S^3 \times S^3$ truncation of IIB supergravity \cite{Inverso:2016eet}, which forms the starting point of our construction.
+The key step in the construction of \cite{Inverso:2016eet} is that we can use the $\SL{4}$ generalised frame \eqref{eq:SLnFrame} to form a generalised Leibniz parallelisation of $\En{7}$ via the embedding
+\begin{equation} \label{eq:SL4Embedding}
+	\En{7} \rightarrow \SL{8} \rightarrow \SL{4}_1 \times \SL{4}_2 \times \mathbb{R}^+ \,.
 \end{equation}
@@
 \end{equation}
-where the first square brackets denote the branching of the $\mathbf{28}$ under $\SL{4} \times \SL{4} \times \mathbb{R}^+$ and the second square brackets that of the $\mathbf{\overline{28}}$.
-Crucially, for the generalised Leibniz condition \eqref{eq:GenLeibniz} to hold, the coordinates and generalised vector fields corresponding to the two $\SL{4}$'s must be embedded within the $\mathbf{28}$ and $\mathbf{\overline{28}}$, respectively, which we will call ``electric'' and ``magnetic'' coordinates, following \cite{Inverso:2017lrz}.
+where the first square brackets denote the branching of the $\mathbf{28}$ under $\SL{4}_1 \times \SL{4}_2 \times \mathbb{R}^+$ and the second square brackets that of the $\mathbf{\overline{28}}$.
+Crucially, for the generalised Leibniz condition \eqref{eq:GenLeibniz} to hold, the coordinates and generalised vector fields corresponding to the $\SL{4}_1$ and $\SL{4}_2$ must be embedded within the $\mathbf{28}$ and $\mathbf{\overline{28}}$, respectively, which we will call ``electric'' and ``magnetic'' coordinates, following \cite{Inverso:2016eet}.
 Thus, we write the 56 $\En{7}$ coordinates as
@@
 with $\cA, \cB = 1, \ldots, 8$ labelling the fundamental of $\SL{8}$, corresponding to the decomposition $\En{7} \rightarrow \SL{8}$.
-Following the conventions of \cite{Inverso:2017lrz}, the coordinates of the two $\SL{4}$ ExFTs are embedded as $Y^{IJ} \subset Y^{\cA\cB}$, with $I, J = 1, 2, 3, 8$, and $Y_{AB} \subset Y_{\cA\cB}$, with $A, B = 4, 5, 6, 7$.
+Following the conventions of \cite{Inverso:2016eet}, the coordinates of the two $\SL{4}$ ExFTs are embedded as $Y^{IJ} \subset Y^{\cA\cB}$, with $I, J = 1, 2, 3, 8$, and $Y_{AB} \subset Y_{\cA\cB}$, with $A, B = 4, 5, 6, 7$.
 Solving the $\SL{4}$ ExFT section condition for $Y^{IJ}$ and $Y_{AB}$ guarantees a solution to the $\En{7}$ ExFT, and we choose the solution where the six physical coordinates of IIB are
@@
 \end{equation}
-
-We can now use one copy of the $\SL{4}$ frame \eqref{eq:SLnFrame} for each $\SL{4}$ subgroup to construct a generalised parallelisation for the full $\En{7}$ ExFT, with an embedding tensor via \eqref{eq:GenLeibniz} \EM{given by \ldots}.
+This solution of the section condition defines the ``geometric'' $\SL{3}_1 \times \mathbb{R}^+_1 \subset \SL{4}_1$ and $\SL{3}_2 \times \mathbb{R}^+_2 \subset \SL{4}_2$ subgroups, that will play an important role soon.
+
+We can now use one copy of the $\SL{4}$ frame \eqref{eq:SLnFrame} for each $\SL{4}$ subgroup of \eqref{eq:SL4Embedding} to construct a generalised parallelisation for the full $\En{7}$ ExFT, with an embedding tensor via \eqref{eq:GenLeibniz} \EM{given by \ldots}.
 
@@
 
+\EM{What we should actually do: Read this and next section again and make sure they make sense.
+Maybe when referring to the $\SL{3}$ subgroups in the next section, we can cite \eqref{eq:PhysicalCoords}}
+
 \CE{(Add $\alpha$ here?)}
@@
 \subsubsection{The $S^3 \times S^3 \times S^1$ truncation} \label{s:S3S3S1}
-We now construct the consistent truncation on $S^3 \times S^3 \times S^1$ by embedding the $\En{7}$ twist matrix corresponding to the $S^3 \times S^3$ truncation reviewed above \ref{s:S3S3} in $\EE$ via the branching $\EE \rightarrow \En{7} \times \SL{2}$, such that $\mathbf{248} \rightarrow \mathbf{\left(133,1\right)} \oplus \mathbf{\left(56,2\right)} \oplus \mathbf{\left(1,3\right)}$.
-As explained in \cite{Galli:2022idq}, we can construct a consistent truncation on $M \times S^1$ to 3-dimensional gauged supergravity by embedding a consistent truncation on $M$ to 4-dimensional supergravity, characterised by a $\En{7}$ twist matrix, as follows.
-The $\EE$ twist matrix is parameterised by the $\En{7}$ twist matrix describing the consistent truncation on $M$ and the $\SL{2}$ twist matrix given by
+We now construct the consistent truncation on $S^3 \times S^3 \times S^1$ by embedding the $\En{7}$ twist matrix corresponding to the $S^3 \times S^3$ truncation reviewed above in \ref{s:S3S3} in $\EE$ via the branching $\EE \rightarrow \En{7} \times \SL{2}$, such that $\mathbf{248} \rightarrow \mathbf{\left(133,1\right)} \oplus \mathbf{\left(56,2\right)} \oplus \mathbf{\left(1,3\right)}$.
+As explained in \cite{Galli:2022idq}, we can construct a consistent truncation on $M \times S^1$ to 3-dimensional gauged supergravity by embedding a consistent truncation on $M$ to 4-dimensional supergravity, characterised by an $\En{7}$ twist matrix and $\En{7}$ scalar density $\sigma$, as well as
+%as follows. The $\EE$ twist matrix is parameterised by the $\En{7}$ twist matrix describing the consistent truncation on $M$ and 
+the $\SL{2}$ twist matrix given by
 \begin{equation}
@@
 		\sigma & 0 \\ 0 & \sigma^{-1}
-	\end{pmatrix} \,,
-\end{equation}
-where $\sigma$ is the $\En{7}$ scalar density used to construct the $\En{7}$ truncation on $M$.
-Finally, the $\EE$ scalar density satisfies $\rho = \sigma^2$ to ensure a consistent truncation on $S^3 \times S^3 \times S^1$.
-However, we still need to add the 7-form flux to obtain the ${\cal N}=(4,4)$ AdS$_3$ vacuum we are looking for.
+	\end{pmatrix} \,.
+\end{equation}
+Finally, the $\EE$ scalar density satisfies $\rho = \sigma^2$ to ensure a consistent truncation on $M \times S^1$.
+
+Employing this procedure for $M = S^3 \times S^3$, gives us the consistent truncation on $S^3 \times S^3 \times S^1$.
+However, this does not have any AdS$_3$ vacua, since we still need to add the 7-form flux.
 To do this, let us first review the group theory of the $S^3 \times S^3$ truncation, since this will allow us to determine whether the 7-form flux is stabilised by the twist matrix.
@@
 %We now wish to add a 7-form flux to the $S^3 \times S^3 \times S^1$ truncation constructed above.
-To add a 7-form flux to the above truncation, we will follow the logic laid out in section \ref{s:AddFlux}, i.e.
-we will investigate whether the 7-form flux is stabilised by the twist matrix on $S^3 \times S^3 \times S^1$ constructed in section \ref{s:S3S3S1}.
+To add a 7-form flux to the above truncation, we need to determine whether the 7-form flux is stabilised by the twist matrix on $S^3 \times S^3 \times S^1$ constructed in section \ref{s:S3S3S1}.
 Thus, we need to understand
@@
 %We want to see if 
-whether IIB supergravity admits a 7-form field strength that is a singlet under these two $\SL{4}$ groups.
+whether IIB supergravity admits a 7-form field strength that is a singlet under the two $\SL{4}$ groups in \eqref{eq:SL4Embedding}.
 To answer this question, we pick a gauge where the 6-form potential lives entirely in $S^3 \times S^3$ but depends on the $S^1$ coordinate, $z$.
-Therefore, in this gauge choice, the 6-form potential corresponds to an adjoint generator of $\En{7}$, and since the $S^1$ coordinate is an $\En{7}$ singlet, this adjoint generator must be a singlet under $\SL{4} \times \SL{4} \subset \SL{8} \subset \En{7}$ in order for us to have a consistent truncation.
+Therefore, in this gauge choice, the 6-form potential corresponds to an adjoint generator of $\En{7}$, and since the $S^1$ coordinate is an $\En{7}$ singlet, this adjoint generator must be a singlet under $\SL{4}_1 \times \SL{4}_2 \subset \SL{8} \subset \En{7}$ for us to have a consistent truncation.
 
@@
 The 6-form doublet corresponds to the $\mathbf{\left(1,2\right)}_{6}$.
-To understand if one of the 6-forms in the doublet are singlets under $\SL{4} \times \SL{4} \subset \En{7}$, we must decompose $\En{7}$ with respect to the common subgroup of $\SL{4} \times \SL{4}$ and $\SL{6} \times \SL{2}$, which is $\SL{3}_1 \times \SL{3}_2 \times \mathbb{R}^+ \times \mathbb{R}^+$.
-The two $\SL{3}$ subgroups are defined by the embedding of the physical coordinates \eqref{eq:PhysicalCoords} into $\SL{4} \times \SL{4} \subset \SL{8} \subset \En{7}$.
-An important for us is to correctly identify the $\mathbb{R}^+$ charges in both decompositions.
+To understand if one of the 6-forms in the doublet are singlets under $\SL{4}_1 \times \SL{4}_2 \subset \En{7}$, we must decompose $\En{7}$ with respect to the common subgroup of $\SL{4}_1 \times \SL{4}_2$ and $\SL{6} \times \SL{2}$, which is $\SL{3}_1 \times \SL{3}_2 \times \mathbb{R}^+_1 \times \mathbb{R}^+_2$, as defined by the embedding of the physical coordinates in \eqref{eq:PhysicalCoords}.
+Important for us is the correct identification of the $\mathbb{R}^+$ charges in both decompositions.
 We have, on the one hand,
@@
 
-The branching of the adjoint \eqref{eq:AdjointSL6} under $\SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB}$ in \eqref{eq:SL6SL2} needs to now be compared with that via $\SL{4} \times \SL{4} \times \mathbb{R}^+_{\SL{8}}$, given by
+The branching of the adjoint \eqref{eq:AdjointSL6} under $\SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB}$ in \eqref{eq:SL6SL2} needs to now be compared with that via $\SL{4}_1 \times \SL{4}_2 \times \mathbb{R}^+_{\SL{8}}$, given by
 \begin{equation}
@@
 Using \eqref{eq:R+charges}, we can now identify each of the singlet generators $\left(1,1\right)_{\pm4}$ with one of the $\SL{2}$ doublet generators of charge $\mp 6$.
-Therefore, we find exactly one singlet $\SL{4} \times \SL{4}$ generator, which we can write as $t_{1238}$, corresponding to a 6-form potential.
-The other $\SL{4} \times \SL{4}$ singlet generator, $t_{4567}$, only differs by a compact generator and thus does not corresponding to a different physical field.
+Therefore, we find exactly one singlet $\SL{4}_1 \times \SL{4}_2$ generator, which we can write as $t_{1238}$, corresponding to a 6-form potential.
+The other $\SL{4}_1 \times \SL{4}_2$ singlet generator, $t_{4567}$, only differs by a compact generator and thus does not corresponding to a different physical field.
 Finally, the other elements of the $\SL{2}$ doublet of 6-form potential can be mapped to the $\mathbf{\left(4,\overline{4}\right)_{2}} \oplus \mathbf{\left(\overline{4},4\right)_{-2}}$ generators, specifically $t_7{}^8$ and $t_8{}^7$ and are clearly not $\SL{4}$ singlets.
@@
 \end{equation}
-with $C_M{}^N = \lambda\, z\, t_{1238\,M}{}^N$ and $\lambda$ a numerical parameter corresponding to the amount of 7-form flux.
-\EM{Is there a density factor that needs to be added?} \CE{Yes.} \EM{The resulting embedding tensor is \ldots}
+with $C_M{}^N = \lambda\, z\,\rho^{-1}\, t_{1238\,M}{}^N$ and $\lambda$ a numerical parameter corresponding to the amount of 7-form flux. \EM{The resulting embedding tensor is \ldots}
+
+\EM{Give embedding tensor components wrt the 3-d basis used for the moduli}\\
+\EM{Vacuum condition for $\lambda$}\\
+\EM{SUSY AdS$_3$ vacuum in 10-d}
 
@@
 
-\section{Moduli of AdS$_3 \times S^3 \times S^3 \times S^1$} \label{s:Moduli}
+\section{Moduli of \texorpdfstring{AdS$_3 \times S^3 \times S^3 \times S^1$}{AdS3xS3xS3xS1}} \label{s:Moduli}
+
+\paragraph{10d solution}
+Pure NSNS solution, after \cite{deBoer:1999gea}
+\begin{equation}
+	\begin{aligned}
+		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) + \alpha^{2}\,\d s^{2}\big(S^{3}\big)+\d s^{2}\big(\ts{S}^{3}\big)+\d\psi^{2},\\
+		H_{(3)} &= 2\left(\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})+\alpha^{2}\,{\rm Vol}\big(S^{3}\big)+{\rm Vol}\big(\ts{S}^{3}\big)\right),
+	\end{aligned}
+\end{equation}
+with $H_{(3)} = \d B_{(2)}$ and
+\begin{equation}
+	\ell_{\rm AdS}^{2} = \frac{\alpha^{2}}{1+\alpha^{2}}.
+\end{equation}
+
+The three-dimensional solution preserves ${\cal N}=(4,4)$ supercharges.
+The isometry group is ${\cal G}=D^{1}(2,1;\alpha)_{\rm L}\times D^{1}(2,1;\alpha)_{\rm R}$, with two copies of the large ${\cal N}=4$ supergroup.
+The parameter $\alpha$ is given by the ratio of the $S^{3}$ spheres radii.
+The even part of $D^{1}(2,1;\alpha)$ is isomorphic to ${\rm SL}(2,\mathbb{R})\times{\rm SO}(3)\times\ts{{\rm SO}(3)}$ and the bosonic isometries of the ${\rm AdS}_{3}\times S^{3}\times\ts{S}^{3}$ background are built from the even part of ${\cal G}$.
+The ${\rm AdS}_{3}$ isometry group is ${\rm SO}(2,2)\simeq{\rm SL}(2,\mathbb{R})_{\rm L}\times{\rm SL}(2,\mathbb{R})_{\rm R}$, and the factors ${\rm SO}(3)_{\rm L}\times{\rm SO}(3)_{\rm R}\times\ts{{\rm SO}(3)}_{\rm L}\times\ts{{\rm SO}(3)}_{\rm R}\simeq{\rm SO}(4)\times\ts{SO(4)}$ combine into the isometry groups of the two spheres.
+
+The spectrum organizes into long representations of ${\cal G}$~\cite{Eberhardt:2017fsi}. The spectrum at the consistent truncation is the one of ref.~\cite{Hohm:2005ui}. \CE{What details do we need?}
 
 \subsection{Moduli in gauged supergravity}
+\paragraph{S-fold like deformations} Scalar spectrum:
+\begin{equation}
+	\begin{aligned}
+		(m_{(0)}\ell_{\rm AdS})^2:	\quad 
+		&8\ [1],\quad \frac{4\,\chi_{1}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{4\,\chi_{2}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{(\chi_{1}+\chi_{2})^{2}}{1+\alpha^{2}}\ [4], \quad \frac{(\chi_{1}-\chi_{2})^{2}}{1+\alpha^{2}}\ [4],	\\
+		&\frac{4\,\alpha^{2}\ts{\chi}_{1}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{4\,\alpha^{2}\ts{\chi}_{2}^{2}}{1+\alpha^{2}}\ [2], \quad \alpha^{2} \frac{(\ts{\chi}_{1}+\ts{\chi}_{2})^{2}}{1+\alpha^{2}}\ [4], \quad \alpha^{2} \frac{(\ts{\chi}_{1}-\ts{\chi}_{2})^{2}}{1+\alpha^{2}}\ [4],	\\
+		& \frac{\left(\chi_{1} + \chi_{2} \pm \alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2})\right)^{2}}{1+\alpha^{2}}\ [2+2], \quad \frac{\left(\chi_{1} - \chi_{2} \pm \alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2})\right)^{2}}{1+\alpha^{2}}\ [2+2],\\
+		&1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+		&1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2].
+	\end{aligned}
+\end{equation}
 
@@
 The seven form flux is unaffected by the deformations.
+
+\paragraph{S-fold like deformations}
+Using spherical coordinates for both spheres:
+\begin{equation}
+	\begin{aligned}
+		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^{2}({\rm AdS}_{3}) +\alpha^{2}\left(\d\theta^{2} + \cos^{2}(\theta)\,\kappa_{1}^{2} + \sin^{2}(\theta)\,\kappa_{2}^{2} \right) \\
+		&\quad +\d\ts{\theta}^{2} + \cos^{2}(\ts{\theta})\,\ts{\kappa}_{1}^{2} + \sin^{2}(\ts{\theta})\,\ts{\kappa}_{2}^{2} + \d\psi^{2}, \\[5pt]
+		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) + 2\,\alpha^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge\kappa_{1}\wedge\kappa_{2}+ 2\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge\ts{\kappa}_{1}\wedge\ts{\kappa}_{2},
+	\end{aligned}
+\end{equation}
+where
+\begin{equation}
+	\begin{aligned}
+		\kappa_{1} &= \d\phi_{1} + \chi_{1}\,\d\psi,\\
+		\kappa_{2} &= \d\phi_{2} - \chi_{2}\,\d\psi,\\
+		\ts{\kappa}_{1} &= \d\ts{\phi}_{1} + \ts{\chi}_{1}\,\d\psi,\\
+		\ts{\kappa}_{2} &= \d\ts{\phi}_{2} - \ts{\chi}_{2}\,\d\psi.
+	\end{aligned}
+\end{equation}
 

### 2023-06-05 Draft_3dH3.tex
Update end of section 5 (embedding tensor and 10d solution) and section 6 (deformation).

@@
 \usepackage{graphicx,tikz}
+\usetikzlibrary{arrows.meta,arrows}
 \usepackage{multirow}
@@
 with the potential%\footnote{To obtain this potential, one has to add the total derivative $-\partial_{M}\left(\sqrt{\vert g\vert}\,\partial_{N}\M^{MN}+(4/3)\,\M^{MN}\partial_{N}\sqrt{\vert g\vert}\right)$ to $\sqrt{\vert g\vert}\,\mathscr{L}_{\rm int}$.}
-\begin{equation}
+\begin{equation} \label{eq:3dpotential}
 	V = X_{\fl{MN}}\,X_{\fl{PQ}}\left(\frac{1}{28}\,\M^{\fl{MP}}\M^{\fl{NQ}}+\frac{1}{2}\,\M^{\fl{MP}}\eta^{\fl{NQ}}+\frac{13}{28}\,\eta^{\fl{MP}}\eta^{\fl{NQ}}\right).
@@
 The fundamental of $\En{7}$ then decomposes as
-\begin{equation}
+\begin{equation} \label{eq:56inSL4SL4}
 	\mathbf{56} \rightarrow \mathbf{28} \oplus \overline{\mathbf{28}} \rightarrow \left[ \mathbf{\left(6,1\right)_2} \oplus \mathbf{\left(1,6\right)_{-2}} \oplus \mathbf{\left(4,4\right)_0} \right] \oplus \left[ \mathbf{\left(6,1\right)_{-2}} \oplus \mathbf{\left(1,6\right)_{2}} \oplus \mathbf{\left(\overline{4},\overline{4}\right)_0} \right] \,,
@@
 Crucially, for the generalised Leibniz condition \eqref{eq:GenLeibniz} to hold, the coordinates and generalised vector fields corresponding to the $\SL{4}_1$ and $\SL{4}_2$ must be embedded within the $\mathbf{28}$ and $\mathbf{\overline{28}}$, respectively, which we will call ``electric'' and ``magnetic'' coordinates, following \cite{Inverso:2016eet}.
-Thus, we write the 56 $\En{7}$ coordinates as
+Thus, we write the 56 $\En{7}$ coordinates as \CE{($M$ already used for adjoint of \EE)}
 \begin{equation}
@@
 \end{equation}
-with $C_M{}^N = \lambda\, z\,\rho^{-1}\, t_{1238\,M}{}^N$ and $\lambda$ a numerical parameter corresponding to the amount of 7-form flux. \EM{The resulting embedding tensor is \ldots}
+with $C_M{}^N = \lambda\, z\,\rho^{-1}\, t_{1238\,M}{}^N$ and $\lambda$ a numerical parameter corresponding to the amount of 7-form flux.
+The resulting embedding tensor is most nicely written using the branching
+\begin{equation} \label{eq:248decompoinSL8}
+	\begin{aligned}
+		\EE & \longrightarrow E_{7(7)}\times {\rm SL}(2) \longrightarrow {\rm SL}(8) \times {\rm SL}(2) \\
+		\mathbf{248} & \ \tikz{\draw[arrows={->[scale=1.1]}] (0,0) -- (3.65
+	,0);}\  (\mathbf{63},\mathbf{1}) \oplus (\mathbf{70},\mathbf{1}) \oplus (\mathbf{28},\mathbf{2}) \oplus (\mathbf{\fl{28}},\mathbf{2}) \oplus (\mathbf{1},\mathbf{3}) \\
+		X^{\fl{M}} & \ \tikz{\draw[arrows={->[scale=1.1]}] (0,0) -- (3.65
+	,0);}\ \left\{X^{\fl{\cal A}}{}_{\fl{\cal B}},X^{\fl{\cal ABCD}},X^{\fl{\cal AB}\,\fl{i}},X_{\fl{\cal AB}}{}^{\fl{i}},X^{\fl{\alpha}}\right\},
+	\end{aligned}
+\end{equation}
+and has the following non-vanishing components:
+\begin{equation} \label{eq:embeddingtensor@origin}
+	\begin{aligned}
+		X_{(\mathbf{63},\mathbf{1});(\mathbf{28},\mathbf{2})}:&
+		\begin{cases}
+			\displaystyle X_{\fl{I}}{}^{\fl{J}}{}_{;\fl{KL}+}=-\frac{1}{\alpha}\,\delta_{\fl{I[K}}\delta_{\fl{L]}}{}^{\fl{J}},\\[7pt]
+			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;\fl{BJ}+}=-\frac{1}{2\alpha}\,\delta_{\fl{AB}}\delta_{\fl{J}}{}^{\fl{I}},\\
+		\end{cases} \\[5pt]
+		X_{(\mathbf{63},\mathbf{1});(\mathbf{\fl{28}},\mathbf{2})}:&
+		\begin{cases}
+			\displaystyle X_{\fl{A}}{}^{\fl{B}}{}_{;}{}^{\fl{CD}}{}_{+}=-\,\delta_{\fl{A}}{}^{\fl{[C}}\delta^{\fl{D]B}},\\[7pt]
+			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;}{}^{\fl{BJ}}{}_{+}=-\frac{1}{2}\,\delta_{\fl{A}}{}^{\fl{B}}\delta^{\fl{IJ}},\\
+		\end{cases} \\[5pt]
+		X_{(\mathbf{70},\mathbf{1});(\mathbf{1},\mathbf{3})}:&\  X_{\fl{IJKL};\fl{\alpha}} = -\frac{\lambda}{12\sqrt{6}}\,\varepsilon_{\fl{IJKL}}\,\delta_{\fl{\alpha}2},
+	\end{aligned}
+\end{equation}
+with the component $\fl{\alpha} = 2$ of the adjoint of ${\rm SL}(2)$ corresponding to the generator $e = \begin{pmatrix} 0 & 1 \\ 0 & 0\end{pmatrix}$ in the basis $\fl{i}=\{+,-\}$.
+With this embedding tensor, the potential~\eqref{eq:3dpotential} is stabilized at the scalar origin for $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$.
+We fix this value in the following.
 
@@
 
-%, which transform under the subgroup $\SL{6} \times \SL{2} \times \mathbb{R}^+_{IIB} \subset \En{7}$ as $\mathbf{\left(1,2\right)_{6}} \subset \mathbf{133}$
-
-%\EM{Describe how $C_6{}^\alpha$ sits in here}
-
-\section{Moduli of \texorpdfstring{AdS$_3 \times S^3 \times S^3 \times S^1$}{AdS3xS3xS3xS1}} \label{s:Moduli}
-
-\paragraph{10d solution}
-Pure NSNS solution, after \cite{deBoer:1999gea}
-\begin{equation}
-	\begin{aligned}
-		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) + \alpha^{2}\,\d s^{2}\big(S^{3}\big)+\d s^{2}\big(\ts{S}^{3}\big)+\d\psi^{2},\\
+\paragraph{} At $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$, the three-dimensional solution described by the embedding tensor~\eqref{eq:embeddingtensor@origin} corresponds to the consistent truncation of the pure NSNS ten-dimensional solution ~\cite{deBoer:1999gea}
+\begin{equation}
+	\begin{aligned}
+		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) + \alpha^{2}\,\d s^{2}\big(S^{3}\big)+\d s^{2}\big(\ts{S}^{3}\big)+\d z^{2},\\
 		H_{(3)} &= 2\left(\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})+\alpha^{2}\,{\rm Vol}\big(S^{3}\big)+{\rm Vol}\big(\ts{S}^{3}\big)\right),
@@
 \end{equation}
-with $H_{(3)} = \d B_{(2)}$ and
+with $H_{(3)} = \d B_{(2)}$ and \CE{(with the normalization in eq.~\eqref{eq:3dpotential} and $\ell_{\rm AdS}^{2}=2/V_{0}$, the code gives an additional factor $1/2$)}
 \begin{equation}
@@
 \end{equation}
-
-The three-dimensional solution preserves ${\cal N}=(4,4)$ supercharges.
-The isometry group is ${\cal G}=D^{1}(2,1;\alpha)_{\rm L}\times D^{1}(2,1;\alpha)_{\rm R}$, with two copies of the large ${\cal N}=4$ supergroup.
-The parameter $\alpha$ is given by the ratio of the $S^{3}$ spheres radii.
+The $S^{1}$ coordinate $z$ has periodicity $z\rightarrow z+1$. \CE{(add $S^{1}$ modulus here?)}
+
+\paragraph{}
+The 3d solution preserves ${\cal N}=(4,4)$ supercharges, with isometry group ${\cal G}=D^{1}(2,1;\alpha)_{\rm L}\times D^{1}(2,1;\alpha)_{\rm R}$, \textit{i.e.} two copies of the large ${\cal N}=4$ supergroup.
 The even part of $D^{1}(2,1;\alpha)$ is isomorphic to ${\rm SL}(2,\mathbb{R})\times{\rm SO}(3)\times\ts{{\rm SO}(3)}$ and the bosonic isometries of the ${\rm AdS}_{3}\times S^{3}\times\ts{S}^{3}$ background are built from the even part of ${\cal G}$.
 The ${\rm AdS}_{3}$ isometry group is ${\rm SO}(2,2)\simeq{\rm SL}(2,\mathbb{R})_{\rm L}\times{\rm SL}(2,\mathbb{R})_{\rm R}$, and the factors ${\rm SO}(3)_{\rm L}\times{\rm SO}(3)_{\rm R}\times\ts{{\rm SO}(3)}_{\rm L}\times\ts{{\rm SO}(3)}_{\rm R}\simeq{\rm SO}(4)\times\ts{SO(4)}$ combine into the isometry groups of the two spheres.
-
-The spectrum organizes into long representations of ${\cal G}$~\cite{Eberhardt:2017fsi}. The spectrum at the consistent truncation is the one of ref.~\cite{Hohm:2005ui}. \CE{What details do we need?}
+The spectrum organizes into representations $\left[\ell,\ts{\ell},\ell,\ts{\ell}\right]$ of ${\cal G}$~\cite{Eberhardt:2017fsi}, where $\ell$ and $\ts{\ell}$ label the levels on the two $S^{3}$.
+The highest-weight state of each representation has conformal dimension \CE{(check all this)}
+\begin{equation}
+	\Delta_{\ell,\ts{\ell},n} = 3 + \sqrt{1 + \frac{\ell(\ell+1)+\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi\,n)^{2}}{1+\alpha^{2}}},
+\end{equation}
+with $n$ corresponding to the $S^{1}$ harmonics.
+The spectrum at the consistent truncation is the one of ref.~\cite{Hohm:2005ui}.
+\CE{(give $\ell,\ts{\ell},n$?
+Distinguish between short and long multiplets?
+What details do we need?)}
+
+%, which transform under the subgroup $\SL{6} \times \SL{2} \times \mathbb{R}^+_{IIB} \subset \En{7}$ as $\mathbf{\left(1,2\right)_{6}} \subset \mathbf{133}$
+
+%\EM{Describe how $C_6{}^\alpha$ sits in here}
+
+\section{Moduli of \texorpdfstring{AdS$_3 \times S^3 \times S^3 \times S^1$}{AdS3xS3xS3xS1}} \label{s:Moduli}
 
 \subsection{Moduli in gauged supergravity}
+We identified a 11-parameter family of solutions, connected to the origin and given by the \EE coset representative \CE{($\fl{28}\leftrightarrow28$ compared to the code, I think we made a mistake and confused down and up indices)}
+\begin{equation}
+	\begin{aligned}
+		{\cal V}_{\rm def} &= \exp\left[\sqrt{2}\left(\chi_{1}\big(t_{(\mathbf{28},\mathbf{2})}\big)_{23,-}+\chi_{2}\big(t_{(\mathbf{28},\mathbf{2})}\big)_{81,-}+\ts{\chi}_{1}\big(t_{(\mathbf{\fl{28}},\mathbf{2})}\big)_{56,-}+\ts{\chi}_{2}\big(t_{(\mathbf{\fl{28}},\mathbf{2})}\big)_{74,-}\right)\right] \\
+		& \times \exp\left[\sqrt{2}\left(\zeta_{1}\big(t_{(\mathbf{\fl{28}},\mathbf{2})}\big)_{23,+}+\zeta_{2}\big(t_{(\mathbf{\fl{28}},\mathbf{2})}\big)_{81,+}+\ts{\zeta}_{1}\big(t_{(\mathbf{28},\mathbf{2})}\big)_{56,+}+\ts{\zeta}_{2}\big(t_{(\mathbf{28},\mathbf{2})}\big)_{74,+}\right)\right] \\
+		& \times \exp\bigg[\Omega\left(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{1}{}^{1}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{2}{}^{2}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{3}{}^{3}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{8}{}^{8}\right)\\
+		&\ \qquad+\ts{\Omega}\left(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{4}{}^{4}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{5}{}^{5}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{6}{}^{6}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{7}{}^{7}\right)\bigg] \\
+		& \times \exp\left[\ln(T)\left(\frac{1}{120}\,\big(t_{(\mathbf{63},\mathbf{1})}\big)_{I}{}^{I}-\frac{1}{120}\,\big(t_{(\mathbf{63},\mathbf{1})}\big)_{A}{}^{A}-\frac{1}{2}\,\big(t_{(\mathbf{1},\mathbf{3})}\big)_{1}\right)\right],
+	\end{aligned}
+\end{equation}
+where we denoted the generators according to the decomposition~\eqref{eq:248decompoinSL8}.
+The $(\chi_{i},\ts{\chi}_{i},\zeta_{i},\ts{\zeta}_{i})$ deformations excite the $(\mathbf{6},\mathbf{1})_{2}$ and $(\mathbf{1},\mathbf{6})_{2}$ generators in the branching~\eqref{eq:56inSL4SL4}.
+\CE{(Describe what we do for $T$?
+I think there is some freedom in the coeff there.)} \CE{(Describe what we do for $\Omega$?
+Possible to change the signs to $(+,+,-,-)$, but very long to compute uplift.)}
+
 \paragraph{S-fold like deformations} Scalar spectrum:
@@
 \subsection{Moduli in 10 dimensions}
-\MG{Maybe we recall what the vacuum at the origin is here and reference somebody?}
 The seven form flux is unaffected by the deformations.
 
-\paragraph{S-fold like deformations}
+\paragraph{S-fold like deformations (only $(\chi, \ts{\chi})$)}
 Using spherical coordinates for both spheres:
@@
 	\begin{aligned}
-		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^{2}({\rm AdS}_{3}) +\alpha^{2}\left(\d\theta^{2} + \cos^{2}(\theta)\,\kappa_{1}^{2} + \sin^{2}(\theta)\,\kappa_{2}^{2} \right) \\
-		&\quad +\d\ts{\theta}^{2} + \cos^{2}(\ts{\theta})\,\ts{\kappa}_{1}^{2} + \sin^{2}(\ts{\theta})\,\ts{\kappa}_{2}^{2} + \d\psi^{2}, \\[5pt]
-		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) + 2\,\alpha^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge\kappa_{1}\wedge\kappa_{2}+ 2\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge\ts{\kappa}_{1}\wedge\ts{\kappa}_{2},
+		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^{2}({\rm AdS}_{3}) +\alpha^{2}\left(\d\theta^{2} + \cos^{2}(\theta)\,\d\phi'_{1}{}^{2} + \sin^{2}(\theta)\,\d\phi'_{2}{}^{2} \right) \\
+		&\quad +\d\ts{\theta}^{2} + \cos^{2}(\ts{\theta})\,\d\ts{\phi}'_{1}{}^{2} + \sin^{2}(\ts{\theta})\,\d\ts{\phi}'_{2}{}^{2} + \d z^{2}, \\[5pt]
+		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) + 2\,\alpha^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge\d\phi'_{1}\wedge\d\phi'_{2}+ 2\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge\d\ts{\phi}'_{1}\wedge\d\ts{\phi}'_{2},
 	\end{aligned}
@@
 	\begin{aligned}
-		\kappa_{1} &= \d\phi_{1} + \chi_{1}\,\d\psi,\\
-		\kappa_{2} &= \d\phi_{2} - \chi_{2}\,\d\psi,\\
-		\ts{\kappa}_{1} &= \d\ts{\phi}_{1} + \ts{\chi}_{1}\,\d\psi,\\
-		\ts{\kappa}_{2} &= \d\ts{\phi}_{2} - \ts{\chi}_{2}\,\d\psi.
+		\d\phi'_{1} &= \d\phi_{1} + \chi_{1}\,\d z,\\
+		\d\phi'_{2} &= \d\phi_{2} + \chi_{2}\,\d z,\\
+		\d\ts{\phi}'_{1} &= \d\ts{\phi}_{1} + \ts{\chi}_{1}\,\d z,\\
+		\d\ts{\phi}'_{2} &= \d\ts{\phi}_{2} + \ts{\chi}_{2}\,\d z.
 	\end{aligned}

### 2023-06-06 Draft_3dH3.tex
Update of the end of sec. 5 with more details on the round solution. Update of sec. 6 with the effect of chi, T on the spectrum. Added app. A on the multiplets of D21a.

@@
 \usepackage{mathrsfs}
+\usepackage{nicefrac}
 
@@
 The ${\rm AdS}_{3}$ isometry group is ${\rm SO}(2,2)\simeq{\rm SL}(2,\mathbb{R})_{\rm L}\times{\rm SL}(2,\mathbb{R})_{\rm R}$, and the factors ${\rm SO}(3)_{\rm L}\times{\rm SO}(3)_{\rm R}\times\ts{{\rm SO}(3)}_{\rm L}\times\ts{{\rm SO}(3)}_{\rm R}\simeq{\rm SO}(4)\times\ts{SO(4)}$ combine into the isometry groups of the two spheres.
-The spectrum organizes into representations $\left[\ell,\ts{\ell},\ell,\ts{\ell}\right]$ of ${\cal G}$~\cite{Eberhardt:2017fsi}, where $\ell$ and $\ts{\ell}$ label the levels on the two $S^{3}$.
-The highest-weight state of each representation has conformal dimension \CE{(check all this)}
-\begin{equation}
-	\Delta_{\ell,\ts{\ell},n} = 3 + \sqrt{1 + \frac{\ell(\ell+1)+\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi\,n)^{2}}{1+\alpha^{2}}},
-\end{equation}
-with $n$ corresponding to the $S^{1}$ harmonics.
-The spectrum at the consistent truncation is the one of ref.~\cite{Hohm:2005ui}.
-\CE{(give $\ell,\ts{\ell},n$?
-Distinguish between short and long multiplets?
-What details do we need?)}
+The spectrum organizes into multiplets of ${\cal G}$, made out of products of long representations $[\ell,\ts{\ell}]$ of $D^{1}(2,1;\alpha)$ (see app.~\ref{app:d21a} for a review of the representations of $D^{1}(2,1;\alpha)$).
+Explicitly, the spectrum is~\cite{Eberhardt:2017fsi}
+\begin{equation} \label{eq:spectrumorigin}
+	\bigoplus_{\ell,\ts{\ell}\geq0} [\ell,\ts{\ell}]\otimes[\ell,\ts{\ell}] \ \ominus\ [0,0]_{\rm s} \otimes [0,0]_{\rm s}.
+\end{equation}
+In each factor the lowest conformal dimension is
+\begin{equation}
+	h_{\rm L} = h_{\rm R} = -\frac{1}{2} + \frac{1}{2}\sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}},
+\end{equation}
+with $n$ corresponding to the $S^{1}$ harmonics, and the lowest conformal dimension of $[\ell,\ts{\ell}]\otimes[\ell,\ts{\ell}]$ is then
+\begin{equation} \label{eq:confdims3s3s1}
+	\Delta_{\ell,\,\ts{\ell},\,n} = h_{\rm L} + h_{\rm R} = - 1 + \sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}}.
+\end{equation}
+ For $n=0$, the representations get shortened whenever $\ell = \ts{\ell}$.
+The spectrum at the consistent truncation is then the one of ref.~\cite{Hohm:2005ui}.
+It corresponds to $\ell=\ts{\ell}=n=0$ in eq.~\eqref{eq:spectrumorigin}:
+ \begin{equation}
+ 	[0,0]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \oplus [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [0,0]_{\rm s} \oplus [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}.
+ \end{equation}
+ The first two terms build the supergravity multiplet, each of them carrying one spin-2 field, four gravitini, seven vectors and four spin-$\nicefrac{1}{2}$ fields, all massless.
+The only propagating degrees of freedom are in $[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}\otimes[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}$ (see the details in the tab.~4 of ref.~\cite{Hohm:2005ui}).
+\CE{(give these details here?)}
 
@@
 		& \times \exp\left[\sqrt{2}\left(\zeta_{1}\big(t_{(\mathbf{\fl{28}},\mathbf{2})}\big)_{23,+}+\zeta_{2}\big(t_{(\mathbf{\fl{28}},\mathbf{2})}\big)_{81,+}+\ts{\zeta}_{1}\big(t_{(\mathbf{28},\mathbf{2})}\big)_{56,+}+\ts{\zeta}_{2}\big(t_{(\mathbf{28},\mathbf{2})}\big)_{74,+}\right)\right] \\
-		& \times \exp\bigg[\Omega\left(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{1}{}^{1}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{2}{}^{2}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{3}{}^{3}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{8}{}^{8}\right)\\
-		&\ \qquad+\ts{\Omega}\left(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{4}{}^{4}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{5}{}^{5}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{6}{}^{6}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{7}{}^{7}\right)\bigg] \\
+		& \times \exp\bigg[\Omega\Big(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{1}{}^{1}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{2}{}^{2}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{3}{}^{3}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{8}{}^{8}\Big)\\
+		&\ \qquad+\ts{\Omega}\Big(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{4}{}^{4}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{5}{}^{5}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{6}{}^{6}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{7}{}^{7}\Big)\bigg] \\
 		& \times \exp\left[\ln(T)\left(\frac{1}{120}\,\big(t_{(\mathbf{63},\mathbf{1})}\big)_{I}{}^{I}-\frac{1}{120}\,\big(t_{(\mathbf{63},\mathbf{1})}\big)_{A}{}^{A}-\frac{1}{2}\,\big(t_{(\mathbf{1},\mathbf{3})}\big)_{1}\right)\right],
@@
 
-\paragraph{S-fold like deformations} Scalar spectrum:
-\begin{equation}
-	\begin{aligned}
-		(m_{(0)}\ell_{\rm AdS})^2:	\quad 
-		&8\ [1],\quad \frac{4\,\chi_{1}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{4\,\chi_{2}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{(\chi_{1}+\chi_{2})^{2}}{1+\alpha^{2}}\ [4], \quad \frac{(\chi_{1}-\chi_{2})^{2}}{1+\alpha^{2}}\ [4],	\\
-		&\frac{4\,\alpha^{2}\ts{\chi}_{1}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{4\,\alpha^{2}\ts{\chi}_{2}^{2}}{1+\alpha^{2}}\ [2], \quad \alpha^{2} \frac{(\ts{\chi}_{1}+\ts{\chi}_{2})^{2}}{1+\alpha^{2}}\ [4], \quad \alpha^{2} \frac{(\ts{\chi}_{1}-\ts{\chi}_{2})^{2}}{1+\alpha^{2}}\ [4],	\\
-		& \frac{\left(\chi_{1} + \chi_{2} \pm \alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2})\right)^{2}}{1+\alpha^{2}}\ [2+2], \quad \frac{\left(\chi_{1} - \chi_{2} \pm \alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2})\right)^{2}}{1+\alpha^{2}}\ [2+2],\\
-		&1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-		&1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-		&1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-		&1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-		&1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-		&1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-		&1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-		&1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2].
-	\end{aligned}
-\end{equation}
+% \paragraph{S-fold like deformations} Scalar spectrum:
+% \begin{equation}
+% 	\begin{aligned}
+% 		(m_{(0)}\ell_{\rm AdS})^2:	\quad 
+% 		&8\ [1],\quad \frac{4\,\chi_{1}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{4\,\chi_{2}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{(\chi_{1}+\chi_{2})^{2}}{1+\alpha^{2}}\ [4], \quad \frac{(\chi_{1}-\chi_{2})^{2}}{1+\alpha^{2}}\ [4],	\\
+% 		&\frac{4\,\alpha^{2}\ts{\chi}_{1}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{4\,\alpha^{2}\ts{\chi}_{2}^{2}}{1+\alpha^{2}}\ [2], \quad \alpha^{2} \frac{(\ts{\chi}_{1}+\ts{\chi}_{2})^{2}}{1+\alpha^{2}}\ [4], \quad \alpha^{2} \frac{(\ts{\chi}_{1}-\ts{\chi}_{2})^{2}}{1+\alpha^{2}}\ [4],	\\
+% 		& \frac{\left(\chi_{1} + \chi_{2} \pm \alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2})\right)^{2}}{1+\alpha^{2}}\ [2+2], \quad \frac{\left(\chi_{1} - \chi_{2} \pm \alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2})\right)^{2}}{1+\alpha^{2}}\ [2+2],\\
+% 		&1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+% 		&1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+% 		&1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+% 		&1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+% 		&1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+% 		&1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+% 		&1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
+% 		&1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2].
+% 	\end{aligned}
+% \end{equation}
 
@@
 
-\paragraph{S-fold like deformations (only $(\chi, \ts{\chi})$)}
+\paragraph{\boldmath $(\chi, \ts{\chi}, T)$}
 Using spherical coordinates for both spheres:
@@
 		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^{2}({\rm AdS}_{3}) +\alpha^{2}\left(\d\theta^{2} + \cos^{2}(\theta)\,\d\phi'_{1}{}^{2} + \sin^{2}(\theta)\,\d\phi'_{2}{}^{2} \right) \\
-		&\quad +\d\ts{\theta}^{2} + \cos^{2}(\ts{\theta})\,\d\ts{\phi}'_{1}{}^{2} + \sin^{2}(\ts{\theta})\,\d\ts{\phi}'_{2}{}^{2} + \d z^{2}, \\[5pt]
+		&\quad +\d\ts{\theta}^{2} + \cos^{2}(\ts{\theta})\,\d\ts{\phi}'_{1}{}^{2} + \sin^{2}(\ts{\theta})\,\d\ts{\phi}'_{2}{}^{2} + T^{2}\,\d z^{2}, \\[5pt]
 		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) + 2\,\alpha^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge\d\phi'_{1}\wedge\d\phi'_{2}+ 2\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge\d\ts{\phi}'_{1}\wedge\d\ts{\phi}'_{2},
@@
 \begin{equation}
-	\begin{aligned}
-		\d\phi'_{1} &= \d\phi_{1} + \chi_{1}\,\d z,\\
-		\d\phi'_{2} &= \d\phi_{2} + \chi_{2}\,\d z,\\
-		\d\ts{\phi}'_{1} &= \d\ts{\phi}_{1} + \ts{\chi}_{1}\,\d z,\\
-		\d\ts{\phi}'_{2} &= \d\ts{\phi}_{2} + \ts{\chi}_{2}\,\d z.
-	\end{aligned}
-\end{equation}
+	\begin{cases}
+		\displaystyle \d\phi'_{1} = \d\phi_{1} + \frac{1}{\alpha}\,\chi_{1}\,\d z,\\[6pt]
+		\displaystyle \d\phi'_{2} = \d\phi_{2} + \frac{1}{\alpha}\,\chi_{2}\,\d z,
+	\end{cases}\qquad
+	\begin{cases}
+		\d\ts{\phi}'_{1} = \d\ts{\phi}_{1} + \ts{\chi}_{1}\,\d z,\\[6pt]
+		\d\ts{\phi}'_{2} = \d\ts{\phi}_{2} + \ts{\chi}_{2}\,\d z.
+	\end{cases}
+\end{equation}
+
+This deformation breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries.
+Concerning the spectrum, the conformal dimension of each field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
+\begin{equation}
+	2\pi n\longrightarrow \frac{2\pi n}{T} + \frac{1}{2T}\Big((q_{\rm R}+q_{\rm L})\,\chi_{1}+(q_{\rm R}-q_{\rm L})\,\chi_{2}+ \alpha\,(\ts{q}_{\rm R}+\ts{q}_{\rm L})\,\ts{\chi}_{1}+ \alpha\,(\ts{q}_{\rm L}-\ts{q}_{\rm R})\,\ts{\chi}_{2}\Big),
+\end{equation}
+where the $q$ denote the charges under the different ${\rm U}(1)$. \CE{(Issue here!)}
+
+\CE{(Discuss SUSY enhancement)}
 
@@
 
+\appendix
+
+\section{Representations of \texorpdfstring{$D^{1}(2,1;\alpha)$}{D(2,1,a)}} \label{app:d21a}
+The supergroup $D^{1}(2,1;\alpha)$ has
+\begin{equation}
+	{\rm SL}(2,\mathbb{R})\times{\rm SU}(2)\times\ts{{\rm SU}(2)}
+\end{equation}
+as even part.
+Its multiplets are labelled by the spins $\ell$ and $\ts{\ell}$ of each ${\rm SU}(2)$ factor and the eigenvalue $h$ of the $\mathfrak{sl}(2,\mathbb{R})$ generator.
+Generic short multiplets $[\ell,\ts{\ell}]_{\rm s}$ are given by~\cite{deBoer:1999gea,Eberhardt:2017fsi}
+\begin{equation}
+	\begin{array}{cc}
+	 h_{0} & \big(\ell,\ts{\ell}\big) \\[5pt]
+	 h_{0} + \nicefrac{1}{2} & \big(\ell+\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \\[5pt]
+	 h_{0}+1 & \big(\ell,\ts{\ell}-1\big) \oplus \big(\ell,\ts{\ell}\big) \oplus \big(\ell-1,\ts{\ell}\big) \\[5pt]
+	 h_{0} + \nicefrac{3}{2} & \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big),
+	\end{array}
+\end{equation}
+with $h_{0}=(\alpha\,\ell+\ts{\ell})/(1+\alpha)$.\footnote{Shortenings occur for $\ell<1$ or $\ts{\ell}<1$, see ref.~\cite{deBoer:1999gea}.
+\CE{(Add them here?)}} Two short multiplets can combine into a long multiplets $[\ell,\ts{\ell}]$ as follows:
+\begin{equation}
+ 	[\ell,\ts{\ell}] = [\ell,\ts{\ell}]_{\rm s} \oplus [\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}]_{\rm s}.
+\end{equation}
+The value of $h$ is then not constrained. The explicit content of the long representation $[\ell,\ts{\ell}]$  is
+\begin{equation}
+	\begin{array}{cc}
+	 h & \big(\ell,\ts{\ell}\big) \\[5pt]
+	 h + \nicefrac{1}{2} & \big(\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus\big(\ell+\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \\[5pt]
+	 h+1 & \big(\ell+1,\ts{\ell}\big) \oplus \big(\ell,\ts{\ell}-1\big) \oplus \big(\ell,\ts{\ell}\big) \oplus \big(\ell,\ts{\ell}\big) \oplus \big(\ell-1,\ts{\ell}\big)\oplus \big(\ell,\ts{\ell}+1\big) \\[5pt]
+	 h + \nicefrac{3}{2} & \big(\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus\big(\ell+\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \\[5pt]
+	 h + 2 & \big(\ell,\ts{\ell}\big).
+	\end{array}
+\end{equation}
+
 \bibliographystyle{JHEP}

### 2023-06-07 Draft_3dH3.tex
SUSY enhancement and metric zeta Omega.

@@
 \begin{equation} \label{eq:3dCovDeriv}
-	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}}-2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M})}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}}\,, \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}} \,.
+	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}}-2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M}}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}}\,, \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}} \,.
 \end{equation}
@@
 \end{equation}
-Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=U_{\fl{M}}{}^{K}U_{\fl{N}}{}^{L}\partial_{K}U^{\fl{P}}{}_{L}$ and the trombone gauging
+Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=\UI_{\fl{M}}{}^{K}\UI_{\fl{N}}{}^{L}\partial_{K}U_{L}{}^{\fl{P}}$ and the trombone gauging
 \begin{equation} \label{eq:Trombone}
@@
 		\begin{cases}
-			\displaystyle X_{\fl{I}}{}^{\fl{J}}{}_{;\fl{KL}+}=-\frac{1}{\alpha}\,\delta_{\fl{I[K}}\delta_{\fl{L]}}{}^{\fl{J}},\\[7pt]
+			\displaystyle X_{\fl{I}}{}^{\fl{J}}{}_{;\fl{KL}+}=-\frac{1}{\alpha}\,\delta_{\fl{I}[\fl{K}}\delta_{\fl{L}]}{}^{\fl{J}},\\[7pt]
 			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;\fl{BJ}+}=-\frac{1}{2\alpha}\,\delta_{\fl{AB}}\delta_{\fl{J}}{}^{\fl{I}},\\
@@
 		\begin{cases}
-			\displaystyle X_{\fl{A}}{}^{\fl{B}}{}_{;}{}^{\fl{CD}}{}_{+}=-\,\delta_{\fl{A}}{}^{\fl{[C}}\delta^{\fl{D]B}},\\[7pt]
+			\displaystyle X_{\fl{A}}{}^{\fl{B}}{}_{;}{}^{\fl{CD}}{}_{+}=-\,\delta_{\fl{A}}{}^{[\fl{C}}\delta^{\fl{D}]\fl{B}},\\[7pt]
 			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;}{}^{\fl{BJ}}{}_{+}=-\frac{1}{2}\,\delta_{\fl{A}}{}^{\fl{B}}\delta^{\fl{IJ}},\\
 		\end{cases} \\[5pt]
-		X_{(\mathbf{70},\mathbf{1});(\mathbf{1},\mathbf{3})}:&\  X_{\fl{IJKL};\fl{\alpha}} = -\frac{\lambda}{12\sqrt{6}}\,\varepsilon_{\fl{IJKL}}\,\delta_{\fl{\alpha}2},
-	\end{aligned}
-\end{equation}
-with the component $\fl{\alpha} = 2$ of the adjoint of ${\rm SL}(2)$ corresponding to the generator $e = \begin{pmatrix} 0 & 1 \\ 0 & 0\end{pmatrix}$ in the basis $\fl{i}=\{+,-\}$.
-With this embedding tensor, the potential~\eqref{eq:3dpotential} is stabilized at the scalar origin for $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$.
-We fix this value in the following.
-
-\EM{Give embedding tensor components wrt the 3-d basis used for the moduli}\\
-\EM{Vacuum condition for $\lambda$}\\
-\EM{SUSY AdS$_3$ vacuum in 10-d}
-
-\paragraph{} At $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$, the three-dimensional solution described by the embedding tensor~\eqref{eq:embeddingtensor@origin} corresponds to the consistent truncation of the pure NSNS ten-dimensional solution ~\cite{deBoer:1999gea}
+		X_{(\mathbf{70},\mathbf{1});(\mathbf{1},\mathbf{3})}:&\  X_{\fl{IJKL};++} = -\frac{\lambda}{12\sqrt{6}}\,\varepsilon_{\fl{IJKL}}.
+	\end{aligned}
+\end{equation}
+With this embedding tensor, the potential~\eqref{eq:3dpotential} is stabilized at the scalar origin for $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$. We fix this value in the following.
+
+% \EM{Give embedding tensor components wrt the 3-d basis used for the moduli}\\
+% \EM{Vacuum condition for $\lambda$}\\
+% \EM{SUSY AdS$_3$ vacuum in 10-d}
+
+\paragraph{} At $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$, the three-dimensional solution described by the embedding tensor~\eqref{eq:embeddingtensor@origin} corresponds to the consistent truncation of the pure NSNS ten-dimensional solution~\cite{deBoer:1999gea}
 \begin{equation}
@@
 \end{equation}
-with $H_{(3)} = \d B_{(2)}$ and \CE{(with the normalization in eq.~\eqref{eq:3dpotential} and $\ell_{\rm AdS}^{2}=2/V_{0}$, the code gives an additional factor $1/2$)}
+with $H_{(3)} = \d B_{(2)}$ and
 \begin{equation}
@@
 \end{equation}
-The $S^{1}$ coordinate $z$ has periodicity $z\rightarrow z+1$. \CE{(add $S^{1}$ modulus here?)}
+The $S^{1}$ coordinate $z$ has periodicity $z\rightarrow z+2\pi$.
 
@@
 It corresponds to $\ell=\ts{\ell}=n=0$ in eq.~\eqref{eq:spectrumorigin}:
- \begin{equation}
- 	[0,0]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \oplus [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [0,0]_{\rm s} \oplus [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}.
+ \begin{equation} \label{eq:CTmultorigin}
+ 	[0,0]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \ \oplus \ [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [0,0]_{\rm s} \ \oplus \ [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}.
  \end{equation}
@@
 The only propagating degrees of freedom are in $[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}\otimes[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}$ (see the details in the tab.~4 of ref.~\cite{Hohm:2005ui}).
-\CE{(give these details here?)}
 
@@
 I think there is some freedom in the coeff there.)} \CE{(Describe what we do for $\Omega$?
+Check coeff with code.
 Possible to change the signs to $(+,+,-,-)$, but very long to compute uplift.)}
@@
 This deformation breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries.
-Concerning the spectrum, the conformal dimension of each field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
-\begin{equation}
-	2\pi n\longrightarrow \frac{2\pi n}{T} + \frac{1}{2T}\Big((q_{\rm R}+q_{\rm L})\,\chi_{1}+(q_{\rm R}-q_{\rm L})\,\chi_{2}+ \alpha\,(\ts{q}_{\rm R}+\ts{q}_{\rm L})\,\ts{\chi}_{1}+ \alpha\,(\ts{q}_{\rm L}-\ts{q}_{\rm R})\,\ts{\chi}_{2}\Big),
-\end{equation}
-where the $q$ denote the charges under the different ${\rm U}(1)$. \CE{(Issue here!)}
-
-\CE{(Discuss SUSY enhancement)}
+Concerning the spectrum, the conformal dimension of each physical field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
+\begin{equation} \label{eq:confdimshiftchi}
+	2\pi n\longrightarrow \frac{2\pi n}{T} + \frac{1}{2T}\Big((q_{\rm L}+q_{\rm R})\,\chi_{1}+(q_{\rm L}-q_{\rm R})\,\chi_{2}+ \alpha\,(\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1}+ \alpha\,(\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big),
+\end{equation}
+where the $q$ denote the charges under the different ${\rm U}(1)$.
+
+Eq.~\eqref{eq:confdimshiftchi} can be used to search for SUSY enhancement points within the 5-parameter landscape.
+At the undeformed origin, the massless gravitini sit in the two first multiplets in eq.~\eqref{eq:CTmultorigin} with ${\rm SO}(3)_{\rm L}\times\ts{{\rm SO}(3)}_{\rm L}\times{\rm SO}(3)_{\rm R}\times\ts{{\rm SO}(3)}_{\rm R}$ spins
+\begin{equation}
+	\big(\nicefrac{1}{2},\nicefrac{1}{2};0,0\big) \quad {\rm and} \quad \big(0,0;\nicefrac{1}{2},\nicefrac{1}{2}\big).
+\end{equation}
+and conformal dimension $\Delta=\nicefrac{3}{2}$.
+Turning on the deformation leads to a split into four groups of two modes, with the following ${\rm U}(1)_{\rm L}\times\ts{{\rm U}(1)}_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm R}$ charges and conformal dimensions:
+\begin{equation}
+	\begin{aligned}
+		\left(\pm1,\pm1;0,0\right):\quad \Delta=\frac{1}{2}+\sqrt{1+\frac{\left(\chi_{1}+\chi_{2}+\alpha\,\big(\ts{\chi}_{1}-\ts{\chi}_{2}\right)^{2}\big)}{4\,T^{2}(1+\alpha^{2})}}, \\
+		\left(\pm1,\mp1;0,0\right):\quad \Delta=\frac{1}{2}+\sqrt{1+\frac{\left(\chi_{1}+\chi_{2}-\alpha\,\big(\ts{\chi}_{1}-\ts{\chi}_{2}\right)^{2}\big)}{4\,T^{2}(1+\alpha^{2})}}, \\
+		\left(0,0;\pm1,\pm1\right):\quad \Delta=\frac{1}{2}+\sqrt{1+\frac{\left(\chi_{1}-\chi_{2}+\alpha\,\big(\ts{\chi}_{1}+\ts{\chi}_{2}\right)^{2}\big)}{4\,T^{2}(1+\alpha^{2})}}, \\
+		\left(0,0;\pm1,\mp1\right):\quad \Delta=\frac{1}{2}+\sqrt{1+\frac{\left(\chi_{1}-\chi_{2}+\alpha\,\big(\ts{\chi}_{1}+\ts{\chi}_{2}\right)^{2}\big)}{4\,T^{2}(1+\alpha^{2})}}.
+	\end{aligned}
+\end{equation}
+SUSY enhancement points are then given by combinations of the parameters that leave some modes invariant with $\Delta=\nicefrac{3}{2}$.
+The different possibilities are listed below.
+\CE{(Shall we give the multiplets?
+At least for the truncation?)}
+
+\begin{itemize}
+	\item {\boldmath ${\cal N}=2$} The four-dimensional hypersurfaces
+	\begin{equation}
+		\chi_{2} = \chi_{1} \pm\alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2}) \quad {\rm or}\quad \chi_{2} = -\chi_{1} \pm\alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2}),
+	\end{equation}
+	give enhancements to ${\cal N}=(2,0)$ and ${\cal N}=(0,2)$, respectively. The spectrum then organizes into multiplets of $\SU{1\vert1,1}$.
+	\item {\boldmath ${\cal N}=4$} Choosing
+	\begin{equation}
+		\begin{cases}
+			\chi_{2} = \chi_{1},\\
+			\ts{\chi}_{2} = -\ts{\chi}_{1},
+		\end{cases}
+		\quad {\rm or}\quad
+		\begin{cases}
+			\chi_{2} = - \chi_{1},\\
+			\ts{\chi}_{2} = \ts{\chi}_{1},
+		\end{cases}
+	\end{equation}
+	leads to enhancements to ${\cal N}=(4,0)$ and ${\cal N}=(0,4)$, respectively.
+On these three-dimensional hyper-surfaces, the isometry group is $\SO{4}\times {\rm U}(1)^{2}$ and the spectrum reorganizes into multiplets of $D^{1}(2,1;\alpha)$.
+Another possibility is to set
+	\begin{equation}
+		\begin{cases}
+			\ts{\chi}_{1} = \pm \chi_{1}/\alpha,\\
+			\ts{\chi}_{2} = \mp \chi_{2}/\alpha,
+		\end{cases}
+		\quad {\rm or}\quad
+		\begin{cases}
+			\ts{\chi}_{1} = \pm \chi_{2}/\alpha,\\
+			\ts{\chi}_{2} = \mp \chi_{1}/\alpha,
+		\end{cases}
+	\end{equation}
+	giving 3-parameter families of ${\cal N}=(2,2)$ solutions, with multiplets of $\SU{1\vert1,1}_{\rm L}\times\SU{1\vert1,1}_{\rm R}$.
+	\item {\boldmath ${\cal N}=6$} Finally, for
+	\begin{equation}
+		\begin{cases}
+			\chi_{2} = \chi_{1},\\
+			\ts{\chi}_{1} = \pm \chi_{1}/\alpha,\\
+			\ts{\chi}_{2} = \mp \chi_{1}/\alpha,
+		\end{cases}
+		\quad {\rm or}\quad
+		\begin{cases}
+			\chi_{2} = -\chi_{1},\\
+			\ts{\chi}_{1} = \pm \chi_{1}/\alpha,\\
+			\ts{\chi}_{2} = \mp \chi_{1}/\alpha,
+		\end{cases}
+	\end{equation}
+	there are enhancements to ${\cal N}=(4,2)$ and ${\cal N}=(2,4)$, respectively.
+The isometry group is $\SO{4}\times {\rm U}(1)^{2}$ and the spectrum is then given by multiplets of $D^{1}(2,1;\alpha)_{\rm L, R}\times\SU{1\vert1,1}_{\rm R,L}$.
+\end{itemize}
+
+\paragraph{\boldmath $(\zeta,\ts{\zeta},T)$}
+Again with spherical coordinates:
+\begin{equation}
+	\begin{aligned}
+		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) -\Delta\,\d z^{2}\\
+		&+ \alpha^{2}\Big[\d\theta^{2} + \Delta\left(\cos^{2}(\theta)\,\d\phi_{1}^{2}+\sin^{2}(\theta)\,\d\phi_{2}^{2}\right)\Big]+\d\ts{\theta}^{2} + \Delta\left(\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}^{2}+\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}^{2}\right)\\
+		&+\Delta\,T^{2}\,\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,T^{2}\,\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
+		&+\Delta\,T^{2}\,\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,T^{2}\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
+		&-2\,\alpha\,\Delta\,T^{2}\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
+		&+\Delta\,T^{2}\,\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+\Delta\,T^{2}\,\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\\
+		&+\Delta\,T^{2}\,\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\Delta\,T^{2}\,\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2},
+	\end{aligned}
+\end{equation}
+with the warp factor
+\begin{equation}
+	\Delta^{-1} = 1+T^{2}\left(\zeta_{1}^{2}\sin^{2}(\theta)+\zeta_{2}^{2}\cos^{2}(\theta)+\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})+\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})\right).
+\end{equation}.
+
+\CE{(Expression of $H$?)}
+
+\paragraph{\boldmath $(\zeta,\ts{\zeta},\Omega,\ts{\Omega})$}
+Again with spherical coordinates:
+\begin{equation}
+	\begin{aligned}
+		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) -\Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\,\d z^{2}\\
+		&+ \alpha^{2}\Big[\d\theta^{2} + \Delta\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big(e^{\Omega}\cos^{2}(\theta)\,\d\phi_{1}^{2}+\sin^{2}(\theta)\,\d\phi_{2}^{2}\Big)\Big]\\
+		&+\d\ts{\theta}^{2} + \Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}^{2}+e^{\ts{\Omega}}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}^{2}\Big)\\
+		&+\Delta\,e^{\Omega}\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,e^{\ts{\Omega}}\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
+		&+\Delta\,e^{\Omega+\ts{\Omega}}\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
+		&-2\,\alpha\,\Delta\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+e^{\Omega}\,\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(e^{\ts{\Omega}}\,\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
+		&+\Delta\,\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big[\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+e^{\Omega}\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\Big]\\
+		&+\Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big[e^{\ts{\Omega}}\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2}\Big],
+	\end{aligned}
+\end{equation}
+with the warp factor
+\begin{equation}
+	\Delta^{-1} = 1+T^{2}\left(\zeta_{1}^{2}\sin^{2}(\theta)+\zeta_{2}^{2}\cos^{2}(\theta)+\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})+\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})\right).
+\end{equation}.
+
+\CE{(Expression of $H$?)}
 
@@
 \end{equation}
-with $h_{0}=(\alpha\,\ell+\ts{\ell})/(1+\alpha)$.\footnote{Shortenings occur for $\ell<1$ or $\ts{\ell}<1$, see ref.~\cite{deBoer:1999gea}.
-\CE{(Add them here?)}} Two short multiplets can combine into a long multiplets $[\ell,\ts{\ell}]$ as follows:
+with $h_{0}=(\alpha\,\ell+\ts{\ell})/(1+\alpha)$. Shortenings occur for $\ell<1$ or $\ts{\ell}<1$~\cite{deBoer:1999gea}. For instance:
+\begin{equation}
+	[0,0]_{\rm s}:\quad h_{0}=0 \quad (0,0),\qquad  [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}: \begin{array}{cc}
+	 h_{0}=\nicefrac{1}{2} & \big(\nicefrac{1}{2},\nicefrac{1}{2}\big) \\[5pt]
+	 1 & \big(1,0\big) \oplus \big(0,0\big) \oplus \big(0,1\big) \\[5pt]
+	 \nicefrac{3}{2} & \big(\nicefrac{1}{2},\nicefrac{1}{2}\big) \\[5pt]
+	 2 & \big(0,0\big).
+	\end{array}
+\end{equation}
+
+Two short multiplets can combine into a long multiplets $[\ell,\ts{\ell}]$ as follows:
 \begin{equation}

### 2023-06-13 Draft_3dH3.tex
Update warp factor Zeta Omega.
Modifications by Emanuel.

@@
 \begin{equation} \label{eq:GSSexample}
-	\begin{aligned}
+	\begin{split}
 		D_{\mu}\M(x,Y) &= U_{M}{}^{\fl{M}}(Y)\,U_{N}{}^{\fl{N}}(Y)\,{\cal D}_{\mu}\M_{\fl{MN}}(x)\,,\\
 		{\cal L}_{(A_{\mu},B_{\nu})}A_{\mu}(x,Y) &= \rho(Y)^{-1}\,\UI_{\fl{M}}{}^{M}(Y)\,\llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}(x)\,,
-	\end{aligned}
-\end{equation}
-where
+	\end{split}
+\end{equation}
+where \EM{Note corrected sign in first equation!}
 \begin{equation} \label{eq:3dCovDeriv}
-	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}}-2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M}}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}}\,, \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}} \,.
+	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}} + 2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M}}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}}\,, \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}} \,.
 \end{equation}
@@
 \begin{equation}
-	\begin{aligned}
+	\begin{split}
 		X_{\fl{MN}}{}^{\fl{P}}&=-\rho^{-1}\,\Gamma_{\fl{MN}}{}^{\fl{P}} + \rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{L}}\,\Gamma_{\fl{KM}}{}^{\fl{L}}-\frac{1}{60}\,\rho^{-1}\,f^{\fl{PK}}{}_{\fl{N}}\,f_{\fl{ML}}{}^{\fl{Q}}\,\Gamma_{\fl{KQ}}{}^{\fl{L}}\\
 		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{M}}\,\Gamma_{\fl{RK}}{}^{\fl{R}}+\left(\delta_{\fl{M}}{}^{\fl{K}}\delta_{\fl{N}}{}^{\fl{P}}-\frac{1}{2}\,f_{\fl{M}}{}^{\fl{LK}}f_{\fl{NL}}{}^{\fl{P}}\right)\,\xi_{\fl{K}}\,.
-	\end{aligned}
+	\end{split}
 \end{equation}
@@
 \begin{equation} \label{eq:symembeddingtensor}
-	\begin{aligned}
+	\begin{split}
 		X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} &= - 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{P}(\fl{M}}{}^{\fl{Q}}\,f_{\fl{N})\fl{Q}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \\
 		&= - 14\,\rho^{-1}\,(\mathbb{P}_{3875})_{\fl{MN}}{}^{\fl{PQ}}\,\Gamma_{\fl{PQ}} - \frac{1}{4}\,\rho^{-1}\,\eta_{\fl{MN}}\,\Gamma_{\fl{P}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \,,
-	\end{aligned}
+	\end{split}
 \end{equation}
@@
 \begin{equation}
-	\begin{aligned}
+	\begin{split}
 		\mathscr{L}_{\rm kin} &= \frac{1}{240}\,D_{\mu}\M_{MN}D^{\mu}\M^{MN} \underset{\rm gSS}{=} \frac{\rho^{2}}{240}\,{\cal D}_{\mu}\M_{\fl{MN}}{\cal D}^{\mu}\M^{\fl{MN}}, \\
 		\mathscr{L}_{\rm CS} &\underset{\rm gSS}{=} -\rho^{-1}\,\varepsilon^{\mu\nu\rho}\,X_{\fl{MN}}\,\A_{\mu}{}^{\fl{M}} \left(\partial_{\nu}\A_{\rho}{}^{\fl{N}}-\frac{1}{3}\,\llbracket\A_{\nu},\A_{\rho}\rrbracket^{\fl{N}}\right)\,.
-	\end{aligned}
+	\end{split}
 \end{equation}
@@
 \begin{equation}
-	\alpha = \frac{1}{28}\,,\quad \beta = \frac{1}{2}\,,\quad a=1\,,\quad \delta=\frac{13}{28} \,. %, \quad \gamma=0.
+	\alpha = \frac{1}{28}\,,\quad \beta = \frac{1}{2}\,, \quad \delta=\frac{13}{28}\,, \quad a=1 \,. %, \quad \gamma=0.
 \end{equation}
@@
 We are interested in the maximal solutions of the section condition \eqref{eq:SLnSC} which preserve a $\SL{n} \subset \SL{n+1}$ subgroup.
-Under this decomposition $\SL{n+1} \rightarrow \SL{n}$ with $V^I = \left( V^i,\, V^0 \right)$, where $i = 1, \ldots, n$, we solve the section condition by having physical coordinates $y^{i0}$ on the $n$-dimensional manifold $M$, i.e.
-$\partial_{ij} = 0$ for all fields with only $\partial_{i0} \neq 0$.
+Under this decomposition $\SL{n+1} \rightarrow \SL{n}$ with $V^I = \left( V^i,\, V^0 \right)$, where $i = 1, \ldots, n$, we solve the section condition by having physical coordinates $y^{0i}$ on the $n$-dimensional manifold $M$, i.e.
+$\partial_{ij} = 0$ for all fields with only $\partial_{0i} = \partial_i \neq 0$.
 Correspondingly, the generalised tangent bundle, whose sections are in the antisymmetric representation of $\SL{n+1}$ and carry weight $\frac{n-3}{n+1}$, decomposes as
@@
 		\gL_{V} V' &= [v, v'] + L_{v} \omega'_{(n-2)} - \imath_{v'} d\omega_{(n-2)} \,, \\
-		\gL_{V} W &= L_v \omega_{(1)} + L_v \omega_{(n)} - \EM{\alpha} \omega_{(1)} \wedge d\omega_{(n-2)} \,,
-	\end{split}
-\end{equation}
-\EM{(I think $\alpha = 1$ but not 100\% sure)}
+		\gL_{V} W &= L_v \omega_{(1)} + L_v \omega_{(n)} + \omega_{(1)} \wedge d\omega_{(n-2)} \,,
+	\end{split}
+\end{equation}
 where we write $V = v + \omega_{(n-2)}$, $V' = v' + \omega'_{(n-2)}$ and $W = \omega_{(1)} + \omega_{(n)}$ as a formal of vectors and $p$-forms, and $L$ denotes the ordinary Lie derivative and $[v,v']$ the ordinary Lie bracket between vector fields $v$ and $v'$.
@@
 Let $Y^I$, $I = 1, \ldots, n+1$ be the embedding coordinates of $S^{n} \subset \mathbb{R}^{n+1}$, such that $Y^I\, Y_I = 1$.
-On $S^n$, we can define a parallelisation of $N$ using the generalised frame \EM{Check sign of A!
-Although I'm pretty confident about it.}
+On $S^n$, we can define a parallelisation of $N$ using the generalised frame
 \begin{equation}\label{eq:SnFrame}
-	\cU^{\fl{I}} = dY^{\fl{I}} + Y^{\fl{I}}\, vol_{S^n} - A \wedge dY^{\fl{I}} \,,
+	\cU^{\fl{I}} = dY^{\fl{I}} + Y^{\fl{I}}\, vol_{S^n} - dY^{\fl{I}} \wedge A \,,
 \end{equation}
@@
 and hence a generalised frame for $E$ or a generalised bundle in any other rep of $\SL{n+1}$.
-
-Evaluating \eqref{eq:SLnFrame} and \eqref{eq:rho} on the northern hemisphere $Y^I = \left( y^i,\, \sqrt{1-y^i y_i}\right)$, $i = 1, \ldots, n$ and using the gauge choice for the potential $A$
-\begin{equation}
-	A_{ij} = \epsilon_{ijk}\, y^k (1 + K(v)) \,,
-\end{equation}
-with $v = y^i\, y^i$ and $\epsilon_{ijk}$ the volume form on $S^3$, we precisely recover the $\SL{4}$ twist matrix of \cite{Hohm:2014qga}, i.e.
+For example, in the generalised tangent bundle \eqref{eq:SLnE}, we have the generalised frame $\cU_{\fl{I}\fl{J}}{}^{IJ} = \left(\det \mathring{g}\right)^{1/2} \cU_{[\fl{I}}{}^{I} \cU_{\fl{J}]}{}^J$, with components given by
+\begin{equation} \label{eq:SLnGenFrame}
+	2\, \cU_{\fl{I}\fl{J}} = v_{\fl{I}\fl{J}} + \star dY_{\fl{I}\fl{J}} + \imath_{v_{\fl{I}\fl{J}}} A \,,
+\end{equation}
+where $v_{\fl{I}\fl{J}}$ are the $\SO{n+1}$ Killing vectors of the round $S^n$, matching precisely the $\SL{n+1}$ parallelisations constructed in \cite{Lee:2014mla}.
+
+Using \eqref{eq:SLnGenLie}, we can easily check that the generalised frame  \eqref{eq:SLnGenFrame}, \eqref{eq:SLnTwist} defines a generalised Leibniz parallelisation.
+In particular, using $dA = (n-1) vol_{S^n}$, we obtain the embedding tensor
+\begin{equation}
+	\gL_{\cU_{\fl{I}\fl{J}}} \cU^{\fl{K}} = - X_{\fl{I}\fl{J}\fl{L}}{}^{\fl{K}}\, \cU^{\fl{L}} \,,
+\end{equation}
+with
+\begin{equation} \label{eq:SLnEmbeddingTensor}
+	X_{\fl{I}\fl{J},\fl{L}}{}^{\fl{K}} = - \delta_{\fl{L}[\fl{I}} \delta_{\fl{J}]}^{\fl{K}} \,.
+\end{equation}
+
+Finally, we can also connect the above with the $\SL{n+1}$ Ansatz construction of \cite{Hohm:2014qga}.
+We do this by evaluating \eqref{eq:SLnFrame} and \eqref{eq:rho} on the northern hemisphere $Y^I = \left( y^i,\, \sqrt{1-y^i y_i}\right)$, $i = 1, \ldots, n$ and using the gauge choice for the potential $A$
+\begin{equation}
+	A_{i_1 \ldots i_{n-1}} = \epsilon_{i_1 \ldots i_{n-1}j}\, y^j (1 + K(v)) \,,
+\end{equation}
+with $v = y^i\, y^i$ and $\epsilon_{i_1 \ldots i_{n-1}j}$ the volume form on $S^n$. With the above choices, we precisely recover the $\SL{n+1}$ twist matrix of \cite{Hohm:2014qga}, i.e.
 \begin{equation} \label{eq:SLnTwist}
 	\UI_{\fl{I}}{}^I = \begin{pmatrix}
-		\left(1-v\right)^{-1/4} \left( \delta_i{}^j + y_i\, y^j K(v) \right) & y_i \left(1-v\right)^{1/4} \\
-		y^j \left(1-v\right)^{1/4} K(v) & \left(1-v\right)^{3/4}
+		\left(1-v\right)^{-1/(n+1)} \left( \delta_i{}^j + y_i\, y^j K(v) \right) & y_i \left(1-v\right)^{(n-1)/(2(n+1))} \\
+		y^j \left(1-v\right)^{(n-1)/(2(n+1))} K(v) & \left(1-v\right)^{\tfrac{n}{n+1}}
 	\end{pmatrix} \,.
 \end{equation}
-Moreover, the generalised frame for $E$ precisely coincides with the twist matrix in \cite{Lee:2014mla,Baguet:2015iou}. \EM{Give it explicitly?}
-
-\EM{To do: Should mention Leibniz parallelisability somewhere and the embedding tensor that arises}
-
-\EM{I think the sign conventions are:
-	\begin{equation}
-		\begin{split}
-			\cU^{\fl{I}} &= dY^{\fl{I}} + Y^{\fl{I}}\, vol_{S^n} + dY^{\fl{I}} \wedge A \,, \\
-			\gL_{V} W &= L_v \omega_{(1)} + L_v \omega_{(n)} + \omega_{(1)} \wedge d\omega_{(n-2)} \,, \\
-			\gL_{\cU_{\fl{I}\fl{J}}} \cU^{\fl{K}} &= - X_{\fl{I}\fl{J},\fl{L}}{}^{\fl{K}}\, \cU^{\fl{L}} \,, \\
-			X_{\fl{I}\fl{J},\fl{L}}{}^{\fl{K}} &= 2\, \delta_{\fl{L}[\fl{I}} \delta_{\fl{J}]}^{\fl{K}} \,.
-		\end{split}
-	\end{equation}
-For the twist matrix in the antisymmetric rep, I find
-\begin{equation}
-	\cU_{[\fl{I}} \cU_{\fl{J}]} = v_{\fl{J}\fl{I}} + \star \left( dY_{\fl{I}} \wedge dY_{\fl{J}} \right) + \left(-1\right)^{n-1} \imath_{v_{\fl{J}\fl{I}}} A \,,
-\end{equation}
-where the vector part is $V^{i\,0}$, the $(n-2)$-form part is $V^{ij} = \frac{1}{(n-2)!} \epsilon^{k_1 \ldots k_{n-2} ij} \lambda_{k_{1} \ldots k_{n-2}}$ and the coordinates are identified as $Y^{i\,0} = y^i$.
-We can probably match the sign of the vector part of \cite{Baguet:2015iou} by taking the vector part to be $V^{0\,i}$ and also changing the coordinates to be $Y^{0\,i} = y^i$.
-We should probably check this carefully since it's useful to write up properly.
-}
 
@@
 \end{equation}
-This solution of the section condition defines the ``geometric'' $\SL{3}_1 \times \mathbb{R}^+_1 \subset \SL{4}_1$ and $\SL{3}_2 \times \mathbb{R}^+_2 \subset \SL{4}_2$ subgroups, that will play an important role soon.
-
-We can now use one copy of the $\SL{4}$ frame \eqref{eq:SLnFrame} for each $\SL{4}$ subgroup of \eqref{eq:SL4Embedding} to construct a generalised parallelisation for the full $\En{7}$ ExFT, with an embedding tensor via \eqref{eq:GenLeibniz} \EM{given by \ldots}.
-
-\EM{Include breaking of adjoint here?}\\
-\EM{Should mention the geometric $\SL{3}$ subgroups here???}
-
-\EM{What we should actually do: Read this and next section again and make sure they make sense.
-Maybe when referring to the $\SL{3}$ subgroups in the next section, we can cite \eqref{eq:PhysicalCoords}}
-
-\CE{(Add $\alpha$ here?)}
+This solution of the section condition defines the ``geometric'' $\SL{3}_1 \times \mathbb{R}^+_1 \subset \SL{4}_1$ and $\SL{3}_2 \times \mathbb{R}^+_2 \subset \SL{4}_2$ subgroups, that will play an important role when adding flux in section \ref{s:AddFluxS3S3S1}.
+
+We can now use one copy of the $\SL{4}$ frame \eqref{eq:SLnFrame} for each $\SL{4}$ subgroup of \eqref{eq:SL4Embedding} to construct a generalised parallelisation for the full $\En{7}$ ExFT, with an embedding tensor via \eqref{eq:GenLeibniz} given as in \eqref{eq:SLnEmbeddingTensor} embedded in $\En{7}$ as follows.
+Under $\En{7} \rightarrow \SL{8}$, the embedding tensor representation branches as
+\begin{equation}
+	\mathbf{912} \rightarrow \mathbf{36} \oplus \overline{\mathbf{36}} \oplus \mathbf{420} \oplus \overline{\mathbf{420}} \,,
+\end{equation}
+and we only generate the $\mathbf{36}$ and $\overline{\mathbf{36}}$ components, $\eta_{{\cal AB}}$, $\eta^{{\cal AB}}$. Thus, the $\En{7}$ embedding tensor is given by
+\begin{equation}
+	\begin{split}
+		X_{{\cal AB, CD}}{}^{\cal EF} &= \eta_{\cA[\cC} \delta_{{\cal D}]\cB}^{{\cal EF}} - \eta_{\cB[\cC} \delta_{{\cal D}]\cA}^{{\cal EF}} \,, \\
+		X^{{\cal AB}}{}_{{\cal CD}}{}^{\cal EF} &= -\eta^{\cA[{\cal E}}_{\phantom{[\cA]}} \delta_{\cC{\cal D}}^{{\cal F}]{\cal B}} + \eta^{\cB[{\cal E}}_{\phantom{[\cA]}} \delta_{\cC{\cal D}}^{{\cal F}]{\cal A}} \,.
+	\end{split}
+\end{equation}
+Because we are embedding the $\SL{4}_1$ coordinates in the $\mathbf{28}$ but those of $\SL{4}_2$ in the $\overline{\mathbf{28}}$, the twist matrix will generate an embedding tensor in the $\mathbf{36}$ for $\SL{4}_1$ and $\overline{\mathbf{36}}$ for $\SL{4}_2$, whose only non-vanishing components are
+\begin{equation}
+	\eta_{IJ} = \delta_{IJ} \,, \qquad \eta^{AB} = \delta^{AB} \,.
+\end{equation}
+
+We can also rescale their $S^3$'s using their corresponding $\mathbf{R}^+$ generator.
+Without loss of generality, we can rescale $S^3$ to have radius $\alpha$, using the $\mathbf{R}^+_1$ generator on the frame.
+The embedding tensor then becomes
+\begin{equation}
+	\eta_{IJ} = \frac{1}{\alpha} \delta_{IJ} \,, \qquad \eta^{AB} = \delta^{AB} \,.
+\end{equation}
 
@@
 
-\subsubsection{Adding flux}
+\subsubsection{Adding flux} \label{s:AddFluxS3S3S1}
 %We now wish to add a 7-form flux to the $S^3 \times S^3 \times S^1$ truncation constructed above.
@@
 Finally, the other elements of the $\SL{2}$ doublet of 6-form potential can be mapped to the $\mathbf{\left(4,\overline{4}\right)_{2}} \oplus \mathbf{\left(\overline{4},4\right)_{-2}}$ generators, specifically $t_7{}^8$ and $t_8{}^7$ and are clearly not $\SL{4}$ singlets.
-\EM{Is this sufficiently clear? I am not so sure...}
 
@@
 		X^{\fl{M}} & \ \tikz{\draw[arrows={->[scale=1.1]}] (0,0) -- (3.65
-	,0);}\ \left\{X^{\fl{\cal A}}{}_{\fl{\cal B}},X^{\fl{\cal ABCD}},X^{\fl{\cal AB}\,\fl{i}},X_{\fl{\cal AB}}{}^{\fl{i}},X^{\fl{\alpha}}\right\},
+	,0);}\ \left\{X^{\fl{\cal A}}{}_{\fl{\cal B}},\,X^{\fl{\cal ABCD}},\,X^{\fl{\cal AB}\,\fl{i}},\,X_{\fl{\cal AB}}{}^{\fl{i}},\,X^{\fl{\alpha}}\right\},
 	\end{aligned}
 \end{equation}
-and has the following non-vanishing components:
+and has the following non-vanishing components under the $\SL{4}_1 \times \SL{4}_2$ subgroups of $\SL{8}$:
 \begin{equation} \label{eq:embeddingtensor@origin}
-	\begin{aligned}
+	\begin{split}
 		X_{(\mathbf{63},\mathbf{1});(\mathbf{28},\mathbf{2})}:&
@@
 			\displaystyle X_{\fl{I}}{}^{\fl{J}}{}_{;\fl{KL}+}=-\frac{1}{\alpha}\,\delta_{\fl{I}[\fl{K}}\delta_{\fl{L}]}{}^{\fl{J}},\\[7pt]
-			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;\fl{BJ}+}=-\frac{1}{2\alpha}\,\delta_{\fl{AB}}\delta_{\fl{J}}{}^{\fl{I}},\\
+			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;\fl{BJ}+}=-\frac{1}{2\alpha}\,\delta_{\fl{AB}}\delta_{\fl{J}}{}^{\fl{I}}\,,\\
 		\end{cases} \\[5pt]
@@
 		\begin{cases}
-			\displaystyle X_{\fl{A}}{}^{\fl{B}}{}_{;}{}^{\fl{CD}}{}_{+}=-\,\delta_{\fl{A}}{}^{[\fl{C}}\delta^{\fl{D}]\fl{B}},\\[7pt]
-			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;}{}^{\fl{BJ}}{}_{+}=-\frac{1}{2}\,\delta_{\fl{A}}{}^{\fl{B}}\delta^{\fl{IJ}},\\
+			\displaystyle X_{\fl{A}}{}^{\fl{B}}{}_{;}{}^{\fl{CD}}{}_{+}=-\,\delta_{\fl{A}}{}^{[\fl{C}}\delta^{\fl{D}]\fl{B}}\,,\\[7pt]
+			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;}{}^{\fl{BJ}}{}_{+}=-\frac{1}{2}\,\delta_{\fl{A}}{}^{\fl{B}}\delta^{\fl{IJ}}\,,\\
 		\end{cases} \\[5pt]
-		X_{(\mathbf{70},\mathbf{1});(\mathbf{1},\mathbf{3})}:&\  X_{\fl{IJKL};++} = -\frac{\lambda}{12\sqrt{6}}\,\varepsilon_{\fl{IJKL}}.
-	\end{aligned}
-\end{equation}
-With this embedding tensor, the potential~\eqref{eq:3dpotential} is stabilized at the scalar origin for $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$. We fix this value in the following.
+		X_{(\mathbf{70},\mathbf{1});(\mathbf{1},\mathbf{3})}:&\  X_{\fl{IJKL};++} = -\frac{\lambda}{12\sqrt{6}}\,\varepsilon_{\fl{IJKL}}\,.
+	\end{split}
+\end{equation}
+With this embedding tensor, the potential~\eqref{eq:3dpotential} has a vacuum at the scalar origin when $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$.
+We choose this value of $\lambda$ from here onwards.
+\EM{Presumably condition is on $\lambda^2$ and the sign of $\lambda$ is fixed by SUSY (which we can ignore)?}
 
@@
 
+%, which transform under the subgroup $\SL{6} \times \SL{2} \times \mathbb{R}^+_{IIB} \subset \En{7}$ as $\mathbf{\left(1,2\right)_{6}} \subset \mathbf{133}$
+
+%\EM{Describe how $C_6{}^\alpha$ sits in here}
+
+\section{Moduli of \texorpdfstring{AdS$_3 \times S^3 \times S^3 \times S^1$}{AdS3xS3xS3xS1}} \label{s:Moduli}
+
+\subsection{The undeformed ${\cal N}=(4,4)$ AdS$_3 \times S^3 \times S^3 \times S^1$ solution}
 \paragraph{} At $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$, the three-dimensional solution described by the embedding tensor~\eqref{eq:embeddingtensor@origin} corresponds to the consistent truncation of the pure NSNS ten-dimensional solution~\cite{deBoer:1999gea}
-\begin{equation}
-	\begin{aligned}
+\begin{equation} \label{eq:AdS3}
+	\begin{split}
 		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) + \alpha^{2}\,\d s^{2}\big(S^{3}\big)+\d s^{2}\big(\ts{S}^{3}\big)+\d z^{2},\\
-		H_{(3)} &= 2\left(\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})+\alpha^{2}\,{\rm Vol}\big(S^{3}\big)+{\rm Vol}\big(\ts{S}^{3}\big)\right),
-	\end{aligned}
+		H_{(3)} &= 2\left(\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})+\alpha^{2}\,{\rm Vol}\big(S^{3}\big)+{\rm Vol}\big(\ts{S}^{3}\big)\right)\,,
+	\end{split}
 \end{equation}
@@
 \begin{equation}
-	\ell_{\rm AdS}^{2} = \frac{\alpha^{2}}{1+\alpha^{2}}.
+	\ell_{\rm AdS}^{2} = \frac{\alpha^{2}}{1+\alpha^{2}}\,.
 \end{equation}
@@
 \paragraph{}
-The 3d solution preserves ${\cal N}=(4,4)$ supercharges, with isometry group ${\cal G}=D^{1}(2,1;\alpha)_{\rm L}\times D^{1}(2,1;\alpha)_{\rm R}$, \textit{i.e.} two copies of the large ${\cal N}=4$ supergroup.
+The AdS$_3$ solution \eqref{eq:AdS3} preserves ${\cal N}=(4,4)$ supersymmetry, with super-isometry group ${\cal G}=D^{1}(2,1;\alpha)_{\rm L}\times D^{1}(2,1;\alpha)_{\rm R}$, \textit{i.e.} two copies of the large ${\cal N}=4$ supergroup.
 The even part of $D^{1}(2,1;\alpha)$ is isomorphic to ${\rm SL}(2,\mathbb{R})\times{\rm SO}(3)\times\ts{{\rm SO}(3)}$ and the bosonic isometries of the ${\rm AdS}_{3}\times S^{3}\times\ts{S}^{3}$ background are built from the even part of ${\cal G}$.
@@
 \begin{equation} \label{eq:spectrumorigin}
-	\bigoplus_{\ell,\ts{\ell}\geq0} [\ell,\ts{\ell}]\otimes[\ell,\ts{\ell}] \ \ominus\ [0,0]_{\rm s} \otimes [0,0]_{\rm s}.
+	\bigoplus_{\ell,\ts{\ell}\geq0} [\ell,\ts{\ell}]\otimes[\ell,\ts{\ell}] \ \ominus\ [0,0]_{\rm s} \otimes [0,0]_{\rm s}\,.
 \end{equation}
@@
 \begin{equation}
-	h_{\rm L} = h_{\rm R} = -\frac{1}{2} + \frac{1}{2}\sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}},
+	h_{\rm L} = h_{\rm R} = -\frac{1}{2} + \frac{1}{2}\sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}}\,,
 \end{equation}
@@
 \begin{equation} \label{eq:confdims3s3s1}
-	\Delta_{\ell,\,\ts{\ell},\,n} = h_{\rm L} + h_{\rm R} = - 1 + \sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}}.
+	\Delta_{\ell,\,\ts{\ell},\,n} = h_{\rm L} + h_{\rm R} = - 1 + \sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}}\,.
 \end{equation}
@@
 \begin{equation} \label{eq:CTmultorigin}
- 	[0,0]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \ \oplus \ [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [0,0]_{\rm s} \ \oplus \ [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}.
+	[0,0]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \ \oplus \ [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [0,0]_{\rm s} \ \oplus \ [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}\,.
 \end{equation}
 The first two terms build the supergravity multiplet, each of them carrying one spin-2 field, four gravitini, seven vectors and four spin-$\nicefrac{1}{2}$ fields, all massless.
-The only propagating degrees of freedom are in $[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}\otimes[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}$ (see the details in the tab.~4 of ref.~\cite{Hohm:2005ui}).
-
-%, which transform under the subgroup $\SL{6} \times \SL{2} \times \mathbb{R}^+_{IIB} \subset \En{7}$ as $\mathbf{\left(1,2\right)_{6}} \subset \mathbf{133}$
-
-%\EM{Describe how $C_6{}^\alpha$ sits in here}
-
-\section{Moduli of \texorpdfstring{AdS$_3 \times S^3 \times S^3 \times S^1$}{AdS3xS3xS3xS1}} \label{s:Moduli}
+The only propagating degrees of freedom are in $[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}\otimes[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}$ (see the details in table 4 of \cite{Hohm:2005ui}).
 
 \subsection{Moduli in gauged supergravity}
-We identified a 11-parameter family of solutions, connected to the origin and given by the \EE coset representative \CE{($\fl{28}\leftrightarrow28$ compared to the code, I think we made a mistake and confused down and up indices)}
-\begin{equation}
-	\begin{aligned}
+Surprisingly, within the 3-dimensional gauged supergravity, the AdS$_3$ vacuum contains a large moduli space, which even has supersymmetric submanifolds.
+In particular, without any attempts at being exhaustive \EM{(too strong?
+does this make us sound lazy?)}, we identified a continuous 11-parameter family of AdS$_3$ solutions, connected to the origin and given by the \EE coset representative \CE{($\fl{28}\leftrightarrow28$ compared to the code, I think we made a mistake and confused down and up indices)}
+\begin{equation} \label{eq:FullDeformation}
+	\begin{split}
 		{\cal V}_{\rm def} &= \exp\left[\sqrt{2}\left(\chi_{1}\big(t_{(\mathbf{28},\mathbf{2})}\big)_{23,-}+\chi_{2}\big(t_{(\mathbf{28},\mathbf{2})}\big)_{81,-}+\ts{\chi}_{1}\big(t_{(\mathbf{\fl{28}},\mathbf{2})}\big)_{56,-}+\ts{\chi}_{2}\big(t_{(\mathbf{\fl{28}},\mathbf{2})}\big)_{74,-}\right)\right] \\
@@
 		&\ \qquad+\ts{\Omega}\Big(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{4}{}^{4}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{5}{}^{5}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{6}{}^{6}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{7}{}^{7}\Big)\bigg] \\
-		& \times \exp\left[\ln(T)\left(\frac{1}{120}\,\big(t_{(\mathbf{63},\mathbf{1})}\big)_{I}{}^{I}-\frac{1}{120}\,\big(t_{(\mathbf{63},\mathbf{1})}\big)_{A}{}^{A}-\frac{1}{2}\,\big(t_{(\mathbf{1},\mathbf{3})}\big)_{1}\right)\right],
-	\end{aligned}
+		& \times \exp\left[\psi\left(\frac{1}{120}\,\big(t_{(\mathbf{63},\mathbf{1})}\big)_{I}{}^{I}-\frac{1}{120}\,\big(t_{(\mathbf{63},\mathbf{1})}\big)_{A}{}^{A}-\frac{1}{2}\,\big(t_{(\mathbf{1},\mathbf{3})}\big)_{1}\right)\right]\,,
+	\end{split}
 \end{equation}
@@
 The $(\chi_{i},\ts{\chi}_{i},\zeta_{i},\ts{\zeta}_{i})$ deformations excite the $(\mathbf{6},\mathbf{1})_{2}$ and $(\mathbf{1},\mathbf{6})_{2}$ generators in the branching~\eqref{eq:56inSL4SL4}.
-\CE{(Describe what we do for $T$?
+\CE{(Describe what we do for $T = \exp{\psi}$?
 I think there is some freedom in the coeff there.)} \CE{(Describe what we do for $\Omega$?
@@
 Possible to change the signs to $(+,+,-,-)$, but very long to compute uplift.)}
+
+\EM{Kinetic terms? Might be interesting for the S-fold deformations to see what kind of metric we have on the moduli space.}
 
@@
 \subsection{Moduli in 10 dimensions}
-The seven form flux is unaffected by the deformations.
-
-\paragraph{\boldmath $(\chi, \ts{\chi}, T)$}
-Using spherical coordinates for both spheres:
-\begin{equation}
-	\begin{aligned}
+The consistent truncation Ansatz we constructed in this paper can be used to uplift the full 11-parameter family of AdS$_3$ vacua of the 3-dimensional gauged supergravity in \eqref{eq:FullDeformation} to IIB supergravity.
+However, this full 11-parameter solution can quickly become unwieldy.
+Therefore, here we will instead focus on a few interesting subsets of deformations.
+
+%In all cases, the internal seven form flux is unaffected by the deformations, i.e. $H_{(3)}\vert_{AdS_3}$ remains unchanged, so that we will not give it explicitly below.
+
+\paragraph{\boldmath $(\chi, \ts{\chi}, \psi)$}
+Using Hopf coordinates for both $S^3$'s we can write the 5-parameter deformation involving $(\chi_i, \ts{\chi}_i, \psi)$, $i = 1,2$, as follows:
+\begin{equation}
+	\begin{split}
 		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^{2}({\rm AdS}_{3}) +\alpha^{2}\left(\d\theta^{2} + \cos^{2}(\theta)\,\d\phi'_{1}{}^{2} + \sin^{2}(\theta)\,\d\phi'_{2}{}^{2} \right) \\
-		&\quad +\d\ts{\theta}^{2} + \cos^{2}(\ts{\theta})\,\d\ts{\phi}'_{1}{}^{2} + \sin^{2}(\ts{\theta})\,\d\ts{\phi}'_{2}{}^{2} + T^{2}\,\d z^{2}, \\[5pt]
-		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) + 2\,\alpha^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge\d\phi'_{1}\wedge\d\phi'_{2}+ 2\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge\d\ts{\phi}'_{1}\wedge\d\ts{\phi}'_{2},
-	\end{aligned}
-\end{equation}
-where
+		&\quad +\d\ts{\theta}^{2} + \cos^{2}(\ts{\theta})\,\d\ts{\phi}'_{1}{}^{2} + \sin^{2}(\ts{\theta})\,\d\ts{\phi}'_{2}{}^{2} + e^{2\psi}\,\d z^{2}\,, \\[5pt]
+		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) + 2\,\alpha^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge\d\phi'_{1}\wedge\d\phi'_{2}+ 2\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge\d\ts{\phi}'_{1}\wedge\d\ts{\phi}'_{2}\,,
+	\end{split}
+\end{equation}
+where \EM{Can we double check the $\alpha$'s? I'm slightly confused}
 \begin{equation}
 	\begin{cases}
-		\displaystyle \d\phi'_{1} = \d\phi_{1} + \frac{1}{\alpha}\,\chi_{1}\,\d z,\\[6pt]
-		\displaystyle \d\phi'_{2} = \d\phi_{2} + \frac{1}{\alpha}\,\chi_{2}\,\d z,
+		\displaystyle \d\phi'_{1} = \d\phi_{1} + \frac{1}{\alpha}\,\chi_{1}\,\d z\,,\\[6pt]
+		\displaystyle \d\phi'_{2} = \d\phi_{2} + \frac{1}{\alpha}\,\chi_{2}\,\d z\,,
 	\end{cases}\qquad
 	\begin{cases}
-		\d\ts{\phi}'_{1} = \d\ts{\phi}_{1} + \ts{\chi}_{1}\,\d z,\\[6pt]
-		\d\ts{\phi}'_{2} = \d\ts{\phi}_{2} + \ts{\chi}_{2}\,\d z.
+		\d\ts{\phi}'_{1} = \d\ts{\phi}_{1} + \ts{\chi}_{1}\,\d z\,,\\[6pt]
+		\d\ts{\phi}'_{2} = \d\ts{\phi}_{2} + \ts{\chi}_{2}\,\d z\,.
 	\end{cases}
@@
 
-This deformation breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries.
-Concerning the spectrum, the conformal dimension of each physical field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
+This 5-parameter deformation generically breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries.
+The $\chi_i$, $\ts{\chi}_i$, $i = 1, 2$ deformations are analogous to the two-parameter ``flat deformations'' \cite{Guarino:2021hrc} of AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
+From the 4-dimensional perspective obtained after reducing on $S^3 \times S^3$, these deformations correspond to turning on Wilson lines for the $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ gauge fields along $S^1$.
+The $\psi$ deformation is even simpler: it just rescales the $S^1$ radius.
+These $\chi_i$, $\ts{\chi}_i$, $\psi$ deformations are completely analogous to $\mathbb{C}$-structure deformations of $T^2$, with the $\chi_i$, $\ts{\chi}_i$ corresponding to the real part and the $\psi$ deformation to the imaginary part of the $\mathbb{C}$-structure deformation.
+
+Therefore, these deformations affect the Kaluza-Klein spectrum as follows: the conformal dimension of each physical field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
 \begin{equation} \label{eq:confdimshiftchi}
-	2\pi n\longrightarrow \frac{2\pi n}{T} + \frac{1}{2T}\Big((q_{\rm L}+q_{\rm R})\,\chi_{1}+(q_{\rm L}-q_{\rm R})\,\chi_{2}+ \alpha\,(\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1}+ \alpha\,(\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big),
-\end{equation}
-where the $q$ denote the charges under the different ${\rm U}(1)$.
+	2\pi n\longrightarrow e^{-2\psi} \left[ 2\pi n + \Big((q_{\rm L}+q_{\rm R})\,\chi_{1}+(q_{\rm L}-q_{\rm R})\,\chi_{2}+ \alpha\,(\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1}+ \alpha\,(\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big) \right]\,,
+\end{equation}
+where the $q$ denote the charges under the different ${\rm U}(1)$. \EM{Somewhere here, we should give the character for all multiplets.}
 
@@
 \begin{equation}
-	\big(\nicefrac{1}{2},\nicefrac{1}{2};0,0\big) \quad {\rm and} \quad \big(0,0;\nicefrac{1}{2},\nicefrac{1}{2}\big).
+	\big(\nicefrac{1}{2},\nicefrac{1}{2};0,0\big) \quad {\rm and} \quad \big(0,0;\nicefrac{1}{2},\nicefrac{1}{2}\big)\,.
 \end{equation}
@@
 \begin{equation}
-	\begin{aligned}
-		\left(\pm1,\pm1;0,0\right):\quad \Delta=\frac{1}{2}+\sqrt{1+\frac{\left(\chi_{1}+\chi_{2}+\alpha\,\big(\ts{\chi}_{1}-\ts{\chi}_{2}\right)^{2}\big)}{4\,T^{2}(1+\alpha^{2})}}, \\
-		\left(\pm1,\mp1;0,0\right):\quad \Delta=\frac{1}{2}+\sqrt{1+\frac{\left(\chi_{1}+\chi_{2}-\alpha\,\big(\ts{\chi}_{1}-\ts{\chi}_{2}\right)^{2}\big)}{4\,T^{2}(1+\alpha^{2})}}, \\
-		\left(0,0;\pm1,\pm1\right):\quad \Delta=\frac{1}{2}+\sqrt{1+\frac{\left(\chi_{1}-\chi_{2}+\alpha\,\big(\ts{\chi}_{1}+\ts{\chi}_{2}\right)^{2}\big)}{4\,T^{2}(1+\alpha^{2})}}, \\
-		\left(0,0;\pm1,\mp1\right):\quad \Delta=\frac{1}{2}+\sqrt{1+\frac{\left(\chi_{1}-\chi_{2}+\alpha\,\big(\ts{\chi}_{1}+\ts{\chi}_{2}\right)^{2}\big)}{4\,T^{2}(1+\alpha^{2})}}.
-	\end{aligned}
-\end{equation}
-SUSY enhancement points are then given by combinations of the parameters that leave some modes invariant with $\Delta=\nicefrac{3}{2}$.
+	\begin{split}
+		\left(\pm1,\pm1;0,0\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(%2\pi n +
+		\chi_{1}+\chi_{2}+\alpha\,\big(\ts{\chi}_{1}-\ts{\chi}_{2}\big)\right)^{2}}{4\, e^{2\psi}\, (1+\alpha^{2})}}\,, \\
+		\left(\pm1,\mp1;0,0\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(%2\pi n +
+		\chi_{1}+\chi_{2}-\alpha\,\big(\ts{\chi}_{1}-\ts{\chi}_{2}\big)\right)^{2}}{4\, e^{2\psi}\, (1+\alpha^{2})}}\,, \\
+		\left(0,0;\pm1,\pm1\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(%2\pi n +
+		\chi_{1}-\chi_{2}+\alpha\,\big(\ts{\chi}_{1}+\ts{\chi}_{2}\big)\right)^{2}}{4\, e^{2\psi}\, (1+\alpha^{2})}}\,, \\
+		\left(0,0;\pm1,\mp1\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(%2\pi n + 
+		\chi_{1}-\chi_{2} - \alpha\,\big(\ts{\chi}_{1}+\ts{\chi}_{2}\big)\right)^{2}}{4\, e^{2\psi}\, (1+\alpha^{2})}}\,.
+	\end{split}
+\end{equation}
+\EM{There was some typo with the $^2$ only acting on the $\alpha$ bracket.}\\
+SUSY enhancement points are then given by combinations of the parameters that yield $\Delta = \nicefrac32$.
+This can either happen by leaving some modes with $\Delta=\nicefrac{3}{2}$ invariant, or where some other, originally massive gravitini outside the consistent truncation, i.e.
+with conformal dimension given by \eqref{eq:confdims3s3s1} with $n \neq 0$, obain $\Delta = \nicefrac32$.
 The different possibilities are listed below.
@@
 	\item {\boldmath ${\cal N}=2$} The four-dimensional hypersurfaces
-	\begin{equation}
-		\chi_{2} = \chi_{1} \pm\alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2}) \quad {\rm or}\quad \chi_{2} = -\chi_{1} \pm\alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2}),
-	\end{equation}
-	give enhancements to ${\cal N}=(2,0)$ and ${\cal N}=(0,2)$, respectively. The spectrum then organizes into multiplets of $\SU{1\vert1,1}$.
+	\begin{equation} \label{eq:N2}
+		\chi_{2} = \chi_{1} \pm\alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2})% + 2\pi k 
+		\quad {\rm or}\quad \chi_{2} = -\chi_{1} \pm\alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2})% + 2\pi k \,, \qquad k \in \mathbb{Z}
+		\,,
+	\end{equation}
+	give enhancements to ${\cal N}=(2,0)$ and ${\cal N}=(0,2)$, respectively. On this hypersurface \eqref{eq:N2}, the spectrum then organizes into multiplets of $\SU{1\vert1,1}$.
 	\item {\boldmath ${\cal N}=4$} Choosing
-	\begin{equation}
+	\begin{equation} \label{eq:N4Large}
 		\begin{cases}
-			\chi_{2} = \chi_{1},\\
-			\ts{\chi}_{2} = -\ts{\chi}_{1},
+			\chi_{2} = \chi_{1}\,,\\% + 2\pi k\,,\\
+			\ts{\chi}_{2} = -\ts{\chi}_{1}\,,% + 2\pi l / \alpha \,,
+		\end{cases}
+		\quad {\rm or }\quad
+		\begin{cases}
+			\chi_{2} = - \chi_{1}\,,\\% + 2\pi k\,,\\
+			\ts{\chi}_{2} = \ts{\chi}_{1}\,,% + 2\pi l / \alpha \,,
+		\end{cases}% \qquad k, l \in \mathbb{Z} \,,
+	\end{equation}
+	leads to enhancements to ${\cal N}=(4,0)$ and ${\cal N}=(0,4)$, respectively.
+On these three-dimensional hyper-surfaces \eqref{eq:N4Large}, the isometry group is $\SO{4}\times {\rm U}(1)^{2}$ and the spectrum reorganizes into multiplets of $D^{1}(2,1;\alpha)$.
+
+	Another possibility is to set
+	\begin{equation} \label{eq:N4Small}
+		\begin{cases}
+			\ts{\chi}_{1} = \pm \chi_{1}/\alpha\,,\\% + 2\pi k \,,\\
+			\ts{\chi}_{2} = \mp \chi_{2}/\alpha\,,% + 2\pi l\,,
 		\end{cases}
@@
 		\begin{cases}
-			\chi_{2} = - \chi_{1},\\
-			\ts{\chi}_{2} = \ts{\chi}_{1},
-		\end{cases}
-	\end{equation}
-	leads to enhancements to ${\cal N}=(4,0)$ and ${\cal N}=(0,4)$, respectively.
-On these three-dimensional hyper-surfaces, the isometry group is $\SO{4}\times {\rm U}(1)^{2}$ and the spectrum reorganizes into multiplets of $D^{1}(2,1;\alpha)$.
-Another possibility is to set
-	\begin{equation}
+			\ts{\chi}_{1} = \pm \chi_{2}/\alpha\,,\\% + 2\pi k\,,\\
+			\ts{\chi}_{2} = \mp \chi_{1}/\alpha\,,% + 2\pi l\,,
+		\end{cases}% \qquad k, l \in \mathbb{Z} \,,
+	\end{equation}
+	giving 3-parameter families of ${\cal N}=(2,2)$ solutions, with multiplets of $\SU{1\vert1,1}_{\rm L}\times\SU{1\vert1,1}_{\rm R}$.
+	\item {\boldmath ${\cal N}=6$} Finally, for
+	\begin{equation} \label{eq:N6}
 		\begin{cases}
-			\ts{\chi}_{1} = \pm \chi_{1}/\alpha,\\
-			\ts{\chi}_{2} = \mp \chi_{2}/\alpha,
+			\chi_{2} = \chi_{1}\,,\\% + 2\pi k\,,\\
+			\ts{\chi}_{1} = %\left(
+			\pm \chi_{1}% + 2 \pi l \right)
+			/\alpha\,,\\
+			\ts{\chi}_{2} = %\left(
+			\mp \chi_{1}% + 2 \pi m \right)
+			/\alpha\,,
 		\end{cases}
@@
 		\begin{cases}
-			\ts{\chi}_{1} = \pm \chi_{2}/\alpha,\\
-			\ts{\chi}_{2} = \mp \chi_{1}/\alpha,
-		\end{cases}
-	\end{equation}
-	giving 3-parameter families of ${\cal N}=(2,2)$ solutions, with multiplets of $\SU{1\vert1,1}_{\rm L}\times\SU{1\vert1,1}_{\rm R}$.
-	\item {\boldmath ${\cal N}=6$} Finally, for
-	\begin{equation}
-		\begin{cases}
-			\chi_{2} = \chi_{1},\\
-			\ts{\chi}_{1} = \pm \chi_{1}/\alpha,\\
-			\ts{\chi}_{2} = \mp \chi_{1}/\alpha,
-		\end{cases}
-		\quad {\rm or}\quad
-		\begin{cases}
-			\chi_{2} = -\chi_{1},\\
-			\ts{\chi}_{1} = \pm \chi_{1}/\alpha,\\
-			\ts{\chi}_{2} = \mp \chi_{1}/\alpha,
-		\end{cases}
+			\chi_{2} = -\chi_{1}\,,\\% + 2\pi k\,,\\
+			\ts{\chi}_{1} = %\left(
+			\pm \chi_{1}% + 2 \pi l\right) 
+			/\alpha\,,\\
+			\ts{\chi}_{2} = %\left(
+			\mp \chi_{1}% + 2\pi m \right)
+			/\alpha\,,
+		\end{cases}% \qquad k, l, m \in \mathbb{Z} \,,
 	\end{equation}
@@
 
-\paragraph{\boldmath $(\zeta,\ts{\zeta},T)$}
+In the above cases, it is easy to see from \eqref{eq:confdimshiftchi} that the spectrum  is invariant under $\chi_i \rightarrow \chi_i + 2\pi k_i$, $\ts{\chi}_i \rightarrow \ts{\chi}_i + 2\pi \ts{k}_i/\alpha$, for $k_i$, $\ts{k}_i \in \mathbb{Z}$, with the SUSY enhancements also occurring if the relations \eqref{eq:N2}, \eqref{eq:N4Large}, \eqref{eq:N4Small} or \eqref{eq:N6} are satisfied up to integer shifts.
+We will return to this point below in section \ref{s:Compact}, when discussing compactness of the moduli space.
+
+For generic values of $\chi_i$, $\ts{\chi}_i$, the AdS$_3$ vacuum will be completely non-supersymmetric.
+However, it is easy to see from inspection of the spectrum \eqref{eq:confdims3s3s1} and \eqref{eq:confdimshiftchi} that the spectrum is bounded from below by the masses of the 3-dimensional gauged supergravity modes at the ${\cal N}=(4,4)$ supersymmetric origin.
+Therefore, these non-supersymmetric AdS$_3$ vacua are still perturbatively stable within IIB supergravity and, similarly to \cite{Giambrone:2021wsm} suggest that there may be a dual non-supersymmetric conformal manifold if there are no instabilities beyond supergravity, such as non-perturbative instabilities triggered by brane nucleation or non-vanishing $\beta$-functions of marginal multi-trace operators \EM{add citations}.
+
+\paragraph{\boldmath $(\zeta,\ts{\zeta},\psi)$}
 Again with spherical coordinates:
 \begin{equation}
-	\begin{aligned}
+	\begin{split}
 		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) -\Delta\,\d z^{2}\\
 		&+ \alpha^{2}\Big[\d\theta^{2} + \Delta\left(\cos^{2}(\theta)\,\d\phi_{1}^{2}+\sin^{2}(\theta)\,\d\phi_{2}^{2}\right)\Big]+\d\ts{\theta}^{2} + \Delta\left(\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}^{2}+\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}^{2}\right)\\
-		&+\Delta\,T^{2}\,\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,T^{2}\,\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
-		&+\Delta\,T^{2}\,\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,T^{2}\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
-		&-2\,\alpha\,\Delta\,T^{2}\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
-		&+\Delta\,T^{2}\,\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+\Delta\,T^{2}\,\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\\
-		&+\Delta\,T^{2}\,\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\Delta\,T^{2}\,\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2},
-	\end{aligned}
+		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
+		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
+		&-2\,\alpha\,\Delta\,e^{2\psi}\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
+		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\\
+		&+\Delta\,e^{2\psi}\,\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2},
+	\end{split}
 \end{equation}
@@
 \begin{equation}
-	\Delta^{-1} = 1+T^{2}\left(\zeta_{1}^{2}\sin^{2}(\theta)+\zeta_{2}^{2}\cos^{2}(\theta)+\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})+\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})\right).
+	\Delta^{-1} = 1+e^{2\psi}\left(\zeta_{1}^{2}\sin^{2}(\theta)+\zeta_{2}^{2}\cos^{2}(\theta)+\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})+\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})\right)\,.
 \end{equation}.
@@
 \begin{equation}
-	\begin{aligned}
+	\begin{split}
 		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) -\Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\,\d z^{2}\\
@@
 		&+\Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big[e^{\ts{\Omega}}\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2}\Big],
+	\end{split}
+\end{equation}
+with the warp factor
+\begin{equation}
+	\begin{aligned}
+	\Delta^{-1} &= \Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\\
+	&+\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\\
+	&+\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right).
 	\end{aligned}
-\end{equation}
-with the warp factor
-\begin{equation}
-	\Delta^{-1} = 1+T^{2}\left(\zeta_{1}^{2}\sin^{2}(\theta)+\zeta_{2}^{2}\cos^{2}(\theta)+\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})+\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})\right).
 \end{equation}.
@@
 
-\subsection{Compactification of the moduli space}
+\subsection{Compactification of the moduli space} \label{s:Compact}
+We can use the Kaluza-Klein spectrum and the uplift of the 3-dimensional gauged supergravity models to IIB supergravity to understand properties of the dual CFTs that are obscured in the lower-dimensional supergravities.
+One such aspect is the compactness of the conformal manifold.
+Consider the deformations $\chi_i$, $\ts{\chi}_i$, which appear non-compact in 3-dimensional ${\cal N}=16$ gauged supergravity, with only the point $\chi_i = \ts{\chi}_i = 0$ having ${\cal N}=(4,4)$ supersymmetry.
+The subset of these deformations corresponding to the SUSY lines $\chi_1 = \chi_2 = \chi$, $\ts{\chi}_i = 0$, \EM{Is this right?} was analysed in the half-maximal theory in \cite{Eloy:2021fhc}.
+Again, within 3-dimensional ${\cal N}=8$ supergravity, this deformation is non-compact, and remains non-compact even after uplifting to 6-dimensional supergravity on $S^3$, with no periodicity in $\chi$ observed in the KK spectrum of the 6-dimensional solution \cite{Eloy:2021fhc}.
+
+However, from  \eqref{eq:confdims3s3s1}, \eqref{eq:confdimshiftchi}, \eqref{eq:Multiplets} we see that the full Kaluza-Klein spectrum is invariant under the shifts
+\begin{equation} \label{eq:ShiftSymmetries}
+	\begin{split}
+		\chi_i &\rightarrow \chi_i + 2\pi k_i\,, \\
+		\ts{\chi}_i &\rightarrow \ts{\chi}_i + 2\pi \ts{k}_i/\alpha \,,
+	\end{split}
+\end{equation}
+for $k_i$, $\ts{k}_i \in \mathbb{Z}$.
+In these cases, higher KK modes on the $S^1$ outside the ${\cal N}=16$ truncation replace those within the consistent truncation.
+Therefore, even though neither the 3-dimensional gauged supergravity, nor 6-dimensional supergravity is invariant under these shifts, upon lifting to the full 10-dimensional IIB theory, the higher KK modes on $S^1$ restore the invariance under the shifts, just as in the analogous deformations studied in AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
+This highlights the importance of the $S^1$ direction, which is often ignored in holographic applications \EM{Maybe remove this last sentence?}.
+
+%One interesting aspect that we observe is that the invariance of the KK spectrum under the shifts requires the inclusion of the $S^1$ direction.
+A subset of the $\chi_i$, $\ts{\chi}_i$ moduli, corresponding to the SUSY line $\chi_1 = \chi_2 = \chi$, $\ts{\chi}_i = 0$, was analysed in the half-maximal theory in \cite{Eloy:2021fhc}.
+The deformation $\chi$ is both non-compact in the 3-dimensional half-maximal gauged supergravity and in its 6-dimensional uplift, with no periodicity in $\chi$ observed in the KK spectrum of the 6-dimensional solution \cite{Eloy:2021fhc}.
+However, as we have shown, the full uplift to 10 dimensions compactifies the moduli space, thanks to the $S^1$ direction, which is often ignored in holographic applications \EM{Maybe forget this last sentence
+
+The compactification of the moduli space in 10 dimensions can also be understood geometrically.
+Each of $\chi_i$, $\ts{\chi}_i$ corresponds to the real part of the complex structure modulus of a $T^2$ fibration with local coordinates $\phi_i$, $\ts{\phi}_i$ together with $z$, respectively.
+Explicitly, the complex structure is given by \EM{Not sure about this, see comment about $\alpha$ above}
+\begin{equation} \label{eq:T2CStructure}
+	\tau = i\,\frac{e^\psi}{\alpha} + \frac1\alpha \chi \,.
+\end{equation}
+Under this identification, the shifts \eqref{eq:ShiftSymmetries} correspond to Dehn twists, or $T$-transformations, of the torus, which belong to the modular group $\SL{2,\mathbb{Z}}$, just as for AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
+
+Given the interpretation of the shifts \eqref{eq:ShiftSymmetries} as $T$-transformations of a $T^2$-fibration, it is natural to ask whether $S$-transformations of these $T^2$ would also leave the AdS$_3 \times S^3 \times S^3 \times S^1$ solution invariant.
+The $S$-transformation acts on the moduli as
+\begin{equation} \label{eq:Stransform}
+	\psi \rightarrow - \psi \,,
+\end{equation}
+thus inverting the radius of the $S^1$.
+The KK spectrum \eqref{eq:confdims3s3s1}, \eqref{eq:confdimshiftchi} is clearly not invariant under this transformation.
+However, the $S$-transformation takes us out of the regime of validity of supergravity, with new string degrees of freedom potentially becoming light.
+Indeed, in this case, after the transformation \eqref{eq:Stransform}, strings wound around $S^1$ will become light, and one would expect them to replace the KK modes that have become heavy, realising the T-duality on $S^1$.
+Thus, in the full IIB string theory, the moduli space of each $T^2$ fibration with complex structure \eqref{eq:T2CStructure} should be identified under the M\"{o}bius group $\SL{2,\mathbb{Z}}$.
+\EM{Can we check the T-dual explicitly?
+Maybe we need a different gauge choice for $C_6$ so that it does not depend on $z$.
+Can we describe the $T^4 \times S^1$ a bit better instead of as a collection of $T^2$'s?}
 

### 2023-06-14 Draft_3dH3.tex
Answers to Emanuel comments.

@@
 \end{equation}
-where \EM{Note corrected sign in first equation!}
+where \EM{Note corrected sign in first equation!} \CE{(Sure? I took it from eq. (4.9) of ref.~\cite{Galli:2022idq}.)}
 \begin{equation} \label{eq:3dCovDeriv}
@@
 On the other hand, the consistent truncation on $S^3$ is conveniently described by twist matrices living in $\SL{4} \simeq \SO{3,3}$ \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou} \EM{I think the twist matrix of \cite{Baguet:2015iou,Lee:2014mla,Hohm:2014qga} coincide in the $\SL{4}$ case, right?
-Camille, do you agree?} with the embedding $\SO{3,3} \subset \SO{4,4} \subset \SO{8,4}$.
+Camille, do you agree?} \CE{(Yes.)} with the embedding $\SO{3,3} \subset \SO{4,4} \subset \SO{8,4}$.
 However, the twist matrix in \cite{Eloy:2021fhc} differs from this $\SO{3,3}$ twist matrix \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou} by an additional parameter, $\lambda$, which gives rise to an external 3-form flux or, equivalently, a new internal 3-form flux.
@@
 \subsubsection{The $S^3$ twist matrix}
-\EM{Move to appendix?!?!}\\
+\EM{Move to appendix?!?!} \CE{(I think I would say yes)}\\
 Since we will use it throughout this paper, let us construct the $\SL{4} \simeq \SO{3,3}$ twist matrix that describes the consistent truncation on $S^3$.
@@
 \end{equation}
-with $C_A$ an element of the $\mathbf{6_{2}}$, and $\left( t^A \right)^{MN}$ the corresponding to $\SO{4,4}$ generator whose only non-zero component is
+with $C_A$ an element of the $\mathbf{6_{2}}$, and $\left( t^A \right)^{MN}$ the generator corresponding to $\SO{4,4}$ whose only non-zero component is
 \begin{equation}
@@
 \end{equation}
-explicitly using \eqref{eq:C2S3example} and setting $C^i = \lambda\, \xi^i$, with $\nabla_i \xi^i = 1$, in the notation of \cite{Eloy:2021fhc}, we obtain precisely the twist matrix used in \cite{Eloy:2021fhc} for the consistent truncation of 6-dimensional ${\cal N}=(1,1)$ supergravity on $S^3$ with $H_3$ flux.
+explicitly using \eqref{eq:C2S3example} and setting $C^i = \lambda\, \xi^i$, \CE{(factor $\rho^{-1}$?)} with $\nabla_i \xi^i = 1$, in the notation of \cite{Eloy:2021fhc}, we obtain precisely the twist matrix used in \cite{Eloy:2021fhc} for the consistent truncation of 6-dimensional ${\cal N}=(1,1)$ supergravity on $S^3$ with $H_3$ flux.
 %\EM{Give precise form of $C^i$ such that we recover $\lambda$?}
@@
 Therefore, we find exactly one singlet $\SL{4}_1 \times \SL{4}_2$ generator, which we can write as $t_{1238}$, corresponding to a 6-form potential.
-The other $\SL{4}_1 \times \SL{4}_2$ singlet generator, $t_{4567}$, only differs by a compact generator and thus does not corresponding to a different physical field.
+The other $\SL{4}_1 \times \SL{4}_2$ singlet generator, $t_{4567}$, only differs by a compact generator and thus does not correspond to a different physical field.
 Finally, the other elements of the $\SL{2}$ doublet of 6-form potential can be mapped to the $\mathbf{\left(4,\overline{4}\right)_{2}} \oplus \mathbf{\left(\overline{4},4\right)_{-2}}$ generators, specifically $t_7{}^8$ and $t_8{}^7$ and are clearly not $\SL{4}$ singlets.
@@
 We choose this value of $\lambda$ from here onwards.
-\EM{Presumably condition is on $\lambda^2$ and the sign of $\lambda$ is fixed by SUSY (which we can ignore)?}
+\EM{Presumably condition is on $\lambda^2$ and the sign of $\lambda$ is fixed by SUSY (which we can ignore)?} \CE{(Exactly, the sign of $\lambda$ exchanges ${\cal N}_{\rm L}$ and ${\cal N}_{\rm R}$ in ${\cal N}=({\cal N}_{\rm L},{\cal N}_{\rm R})$)}
 
@@
 The even part of $D^{1}(2,1;\alpha)$ is isomorphic to ${\rm SL}(2,\mathbb{R})\times{\rm SO}(3)\times\ts{{\rm SO}(3)}$ and the bosonic isometries of the ${\rm AdS}_{3}\times S^{3}\times\ts{S}^{3}$ background are built from the even part of ${\cal G}$.
-The ${\rm AdS}_{3}$ isometry group is ${\rm SO}(2,2)\simeq{\rm SL}(2,\mathbb{R})_{\rm L}\times{\rm SL}(2,\mathbb{R})_{\rm R}$, and the factors ${\rm SO}(3)_{\rm L}\times{\rm SO}(3)_{\rm R}\times\ts{{\rm SO}(3)}_{\rm L}\times\ts{{\rm SO}(3)}_{\rm R}\simeq{\rm SO}(4)\times\ts{SO(4)}$ combine into the isometry groups of the two spheres.
+The ${\rm AdS}_{3}$ isometry group is ${\rm SO}(2,2)\simeq{\rm SL}(2,\mathbb{R})_{\rm L}\times{\rm SL}(2,\mathbb{R})_{\rm R}$, and the factors ${\rm SO}(3)_{\rm L}\times{\rm SO}(3)_{\rm R}\times\ts{{\rm SO}(3)}_{\rm L}\times\ts{{\rm SO}(3)}_{\rm R}\simeq{\rm SO}(4)\times\ts{{\rm SO}(4)}$ combine into the isometry groups of the two spheres.
 The spectrum organizes into multiplets of ${\cal G}$, made out of products of long representations $[\ell,\ts{\ell}]$ of $D^{1}(2,1;\alpha)$ (see app.~\ref{app:d21a} for a review of the representations of $D^{1}(2,1;\alpha)$).
@@
 In particular, without any attempts at being exhaustive \EM{(too strong?
-does this make us sound lazy?)}, we identified a continuous 11-parameter family of AdS$_3$ solutions, connected to the origin and given by the \EE coset representative \CE{($\fl{28}\leftrightarrow28$ compared to the code, I think we made a mistake and confused down and up indices)}
+does this make us sound lazy?)} \CE{(I think it's fine.)}, we identified a continuous 11-parameter family of AdS$_3$ solutions, connected to the origin and given by the \EE coset representative \CE{($\fl{28}\leftrightarrow28$ compared to the code, I think we made a mistake and confused down and up indices)}
 \begin{equation} \label{eq:FullDeformation}
@@
 		& \times \exp\left[\sqrt{2}\left(\zeta_{1}\big(t_{(\mathbf{\fl{28}},\mathbf{2})}\big)_{23,+}+\zeta_{2}\big(t_{(\mathbf{\fl{28}},\mathbf{2})}\big)_{81,+}+\ts{\zeta}_{1}\big(t_{(\mathbf{28},\mathbf{2})}\big)_{56,+}+\ts{\zeta}_{2}\big(t_{(\mathbf{28},\mathbf{2})}\big)_{74,+}\right)\right] \\
-		& \times \exp\bigg[\Omega\Big(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{1}{}^{1}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{2}{}^{2}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{3}{}^{3}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{8}{}^{8}\Big)\\
-		&\ \qquad+\ts{\Omega}\Big(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{4}{}^{4}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{5}{}^{5}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{6}{}^{6}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{7}{}^{7}\Big)\bigg] \\
+		& \times \exp\bigg[\frac{\Omega}{120}\Big(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{1}{}^{1}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{2}{}^{2}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{3}{}^{3}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{8}{}^{8}\Big)\\
+		&\ \qquad+\frac{\ts{\Omega}}{120}\Big(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{4}{}^{4}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{5}{}^{5}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{6}{}^{6}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{7}{}^{7}\Big)\bigg] \\
 		& \times \exp\left[\psi\left(\frac{1}{120}\,\big(t_{(\mathbf{63},\mathbf{1})}\big)_{I}{}^{I}-\frac{1}{120}\,\big(t_{(\mathbf{63},\mathbf{1})}\big)_{A}{}^{A}-\frac{1}{2}\,\big(t_{(\mathbf{1},\mathbf{3})}\big)_{1}\right)\right]\,,
@@
 \EM{Kinetic terms? Might be interesting for the S-fold deformations to see what kind of metric we have on the moduli space.}
+
+\begin{equation}
+	\begin{aligned}
+		\d s^{2}_{\rm Zam.} &= -\frac{1}{2}\bigg[e^{2\psi}\left(e^{-\Omega}\,\d\zeta_{1}^{2}+e^{\Omega}\,\d\zeta_{2}^{2}+e^{\ts{\Omega}}\,\d\ts{\zeta}_{1}^{2}+e^{-\ts{\Omega}}\,\d\ts{\zeta}_{2}^{2}\right) \\
+		&+ \left(e^{-2\psi-\ts{\Omega}}+\ts{\zeta}_{1}^{2}+e^{-\Omega-\ts{\Omega}}\zeta_{1}^{2}\right)\left(e^{\Omega+\ts{\Omega}}+e^{2\psi+\Omega}\ts{\zeta}_{2}^{2}+e^{2\psi+\ts{\Omega}}\zeta_{1}^{2}\right) \,\d\chi_{1}^{2} \\
+		&+ \left(e^{-2\psi-\Omega}+e^{-\Omega-\ts{\Omega}}\ts{\zeta}_{2}^{2}+\zeta_{2}^{2}\right)\left(1+e^{2\psi+\ts{\Omega}}\ts{\zeta}_{1}^{2}+e^{2\psi+\Omega}\zeta_{2}^{2}\right) \,\d\chi_{2}^{2}\\
+		&+ \left(e^{-2\psi-\ts{\Omega}}+\ts{\zeta}_{1}^{2}+e^{-\Omega-\ts{\Omega}}\zeta_{1}^{2}\right)\left(1+e^{2\psi+\ts{\Omega}}\ts{\zeta}_{1}^{2}+e^{2\psi+\Omega}\zeta_{2}^{2}\right) \,\d\ts{\chi}_{1}^{2} \\
+		&+ \left(e^{-2\psi-\Omega}+e^{-\Omega-\ts{\Omega}}\ts{\zeta}_{2}^{2}+\zeta_{2}^{2}\right)\left(e^{\Omega+\ts{\Omega}}+e^{2\psi+\Omega}\ts{\zeta}_{2}^{2}+e^{2\psi+\ts{\Omega}}\zeta_{1}^{2}\right) \,\d\ts{\chi}_{2}^{2} + \ldots \\
+		&+2\,\d\psi^{2}\bigg]
+	\end{aligned}
+\end{equation}
 
@@
 \paragraph{\boldmath $(\chi, \ts{\chi}, \psi)$}
-Using Hopf coordinates for both $S^3$'s we can write the 5-parameter deformation involving $(\chi_i, \ts{\chi}_i, \psi)$, $i = 1,2$, as follows:
+Using Hopf coordinates for both $S^3$'s we can write the 5-parameter deformation involving $(\chi_i, \ts{\chi}_i, \psi)$, $i = 1,2$, as follows: \CE{(Are those Hopf coordinates?)}
 \begin{equation}
@@
 \end{equation}
-where \EM{Can we double check the $\alpha$'s? I'm slightly confused}
+where \EM{Can we double check the $\alpha$'s? I'm slightly confused} \CE{(I think it's correct.)}
 \begin{equation}
@@
 \end{equation}
-\EM{There was some typo with the $^2$ only acting on the $\alpha$ bracket.}\\
 SUSY enhancement points are then given by combinations of the parameters that yield $\Delta = \nicefrac32$.
 This can either happen by leaving some modes with $\Delta=\nicefrac{3}{2}$ invariant, or where some other, originally massive gravitini outside the consistent truncation, i.e.
-with conformal dimension given by \eqref{eq:confdims3s3s1} with $n \neq 0$, obain $\Delta = \nicefrac32$.
+with conformal dimension given by \eqref{eq:confdims3s3s1} with $n \neq 0$, obtain $\Delta = \nicefrac32$.
 The different possibilities are listed below.
-\CE{(Shall we give the multiplets?
-At least for the truncation?)}
+\CE{(Shall we include the $n$?
+Shall we give the multiplets?
+At least for the truncation?
+Not sure it's worth it.)}
 
@@
 On these three-dimensional hyper-surfaces \eqref{eq:N4Large}, the isometry group is $\SO{4}\times {\rm U}(1)^{2}$ and the spectrum reorganizes into multiplets of $D^{1}(2,1;\alpha)$.
+
+	\CE{(Mention here the SUSY family of \cite{Eloy:2021fhc}.)}
 
@@
 Therefore, these non-supersymmetric AdS$_3$ vacua are still perturbatively stable within IIB supergravity and, similarly to \cite{Giambrone:2021wsm} suggest that there may be a dual non-supersymmetric conformal manifold if there are no instabilities beyond supergravity, such as non-perturbative instabilities triggered by brane nucleation or non-vanishing $\beta$-functions of marginal multi-trace operators \EM{add citations}.
-
-\paragraph{\boldmath $(\zeta,\ts{\zeta},\psi)$}
-Again with spherical coordinates:
-\begin{equation}
-	\begin{split}
-		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) -\Delta\,\d z^{2}\\
-		&+ \alpha^{2}\Big[\d\theta^{2} + \Delta\left(\cos^{2}(\theta)\,\d\phi_{1}^{2}+\sin^{2}(\theta)\,\d\phi_{2}^{2}\right)\Big]+\d\ts{\theta}^{2} + \Delta\left(\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}^{2}+\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}^{2}\right)\\
-		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
-		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
-		&-2\,\alpha\,\Delta\,e^{2\psi}\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
-		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\\
-		&+\Delta\,e^{2\psi}\,\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2},
-	\end{split}
-\end{equation}
-with the warp factor
-\begin{equation}
-	\Delta^{-1} = 1+e^{2\psi}\left(\zeta_{1}^{2}\sin^{2}(\theta)+\zeta_{2}^{2}\cos^{2}(\theta)+\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})+\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})\right)\,.
-\end{equation}.
-
-\CE{(Expression of $H$?)}
-
-\paragraph{\boldmath $(\zeta,\ts{\zeta},\Omega,\ts{\Omega})$}
+\CE{(Mention the continuous limits to SUSY vacua?)}
+
+% \paragraph{\boldmath $(\zeta,\ts{\zeta},\psi)$}
+% Again with spherical coordinates:
+% \begin{equation}
+% 	\begin{split}
+% 		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) -\Delta\,\d z^{2}\\
+% 		&+ \alpha^{2}\Big[\d\theta^{2} + \Delta\left(\cos^{2}(\theta)\,\d\phi_{1}^{2}+\sin^{2}(\theta)\,\d\phi_{2}^{2}\right)\Big]+\d\ts{\theta}^{2} + \Delta\left(\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}^{2}+\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}^{2}\right)\\
+% 		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
+% 		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
+% 		&-2\,\alpha\,\Delta\,e^{2\psi}\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
+% 		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\\
+% 		&+\Delta\,e^{2\psi}\,\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2},
+% 	\end{split}
+% \end{equation}
+% with the warp factor
+% \begin{equation}
+% 	\Delta^{-1} = 1+e^{2\psi}\left(\zeta_{1}^{2}\sin^{2}(\theta)+\zeta_{2}^{2}\cos^{2}(\theta)+\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})+\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})\right)\,.
+% \end{equation}
+
+% \paragraph{\boldmath $(\zeta,\ts{\zeta},\Omega,\ts{\Omega})$}
+% Again with spherical coordinates:
+% \begin{equation}
+% 	\begin{split}
+% 		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) -\Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\,\d z^{2}\\
+% 		&+ \alpha^{2}\Big[\d\theta^{2} + \Delta\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big(e^{\Omega}\cos^{2}(\theta)\,\d\phi_{1}^{2}+\sin^{2}(\theta)\,\d\phi_{2}^{2}\Big)\Big]\\
+% 		&+\d\ts{\theta}^{2} + \Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}^{2}+e^{\ts{\Omega}}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}^{2}\Big)\\
+% 		&+\Delta\,e^{\Omega}\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,e^{\ts{\Omega}}\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
+% 		&+\Delta\,e^{\Omega+\ts{\Omega}}\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
+% 		&-2\,\alpha\,\Delta\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+e^{\Omega}\,\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(e^{\ts{\Omega}}\,\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
+% 		&+\Delta\,\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big[\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+e^{\Omega}\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\Big]\\
+% 		&+\Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big[e^{\ts{\Omega}}\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2}\Big],
+% 	\end{split}
+% \end{equation}
+% with the warp factor
+% \begin{equation}
+% 	\begin{aligned}
+% 	\Delta^{-1} &= \Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\\
+% 	&+\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\\
+% 	&+\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right).
+% 	\end{aligned}
+% \end{equation}
+
+\paragraph{\boldmath $(\zeta,\ts{\zeta},\Omega,\ts{\Omega},\psi)$}
 Again with spherical coordinates:
@@
 		&+\d\ts{\theta}^{2} + \Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}^{2}+e^{\ts{\Omega}}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}^{2}\Big)\\
-		&+\Delta\,e^{\Omega}\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,e^{\ts{\Omega}}\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
-		&+\Delta\,e^{\Omega+\ts{\Omega}}\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
-		&-2\,\alpha\,\Delta\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+e^{\Omega}\,\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(e^{\ts{\Omega}}\,\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
-		&+\Delta\,\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big[\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+e^{\Omega}\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\Big]\\
-		&+\Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big[e^{\ts{\Omega}}\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2}\Big],
+		&+\Delta\,e^{2\psi}\,e^{\Omega}\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,e^{2\psi}\,e^{\ts{\Omega}}\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
+		&+\Delta\,e^{2\psi}\,e^{\Omega+\ts{\Omega}}\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
+		&-2\,\alpha\,\Delta\,e^{2\psi}\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+e^{\Omega}\,\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(e^{\ts{\Omega}}\,\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
+		&+\Delta\,e^{2\psi}\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big[\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+e^{\Omega}\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\Big]\\
+		&+\Delta\,e^{2\psi}\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big[e^{\ts{\Omega}}\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2}\Big],
 	\end{split}
@@
 	\Delta^{-1} &= \Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\\
-	&+\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\\
-	&+\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right).
+	&+e^{2\psi}\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\\
+	&+e^{2\psi}\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right).
 	\end{aligned}
-\end{equation}.
+\end{equation}
 
@@
 \subsection{Compactification of the moduli space} \label{s:Compact}
+
 We can use the Kaluza-Klein spectrum and the uplift of the 3-dimensional gauged supergravity models to IIB supergravity to understand properties of the dual CFTs that are obscured in the lower-dimensional supergravities.
@@
 This highlights the importance of the $S^1$ direction, which is often ignored in holographic applications \EM{Maybe remove this last sentence?}.
+\CE{(Maybe the last part, but I would keep the first part.)}
 

### 2023-06-14 Draft_3dH3.tex
Update during meeting with Emanuel and Michele.

@@
 Our truncation Ansatz includes, in addition to the ${\cal N}=(4,4)$ vacuum, a host of moduli breaking some or all of the supersymmetries.
-We explicitly construct the uplift of a subset of these to construct new supersymmetric and non-supersymmetric AdS$_3$ vacua of IIB string theory, and show how the moduli space of AdS$_3$ vacua of six-dimensional gauged supergravity studied in \cite{Eloy:2021fhc} is compactified upon lifting to 10 dimensions.
+We explicitly construct the uplift of a subset of these to construct new supersymmetric and non-supersymmetric AdS$_3$ vacua of IIB string theory, which include a range of fully perturbatively stable non-supersymmetric cases.
+Moreover, we show how the supersymmetric direction of the moduli space of AdS$_3$ vacua of six-dimensional gauged supergravity studied in \cite{Eloy:2021fhc} is compactified upon lifting to 10 dimensions.
 Along the way, we also derive the form of 3-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor and rule out a 10-/11-dimensional origin of some 3-dimensional gauged supergravities.
@@
 	\item Think about title - mention new AdS$_3$ vacua? Lifting AdS$_3$ vacua?
-	\item Check the $\SL{n}$ equations
-	\item Move 3-d gauged SUGRA to somewhere else??
-	\item Construct 10-parameter uplift
+	\item Comment earlier on uplift of 6d gSUGRA
+	\item Add references to introduction
 	\item Complex geometry of moduli space?
@@
 \end{equation}
-where \EM{Note corrected sign in first equation!} \CE{(Sure? I took it from eq. (4.9) of ref.~\cite{Galli:2022idq}.)}
+where 
 \begin{equation} \label{eq:3dCovDeriv}
@@
 As discussed in \cite{Eloy:2021fhc}, the consistent truncation of ${\cal N}=(1,1)$ 6-dimensional supergravity to 3-dimensional half-maximal gauged supergravity can be described using the $\SO{8,4}$ ExFT \cite{Hohm:2017wtr,Samtleben:2019zrh}.
-On the other hand, the consistent truncation on $S^3$ is conveniently described by twist matrices living in $\SL{4} \simeq \SO{3,3}$ \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou} \EM{I think the twist matrix of \cite{Baguet:2015iou,Lee:2014mla,Hohm:2014qga} coincide in the $\SL{4}$ case, right?
-Camille, do you agree?} \CE{(Yes.)} with the embedding $\SO{3,3} \subset \SO{4,4} \subset \SO{8,4}$.
+On the other hand, the consistent truncation on $S^3$ is conveniently described by twist matrices living in $\SL{4} \simeq \SO{3,3}$ \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou} with the embedding $\SO{3,3} \subset \SO{4,4} \subset \SO{8,4}$.
 However, the twist matrix in \cite{Eloy:2021fhc} differs from this $\SO{3,3}$ twist matrix \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou} by an additional parameter, $\lambda$, which gives rise to an external 3-form flux or, equivalently, a new internal 3-form flux.
@@
 \end{equation}
-explicitly using \eqref{eq:C2S3example} and setting $C^i = \lambda\, \xi^i$, \CE{(factor $\rho^{-1}$?)} with $\nabla_i \xi^i = 1$, in the notation of \cite{Eloy:2021fhc}, we obtain precisely the twist matrix used in \cite{Eloy:2021fhc} for the consistent truncation of 6-dimensional ${\cal N}=(1,1)$ supergravity on $S^3$ with $H_3$ flux.
+explicitly using \eqref{eq:C2S3example} and setting $C^i = \rho^{-1}\,\lambda\, \xi^i$, with $\nabla_i \xi^i = 1$, in the notation of \cite{Eloy:2021fhc}, we obtain precisely the twist matrix used in \cite{Eloy:2021fhc} for the consistent truncation of 6-dimensional ${\cal N}=(1,1)$ supergravity on $S^3$ with $H_3$ flux.
 %\EM{Give precise form of $C^i$ such that we recover $\lambda$?}
@@
 Crucially, for the generalised Leibniz condition \eqref{eq:GenLeibniz} to hold, the coordinates and generalised vector fields corresponding to the $\SL{4}_1$ and $\SL{4}_2$ must be embedded within the $\mathbf{28}$ and $\mathbf{\overline{28}}$, respectively, which we will call ``electric'' and ``magnetic'' coordinates, following \cite{Inverso:2016eet}.
-Thus, we write the 56 $\En{7}$ coordinates as \CE{($M$ already used for adjoint of \EE)}
+Thus, we write the 56 $\En{7}$ coordinates as
 \begin{equation}
@@
 \end{equation}
-and we only generate the $\mathbf{36}$ and $\overline{\mathbf{36}}$ components, $\eta_{{\cal AB}}$, $\eta^{{\cal AB}}$. Thus, the $\En{7}$ embedding tensor is given by
+and we only generate the $\mathbf{36}$ and $\overline{\mathbf{36}}$ components, $\eta_{{\cal AB}}$, $\tilde{\eta}^{{\cal AB}}$. Thus, the $\En{7}$ embedding tensor is given by
 \begin{equation}
@@
 		X_{{\cal AB, CD}}{}^{\cal EF} &= \eta_{\cA[\cC} \delta_{{\cal D}]\cB}^{{\cal EF}} - \eta_{\cB[\cC} \delta_{{\cal D}]\cA}^{{\cal EF}} \,, \\
-		X^{{\cal AB}}{}_{{\cal CD}}{}^{\cal EF} &= -\eta^{\cA[{\cal E}}_{\phantom{[\cA]}} \delta_{\cC{\cal D}}^{{\cal F}]{\cal B}} + \eta^{\cB[{\cal E}}_{\phantom{[\cA]}} \delta_{\cC{\cal D}}^{{\cal F}]{\cal A}} \,.
+		X^{{\cal AB}}{}_{{\cal CD}}{}^{\cal EF} &= -\tilde{\eta}^{\cA[{\cal E}}_{\phantom{[\cA]}} \delta_{\cC{\cal D}}^{{\cal F}]{\cal B}} + \tilde{\eta}^{\cB[{\cal E}}_{\phantom{[\cA]}} \delta_{\cC{\cal D}}^{{\cal F}]{\cal A}} \,.
 	\end{split}
@@
 \begin{equation}
-	\eta_{IJ} = \delta_{IJ} \,, \qquad \eta^{AB} = \delta^{AB} \,.
+	\eta_{IJ} = \delta_{IJ} \,, \qquad \tilde{\eta}^{AB} = \delta^{AB} \,.
 \end{equation}
@@
 \begin{equation}
-	\eta_{IJ} = \frac{1}{\alpha} \delta_{IJ} \,, \qquad \eta^{AB} = \delta^{AB} \,.
+	\eta_{IJ} = \frac{1}{\alpha} \delta_{IJ} \,, \qquad \tilde{\eta}^{AB} = \delta^{AB} \,.
 \end{equation}
@@
 \end{equation}
-With this embedding tensor, the potential~\eqref{eq:3dpotential} has a vacuum at the scalar origin when $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$.
-We choose this value of $\lambda$ from here onwards.
-\EM{Presumably condition is on $\lambda^2$ and the sign of $\lambda$ is fixed by SUSY (which we can ignore)?} \CE{(Exactly, the sign of $\lambda$ exchanges ${\cal N}_{\rm L}$ and ${\cal N}_{\rm R}$ in ${\cal N}=({\cal N}_{\rm L},{\cal N}_{\rm R})$)}
+With this embedding tensor, the potential~\eqref{eq:3dpotential} has a vacuum at the scalar origin when $\lambda=\pm 4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$.
+The sign changes the chirality of the Killing spinors and, therefore, without loss of generality, we will choose $\lambda = 4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$ from here onwards.
 
@@
 \end{equation}
-The $S^{1}$ coordinate $z$ has periodicity $z\rightarrow z+2\pi$.
+The $S^{1}$ coordinate $z$ has periodicity $z\rightarrow z+1$.
 
@@
 The ${\rm AdS}_{3}$ isometry group is ${\rm SO}(2,2)\simeq{\rm SL}(2,\mathbb{R})_{\rm L}\times{\rm SL}(2,\mathbb{R})_{\rm R}$, and the factors ${\rm SO}(3)_{\rm L}\times{\rm SO}(3)_{\rm R}\times\ts{{\rm SO}(3)}_{\rm L}\times\ts{{\rm SO}(3)}_{\rm R}\simeq{\rm SO}(4)\times\ts{{\rm SO}(4)}$ combine into the isometry groups of the two spheres.
-The spectrum organizes into multiplets of ${\cal G}$, made out of products of long representations $[\ell,\ts{\ell}]$ of $D^{1}(2,1;\alpha)$ (see app.~\ref{app:d21a} for a review of the representations of $D^{1}(2,1;\alpha)$).
+Additionally, there is a $\U{1}_F$ symmetry due to the $S^1$ factor in \eqref{eq:AdS3}.
+The spectrum organizes into multiplets of ${\cal G}$, made out of products of long representations $[\ell,\ts{\ell}]$ of $D^{1}(2,1;\alpha)$ (see app.~\ref{app:d21a} for a review of the representations of $D^{1}(2,1;\alpha)$), and carrying a charge under the $\U{1}_F$.
 Explicitly, the spectrum is~\cite{Eberhardt:2017fsi}
 \begin{equation} \label{eq:spectrumorigin}
-	\bigoplus_{\ell,\ts{\ell}\geq0} [\ell,\ts{\ell}]\otimes[\ell,\ts{\ell}] \ \ominus\ [0,0]_{\rm s} \otimes [0,0]_{\rm s}\,.
+	\bigoplus_{\ell,\ts{\ell}\geq0,\,n} \Big([\ell,\ts{\ell}]\otimes[\ell,\ts{\ell}]\Big)_n \ \ominus\ [0,0]_{\rm s} \otimes [0,0]_{\rm s} \,.
 \end{equation}
@@
 \begin{equation}
-	h_{\rm L} = h_{\rm R} = -\frac{1}{2} + \frac{1}{2}\sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}}\,,
+	h_{\rm L} = h_{\rm R} = -\frac{1}{2} + \frac{1}{2}\sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+\alpha^2(2\pi n)^{2}}{1+\alpha^{2}}}\,,
 \end{equation}
@@
 \begin{equation} \label{eq:confdims3s3s1}
-	\Delta_{\ell,\,\ts{\ell},\,n} = h_{\rm L} + h_{\rm R} = - 1 + \sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}}\,.
+	\Delta_{\ell,\,\ts{\ell},\,n} = h_{\rm L} + h_{\rm R} = - 1 + \sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+\alpha^2(2\pi n)^{2}}{1+\alpha^{2}}}\,.
 \end{equation}
@@
 Surprisingly, within the 3-dimensional gauged supergravity, the AdS$_3$ vacuum contains a large moduli space, which even has supersymmetric submanifolds.
-In particular, without any attempts at being exhaustive \EM{(too strong?
-does this make us sound lazy?)} \CE{(I think it's fine.)}, we identified a continuous 11-parameter family of AdS$_3$ solutions, connected to the origin and given by the \EE coset representative \CE{($\fl{28}\leftrightarrow28$ compared to the code, I think we made a mistake and confused down and up indices)}
+In particular, a simple search already reveals a continuous 11-parameter family of AdS$_3$ solutions, connected to the origin and given by the \EE coset representative
 \begin{equation} \label{eq:FullDeformation}
@@
 The $(\chi_{i},\ts{\chi}_{i},\zeta_{i},\ts{\zeta}_{i})$ deformations excite the $(\mathbf{6},\mathbf{1})_{2}$ and $(\mathbf{1},\mathbf{6})_{2}$ generators in the branching~\eqref{eq:56inSL4SL4}.
-\CE{(Describe what we do for $T = \exp{\psi}$?
-I think there is some freedom in the coeff there.)} \CE{(Describe what we do for $\Omega$?
-Check coeff with code.
-Possible to change the signs to $(+,+,-,-)$, but very long to compute uplift.)}
-
-\EM{Kinetic terms? Might be interesting for the S-fold deformations to see what kind of metric we have on the moduli space.}
+Note that changing the sign in some terms in \eqref{eq:FullDeformation}, e.g.
+changing the factor with $\Omega$ to
+\begin{equation}
+	\exp\bigg[\frac{\Omega'}{120}\Big(\big(t_{(\mathbf{63},\mathbf{1})}\big)_{1}{}^{1}+\big(t_{(\mathbf{63},\mathbf{1})}\big)_{2}{}^{2}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{3}{}^{3}-\big(t_{(\mathbf{63},\mathbf{1})}\big)_{8}{}^{8}\Big) \bigg] \,,
+\end{equation}
+creates yet another flat direction of the potential. This highlights how many flat directions the AdS$_3$ vacuum appears to have.
+
+\EM{Kinetic terms? Might be interesting for the S-fold deformations to see what kind of metric we have on the moduli space. This will go below the specific zoom-ins}
 
@@
 \paragraph{\boldmath $(\chi, \ts{\chi}, \psi)$}
-Using Hopf coordinates for both $S^3$'s we can write the 5-parameter deformation involving $(\chi_i, \ts{\chi}_i, \psi)$, $i = 1,2$, as follows: \CE{(Are those Hopf coordinates?)}
+Using Hopf coordinates for both $S^3$'s we can write the 5-parameter deformation involving $(\chi_i, \ts{\chi}_i, \psi)$, $i = 1,2$, as follows:
 \begin{equation}
@@
 \end{equation}
-where \EM{Can we double check the $\alpha$'s? I'm slightly confused} \CE{(I think it's correct.)}
+where
 \begin{equation}
@@
 \begin{equation} \label{eq:confdimshiftchi}
-	2\pi n\longrightarrow e^{-2\psi} \left[ 2\pi n + \Big((q_{\rm L}+q_{\rm R})\,\chi_{1}+(q_{\rm L}-q_{\rm R})\,\chi_{2}+ \alpha\,(\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1}+ \alpha\,(\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big) \right]\,,
-\end{equation}
-where the $q$ denote the charges under the different ${\rm U}(1)$. \EM{Somewhere here, we should give the character for all multiplets.}
+	2\pi n\longrightarrow e^{-2\psi} \left[ 2\pi n + \Big((q_{\rm L}+q_{\rm R})\,\frac{\chi_{1}}{\alpha}+(q_{\rm L}-q_{\rm R})\,\frac{\chi_{2}}{\alpha}+ (\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1} + (\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big) \right]\,,
+\end{equation}
+where the $q$ denote the charges under the different ${\rm U}(1)$.
 
@@
 and conformal dimension $\Delta=\nicefrac{3}{2}$.
-Turning on the deformation leads to a split into four groups of two modes, with the following ${\rm U}(1)_{\rm L}\times\ts{{\rm U}(1)}_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm R}$ charges and conformal dimensions:
+Turning on the deformation leads to a split into four groups of two modes, with the following ${\rm U}(1)_{\rm L}\times\ts{{\rm U}(1)}_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm R}$ charges and conformal dimensions within the 3-dimensional truncation:
 \begin{equation}
@@
 with conformal dimension given by \eqref{eq:confdims3s3s1} with $n \neq 0$, obtain $\Delta = \nicefrac32$.
+Here we will focus on the supersymmetry enhancement within the 3-dimensional truncation and will discuss the higher KK modes in section \ref{s:Compact}.
 The different possibilities are listed below.
-\CE{(Shall we include the $n$?
-Shall we give the multiplets?
-At least for the truncation?
-Not sure it's worth it.)}
 
@@
 
-In the above cases, it is easy to see from \eqref{eq:confdimshiftchi} that the spectrum  is invariant under $\chi_i \rightarrow \chi_i + 2\pi k_i$, $\ts{\chi}_i \rightarrow \ts{\chi}_i + 2\pi \ts{k}_i/\alpha$, for $k_i$, $\ts{k}_i \in \mathbb{Z}$, with the SUSY enhancements also occurring if the relations \eqref{eq:N2}, \eqref{eq:N4Large}, \eqref{eq:N4Small} or \eqref{eq:N6} are satisfied up to integer shifts.
+In the above cases, it is easy to see from \eqref{eq:confdimshiftchi} that the spectrum  is invariant under $\chi_i \rightarrow \chi_i + 2\pi k_i\,\alpha$, $\ts{\chi}_i \rightarrow \ts{\chi}_i + 2\pi \ts{k}_i$, for $k_i$, $\ts{k}_i \in \mathbb{Z}$, with the SUSY enhancements also occurring if the relations \eqref{eq:N2}, \eqref{eq:N4Large}, \eqref{eq:N4Small} or \eqref{eq:N6} are satisfied up to integer shifts.
 We will return to this point below in section \ref{s:Compact}, when discussing compactness of the moduli space.
@@
 Therefore, these non-supersymmetric AdS$_3$ vacua are still perturbatively stable within IIB supergravity and, similarly to \cite{Giambrone:2021wsm} suggest that there may be a dual non-supersymmetric conformal manifold if there are no instabilities beyond supergravity, such as non-perturbative instabilities triggered by brane nucleation or non-vanishing $\beta$-functions of marginal multi-trace operators \EM{add citations}.
-\CE{(Mention the continuous limits to SUSY vacua?)}
+However, it is worth stressing that the vacua here may have further protection against such instabilities due to their continuous limits to the SUSY vacua.
 
@@
 \paragraph{\boldmath $(\zeta,\ts{\zeta},\Omega,\ts{\Omega},\psi)$}
-Again with spherical coordinates:
+Again in Euler coordinates:
 \begin{equation}
@@
 \CE{(Expression of $H$?)}
-
-\paragraph{SUSY deformation}
-
-%In Hopf coordinates:
+%
+%\paragraph{SUSY deformation}
+%
+%%In Hopf coordinates:
+%%\begin{equation}
+%%	\begin{split}
+%%		ds^2 &= \alpha^2 \left[ ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
+%%		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{\CE{-}(1-e^{2\omega})} d\psi \,, \\
+%%		d\sigma &= vol_{\mathbb{CP}^1} \,.
+%%	\end{split}
+%%\end{equation}
+%
+%It is convenient to use the Hopf fibration to describe this, we denote by $\phi$ the coordinate on the $S^1$ fibre and by $\xi$ the homogeneous coordinate on $\mathbb{CP}^1$.
+The round metric on $S^3$ then reads
+%\begin{equation}
+%	g= \mathrm{d}s^2_{\mathbb{CP}^1} + (\sigma + \mathrm{d}\phi)^2
+%\end{equation}
+%where 
 %\begin{equation}
 %	\begin{split}
-%		ds^2 &= \alpha^2 \left[ ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
-%		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{\CE{-}(1-e^{2\omega})} d\psi \,, \\
-%		d\sigma &= vol_{\mathbb{CP}^1} \,.
+%		\mathrm{d}s^2_{\mathbb{CP}^1} &= \frac1{(1+|\xi|^2)^2}\mathrm{d}\xi\,\mathrm{ d}\ov{\xi}\\
+%		\sigma&=\frac{i}{2(1+|\xi|^2)}(\xi \mathrm{d} \ov{\xi}-\ov{\xi}\mathrm{d}\xi)\\ 
+%		vol_{S^3}&=vol_{\mathbb{CP}^1}\wedge \mathrm{d}\psi .
 %	\end{split}
 %\end{equation}
-
-It is convenient to use the Hopf fibration to describe this, we denote by $\phi$ the coordinate on the $S^1$ fibre and by $\xi$ the homogeneous coordinate on $\mathbb{CP}^1$.
-The round metric on $S^3$ then reads
-\begin{equation}
-	g= \mathrm{d}s^2_{\mathbb{CP}^1} + (\sigma + \mathrm{d}\phi)^2
-\end{equation}
-where 
-\begin{equation}
-	\begin{split}
-		\mathrm{d}s^2_{\mathbb{CP}^1} &= \frac1{(1+|\xi|^2)^2}\mathrm{d}\xi\,\mathrm{ d}\ov{\xi}\\
-		\sigma&=\frac{i}{2(1+|\xi|^2)}(\xi \mathrm{d} \ov{\xi}-\ov{\xi}\mathrm{d}\xi)\\ 
-		vol_{S^3}&=vol_{\mathbb{CP}^1}\wedge \mathrm{d}\psi .
-	\end{split}
-\end{equation}
-The deformation does not affect $S_+^3$, but it mixes the $S^1$ factor in the internal space with the Hopf fibre of $S_-^3$. It is parametrised by a real number $\Omega$, such that the metric reads
-\begin{equation}
-	\begin{split}
-		\mathrm{d}s^2 &= \alpha^2(\mathrm{d}s^2_{\mathbb{CP}^1}+\kappa^2) + \mathrm{d}s^2_{S_+^3} + e^{-4\Omega}\mathrm{d}\psi^2\\
-		\kappa &= \mathrm{d}\phi + \sigma - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi.
-	\end{split}
-\end{equation}
- The three form flux gets changed according to the prescription $\d\phi \rightarrow \d\phi -  \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d \psi$ and we find:
-\begin{equation}
-	H_{(3)}=\alpha^2vol_{\mathbb{CP}^1}\wedge (\d\phi - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi) + vol_{S_+^3}.
-\end{equation}
-
+%The deformation does not affect $S_+^3$, but it mixes the $S^1$ factor in the internal space with the Hopf fibre of $S_-^3$. It is parametrised by a real number $\Omega$, such that the metric reads
+%\begin{equation}
+%	\begin{split}
+%		\mathrm{d}s^2 &= \alpha^2(\mathrm{d}s^2_{\mathbb{CP}^1}+\kappa^2) + \mathrm{d}s^2_{S_+^3} + e^{-4\Omega}\mathrm{d}\psi^2\\
+%		\kappa &= \mathrm{d}\phi + \sigma - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi.
+%	\end{split}
+%\end{equation}
+% The three form flux gets changed according to the prescription $\d\phi \rightarrow \d\phi -  \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d \psi$ and we find:
+%\begin{equation}
+%	H_{(3)}=\alpha^2vol_{\mathbb{CP}^1}\wedge (\d\phi - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi) + vol_{S_+^3}.
+%\end{equation}
 %
-%In spherical coordinates:
+%%
+%%In spherical coordinates:
+%%\begin{equation}
+%%	\begin{aligned}
+%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+\alpha^{2}\,\d s^2\left(S^{3}_{-}\right) +e^{-2\omega}\,\d\psi^{2}\\
+%%		&\quad+2\,\alpha\,e^{-2\omega}\,\sqrt{-1+e^{2\omega}}\left(-\cos^{2}(\theta)\,\d\varphi_{1}+\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi\\[5pt]
+%%		&= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+e^{-4\omega}\,\d\psi^{2}\\
+%%		&\quad+\alpha^{2}\bigg[\d \theta^2+\cos^{2}(\theta)\left(\d\varphi_{1}-\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}+\sin^{2}(\theta)\left(\d\varphi_{2}+\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}\bigg] ,\\[5pt]
+%%		\d s^2\left(S^{3}_{-}\right) &= \d\theta^{2}+\cos^{2}(\theta)\,\d\varphi_{1}^{2}+\sin^{2}(\theta)\,\d\varphi_{2}^{2}.
+%%	\end{aligned}
+%%\end{equation}
+%
+%\paragraph{Non-SUSY deformation}
+%Here we study a more general deformation depending on three parameters $\Omega$, $\zeta_{1,8}$ and $\zeta_{2,3}$.
+It is convenient to write down the uplift in terms of the Hopf coordinates on $S_-^3$, while again $S_+^3$ is not deformed.\\
+%\noindent For the metric we find
+%%\begin{equation}
+%%	\begin{aligned}
+%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+%%		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
+%%		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
+%%		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2}.\\[5pt]
+%%		\Delta^{-1} &= 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
+%%	\end{aligned}
+%%\end{equation}
 %\begin{equation}
 %	\begin{aligned}
-%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+\alpha^{2}\,\d s^2\left(S^{3}_{-}\right) +e^{-2\omega}\,\d\psi^{2}\\
-%		&\quad+2\,\alpha\,e^{-2\omega}\,\sqrt{-1+e^{2\omega}}\left(-\cos^{2}(\theta)\,\d\varphi_{1}+\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi\\[5pt]
-%		&= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+e^{-4\omega}\,\d\psi^{2}\\
-%		&\quad+\alpha^{2}\bigg[\d \theta^2+\cos^{2}(\theta)\left(\d\varphi_{1}-\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}+\sin^{2}(\theta)\left(\d\varphi_{2}+\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}\bigg] ,\\[5pt]
-%		\d s^2\left(S^{3}_{-}\right) &= \d\theta^{2}+\cos^{2}(\theta)\,\d\varphi_{1}^{2}+\sin^{2}(\theta)\,\d\varphi_{2}^{2}.
+%		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+%		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
+%		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
+%		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2},
 %	\end{aligned}
 %\end{equation}
-
-\paragraph{Non-SUSY deformation}
-Here we study a more general deformation depending on three parameters $\Omega$, $\zeta_{1,8}$ and $\zeta_{2,3}$.
-It is convenient to write down the uplift in terms of spherical coordinates on $S_-^3$, while again $S_+^3$ is not deformed.\\
-\noindent For the metric we find
+%where $\Delta$ is the warp factor
 %\begin{equation}
-%	\begin{aligned}
-%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-%		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
-%		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
-%		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2}.\\[5pt]
-%		\Delta^{-1} &= 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
-%	\end{aligned}
+%		\Delta^{-1} = 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
 %\end{equation}
-\begin{equation}
-	\begin{aligned}
-		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
-		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
-		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2},
-	\end{aligned}
-\end{equation}
-where $\Delta$ is the warp factor
-\begin{equation}
-		\Delta^{-1} = 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
-\end{equation}
-The three-form flux is 
-\begin{equation}
-	H_{(3)}=vol_{S_-^3}+\alpha ^2\sin(\theta)\cos (\theta)(2+e^{2\Omega}\zeta^2_{1,8})(2e^{2\Omega}+\zeta_{2,3}^2)\Delta^2\mathrm{d}\theta\wedge\kappa_1\wedge\kappa_2,
-\end{equation}
-with the two one forms $\kappa_{1,2}$ defined by 
-\begin{equation}
-\begin{split}
-		\kappa_1&=\mathrm{d}\phi_1-\frac{\zeta_{2,3}}{\alpha(2e^{2\Omega}+\zeta_{2,3}^2)}\mathrm{d}\psi \\
-	\kappa_2&=\mathrm{d}\phi_2+ \frac{\zeta_{1,8}}{\alpha(2+e^{2\Omega}\zeta_{1,8}^2)}\mathrm{d}\psi.
-\end{split}
-\end{equation}
-Note that setting $...$ recovers the supersymmetric deformation described earlier.
-%In Hopf coordinates:
-% \begin{equation}
-% \begin{split}
-% ds^2 &= \alpha^2 \left[ d\alpha_1^2 +  ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
-% \kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
-% d\sigma &= vol_{\mathbb{CP}^1} \,.
-% \end{split}
-% \end{equation}
-% \begin{equation}
-% 	\begin{aligned}
-% 		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-% 		&\quad + \Delta\,\alpha^{2}\bigg[\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm I}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm R}^{2}\Big)\,\d z_{\rm R}^{2}\\
-% 		&\qquad\ \  + \frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm R}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm I}^{2}\Big)\,\d z_{\rm I}^{2}\\
-% 		&\qquad\ \  + 2\,\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(-\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(2+\vert z\vert^{2}\right)+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d z_{\rm R}\d z_{\rm I}\\
-% 		&\qquad\ \  +2\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\,\vert z\vert^{2}+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d\theta^{2}\bigg]\\
-% 		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
-% 		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
-% 		\Delta^{-1} &= 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
-% 	\end{aligned}
-% \end{equation}
-
-%%%%
-
+%The three-form flux is 
 %\begin{equation}
-%	\begin{aligned}
-%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-%		&\quad + \frac{\alpha^{2}}{1+\gamma\,\vert z\vert^{2}}\bigg[\Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm I}^{2}\right)+\left(\gamma-1\right)\,z_{\rm R}^{2}\Big)\,\frac{\d z_{\rm R}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
-%		&\qquad + \Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm R}^{2}\right)+\left(\gamma-1\right)\,z_{\rm I}^{2}\Big)\,\frac{\d z_{\rm I}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}} - 2\,\Big(1+\vert z\vert^{2}-\left(\gamma-1\right)\Big)\,\frac{\d z_{\rm R}\d z_{\rm I}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
-%		&\qquad+2\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\left(\gamma+\vert z\vert^{2}\right)\d\theta^{2}\bigg]\\
-%		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
-%		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
-%		\gamma &= \frac{2\,e^{2\Omega}+\zeta_{2,3}^{2}}{2+e^{2\Omega}\zeta_{1,8}^{2}},\qquad \Delta^{-1} = 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
-%	\end{aligned}
+%	H_{(3)}=vol_{S_-^3}+\alpha ^2\sin(\theta)\cos (\theta)(2+e^{2\Omega}\zeta^2_{1,8})(2e^{2\Omega}+\zeta_{2,3}^2)\Delta^2\mathrm{d}\theta\wedge\kappa_1\wedge\kappa_2,
 %\end{equation}
+%with the two one forms $\kappa_{1,2}$ defined by 
+%\begin{equation}
+%\begin{split}
+%		\kappa_1&=\mathrm{d}\phi_1-\frac{\zeta_{2,3}}{\alpha(2e^{2\Omega}+\zeta_{2,3}^2)}\mathrm{d}\psi \\
+%	\kappa_2&=\mathrm{d}\phi_2+ \frac{\zeta_{1,8}}{\alpha(2+e^{2\Omega}\zeta_{1,8}^2)}\mathrm{d}\psi.
+%\end{split}
+%\end{equation}
+%Note that setting $...$ recovers the supersymmetric deformation described earlier.
+%%In Hopf coordinates:
+%% \begin{equation}
+%% \begin{split}
+%% ds^2 &= \alpha^2 \left[ d\alpha_1^2 +  ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
+%% \kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
+%% d\sigma &= vol_{\mathbb{CP}^1} \,.
+%% \end{split}
+%% \end{equation}
+%% \begin{equation}
+%% 	\begin{aligned}
+%% 		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+%% 		&\quad + \Delta\,\alpha^{2}\bigg[\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm I}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm R}^{2}\Big)\,\d z_{\rm R}^{2}\\
+%% 		&\qquad\ \  + \frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm R}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm I}^{2}\Big)\,\d z_{\rm I}^{2}\\
+%% 		&\qquad\ \  + 2\,\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(-\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(2+\vert z\vert^{2}\right)+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d z_{\rm R}\d z_{\rm I}\\
+%% 		&\qquad\ \  +2\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\,\vert z\vert^{2}+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d\theta^{2}\bigg]\\
+%% 		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
+%% 		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
+%% 		\Delta^{-1} &= 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
+%% 	\end{aligned}
+%% \end{equation}
+%
+%%%%%
+%
+%%\begin{equation}
+%%	\begin{aligned}
+%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+%%		&\quad + \frac{\alpha^{2}}{1+\gamma\,\vert z\vert^{2}}\bigg[\Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm I}^{2}\right)+\left(\gamma-1\right)\,z_{\rm R}^{2}\Big)\,\frac{\d z_{\rm R}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
+%%		&\qquad + \Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm R}^{2}\right)+\left(\gamma-1\right)\,z_{\rm I}^{2}\Big)\,\frac{\d z_{\rm I}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}} - 2\,\Big(1+\vert z\vert^{2}-\left(\gamma-1\right)\Big)\,\frac{\d z_{\rm R}\d z_{\rm I}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
+%%		&\qquad+2\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\left(\gamma+\vert z\vert^{2}\right)\d\theta^{2}\bigg]\\
+%%		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
+%%		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
+%%		\gamma &= \frac{2\,e^{2\Omega}+\zeta_{2,3}^{2}}{2+e^{2\Omega}\zeta_{1,8}^{2}},\qquad \Delta^{-1} = 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
+%%	\end{aligned}
+%%\end{equation}
 
@@
 Consider the deformations $\chi_i$, $\ts{\chi}_i$, which appear non-compact in 3-dimensional ${\cal N}=16$ gauged supergravity, with only the point $\chi_i = \ts{\chi}_i = 0$ having ${\cal N}=(4,4)$ supersymmetry.
-The subset of these deformations corresponding to the SUSY lines $\chi_1 = \chi_2 = \chi$, $\ts{\chi}_i = 0$, \EM{Is this right?} was analysed in the half-maximal theory in \cite{Eloy:2021fhc}.
+The subset of these deformations corresponding to the SUSY lines $\chi_1 = \chi_2 = \chi$, $\ts{\chi}_i = 0$, \EM{Camille will fix this} was analysed in the half-maximal theory in \cite{Eloy:2021fhc}.
 Again, within 3-dimensional ${\cal N}=8$ supergravity, this deformation is non-compact, and remains non-compact even after uplifting to 6-dimensional supergravity on $S^3$, with no periodicity in $\chi$ observed in the KK spectrum of the 6-dimensional solution \cite{Eloy:2021fhc}.
 
-However, from  \eqref{eq:confdims3s3s1}, \eqref{eq:confdimshiftchi}, \eqref{eq:Multiplets} we see that the full Kaluza-Klein spectrum is invariant under the shifts
+However, from  \eqref{eq:spectrumorigin}, \eqref{eq:confdims3s3s1}, \eqref{eq:confdimshiftchi} we see that the full Kaluza-Klein spectrum is invariant under the shifts
 \begin{equation} \label{eq:ShiftSymmetries}
 	\begin{split}
-		\chi_i &\rightarrow \chi_i + 2\pi k_i\,, \\
-		\ts{\chi}_i &\rightarrow \ts{\chi}_i + 2\pi \ts{k}_i/\alpha \,,
+		\chi_i &\rightarrow \chi_i + 2\pi\alpha\, k_i\,, \\
+		\ts{\chi}_i &\rightarrow \ts{\chi}_i + 2\pi \ts{k}_i \,,
 	\end{split}
@@
 Therefore, even though neither the 3-dimensional gauged supergravity, nor 6-dimensional supergravity is invariant under these shifts, upon lifting to the full 10-dimensional IIB theory, the higher KK modes on $S^1$ restore the invariance under the shifts, just as in the analogous deformations studied in AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
-This highlights the importance of the $S^1$ direction, which is often ignored in holographic applications \EM{Maybe remove this last sentence?}.
-\CE{(Maybe the last part, but I would keep the first part.)}
+This highlights the importance of the $S^1$ direction in studying the AdS$_3$ vacua.
 
@@
 Each of $\chi_i$, $\ts{\chi}_i$ corresponds to the real part of the complex structure modulus of a $T^2$ fibration with local coordinates $\phi_i$, $\ts{\phi}_i$ together with $z$, respectively.
-Explicitly, the complex structure is given by \EM{Not sure about this, see comment about $\alpha$ above}
+Explicitly, the complex structures for the $T^2_{(\phi_i,\, z)}$ and $T^2_{(\ts{\phi}_i,\, z)}$ are given by
 \begin{equation} \label{eq:T2CStructure}
-	\tau = i\,\frac{e^\psi}{\alpha} + \frac1\alpha \chi \,.
-\end{equation}
-Under this identification, the shifts \eqref{eq:ShiftSymmetries} correspond to Dehn twists, or $T$-transformations, of the torus, which belong to the modular group $\SL{2,\mathbb{Z}}$, just as for AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
+	\tau_i = i\,\frac{e^\psi}{\alpha} + \frac1\alpha \chi_i \,, \qquad \ts{\tau}_i = i\,e^\psi + \ts{\chi}_i \,.
+\end{equation}
+Under this identification, the shifts \eqref{eq:ShiftSymmetries} correspond to $T$-transformations of the tori, which belong to the modular group $\SL{2,\mathbb{Z}}$, just as for AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
 
@@
 The $S$-transformation acts on the moduli as
-\begin{equation} \label{eq:Stransform}
-	\psi \rightarrow - \psi \,,
-\end{equation}
-thus inverting the radius of the $S^1$.
+\begin{equation} \label{eq:Stransformchi}
+	\chi_i \rightarrow - \frac{\alpha^2 \chi_i}{\chi_i^2+e^{2\psi}} \,, \qquad e^{\psi} \rightarrow \frac{\alpha^2\, e^{\psi}}{\chi_i^2+e^{2\psi}} \,,
+\end{equation}
+for the $T^2_{(\phi_i,\, z)}$ and
+\begin{equation} \label{eq:Stransformchitilde}
+	\ts{\chi}_i \rightarrow - \frac{\ts{\chi}_i}{\ts{\chi}_i^2+e^{2\psi}} \,, \qquad e^{\psi} \rightarrow \frac{e^{\psi}}{\ts{\chi}_i^2+e^{2\psi}} \,,
+\end{equation}
+for the $T^2_{(\ts{\phi}_i,\, z)}$. Thus, the $S$-transformation effectively inverts the radius of the $S^1$, while transforming the combinations
+\begin{equation}
+	e^{-\psi}\chi_i \rightarrow - e^{-\psi}\chi_i \,, \qquad e^{-\psi} \ts{\chi}_i \rightarrow - e^{-\psi}\ts{\chi}_i \,.
+\end{equation}
+\EM{EM To clean this up!}\\
 The KK spectrum \eqref{eq:confdims3s3s1}, \eqref{eq:confdimshiftchi} is clearly not invariant under this transformation.

### 2023-06-14 Draft_3dH3.tex
Update: sign of f term in (3.8), checked factors in (4.6)-(4.9), uplift of \chi, \Omega, \psi in sec. 6.3, kinetic terms in (6.11) and (6.23), discussion of AdS3xS3 in (6.18).

@@
 		X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} &= - 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{P}(\fl{M}}{}^{\fl{Q}}\,f_{\fl{N})\fl{Q}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \\
-		&= - 14\,\rho^{-1}\,(\mathbb{P}_{3875})_{\fl{MN}}{}^{\fl{PQ}}\,\Gamma_{\fl{PQ}} - \frac{1}{4}\,\rho^{-1}\,\eta_{\fl{MN}}\,\Gamma_{\fl{P}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \,,
+		&= - 14\,\rho^{-1}\,(\mathbb{P}_{3875})_{\fl{MN}}{}^{\fl{PQ}}\,\Gamma_{\fl{PQ}} - \frac{1}{4}\,\rho^{-1}\,\eta_{\fl{MN}}\,\Gamma_{\fl{P}}{}^{\fl{P}} - \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \,,
 	\end{split}
@@
 We can square eq.~\eqref{eq:symembeddingtensor} to derive an expression for $X_{\ov{MN}}X^{\ov{MN}}$ in terms of the current $\Gamma$.
-We find \EM{check coefficient of last term}
+We find
 \begin{equation}\label{eq:XXwitheta}
@@
 
-\begin{equation}
-	\begin{aligned}
-		\d s^{2}_{\rm Zam.} &= -\frac{1}{2}\bigg[e^{2\psi}\left(e^{-\Omega}\,\d\zeta_{1}^{2}+e^{\Omega}\,\d\zeta_{2}^{2}+e^{\ts{\Omega}}\,\d\ts{\zeta}_{1}^{2}+e^{-\ts{\Omega}}\,\d\ts{\zeta}_{2}^{2}\right) \\
-		&+ \left(e^{-2\psi-\ts{\Omega}}+\ts{\zeta}_{1}^{2}+e^{-\Omega-\ts{\Omega}}\zeta_{1}^{2}\right)\left(e^{\Omega+\ts{\Omega}}+e^{2\psi+\Omega}\ts{\zeta}_{2}^{2}+e^{2\psi+\ts{\Omega}}\zeta_{1}^{2}\right) \,\d\chi_{1}^{2} \\
-		&+ \left(e^{-2\psi-\Omega}+e^{-\Omega-\ts{\Omega}}\ts{\zeta}_{2}^{2}+\zeta_{2}^{2}\right)\left(1+e^{2\psi+\ts{\Omega}}\ts{\zeta}_{1}^{2}+e^{2\psi+\Omega}\zeta_{2}^{2}\right) \,\d\chi_{2}^{2}\\
-		&+ \left(e^{-2\psi-\ts{\Omega}}+\ts{\zeta}_{1}^{2}+e^{-\Omega-\ts{\Omega}}\zeta_{1}^{2}\right)\left(1+e^{2\psi+\ts{\Omega}}\ts{\zeta}_{1}^{2}+e^{2\psi+\Omega}\zeta_{2}^{2}\right) \,\d\ts{\chi}_{1}^{2} \\
-		&+ \left(e^{-2\psi-\Omega}+e^{-\Omega-\ts{\Omega}}\ts{\zeta}_{2}^{2}+\zeta_{2}^{2}\right)\left(e^{\Omega+\ts{\Omega}}+e^{2\psi+\Omega}\ts{\zeta}_{2}^{2}+e^{2\psi+\ts{\Omega}}\zeta_{1}^{2}\right) \,\d\ts{\chi}_{2}^{2} + \ldots \\
-		&+2\,\d\psi^{2}\bigg]
-	\end{aligned}
-\end{equation}
-
 % \paragraph{S-fold like deformations} Scalar spectrum:
@@
 
-\paragraph{\boldmath $(\chi, \ts{\chi}, \psi)$}
-Using Hopf coordinates for both $S^3$'s we can write the 5-parameter deformation involving $(\chi_i, \ts{\chi}_i, \psi)$, $i = 1,2$, as follows:
-\begin{equation}
-	\begin{split}
-		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^{2}({\rm AdS}_{3}) +\alpha^{2}\left(\d\theta^{2} + \cos^{2}(\theta)\,\d\phi'_{1}{}^{2} + \sin^{2}(\theta)\,\d\phi'_{2}{}^{2} \right) \\
-		&\quad +\d\ts{\theta}^{2} + \cos^{2}(\ts{\theta})\,\d\ts{\phi}'_{1}{}^{2} + \sin^{2}(\ts{\theta})\,\d\ts{\phi}'_{2}{}^{2} + e^{2\psi}\,\d z^{2}\,, \\[5pt]
-		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) + 2\,\alpha^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge\d\phi'_{1}\wedge\d\phi'_{2}+ 2\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge\d\ts{\phi}'_{1}\wedge\d\ts{\phi}'_{2}\,,
+\paragraph{\boldmath $(\chi, \ts{\chi}, \Omega, \ts{\Omega}, \psi)$}
+Using Hopf coordinates for both $S^3$'s we can write the 7-parameter deformation involving $(\chi_i, \ts{\chi}_i, \Omega, \ts{\Omega}, \psi)$, $i = 1,2$, as follows:
+\begin{equation} \label{eq:chiomegapsi}
+	\begin{split}
+		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^{2}({\rm AdS}_{3}) + \alpha^{2}\,\d\theta^{2} +\frac{\alpha^{2}}{\cos^{2}(\theta)+e^{\Omega}\,\sin^{2}(\theta)}\left( e^{\Omega}\cos^{2}(\theta)\,\d\phi'_{1}{}^{2} + \sin^{2}(\theta)\,\d\phi'_{2}{}^{2} \right) \\
+		&\quad +\d\ts{\theta}^{2} + \frac{1}{e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})} \left(\cos^{2}(\ts{\theta})\,\d\ts{\phi}'_{1}{}^{2} + e^{\ts{\Omega}}\sin^{2}(\ts{\theta})\,\d\ts{\phi}'_{2}{}^{2}\right) + e^{2\psi}\,\d z^{2}\,, \\[10pt]
+		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) \\
+		&\quad + \frac{2\,\alpha^{2}\,e^{\Omega}\cos(\theta)\sin(\theta)}{\left(\cos^{2}(\theta)+e^{\Omega}\,\sin^{2}(\theta)\right)^{2}}\,\d\theta\wedge\d\phi'_{1}\wedge\d\phi'_{2}+ \frac{2\,e^{\ts{\Omega}}\cos(\ts{\theta})\sin(\ts{\theta})}{\left(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\right)^{2}}\,\d\ts{\theta}\wedge\d\ts{\phi}'_{1}\wedge\d\ts{\phi}'_{2}\,,
 	\end{split}
@@
 \end{equation}
-
-This 5-parameter deformation generically breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries.
+This 7-parameter deformation generically breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries.
+The moduli space of the solution is described by the following metric:
+\begin{equation}
+	\begin{aligned}
+		\d s^{2}_{\rm mod.} &= -\frac{1}{2}\bigg[e^{-2\psi}\left(e^{\Omega}\,\d\chi_{1}^{2}+e^{-\Omega}\,\d\chi_{2}^{2}+e^{-\ts{\Omega}}\,\d\ts{\chi}_{1}^{2}+e^{\ts{\Omega}}\,\d\ts{\chi}_{2}^{2}\right) +2\,\d\psi^{2} + \frac{1}{2}\,\d\Omega^{2}+ \frac{1}{2}\,\d\ts{\Omega}^{2}\bigg].
+	\end{aligned}
+\end{equation}
+
+\paragraph{}
+A particularly interesting family of solutions is obtained in the case $\Omega=\ts{\Omega}=0$, where eq.~\eqref{eq:chiomegapsi} reduces to
+\begin{equation} \label{eq:chipsi}
+	\begin{split}
+		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^{2}({\rm AdS}_{3}) +\alpha^{2}\left(\d\theta^{2} + \cos^{2}(\theta)\,\d\phi'_{1}{}^{2} + \sin^{2}(\theta)\,\d\phi'_{2}{}^{2} \right) \\[3pt]
+		&\quad +\d\ts{\theta}^{2} + \cos^{2}(\ts{\theta})\,\d\ts{\phi}'_{1}{}^{2} + \sin^{2}(\ts{\theta})\,\d\ts{\phi}'_{2}{}^{2} + e^{2\psi}\,\d z^{2}\,, \\[5pt]
+		H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}}) + 2\,\alpha^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge\d\phi'_{1}\wedge\d\phi'_{2}+ 2\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge\d\ts{\phi}'_{1}\wedge\d\ts{\phi}'_{2}\,.
+	\end{split}
+\end{equation}
+Again, the deformation generically breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries.
 The $\chi_i$, $\ts{\chi}_i$, $i = 1, 2$ deformations are analogous to the two-parameter ``flat deformations'' \cite{Guarino:2021hrc} of AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
@@
 	\end{equation}
-	give enhancements to ${\cal N}=(2,0)$ and ${\cal N}=(0,2)$, respectively. On this hypersurface \eqref{eq:N2}, the spectrum then organizes into multiplets of $\SU{1\vert1,1}$.
+	give enhancements to ${\cal N}=(0,2)$ and ${\cal N}=(2,0)$, respectively. On this hypersurface \eqref{eq:N2}, the spectrum then organizes into multiplets of $\SU{1\vert1,1}$.
 	\item {\boldmath ${\cal N}=4$} Choosing
@@
 	\end{equation}
-	leads to enhancements to ${\cal N}=(4,0)$ and ${\cal N}=(0,4)$, respectively.
+	leads to enhancements to ${\cal N}=(0,4)$ and ${\cal N}=(4,0)$, respectively.
 On these three-dimensional hyper-surfaces \eqref{eq:N4Large}, the isometry group is $\SO{4}\times {\rm U}(1)^{2}$ and the spectrum reorganizes into multiplets of $D^{1}(2,1;\alpha)$.
-
-	\CE{(Mention here the SUSY family of \cite{Eloy:2021fhc}.)}
+In the special limit where
+	\begin{equation} \label{eq:limittoT4}
+		\begin{cases}
+			\chi_{1}=\chi_{2}= \chi,\\
+			\ts{\chi}_{1}=\ts{\chi}_{2}=0,\\
+			\psi=0,\\
+			\alpha \rightarrow 0,
+		\end{cases}
+	\end{equation}
+	the solution~\eqref{eq:chipsi} corresponds to the 10-dimensional uplift on $T^{4}$ of the one-parameter deformation of ${\rm AdS}_{3}\times S^{3}$ preserving ${\cal N}=(0,4)$ supersymmetries of ref.~\cite{Eloy:2021fhc} (using the notations there, the precise matching is obtained for $\chi=\sqrt{e^{2\omega}-1}$).
+In this limit, $D^{1}(2,1;\alpha)$ breaks into its small counterpart $\SU{2\vert1,1}$.
 
@@
 	\end{equation}
-	there are enhancements to ${\cal N}=(4,2)$ and ${\cal N}=(2,4)$, respectively.
+	there are enhancements to ${\cal N}=(2,4)$ and ${\cal N}=(4,2)$, respectively.
 The isometry group is $\SO{4}\times {\rm U}(1)^{2}$ and the spectrum is then given by multiplets of $D^{1}(2,1;\alpha)_{\rm L, R}\times\SU{1\vert1,1}_{\rm R,L}$.
@@
 \CE{(Expression of $H$?)}
+
+The metric parametrising this moduli space is:
+\begin{equation}
+	\begin{aligned}
+		\d s^{2}_{\rm mod.} &= -\frac{1}{2}\bigg[e^{2\psi}\left(e^{-\Omega}\,\d\zeta_{1}^{2}+e^{\Omega}\,\d\zeta_{2}^{2}+e^{\ts{\Omega}}\,\d\ts{\zeta}_{1}^{2}+e^{-\ts{\Omega}}\,\d\ts{\zeta}_{2}^{2}\right) +2\,\d\psi^{2} + \frac{1}{2}\,\d\Omega^{2}+ \frac{1}{2}\,\d\ts{\Omega}^{2}\bigg].
+	\end{aligned}
+\end{equation}
+
 %
@@
 Consider the deformations $\chi_i$, $\ts{\chi}_i$, which appear non-compact in 3-dimensional ${\cal N}=16$ gauged supergravity, with only the point $\chi_i = \ts{\chi}_i = 0$ having ${\cal N}=(4,4)$ supersymmetry.
-The subset of these deformations corresponding to the SUSY lines $\chi_1 = \chi_2 = \chi$, $\ts{\chi}_i = 0$, \EM{Camille will fix this} was analysed in the half-maximal theory in \cite{Eloy:2021fhc}.
+The subset of these deformations corresponding to the limit~\eqref{eq:limittoT4} was analysed in the half-maximal theory in ref.~\cite{Eloy:2021fhc}.
 Again, within 3-dimensional ${\cal N}=8$ supergravity, this deformation is non-compact, and remains non-compact even after uplifting to 6-dimensional supergravity on $S^3$, with no periodicity in $\chi$ observed in the KK spectrum of the 6-dimensional solution \cite{Eloy:2021fhc}.
@@
 \begin{equation}
-	{\rm SL}(2,\mathbb{R})\times{\rm SU}(2)\times\ts{{\rm SU}(2)}
+	{\rm SU}(1\vert1)\times{\rm SU}(2)\times\ts{{\rm SU}(2)}
 \end{equation}
 as even part.
-Its multiplets are labelled by the spins $\ell$ and $\ts{\ell}$ of each ${\rm SU}(2)$ factor and the eigenvalue $h$ of the $\mathfrak{sl}(2,\mathbb{R})$ generator.
+Its multiplets are labelled by the spins $\ell$ and $\ts{\ell}$ of each ${\rm SU}(2)$ factor and the eigenvalue $h$ of the $\mathfrak{su}(1\vert1)\simeq\mathfrak{sl}(2,\mathbb{R})$ generator.
 Generic short multiplets $[\ell,\ts{\ell}]_{\rm s}$ are given by~\cite{deBoer:1999gea,Eberhardt:2017fsi}

### 2023-06-15 Draft_3dH3.tex
Correction of the shift formula (6.13) (error comes from Log(T)=\psi on 13/06), and of the link to AdS3xS3 in (6.18).

@@
 \begin{equation} \label{eq:confdimshiftchi}
-	2\pi n\longrightarrow e^{-2\psi} \left[ 2\pi n + \Big((q_{\rm L}+q_{\rm R})\,\frac{\chi_{1}}{\alpha}+(q_{\rm L}-q_{\rm R})\,\frac{\chi_{2}}{\alpha}+ (\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1} + (\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big) \right]\,,
+	2\pi n\longrightarrow e^{-\psi} \left[ 2\pi n + \frac{1}{2}\Big((q_{\rm L}+q_{\rm R})\,\frac{\chi_{1}}{\alpha}+(q_{\rm L}-q_{\rm R})\,\frac{\chi_{2}}{\alpha}+ (\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1} + (\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big) \right]\,,
 \end{equation}
@@
 On these three-dimensional hyper-surfaces \eqref{eq:N4Large}, the isometry group is $\SO{4}\times {\rm U}(1)^{2}$ and the spectrum reorganizes into multiplets of $D^{1}(2,1;\alpha)$.
-In the special limit where
+In the special case
 	\begin{equation} \label{eq:limittoT4}
 		\begin{cases}
-			\chi_{1}=\chi_{2}= \chi,\\
-			\ts{\chi}_{1}=\ts{\chi}_{2}=0,\\
-			\psi=0,\\
-			\alpha \rightarrow 0,
+			\chi_{1}=\chi_{2}= 0,\\
+			\ts{\chi}_{1}=-\,\ts{\chi}_{2}=\sqrt{1-e^{2\omega}},\\
+			\psi = -\,\omega,
 		\end{cases}
 	\end{equation}
-	the solution~\eqref{eq:chipsi} corresponds to the 10-dimensional uplift on $T^{4}$ of the one-parameter deformation of ${\rm AdS}_{3}\times S^{3}$ preserving ${\cal N}=(0,4)$ supersymmetries of ref.~\cite{Eloy:2021fhc} (using the notations there, the precise matching is obtained for $\chi=\sqrt{e^{2\omega}-1}$).
-In this limit, $D^{1}(2,1;\alpha)$ breaks into its small counterpart $\SU{2\vert1,1}$.
+	the solution~\eqref{eq:chipsi} corresponds to the 10-dimensional uplift on $S^{3}\times S^{1}$ of the one-parameter deformation of ${\rm AdS}_{3}\times S^{3}$ preserving ${\cal N}=(0,4)$ supersymmetries of ref.~\cite{Eloy:2021fhc}.
 

### 2023-06-15 Draft_3dH3.tex
Changes by Emanuel.

@@
 
-\EM{Kinetic terms? Might be interesting for the S-fold deformations to see what kind of metric we have on the moduli space. This will go below the specific zoom-ins}
-
 % \paragraph{S-fold like deformations} Scalar spectrum:
@@
 The moduli space of the solution is described by the following metric:
-\begin{equation}
+\begin{equation} \label{eq:Zam7Param}
 	\begin{aligned}
-		\d s^{2}_{\rm mod.} &= -\frac{1}{2}\bigg[e^{-2\psi}\left(e^{\Omega}\,\d\chi_{1}^{2}+e^{-\Omega}\,\d\chi_{2}^{2}+e^{-\ts{\Omega}}\,\d\ts{\chi}_{1}^{2}+e^{\ts{\Omega}}\,\d\ts{\chi}_{2}^{2}\right) +2\,\d\psi^{2} + \frac{1}{2}\,\d\Omega^{2}+ \frac{1}{2}\,\d\ts{\Omega}^{2}\bigg].
+		\d s^{2}_{\rm mod.} &= -\frac{1}{2}\bigg[e^{-2\psi}\left(e^{\Omega}\,\d\chi_{1}^{2}+e^{-\Omega}\,\d\chi_{2}^{2}+e^{-\ts{\Omega}}\,\d\ts{\chi}_{1}^{2}+e^{\ts{\Omega}}\,\d\ts{\chi}_{2}^{2}\right) +2\,\d\psi^{2} + \frac{1}{2}\,\d\Omega^{2}+ \frac{1}{2}\,\d\ts{\Omega}^{2}\bigg] \,.
 	\end{aligned}
@@
 These $\chi_i$, $\ts{\chi}_i$, $\psi$ deformations are completely analogous to $\mathbb{C}$-structure deformations of $T^2$, with the $\chi_i$, $\ts{\chi}_i$ corresponding to the real part and the $\psi$ deformation to the imaginary part of the $\mathbb{C}$-structure deformation.
-
-Therefore, these deformations affect the Kaluza-Klein spectrum as follows: the conformal dimension of each physical field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
+Note that the $\psi$ deformation does not exist in the otherwise analogous AdS$_4 \times S^5 \times S^1$ vacua in \cite{Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}, due to the ``S-fold'' identification in that case.
+This leads to an important difference in the global structure of the moduli space that we will discuss in section \ref{s:Compact}.
+
+These deformations affect the Kaluza-Klein spectrum as follows: the conformal dimension of each physical field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
 \begin{equation} \label{eq:confdimshiftchi}
-	2\pi n\longrightarrow e^{-\psi} \left[ 2\pi n + \frac{1}{2}\Big((q_{\rm L}+q_{\rm R})\,\frac{\chi_{1}}{\alpha}+(q_{\rm L}-q_{\rm R})\,\frac{\chi_{2}}{\alpha}+ (\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1} + (\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big) \right]\,,
+	2\pi n\longrightarrow e^{-2\psi} \left[ 2\pi n + \Big((q_{\rm L}+q_{\rm R})\,\frac{\chi_{1}}{\alpha}+(q_{\rm L}-q_{\rm R})\,\frac{\chi_{2}}{\alpha}+ (\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1} + (\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big) \right]\,,
 \end{equation}
@@
 For generic values of $\chi_i$, $\ts{\chi}_i$, the AdS$_3$ vacuum will be completely non-supersymmetric.
-However, it is easy to see from inspection of the spectrum \eqref{eq:confdims3s3s1} and \eqref{eq:confdimshiftchi} that the spectrum is bounded from below by the masses of the 3-dimensional gauged supergravity modes at the ${\cal N}=(4,4)$ supersymmetric origin.
-Therefore, these non-supersymmetric AdS$_3$ vacua are still perturbatively stable within IIB supergravity and, similarly to \cite{Giambrone:2021wsm} suggest that there may be a dual non-supersymmetric conformal manifold if there are no instabilities beyond supergravity, such as non-perturbative instabilities triggered by brane nucleation or non-vanishing $\beta$-functions of marginal multi-trace operators \EM{add citations}.
-However, it is worth stressing that the vacua here may have further protection against such instabilities due to their continuous limits to the SUSY vacua.
+However, it is easy to see from inspection of the spectrum \eqref{eq:confdims3s3s1} and \eqref{eq:confdimshiftchi} that the spectrum is bounded from below by the masses of the 3-dimensional gauged supergravity modes at the ${\cal N}=(4,4)$ supersymmetric origin, i.e.
+where $\chi_i = \ts{\chi}_i = n = \ell = \ts{\ell} = 0$.
+Therefore, these non-supersymmetric AdS$_3$ vacua are perturbatively stable within IIB supergravity and, similarly to \cite{Giambrone:2021wsm} suggest that there may be a dual non-supersymmetric conformal manifold if there are no instabilities beyond supergravity.
+However, just as in \cite{Giambrone:2021wsm}, the non-SUSY vacua are protected against perturbative $\alpha'$ or $g_s$ corrections of string theory, which might have lifted the moduli $\chi_i$, $\ts{\chi}_i$, and there are no scalars at the BF bound which may have been pushed below by such corrections.
+The moduli $\chi_i$, $\ts{\chi}_i$ locally correspond to diffeomorphisms and, therefore, any diffeomorphism-invariant quantity, such as higher powers of the curvature tensor or fluxes, as would appear in $\alpha'$ or $g_s$ corrections, will be independent of $\chi_i$ and $\ts{\chi}_i$.
+The vacua are also protected against Witten's bubbles of nothing \cite{Witten:1981gj}, due to flux quantisation on $S^3$ and the spin structure on $S^1$.
+This does not rule out all potential sources of instabilities.
+For example, the non-SUSY vacua may suffer from non-perturbative instabilities triggered by brane nucleation \cite{Ooguri:2016pdq,Bomans:2021ara} or non-vanishing $\beta$-functions of marginal multi-trace operators \cite{Witten:2001ua}.
+However, our non-SUSY vacua here may have further protection against such instabilities due to their continuous limits to the SUSY vacua, just as they have against perturbative higher-derivative corrections.
 
@@
 \paragraph{\boldmath $(\zeta,\ts{\zeta},\Omega,\ts{\Omega},\psi)$}
-Again in Euler coordinates:
+Again in Hopf coordinates:
 \begin{equation}
@@
 	\begin{aligned}
-		\d s^{2}_{\rm mod.} &= -\frac{1}{2}\bigg[e^{2\psi}\left(e^{-\Omega}\,\d\zeta_{1}^{2}+e^{\Omega}\,\d\zeta_{2}^{2}+e^{\ts{\Omega}}\,\d\ts{\zeta}_{1}^{2}+e^{-\ts{\Omega}}\,\d\ts{\zeta}_{2}^{2}\right) +2\,\d\psi^{2} + \frac{1}{2}\,\d\Omega^{2}+ \frac{1}{2}\,\d\ts{\Omega}^{2}\bigg].
+		\d s^{2}_{\rm mod.} &= -\frac{1}{2}\bigg[e^{2\psi}\left(e^{-\Omega}\,\d\zeta_{1}^{2}+e^{\Omega}\,\d\zeta_{2}^{2}+e^{\ts{\Omega}}\,\d\ts{\zeta}_{1}^{2}+e^{-\ts{\Omega}}\,\d\ts{\zeta}_{2}^{2}\right) +2\,\d\psi^{2} + \frac{1}{2}\,\d\Omega^{2}+ \frac{1}{2}\,\d\ts{\Omega}^{2}\bigg]\,.
 	\end{aligned}
@@
 Therefore, even though neither the 3-dimensional gauged supergravity, nor 6-dimensional supergravity is invariant under these shifts, upon lifting to the full 10-dimensional IIB theory, the higher KK modes on $S^1$ restore the invariance under the shifts, just as in the analogous deformations studied in AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
-This highlights the importance of the $S^1$ direction in studying the AdS$_3$ vacua.
+This highlights the importance of the $S^1$ direction in studying these AdS$_3$ vacua.
 
@@
 for the $T^2_{(\ts{\phi}_i,\, z)}$. Thus, the $S$-transformation effectively inverts the radius of the $S^1$, while transforming the combinations
-\begin{equation}
+\begin{equation} \label{eq:STransformChi}
 	e^{-\psi}\chi_i \rightarrow - e^{-\psi}\chi_i \,, \qquad e^{-\psi} \ts{\chi}_i \rightarrow - e^{-\psi}\ts{\chi}_i \,.
 \end{equation}
-\EM{EM To clean this up!}\\
-The KK spectrum \eqref{eq:confdims3s3s1}, \eqref{eq:confdimshiftchi} is clearly not invariant under this transformation.
-However, the $S$-transformation takes us out of the regime of validity of supergravity, with new string degrees of freedom potentially becoming light.
-Indeed, in this case, after the transformation \eqref{eq:Stransform}, strings wound around $S^1$ will become light, and one would expect them to replace the KK modes that have become heavy, realising the T-duality on $S^1$.
-Thus, in the full IIB string theory, the moduli space of each $T^2$ fibration with complex structure \eqref{eq:T2CStructure} should be identified under the M\"{o}bius group $\SL{2,\mathbb{Z}}$.
-\EM{Can we check the T-dual explicitly?
-Maybe we need a different gauge choice for $C_6$ so that it does not depend on $z$.
-Can we describe the $T^4 \times S^1$ a bit better instead of as a collection of $T^2$'s?}
+If we consider a truncation where the $n \neq 0$ modes are discarded, for example, by uplifting only on $S^3$ to 6 dimensions as in \cite{Eloy:2021fhc} or on $S^3 \times S^3 \times S^1$ to 9 dimensions, then the $S$-transformation clearly leaves the KK spectrum \eqref{eq:spectrumorigin}, \eqref{eq:confdims3s3s1}, \eqref{eq:confdimshiftchi} invariant.
+This is because the spectrum for the $n = 0$ modes only depends on the combinations $e^{-\psi}\chi_i$ and $e^{-\psi}\ts{\chi}_i$, which pick up minus signs, as in \eqref{eq:STransformChi}.
+The effect of \eqref{eq:Stransformchi} is to simply exchanges modes of the opposite charges under the ${\rm U}(1)_{\rm L}\times\ts{{\rm U}(1)}_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm R}$ within the spectrum.
+
+However, if we include the $n \neq 0$ modes by going to the full 10-dimensional IIB supergravity theory, the KK spectrum \eqref{eq:spectrumorigin}, \eqref{eq:confdims3s3s1}, \eqref{eq:confdimshiftchi} is not invariant under the $S$ transformation.
+At the same time, the $S$-transformation effectively inverts the radius of the $S^1$, as in \eqref{eq:STransformChi} and, thus, takes us out of the regime of validity of supergravity, with new string degrees of freedom potentially becoming light.
+Indeed, in this case, after the transformation \eqref{eq:STransformChi}, strings wound around $S^1$ will become light, and one would expect them to replace the KK modes that have become heavy, realising the T-duality on $S^1$.
+This suggests that in the full IIB string theory, the moduli space of each $T^2$ fibration with complex structure \eqref{eq:T2CStructure} should be identified under the M\"{o}bius group $\SL{2,\mathbb{Z}}$, which has a natural action on the metric of this 5-parameter submanifold of moduli space \eqref{eq:Zam7Param}.
+Note that this is quite different from the AdS$_4 \times S^5 \times S^1$ ``S-fold'' vacua \cite{Giambrone:2021zvp,Giambrone:2021wsm}, which do not have a $S^1$ rescaling modulus and, therefore, do not carry the natural action of $\SL{2,\mathbb{Z}}$ on each complex structure modulus that we find here.
 
 \section{Conclusions} \label{s:Conclusions}
+In this paper, we used $\EE$ ExFT to construct the consistent truncation of IIB supergravity around the ${\cal N}=(4,4)$ AdS$_3 \times S^3 \times S^3 \times S^1$ vacuum.
+Even though the vacuum breaks half of the supersymmetries, we are able to construct a consistent truncation to 3-dimensional maximal gauged supergravity, providing an uplift to the ${\cal N}=16$ gauged supergravity proposed in \cite{Hohm:2005ui} for the 3-dimensional description of this AdS$_3$ vacuum.
+We constructed our consistent truncation by doing a $S^1$ reduction of the truncation of IIB on $S^3 \times S^3$ \cite{Inverso:2016eet}, and turning on an additional $H_7$ flux on $S^3 \times S^3 \times S^1$, which is necessary to obtain an AdS$_3$ vacuum.
+We also show that it is not possible to turn on such an additional flux for the other ``dyonic'' consistent truncations on $S^6$, $S^5 \times S^1$, $S^4 \times S^2$ \cite{Guarino:2015jca,Inverso:2016eet} reduced on $S^1$, whilst maintining a consistent truncation to ${\cal N}=16$ gauged supergravity.
+
+To find this vacuum, we had to construct the potential of 3-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor, which was not previously known.
+Since the vector fields of ${\cal N}=16$ gauged supergravity transform in the adjoint of $\EE$, the Cartan-Killing metric of $\EE$ can be used to construct new terms in the potential, which leads to a different form of the potential compared to the universal one found in $D \geq 4$ dimensions.
+Nonetheless, we used the generalised Scherk-Schwarz Ansatz of $\EE$ ExFT \cite{Galli:2022idq} to obtain the potential in terms of the embedding tensor, for all gauged supergravities that can be uplifted to maximal 10-/11-dimensional supergravity.
+This condition of being able to uplift imposes additional quadratic constraints on the embedding tensor \eqref{eq:reltrX}, beyond the usual quadratic constraints of gauged supergravity.
+This can be used to rule out the higher-dimensional origin of some 3-dimensional ${\cal N}=16$ gauged supergravities.
+\EM{Mention if we actually use this.}
+
+Using our consistent truncation and the 3-dimensional potential, we studied the moduli space of the AdS$_3$ vacuum within 3-dimensional gauged supergravity.
+Even a simple search led to a surprisingly large 11-dimensional moduli space of AdS$_3 \times S^3 \times S^3 \times S^1$ vacua, with more moduli likely.
+While most of these moduli break all supersymmetries, we also identified submanifolds where ${\cal N}=(4,2),\, (4,0),\, (2,2),\, (2,0)$ is preserved, where the ${\cal N}=4$ cases always correspond to the ``large'' superconformal algebra.
+The corresponding moduli are analogous to the  ``flat deformations'' that arise in the AdS$_4 \times S^5 \times S^1$ vacuum \cite{Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}.
+I.e.
+they correspond to local diffeomorphisms mixing angles on the $S^3$'s with the $S^1$, but which are not globally well-defined, much like complex structure deformations of $T^2$, allowing us to compute the full Kaluza-Klein spectrum of these deformed AdS$_3$ vacua.
+Generic ``flat deformations'' of this type break all supersymmetries but are still perturbatively stable.
+Moreover, they are protected against perturbative higher-derivative corrections because the deformations locally correspond to diffeomorphisms.
+
+We also saw that uplifting our AdS$_3$ vacua to IIB string theory leads to the compactness of some directions of moduli space.
+The ``flat deformations'' that we studied appear non-compact within the 3-dimensional gauged supergravity, but upon uplifting to 10 dimensions, the moduli become compact, similar to \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
+Interestingly, this compactness is not visible upon only uplifting on $S^3$ to 6-dimensional supergravity \cite{Eloy:2021fhc}, but require the uplift on the additional $S^1$ direction.
+The compactification of the moduli can be understood geometrically as the $T$-action of $\SL{2,\mathbb{Z}}$ on $T^2$-fibration.
+Differently from the AdS$_4 \times S^5 \times S^1$ case \cite{Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}, in the AdS$_3 \times S^3 \times S^3 \times S^1$ case we also have a $S^1$ rescaling modulus, so that we naturally have the full complex structure moduli related to the $T^2$-fibrations and which carry a natural action of the full $\SL{2,\mathbb{Z}}$.
+While the $S$-action of $\SL{2,\mathbb{Z}}$ left the Kaluza-Klein spectrum of 6-dimensional supergravity on AdS$_3 \times S^3$ \cite{Eloy:2021fhc} invariant, it is broken by the additional $S^1$ direction when uplifting to IIB supergravity.
+However, we argued that the $S$-action leave invariant the full AdS$_3 \times S^3 \times S^1$ solution of IIB string theory, once string winding modes around $S^1$ are included.
+In this case, the complex structure deformations live in the fundamental domain of $\SL{2,\mathbb{Z}}$, rather than the whole $\mathbb{C}$-plane, as the 3-dimensional supergravity would suggest.
+
+Our work raises several questions that deserve further inquiry.
+Firstly, we only performed a simple search, yielding an 11-dimensional moduli space of AdS$_3 \times S^3 \times S^3 \times S^1$ within the ${\cal N}=16$ gauged supergravity.
+It would be good to complete our analysis to compute the full 3-dimensional moduli space and to understand why it is so large.
+Our consistent truncation Ansatz could then be used to uplift the moduli space to IIB supergravity, and to use Kaluza-Klein spectrometry \cite{Malek:2019eaz,Malek:2020yue,Eloy:2020uix} to obtain the conformal dimensions of all single-trace operators and determine the perturbative stability of the non-SUSY vacua.
+Secondly, it would be interesting to study the string sigma model \cite{Eberhardt:2019niq} on the ``flat deformations'' of AdS$_3 \times S^3 \times S^3 \times S^1$, or the analogous deformations of AdS$_3 \times S^3 \times T^4$.
+Since these deformations locally are diffeomorphisms, one may expect a simple sigma model description on the ${\cal N}=(4,2),\, (4,0),\, (2,2),\, (2,0)$ SUSY vacua and, potentially, even for the non-SUSY AdS$_3 \times S^3 \times S^3 \times S^1$ vacua obtained this way.
+Finally, the non-perturbative stability of the perturbative stability non-supersymmetric AdS$_3$ vacua we found deserves further study.
+We leave these questions for future work.
 
 \section*{Acknowledgements}
-We are grateful to XXX for useful discussions and correspondence.
+We are grateful to \EM{add others} Nikolay Bobev, Yolanda Lozano, Niall Macpherson for useful discussions and correspondence.
 CE is supported by the FWO-Vlaanderen through the project G006119N and by the Vrije Universiteit Brussel through the Strategic Research Program ``High-Energy Physics''.
@@
 \end{equation}
-as even part.
+as its even part.
 Its multiplets are labelled by the spins $\ell$ and $\ts{\ell}$ of each ${\rm SU}(2)$ factor and the eigenvalue $h$ of the $\mathfrak{su}(1\vert1)\simeq\mathfrak{sl}(2,\mathbb{R})$ generator.
@@
 	 h_{0}+1 & \big(\ell,\ts{\ell}-1\big) \oplus \big(\ell,\ts{\ell}\big) \oplus \big(\ell-1,\ts{\ell}\big) \\[5pt]
-	 h_{0} + \nicefrac{3}{2} & \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big),
+	 h_{0} + \nicefrac{3}{2} & \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big)\,,
 	\end{array}
@@
 	 \nicefrac{3}{2} & \big(\nicefrac{1}{2},\nicefrac{1}{2}\big) \\[5pt]
-	 2 & \big(0,0\big).
+	 2 & \big(0,0\big)\,.
 	\end{array}
@@
 \begin{equation}
- 	[\ell,\ts{\ell}] = [\ell,\ts{\ell}]_{\rm s} \oplus [\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}]_{\rm s}.
+ 	[\ell,\ts{\ell}] = [\ell,\ts{\ell}]_{\rm s} \oplus [\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}]_{\rm s}\,.
 \end{equation}
@@
 	 h + \nicefrac{3}{2} & \big(\ell+\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus\big(\ell+\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}+\nicefrac{1}{2}\big) \oplus \big(\ell-\nicefrac{1}{2},\ts{\ell}-\nicefrac{1}{2}\big) \\[5pt]
-	 h + 2 & \big(\ell,\ts{\ell}\big).
+	 h + 2 & \big(\ell,\ts{\ell}\big)\,.
 	\end{array}

### 2023-06-15 Draft_3dH3.tex
Correction (6.13).
Updated discussion of the zeta family.

@@
 Again in Hopf coordinates:
-\begin{equation}
+\begin{equation} \label{eq:metriczeta}
 	\begin{split}
@@
 
-%
-%\paragraph{SUSY deformation}
-%
-%%In Hopf coordinates:
-%%\begin{equation}
-%%	\begin{split}
-%%		ds^2 &= \alpha^2 \left[ ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
-%%		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{\CE{-}(1-e^{2\omega})} d\psi \,, \\
-%%		d\sigma &= vol_{\mathbb{CP}^1} \,.
-%%	\end{split}
-%%\end{equation}
-%
-%It is convenient to use the Hopf fibration to describe this, we denote by $\phi$ the coordinate on the $S^1$ fibre and by $\xi$ the homogeneous coordinate on $\mathbb{CP}^1$.
+As previously, the deformation breaks the isometry group down to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries.
+Note that for
+\begin{equation}
+	\zeta_{1}=\pm\zeta_{2},\quad \ts{\zeta}_{1}=\mp\ts{\zeta}_{2}\,\quad\Omega=\ts{\Omega}=0,
+\end{equation}
+the solution~\eqref{eq:metriczeta} reproduces eq.~\eqref{eq:chipsi} for
+\begin{equation}
+	\chi_{1}=\pm\chi_{2}=\frac{\zeta_{1}}{1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2}},\quad \ts{\chi}_{1}=\mp\ts{\chi}_{2}=-\frac{\ts{\zeta}_{1}}{1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2}},\quad e^{2\psi}=\frac{1}{(1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2})^{2}},
+\end{equation}
+with ${\cal N}=(4,0)$ (or $(0,4)$) and symmetry enhancement to ${\rm SO}(4)\times{\rm U}(1)^{2}$. There seems to be no other points with (super)-symmetry enhancement in the scalar manifold.
+
+% \paragraph{SUSY deformation}
+
+% %In Hopf coordinates:
+% %\begin{equation}
+% %	\begin{split}
+% %		ds^2 &= \alpha^2 \left[ ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
+% %		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{\CE{-}(1-e^{2\omega})} d\psi \,, \\
+% %		d\sigma &= vol_{\mathbb{CP}^1} \,.
+% %	\end{split}
+% %\end{equation}
+
+% It is convenient to use the Hopf fibration to describe this, we denote by $\phi$ the coordinate on the $S^1$ fibre and by $\xi$ the homogeneous coordinate on $\mathbb{CP}^1$.
 The round metric on $S^3$ then reads
-%\begin{equation}
+% \begin{equation}
 % 	g= \mathrm{d}s^2_{\mathbb{CP}^1} + (\sigma + \mathrm{d}\phi)^2
-%\end{equation}
-%where 
-%\begin{equation}
+% \end{equation}
+% where 
+% \begin{equation}
 % 	\begin{split}
@@
 % 	\end{split}
-%\end{equation}
-%The deformation does not affect $S_+^3$, but it mixes the $S^1$ factor in the internal space with the Hopf fibre of $S_-^3$. It is parametrised by a real number $\Omega$, such that the metric reads
-%\begin{equation}
+% \end{equation}
+% The deformation does not affect $S_+^3$, but it mixes the $S^1$ factor in the internal space with the Hopf fibre of $S_-^3$. It is parametrised by a real number $\Omega$, such that the metric reads
+% \begin{equation}
 % 	\begin{split}
@@
 % 	\end{split}
-%\end{equation}
+% \end{equation}
 % The three form flux gets changed according to the prescription $\d\phi \rightarrow \d\phi -  \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d \psi$ and we find:
-%\begin{equation}
+% \begin{equation}
 % 	H_{(3)}=\alpha^2vol_{\mathbb{CP}^1}\wedge (\d\phi - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi) + vol_{S_+^3}.
-%\end{equation}
-%
-%%
-%%In spherical coordinates:
-%%\begin{equation}
-%%	\begin{aligned}
-%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+\alpha^{2}\,\d s^2\left(S^{3}_{-}\right) +e^{-2\omega}\,\d\psi^{2}\\
-%%		&\quad+2\,\alpha\,e^{-2\omega}\,\sqrt{-1+e^{2\omega}}\left(-\cos^{2}(\theta)\,\d\varphi_{1}+\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi\\[5pt]
-%%		&= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+e^{-4\omega}\,\d\psi^{2}\\
-%%		&\quad+\alpha^{2}\bigg[\d \theta^2+\cos^{2}(\theta)\left(\d\varphi_{1}-\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}+\sin^{2}(\theta)\left(\d\varphi_{2}+\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}\bigg] ,\\[5pt]
-%%		\d s^2\left(S^{3}_{-}\right) &= \d\theta^{2}+\cos^{2}(\theta)\,\d\varphi_{1}^{2}+\sin^{2}(\theta)\,\d\varphi_{2}^{2}.
-%%	\end{aligned}
-%%\end{equation}
-%
-%\paragraph{Non-SUSY deformation}
-%Here we study a more general deformation depending on three parameters $\Omega$, $\zeta_{1,8}$ and $\zeta_{2,3}$.
+% \end{equation}
+
+% %
+% %In spherical coordinates:
+% %\begin{equation}
+% %	\begin{aligned}
+% %		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+\alpha^{2}\,\d s^2\left(S^{3}_{-}\right) +e^{-2\omega}\,\d\psi^{2}\\
+% %		&\quad+2\,\alpha\,e^{-2\omega}\,\sqrt{-1+e^{2\omega}}\left(-\cos^{2}(\theta)\,\d\varphi_{1}+\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi\\[5pt]
+% %		&= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+e^{-4\omega}\,\d\psi^{2}\\
+% %		&\quad+\alpha^{2}\bigg[\d \theta^2+\cos^{2}(\theta)\left(\d\varphi_{1}-\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}+\sin^{2}(\theta)\left(\d\varphi_{2}+\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}\bigg] ,\\[5pt]
+% %		\d s^2\left(S^{3}_{-}\right) &= \d\theta^{2}+\cos^{2}(\theta)\,\d\varphi_{1}^{2}+\sin^{2}(\theta)\,\d\varphi_{2}^{2}.
+% %	\end{aligned}
+% %\end{equation}
+
+% \paragraph{Non-SUSY deformation}
+% Here we study a more general deformation depending on three parameters $\Omega$, $\zeta_{1,8}$ and $\zeta_{2,3}$.
 It is convenient to write down the uplift in terms of the Hopf coordinates on $S_-^3$, while again $S_+^3$ is not deformed.\\
-%\noindent For the metric we find
-%%\begin{equation}
-%%	\begin{aligned}
-%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-%%		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
-%%		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
-%%		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2}.\\[5pt]
-%%		\Delta^{-1} &= 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
-%%	\end{aligned}
-%%\end{equation}
-%\begin{equation}
+% \noindent For the metric we find
+% %\begin{equation}
+% %	\begin{aligned}
+% %		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+% %		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
+% %		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
+% %		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2}.\\[5pt]
+% %		\Delta^{-1} &= 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
+% %	\end{aligned}
+% %\end{equation}
+% \begin{equation}
 % 	\begin{aligned}
@@
 % 	\end{aligned}
-%\end{equation}
-%where $\Delta$ is the warp factor
-%\begin{equation}
+% \end{equation}
+% where $\Delta$ is the warp factor
+% \begin{equation}
 % 		\Delta^{-1} = 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
-%\end{equation}
-%The three-form flux is 
-%\begin{equation}
+% \end{equation}
+% The three-form flux is 
+% \begin{equation}
 % 	H_{(3)}=vol_{S_-^3}+\alpha ^2\sin(\theta)\cos (\theta)(2+e^{2\Omega}\zeta^2_{1,8})(2e^{2\Omega}+\zeta_{2,3}^2)\Delta^2\mathrm{d}\theta\wedge\kappa_1\wedge\kappa_2,
-%\end{equation}
-%with the two one forms $\kappa_{1,2}$ defined by 
-%\begin{equation}
-%\begin{split}
+% \end{equation}
+% with the two one forms $\kappa_{1,2}$ defined by 
+% \begin{equation}
+% \begin{split}
 % 		\kappa_1&=\mathrm{d}\phi_1-\frac{\zeta_{2,3}}{\alpha(2e^{2\Omega}+\zeta_{2,3}^2)}\mathrm{d}\psi \\
 % 	\kappa_2&=\mathrm{d}\phi_2+ \frac{\zeta_{1,8}}{\alpha(2+e^{2\Omega}\zeta_{1,8}^2)}\mathrm{d}\psi.
-%\end{split}
-%\end{equation}
-%Note that setting $...$ recovers the supersymmetric deformation described earlier.
-%%In Hopf coordinates:
-%% \begin{equation}
-%% \begin{split}
-%% ds^2 &= \alpha^2 \left[ d\alpha_1^2 +  ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
-%% \kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
-%% d\sigma &= vol_{\mathbb{CP}^1} \,.
-%% \end{split}
-%% \end{equation}
-%% \begin{equation}
-%% 	\begin{aligned}
-%% 		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-%% 		&\quad + \Delta\,\alpha^{2}\bigg[\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm I}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm R}^{2}\Big)\,\d z_{\rm R}^{2}\\
-%% 		&\qquad\ \  + \frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm R}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm I}^{2}\Big)\,\d z_{\rm I}^{2}\\
-%% 		&\qquad\ \  + 2\,\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(-\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(2+\vert z\vert^{2}\right)+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d z_{\rm R}\d z_{\rm I}\\
-%% 		&\qquad\ \  +2\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\,\vert z\vert^{2}+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d\theta^{2}\bigg]\\
-%% 		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
-%% 		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
-%% 		\Delta^{-1} &= 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
-%% 	\end{aligned}
-%% \end{equation}
-%
-%%%%%
-%
-%%\begin{equation}
-%%	\begin{aligned}
-%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-%%		&\quad + \frac{\alpha^{2}}{1+\gamma\,\vert z\vert^{2}}\bigg[\Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm I}^{2}\right)+\left(\gamma-1\right)\,z_{\rm R}^{2}\Big)\,\frac{\d z_{\rm R}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
-%%		&\qquad + \Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm R}^{2}\right)+\left(\gamma-1\right)\,z_{\rm I}^{2}\Big)\,\frac{\d z_{\rm I}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}} - 2\,\Big(1+\vert z\vert^{2}-\left(\gamma-1\right)\Big)\,\frac{\d z_{\rm R}\d z_{\rm I}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
-%%		&\qquad+2\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\left(\gamma+\vert z\vert^{2}\right)\d\theta^{2}\bigg]\\
-%%		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
-%%		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
-%%		\gamma &= \frac{2\,e^{2\Omega}+\zeta_{2,3}^{2}}{2+e^{2\Omega}\zeta_{1,8}^{2}},\qquad \Delta^{-1} = 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
-%%	\end{aligned}
-%%\end{equation}
+% \end{split}
+% \end{equation}
+% Note that setting $...$ recovers the supersymmetric deformation described earlier.
+% %In Hopf coordinates:
+% % \begin{equation}
+% % \begin{split}
+% % ds^2 &= \alpha^2 \left[ d\alpha_1^2 +  ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
+% % \kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
+% % d\sigma &= vol_{\mathbb{CP}^1} \,.
+% % \end{split}
+% % \end{equation}
+% % \begin{equation}
+% % 	\begin{aligned}
+% % 		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+% % 		&\quad + \Delta\,\alpha^{2}\bigg[\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm I}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm R}^{2}\Big)\,\d z_{\rm R}^{2}\\
+% % 		&\qquad\ \  + \frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm R}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm I}^{2}\Big)\,\d z_{\rm I}^{2}\\
+% % 		&\qquad\ \  + 2\,\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(-\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(2+\vert z\vert^{2}\right)+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d z_{\rm R}\d z_{\rm I}\\
+% % 		&\qquad\ \  +2\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\,\vert z\vert^{2}+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d\theta^{2}\bigg]\\
+% % 		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
+% % 		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
+% % 		\Delta^{-1} &= 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
+% % 	\end{aligned}
+% % \end{equation}
+
+% %%%%
+
+% %\begin{equation}
+% %	\begin{aligned}
+% %		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
+% %		&\quad + \frac{\alpha^{2}}{1+\gamma\,\vert z\vert^{2}}\bigg[\Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm I}^{2}\right)+\left(\gamma-1\right)\,z_{\rm R}^{2}\Big)\,\frac{\d z_{\rm R}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
+% %		&\qquad + \Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm R}^{2}\right)+\left(\gamma-1\right)\,z_{\rm I}^{2}\Big)\,\frac{\d z_{\rm I}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}} - 2\,\Big(1+\vert z\vert^{2}-\left(\gamma-1\right)\Big)\,\frac{\d z_{\rm R}\d z_{\rm I}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
+% %		&\qquad+2\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\left(\gamma+\vert z\vert^{2}\right)\d\theta^{2}\bigg]\\
+% %		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
+% %		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
+% %		\gamma &= \frac{2\,e^{2\Omega}+\zeta_{2,3}^{2}}{2+e^{2\Omega}\zeta_{1,8}^{2}},\qquad \Delta^{-1} = 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
+% %	\end{aligned}
+% %\end{equation}
 

### 2023-06-15 Draft_3dH3.tex
Update by Emanuel.

--- 2023-06-15 Draft_3dH3.tex
@@
 Our truncation Ansatz includes, in addition to the ${\cal N}=(4,4)$ vacuum, a host of moduli breaking some or all of the supersymmetries.
-We explicitly construct the uplift of a subset of these to construct new supersymmetric and non-supersymmetric AdS$_3$ vacua of IIB string theory, which include a range of fully perturbatively stable non-supersymmetric cases.
-Moreover, we show how the supersymmetric direction of the moduli space of AdS$_3$ vacua of six-dimensional gauged supergravity studied in \cite{Eloy:2021fhc} is compactified upon lifting to 10 dimensions.
+We explicitly construct the uplift of a subset of these to construct new supersymmetric and non-supersymmetric AdS$_3$ vacua of IIB string theory, which include a range of perturbatively stable non-supersymmetric 10-d vacua.
+Moreover, we show how the supersymmetric direction of the moduli space of AdS$_3$ vacua of six-dimensional gauged supergravity studied in \cite{Eloy:2021fhc} is compactified upon lifting to 10 dimensions, and find evidence of T-duality playing a role in global aspects of the moduli space.
 Along the way, we also derive the form of 3-dimensional ${\cal N}=16$ gauged supergravity in terms of the embedding tensor and rule out a 10-/11-dimensional origin of some 3-dimensional gauged supergravities.
@@
 Exceptional Field Theory (ExFT) is a reformulation of 10-/11-dimensional supergravity that unifies the metric and flux degrees of freedom and thereby makes manifest an exceptional symmetry group\footnote{For the purposes of this paper, we do not draw a distinction between ExFT and Exceptional Generalised Geometry, since these agree when the ``section condition'' is solved, which we will always assume here.}.
-Over the last decade, this has proven an extremely useful tool for constructing consistent truncations, leading to a number of new examples preserving various amounts of supersymmetry \cite{Hohm:2014qga,Lee:2014mla,Malek:2015hma,Baguet:2015sma,Baguet:2015iou,Lee:2015xga,Malek:2016bpu,Ciceri:2016dmd,Cassani:2016ncu,Inverso:2016eet,Malek:2017cle,Malek:2017njj,Malek:2018zcz,Malek:2019ucd,Cassani:2019vcl,Malek:2020jsa,Cassani:2020cod}.
+Over the last decade, this has proven extremely useful for constructing consistent truncations, leading to a number of new examples preserving various amounts of supersymmetry \cite{Hohm:2014qga,Lee:2014mla,Malek:2015hma,Baguet:2015sma,Baguet:2015iou,Lee:2015xga,Malek:2016bpu,Ciceri:2016dmd,Cassani:2016ncu,Inverso:2016eet,Malek:2017cle,Malek:2017njj,Malek:2018zcz,Malek:2019ucd,Cassani:2019vcl,Malek:2020jsa,Cassani:2020cod}.
 However, consistent truncations to three dimensions have, until recently \cite{Galli:2022idq}, remained largely unexplored.
@@
 
-Here we will focus on the ${\cal N}=(4,4)$ AdS$_3 \times S^3 \times S^3 \times S^1$ vacuum of IIB string theory and show that it admits a consistent truncation to a maximal gauged supergravity, which was first studied in \cite{Hohm:2005ui}.
+Here we will focus on the ${\cal N}=(4,4)$ AdS$_3 \times S^3 \times S^3 \times S^1$ vacuum of IIB string theory and show that it admits a consistent truncation to a 3-dimensional maximal gauged supergravity, which was first studied in \cite{Hohm:2005ui}.
 All vacua of this theory break at least half the supersymmetries, reflecting the absence of a maximally supersymmetric AdS$_3$ vacuum in string theory.
 Key to constructing this consistent truncation is to add new fluxes to the $S^1$ reduction of the consistent truncation of IIB supergravity on $S^3 \times S^3$ \cite{Inverso:2016eet}.
+We will also show that this procedure for adding flux fails to produce a consistent truncation for the $S^1$ reduction of other ``dyonic'' truncations to 4 dimensions \cite{Guarino:2015jca,Inverso:2016eet}.
 
 Using our consistent truncation, we will show that the AdS$_3 \times S^3 \times S^3 \times S^1$ has a rich moduli space of symmetry- and supersymmetry-breaking deformations, including some that are analogous to the ``flat deformations'' studied for AdS$_4 \times S^5 \times S^1$ \cite{Guarino:2020gfe,Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}.
-While some of these deformations preserve some amounts of supersymmetry, others break all supersymmetries, yet, surprisingly, at least a subset of vacua continue to be perturbatively stable within IIB supergravity, similar to \cite{Giambrone:2021wsm}.
+While some of these deformations preserve some amounts of supersymmetry, others break all supersymmetries.
+Yet, surprisingly, at least a subset of vacua continue to be perturbatively stable within IIB supergravity, similar to \cite{Giambrone:2021wsm}.
 Our work also provides an uplift of 6-dimensional supergravity on $S^3$ studied in \cite{Eloy:2021fhc} to IIB string theory.
-As we will show, some deformations that appear non-compact in 6-dimensional supergravity \cite{Eloy:2021fhc} are compactified within the full 10-dimensional supergravity theory.
-
-Another technical result of our work is the derivation of the potential of 3-dimensional gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv} in terms of the embedding tensor, which was previously only expressed in terms of fermion shift matrices.
-As a by-product, we find that a constraint that must be obeyed by the embedding tensor of any 3-dimensional gauged supergravity that can be uplifted to 10-/11-dimensional supergravity.
-As we show, this allows us to prove a higher-dimensional origin of some 3-dimensional gaugings.
+As we will show, some supersymmetric deformations that appear non-compact in 6-dimensional supergravity \cite{Eloy:2021fhc} are compactified within the full 10-dimensional supergravity theory.
+We will also find evidence of T-duality playing a role in the global properties of the moduli space.
+
+Another technical result of our work is the derivation of the potential of 3-dimensional gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv} in terms of the embedding tensor.
+The potential was previously only known in terms of fermion shift matrices.
+As a by-product, we find a constraint that must be obeyed by the embedding tensor of any 3-dimensional gauged supergravity that can be uplifted to 10-/11-dimensional supergravity.
+As we show, this allows us to prove the lack of a higher-dimensional origin of some 3-dimensional gaugings.
+\EM{update}
 
@@
 
-\subsubsection{The $S^3$ twist matrix}
+\subsubsection{The $S^n$ twist matrix} \label{s:SLn}
 \EM{Move to appendix?!?!} \CE{(I think I would say yes)}\\
@@
 
+\subsection{Adding fluxes to other dyonic truncations}
+One could also imagine applying the same procedure we described here to turn on fluxes in other maximally supersymmetric compactifications.
+Natural candidates are the $S^1$ reductions of the consistent truncations to dyonically gauged 4-dimensional maximal supergravities \cite{Guarino:2015jca,Inverso:2016eet}.
+The 4-dimensional truncations arise from compactifications of 10-dimensional supergravity on $S^6$, $S^5\times S^1$, $S^4\times S^2$, with the 10-d theory corresponding to (massive) IIA/IIB when the spheres have even/odd dimensions, respectively.
+The corresponding twist matrices for $S^6$, $S^5\times S^1$, $S^4\times S^2$ belong to $\SL{7}$, $\SL{6}\times \SL{2}$ and $\SL{5}\times \SL{3}$, as reviewed in \ref{s:SLn}.
+
+In order to use our procedure for turning on a flux we would have to find singlets in the $\mbf{133}$ of $\En{7}$ under $\SL{7}$, $\SL{6}\times \SL{2}$ and $\SL{5}\times \SL{3}$ for the respective cases.
+However, it is straightforward to check that there are no singlets corresponding to a $(p-1)$-form potential in the adjoint of $\En{7}$ under these groups.
+This also stresses why the $S^3\times S^3$ case is special: the $\mbf{133}$ contains a 4 form of $\SL{8}$, which naturally contains the relevant singlets under $\SL{4}\times \SL{4}$.
+\EM{Needs some thinking -- EM}
+
 % \EM{Give embedding tensor components wrt the 3-d basis used for the moduli}\\
@@
 \end{equation}
-
-\CE{(Expression of $H$?)}
-
-The metric parametrising this moduli space is:
+We can also provide an expression for $H_3$ in the simplified case where $\Omega=\tilde\Omega=0$. It is convenient to first define some forms.
+\begin{equation}\label{eq:forms}
+	\begin{split}
+		Z(\theta,u,v,w)&=2+2e^{2\psi}(u^2\sin \theta^2+v^2\cos \theta^2+w^2)\\
+		\gamma&=4\sin\tilde\theta\cos\tilde \theta(\tilde{\zeta}_1^2-\tilde{\zeta}_2 ^2)\left(\zeta_2\cos \theta ^2\d \phi _1+\zeta _1\sin\theta ^2\d\phi _2\right)\\
+		\kappa_{ij}&=2\sin \theta \cos \theta Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_i)\zeta_j\d\phi_i\\
+		\omega_{ij} &=2\sin\tilde\theta \cos\tilde\theta Z(\theta,\zeta_1,\zeta_2,\tilde\zeta _i)\d \tilde \phi _i\wedge \left [(\zeta _1\tilde \zeta _j + \tilde \zeta _i \zeta _2)\cos \theta ^2 \d \phi_1+ (\zeta _1\tilde \zeta _i + \tilde \zeta _j \zeta _2)\sin \theta ^2 \d \phi_2\right]\\
+		\Theta&=(\zeta _1^2-\zeta_2 ^2)(\tilde{\zeta}_1 ^2-\tilde \zeta _2^2)\sin\tilde\theta \cos \tilde\theta \sin (2 \theta) ^2\d\tilde \theta\wedge\d \phi _1\wedge\d   \phi _2
+	\end{split}
+\end{equation}
+where we take $i,j\in\{1,2\}$ and they are not summed over. It is further useful to introduce (now sum over repeated $i,j$ as usual)
+\begin{equation}\label{eq:omegagamma}
+	\kappa = \epsilon^{ij}\kappa_{ij},\quad \omega=\epsilon^{ij}\omega _{ij}.
+\end{equation}
+In terms of the objects in \eqref{eq:forms} and \eqref{eq:omegagamma} we can write 
+\begin{equation}\label{eq:defH3}
+	\begin{split}
+		H_3=&\Delta^2\alpha^2\sin\theta \cos \theta Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_1) Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_2)\d \theta\wedge\d\phi_1\wedge\d\phi _2\\
+		&+\Delta^2\sin\tilde\theta \cos \tilde\theta Z(\theta,\zeta_1,\zeta_2,\tilde{\zeta}_1) Z( \theta,\zeta_1,\zeta_2,\tilde{\zeta}_2)\d \tilde\theta\wedge\d\tilde{\phi}_1\wedge\d\tilde{\phi} _2\\
+		&+e^{2\psi}\alpha\Delta^2\left(\omega\wedge\d \tilde\theta+\tilde\omega\wedge\d \theta\right)+e^{4\psi}\Delta^2\alpha ^2\left(\Theta +\frac 1{\alpha^2}\tilde \Theta \right)\\
+		&+\Delta^2e^{2\psi}\alpha\left(\d \theta\wedge \kappa +\frac 1{\alpha}\d \tilde \theta \wedge \tilde \kappa\right)\wedge\d\psi+e^{4\psi}\alpha\Delta^2\left(\d\tilde \theta \wedge \gamma +\frac 1{\alpha}\d \theta\wedge\tilde\gamma\right)\wedge\d\psi.
+	\end{split}
+\end{equation}
+Note that in equation \eqref{eq:defH3} all forms with a tilde correspond to the analogues of \eqref{eq:forms} and \eqref{eq:omegagamma} where every variable and form is ``conjugated" as $x\mapsto\tilde x$, $\tilde x\mapsto x$.
+For example
+\begin{equation}
+	\tilde\gamma=4\sin\theta\cos\theta(\zeta_1^2-\zeta_2 ^2)\left(\tilde{\zeta}_2\cos\tilde \theta ^2\d \tilde \phi _1+\tilde{\zeta} _1\sin\tilde\theta ^2\d\tilde\phi _2\right).
+\end{equation} 
+%\CE{(Expression of $H$?)}
+
+Finally, the metric parametrising this moduli space is:
 \begin{equation}
@@
 While the $S$-action of $\SL{2,\mathbb{Z}}$ left the Kaluza-Klein spectrum of 6-dimensional supergravity on AdS$_3 \times S^3$ \cite{Eloy:2021fhc} invariant, it is broken by the additional $S^1$ direction when uplifting to IIB supergravity.
-However, we argued that the $S$-action leave invariant the full AdS$_3 \times S^3 \times S^1$ solution of IIB string theory, once string winding modes around $S^1$ are included.
+However, we argued that the $S$-action leave invariant the full AdS$_3 \times S^3 \times S^3 \times S^1$ solution of IIB string theory, once string winding modes around $S^1$ are included.
 In this case, the complex structure deformations live in the fundamental domain of $\SL{2,\mathbb{Z}}$, rather than the whole $\mathbb{C}$-plane, as the 3-dimensional supergravity would suggest.
@@
 Since these deformations locally are diffeomorphisms, one may expect a simple sigma model description on the ${\cal N}=(4,2),\, (4,0),\, (2,2),\, (2,0)$ SUSY vacua and, potentially, even for the non-SUSY AdS$_3 \times S^3 \times S^3 \times S^1$ vacua obtained this way.
-Finally, the non-perturbative stability of the perturbative stability non-supersymmetric AdS$_3$ vacua we found deserves further study.
+Finally, the non-perturbative stability of the perturbatively stable non-supersymmetric AdS$_3$ vacua we found deserves further study.
 We leave these questions for future work.

### 2023-06-15 Draft_3dH3.tex
Renewed discussion of zeta family.

@@
 \end{equation}
+As previously, the deformation breaks the isometry group down to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries.
+Note that for
+\begin{equation}
+	\zeta_{1}=\pm\zeta_{2},\quad \ts{\zeta}_{1}=\mp\ts{\zeta}_{2}\,\quad\Omega=\ts{\Omega}=0,
+\end{equation}
+the solution~\eqref{eq:metriczeta} reproduces eq.~\eqref{eq:chipsi} for
+\begin{equation}
+	\chi_{1}=\pm\chi_{2}=\frac{\zeta_{1}}{1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2}},\quad \ts{\chi}_{1}=\mp\ts{\chi}_{2}=-\frac{\ts{\zeta}_{1}}{1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2}},\quad e^{2\psi}=\frac{1}{(1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2})^{2}},
+\end{equation}
+with ${\cal N}=(4,0)$ (or $(0,4)$) and symmetry enhancement to ${\rm SO}(4)\times{\rm U}(1)^{2}$. There seems to be no other points with (super)-symmetry enhancement in the scalar manifold.
 

### 2023-06-19 Draft_3dH3.tex
Changes by Emanuel.

@@
 \newcommand{\dg}{\vert g \vert}
+\newcommand{\CG}{\Com{G}{\EE}}
+\newcommand{\cJ}{{\cal J}}
+\newcommand{\RO}{\mathbb{R}^+_{\SL{3}_1}}
+\newcommand{\RT}{\mathbb{R}^+_{\SL{3}_2}}
 
@@
 \newcommand{\CE}[1]{\textcolor{darkorange}{#1}}
-\newcommand{\CG}{\Com{G}{\EE}}
-\newcommand{\cJ}{{\cal J}}
 
@@
 	\begin{flushright}
-		HU-EP-23/XX
+		HU-EP-23/18
 	\end{flushright}
@@
 \begin{itemize}
-	\item Think about title - mention new AdS$_3$ vacua? Lifting AdS$_3$ vacua?
+	\item Periodicity $4\pi$ or $2\pi$
+	\item Mention lack of higher-dimensional origin for Berg and Samtleben
 	\item Comment earlier on uplift of 6d gSUGRA
 	\item Add references to introduction
-	\item Complex geometry of moduli space?
-	\item Compare with classification known in literature, e.g. in IIA (and IIB -- Jerome's story)
+	%\item Complex geometry of moduli space?
+	%\item Compare with classification known in literature, e.g. in IIA (and IIB -- Jerome's story)
 	\item Email DW and MP to ask who we should cite for \eqref{eq:Twisting}
@@
 Not only does this mean that there are also heterotic versions of these vacua (preserving ${\cal N}=(4,0)$ supersymmetry), but also that they can be readily studied via the string worldsheet CFT \cite{Maldacena:2000hw,Eberhardt:2018ouy,Eberhardt:2019niq,Eberhardt:2019ywk}.
-Moreover, the string sigma model in these vacua is also integrable \cite{}.
+\EM{Cut?} Moreover, the string sigma model in these vacua is also integrable \cite{}.
 Finally, the AdS$_3$/CFT$_2$ correspondence has seen much progress recently, with many new holographic duals being established \cite{}.
@@
 \end{equation}
-This solution of the section condition defines the ``geometric'' $\SL{3}_1 \times \mathbb{R}^+_1 \subset \SL{4}_1$ and $\SL{3}_2 \times \mathbb{R}^+_2 \subset \SL{4}_2$ subgroups, that will play an important role when adding flux in section \ref{s:AddFluxS3S3S1}.
+This solution of the section condition defines the ``geometric'' $\SL{3}_1 \times \RO \subset \SL{4}_1$ and $\SL{3}_2 \times \RT \subset \SL{4}_2$ subgroups, that will play an important role when adding flux in section \ref{s:AddFluxS3S3S1}.
 
@@
 The 6-form doublet corresponds to the $\mathbf{\left(1,2\right)}_{6}$.
-To understand if one of the 6-forms in the doublet are singlets under $\SL{4}_1 \times \SL{4}_2 \subset \En{7}$, we must decompose $\En{7}$ with respect to the common subgroup of $\SL{4}_1 \times \SL{4}_2$ and $\SL{6} \times \SL{2}$, which is $\SL{3}_1 \times \SL{3}_2 \times \mathbb{R}^+_1 \times \mathbb{R}^+_2$, as defined by the embedding of the physical coordinates in \eqref{eq:PhysicalCoords}.
+To understand if one of the 6-forms in the doublet are singlets under $\SL{4}_1 \times \SL{4}_2 \subset \En{7}$, we must decompose $\En{7}$ with respect to the common subgroup of $\SL{4}_1 \times \SL{4}_2$ and $\SL{6} \times \SL{2}$, which is $\SL{3}_1 \times \SL{3}_2 \times \RO \times \RT$, as defined by the embedding of the physical coordinates in \eqref{eq:PhysicalCoords}.
 Important for us is the correct identification of the $\mathbb{R}^+$ charges in both decompositions.
@@
 		\En{7} &\rightarrow \SL{8} \rightarrow \SL{4} \times \SL{4} \times \mathbb{R}^+_{\SL{8}} \\
-		&\rightarrow \SL{3}_1 \times \SL{3}_2 \times \mathbb{R}^+_1 \times \mathbb{R}^+_2 \times \mathbb{R}^+_{\SL{8}} \,,
+		&\rightarrow \SL{3}_1 \times \SL{3}_2 \times \RO \times \RT \times \mathbb{R}^+_{\SL{8}} \,,
 	\end{split}
@@
 	\begin{split}
-		\mathbb{R}^+_{\SL{6}} &= - \frac12 \left( \mathbb{R}^+_{\SL{3}_1} + \mathbb{R}^+_{\SL{3}_2} \right) \,, \\
-		\mathbb{R}^+_{\SL{2}} &= \frac14 \left( \mathbb{R}^+_{\SL{3}_1} - \mathbb{R}^+_{\SL{3}_2} + \mathbb{R}^+_{\SL{8}} \right) \,, \\
-		\mathbb{R}^+_{\rm IIB} &= \frac12 \left( \mathbb{R}^+_{\SL{3}_1} - \mathbb{R}^+_{\SL{3}_2} - 3\, \mathbb{R}^+_{\SL{8}} \right) \,.
+		\mathbb{R}^+_{\SL{6}} &= - \frac12 \left( \RO + \RT \right) \,, \\
+		\mathbb{R}^+_{\SL{2}} &= \frac14 \left( \RO - \RT + \mathbb{R}^+_{\SL{8}} \right) \,, \\
+		\mathbb{R}^+_{\rm IIB} &= \frac12 \left( \RO - \RT - 3\, \mathbb{R}^+_{\SL{8}} \right) \,.
 	\end{split}
@@
 The branching of the adjoint \eqref{eq:AdjointSL6} under $\SL{6} \times \SL{2} \times \mathbb{R}^+_{\rm IIB}$ in \eqref{eq:SL6SL2} needs to now be compared with that via $\SL{4}_1 \times \SL{4}_2 \times \mathbb{R}^+_{\SL{8}}$, given by
-\begin{equation}
+\begin{equation} \label{eq:133DecompSL4SL4}
 	\begin{split}
@@
 
-\subsection{Adding fluxes to other dyonic truncations}
-One could also imagine applying the same procedure we described here to turn on fluxes in other maximally supersymmetric compactifications.
-Natural candidates are the $S^1$ reductions of the consistent truncations to dyonically gauged 4-dimensional maximal supergravities \cite{Guarino:2015jca,Inverso:2016eet}.
-The 4-dimensional truncations arise from compactifications of 10-dimensional supergravity on $S^6$, $S^5\times S^1$, $S^4\times S^2$, with the 10-d theory corresponding to (massive) IIA/IIB when the spheres have even/odd dimensions, respectively.
-The corresponding twist matrices for $S^6$, $S^5\times S^1$, $S^4\times S^2$ belong to $\SL{7}$, $\SL{6}\times \SL{2}$ and $\SL{5}\times \SL{3}$, as reviewed in \ref{s:SLn}.
-
-In order to use our procedure for turning on a flux we would have to find singlets in the $\mbf{133}$ of $\En{7}$ under $\SL{7}$, $\SL{6}\times \SL{2}$ and $\SL{5}\times \SL{3}$ for the respective cases.
-However, it is straightforward to check that there are no singlets corresponding to a $(p-1)$-form potential in the adjoint of $\En{7}$ under these groups.
-This also stresses why the $S^3\times S^3$ case is special: the $\mbf{133}$ contains a 4 form of $\SL{8}$, which naturally contains the relevant singlets under $\SL{4}\times \SL{4}$.
-\EM{Needs some thinking -- EM}
+\subsection{Adding fluxes to other consistent truncations}
+We can also try to apply the same procedure we described here to turn on fluxes in other consistent truncations.
+One set of natural candidates are the $S^1$ reductions of the consistent truncations to dyonically gauged 4-dimensional maximal supergravities \cite{Guarino:2015jca,Inverso:2016eet}.
+These 4-dimensional truncations arise from compactifications of 10-dimensional supergravity on $S^6$, $S^5\times S^1$, $S^4\times S^2$, with the 10-d theory corresponding to (massive) IIA/IIB when the spheres have even/odd dimensions, respectively.
+The corresponding twist matrices for $S^6$, $S^5\times S^1$, $S^4\times S^2$ belong to $\SL{8-p} \times \SL{p}$, with $p = 1,\, 2,\, 3$ for the respective cases, and are constructed as in section \ref{s:SLn}.
+
+Let us see whether we can turn on a similar flux as in the case of $S^3 \times S^3 \times S^1$ for these cases.
+Here we will consider the case of a flux which has one leg on $S^1$, so as to require the truncation to 3 dimensions.
+In this case, we can always choose a gauge where the potential is fully on $S^{7-p} \times S^{p-1}$ and depends on the $S^1$ coordinate.
+Turning on such a flux only leads to a consistent truncation if we can find singlets in the $\mbf{133}$ of $\En{7}$ under $\SL{8-p} \times \SL{p}$ for the respective cases of $S^{7-p} \times S^{p-1}$, $p = 1,\, 2,\, 3$, that correspond to $p$-form potential.
+And, indeed for all these cases, the $\mbf{133}$ only contains exactly one singlet, corresponding to the $\mathbb{R}^+$ generator that commutes with $\SL{8-p} \times \SL{p}$.
+
+However, this $\mathbb{R}^+$ generator cannot correspond to a form potential.
+If it did, there would also have be a corresponding compact generator in the same representation (with possibly different $\mathbb{R}^+$ chargse), just as in \eqref{eq:133DecompSL4SL4}, associated to the ``dual'' potential.
+Since we only have one $\SL{8-p} \times \SL{p}$ singlet, this cannot be a $p$-form potential and, therefore, turning on new fluxes with legs on $S^1$ will not lead to consistent truncation for $S^{7-p} \times S^{p-1} \times S^1$, $p = 1,\, 2,\, 3$.
+This analysis also reveals why the $S^3\times S^3 \times S^1$ case is special: the $\mbf{133}$ contains a 4 form of $\SL{8}$, i.e.
+the $\mathbf{70}$, which naturally contains the relevant singlets under $\SL{4}\times \SL{4}$.
+
+Our analysis does not rule out the possibility of adding fluxes whose only legs are on $S^{7-p} \times S^p$, with none on $S^1$.
+In this case, we could use the analysis above but look for singlets in the $\mathbf{56} \otimes \mathbf{133}$, corresponding to the fluxes on $S^{7-p} \times S^p$.
 
@@
 Again, the deformation generically breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries.
-The $\chi_i$, $\ts{\chi}_i$, $i = 1, 2$ deformations are analogous to the two-parameter ``flat deformations'' \cite{Guarino:2021hrc} of AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
+The $\chi_i$, $\ts{\chi}_i$, $i = 1, 2$ deformations are analogous to the two-parameter ``flat deformations'' \cite{Guarino:2021hrc} of AdS$_4 \times S^5 \times S^1$ \cite{Guarino:2020gfe,Giambrone:2021zvp,Giambrone:2021wsm}.
 From the 4-dimensional perspective obtained after reducing on $S^3 \times S^3$, these deformations correspond to turning on Wilson lines for the $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ gauge fields along $S^1$.
@@
 These $\chi_i$, $\ts{\chi}_i$, $\psi$ deformations are completely analogous to $\mathbb{C}$-structure deformations of $T^2$, with the $\chi_i$, $\ts{\chi}_i$ corresponding to the real part and the $\psi$ deformation to the imaginary part of the $\mathbb{C}$-structure deformation.
-Note that the $\psi$ deformation does not exist in the otherwise analogous AdS$_4 \times S^5 \times S^1$ vacua in \cite{Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}, due to the ``S-fold'' identification in that case.
+Note that the $\psi$ deformation does not exist in the otherwise analogous AdS$_4 \times S^5 \times S^1$ vacua in \cite{Guarino:2020gfe,Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}, due to the ``S-fold'' identification in that case.
 This leads to an important difference in the global structure of the moduli space that we will discuss in section \ref{s:Compact}.
@@
 While most of these moduli break all supersymmetries, we also identified submanifolds where ${\cal N}=(4,2),\, (4,0),\, (2,2),\, (2,0)$ is preserved, where the ${\cal N}=4$ cases always correspond to the ``large'' superconformal algebra.
-The corresponding moduli are analogous to the  ``flat deformations'' that arise in the AdS$_4 \times S^5 \times S^1$ vacuum \cite{Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}.
+The corresponding moduli are analogous to the  ``flat deformations'' that arise in the AdS$_4 \times S^5 \times S^1$ vacuum \cite{Guarino:2020gfe,Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}.
 I.e.
@@
 The compactification of the moduli can be understood geometrically as the $T$-action of $\SL{2,\mathbb{Z}}$ on $T^2$-fibration.
-Differently from the AdS$_4 \times S^5 \times S^1$ case \cite{Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}, in the AdS$_3 \times S^3 \times S^3 \times S^1$ case we also have a $S^1$ rescaling modulus, so that we naturally have the full complex structure moduli related to the $T^2$-fibrations and which carry a natural action of the full $\SL{2,\mathbb{Z}}$.
+Differently from the AdS$_4 \times S^5 \times S^1$ case \cite{Guarino:2020gfe,Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}, in the AdS$_3 \times S^3 \times S^3 \times S^1$ case we also have a $S^1$ rescaling modulus, so that we naturally have the full complex structure moduli related to the $T^2$-fibrations and which carry a natural action of the full $\SL{2,\mathbb{Z}}$.
 While the $S$-action of $\SL{2,\mathbb{Z}}$ left the Kaluza-Klein spectrum of 6-dimensional supergravity on AdS$_3 \times S^3$ \cite{Eloy:2021fhc} invariant, it is broken by the additional $S^1$ direction when uplifting to IIB supergravity.
@@
 Our consistent truncation Ansatz could then be used to uplift the moduli space to IIB supergravity, and to use Kaluza-Klein spectrometry \cite{Malek:2019eaz,Malek:2020yue,Eloy:2020uix} to obtain the conformal dimensions of all single-trace operators and determine the perturbative stability of the non-SUSY vacua.
-Secondly, it would be interesting to study the string sigma model \cite{Eberhardt:2019niq} on the ``flat deformations'' of AdS$_3 \times S^3 \times S^3 \times S^1$, or the analogous deformations of AdS$_3 \times S^3 \times T^4$.
-Since these deformations locally are diffeomorphisms, one may expect a simple sigma model description on the ${\cal N}=(4,2),\, (4,0),\, (2,2),\, (2,0)$ SUSY vacua and, potentially, even for the non-SUSY AdS$_3 \times S^3 \times S^3 \times S^1$ vacua obtained this way.
-Finally, the non-perturbative stability of the perturbatively stable non-supersymmetric AdS$_3$ vacua we found deserves further study.
+This would shed light on the dual conformal manifold.
+Secondly, it would be interesting to study the string sigma-model \cite{Eberhardt:2019niq} on the ``flat deformations'' of AdS$_3 \times S^3 \times S^3 \times S^1$, or the analogous deformations of AdS$_3 \times S^3 \times T^4$.
+Since these deformations locally are diffeomorphisms, one may expect a simple worldsheet description on the ${\cal N}=(4,2),\, (4,0),\, (2,2),\, (2,0)$ SUSY vacua and, potentially, even for the non-SUSY AdS$_3 \times S^3 \times S^3 \times S^1$ vacua obtained this way.
+The non-perturbative stability of the perturbatively stable non-supersymmetric AdS$_3$ vacua we found also deserves further study.
+Finally, similar ``flat deformations'' arise in any string compactification involving an $S^1$, in particular AdS$_3 \times S^3 \times T^4$.
+It would be interesting to understand universal features of these deformations and their CFT duals.
 We leave these questions for future work.
@@
 \section*{Acknowledgements}
-We are grateful to \EM{add others} Nikolay Bobev, Yolanda Lozano, Niall Macpherson for useful discussions and correspondence.
+We are grateful to \EM{add others} Nikolay Bobev, Adolfo Guarino, Yolanda Lozano, Niall Macpherson and Colin Sterckx for useful discussions and correspondence.
 CE is supported by the FWO-Vlaanderen through the project G006119N and by the Vrije Universiteit Brussel through the Strategic Research Program ``High-Energy Physics''.

### 2023-06-19 Draft_3dH3.tex
Update of sec. 4 with ruling out gaugings.

@@
 \newcommand{\cJ}{{\cal J}}
-\newcommand{\RO}{\mathbb{R}^+_{\SL{3}_1}}
-\newcommand{\RT}{\mathbb{R}^+_{\SL{3}_2}}
+\newcommand{\RO}{\mathbb{R}^+_{\SL{4}_1}}
+\newcommand{\RT}{\mathbb{R}^+_{\SL{4}_2}}
 
@@
 	%\item Complex geometry of moduli space?
-	%\item Compare with classification known in literature, e.g. in IIA (and IIB -- Jerome's story)
+	%\item Compare with classification known in literature, \textit{e.g.} in IIA (and IIB -- Jerome's story)
 	\item Email DW and MP to ask who we should cite for \eqref{eq:Twisting}
@@
 However, consistent truncations to three dimensions have, until recently \cite{Galli:2022idq}, remained largely unexplored.
-One reason is that the $\EE$ ExFT requires modifications for its local symmetry structure, i.e.
-the generalised Lie derivative, to close into an algebra \cite{Hohm:2014fxa,Cederwall:2015ica}.
-Another is that there are no maximally supersymmetric AdS$_3$ vacua, i.e.
-preserving 32 supercharges, of string theory, leaving no natural candidate for constructing a consistent truncation with vacua.
+One reason is that the $\EE$ ExFT requires modifications for its local symmetry structure, \textit{i.e.} the generalised Lie derivative, to close into an algebra \cite{Hohm:2014fxa,Cederwall:2015ica}.
+Another is that there are no maximally supersymmetric AdS$_3$ vacua, \textit{i.e.} preserving 32 supercharges, of string theory, leaving no natural candidate for constructing a consistent truncation with vacua.
 Indeed, while the consistent truncations of 11-dimensional supergravity on $S^7$ and $S^4$ and of 10-dimensional supergravity on $S^5$ contain maximally supersymmetric AdS vacua and are captured by a universal Ansatz in ExFT \cite{Hohm:2014qga,Lee:2014mla}, the analogous $S^8$ truncation of 11-dimensional supergravity does not exist, while there are two $S^7$ truncations of 10-dimensional supergravity but neither contains a maximally symmetric vacuum\cite{Fischbacher:2003yw,Galli:2022idq}.
 
-Nonetheless, there are half-maximal, i.e.
-${\cal N}=(4,4)$, supersymmetric AdS$_3$ vacua of string theory that are extremely intriguing.
+Nonetheless, there are half-maximal, \textit{i.e.} ${\cal N}=(4,4)$, supersymmetric AdS$_3$ vacua of string theory that are extremely intriguing.
 These are the AdS$_3 \times S^3 \times S^3 \times S^1$ and AdS$_3 \times S^3 \times T^4$ of IIB string theory (realising the ``large'' and ``small'' ${\cal N}=(4,4)$ superconformal symmetries), and, unlike in higher dimensions, can be supported by pure NS-NS flux.
@@
 Yet, surprisingly, at least a subset of vacua continue to be perturbatively stable within IIB supergravity, similar to \cite{Giambrone:2021wsm}.
-Our work also provides an uplift of 6-dimensional supergravity on $S^3$ studied in \cite{Eloy:2021fhc} to IIB string theory.
+Our work also provides an uplift of the supersymmetric deformation of 6-dimensional supergravity on $S^3$ studied in \cite{Eloy:2021fhc} to IIB string theory.
 As we will show, some supersymmetric deformations that appear non-compact in 6-dimensional supergravity \cite{Eloy:2021fhc} are compactified within the full 10-dimensional supergravity theory.
@@
 As a by-product, we find a constraint that must be obeyed by the embedding tensor of any 3-dimensional gauged supergravity that can be uplifted to 10-/11-dimensional supergravity.
-As we show, this allows us to prove the lack of a higher-dimensional origin of some 3-dimensional gaugings.
+As we show, this allows to prove the lack of a higher-dimensional origin of some 3-dimensional gaugings, as we illustrate on an example.
 \EM{update}
@@
 The \EE exceptional field theory, first constructed in ref.~\cite{Hohm:2014fxa}, is an \EE duality-covariant formulation of type II and 11d supergravities.
-It is defined on a set of $3+248$ coordinates made of three-dimensonal external coordinates $\{x^{\mu}\}$ and internal coordinates $\{Y^{M}\}$ in the 248-dimensional adjoint representation of \EE.
-The dependance of the fields on these coordinates is constrained by the ``section constraints''\footnote{We use the notation $\otimes$ to indicate that both derivatives may act on different functions.}
+It is defined on a set of $3+248$ coordinates made of three-dimensional external coordinates $\{x^{\mu}\}$ and internal coordinates $\{Y^{M}\}$ in the 248-dimensional adjoint representation of \EE.
+The dependence of the fields on these coordinates is constrained by the ``section constraints''\footnote{We use the notation $\otimes$ to indicate that both derivatives may act on different functions.}
 \begin{equation} \label{eq:sectionconstraints}
@@
 \end{equation}
-The fields with flat indices $\fl{M}$ (in the $\mathbf{248}$ representation of \EE) belong to the three-dimensional theory; all the dependence on the internal manifold is factored out in $U_{\fl{M}}{}^{M}$ and $\rho$.
+The fields with flat indices $\fl{M}$ (in the $\mathbf{248}$ representation of \EE) belong to the three-dimensional theory; all the dependence on the internal manifold is factored out in $U_{M}{}^{\fl{M}}$ and $\rho$.
 Note that with the definition of $\Sigma_{\fl{M}\,M}$ the condition~\eqref{eq:sectionconstraint2} is automatically satisfied.
@@
 From eq.
-\eqref{eq:GenLeibniz}, it has the following expression in terms of the twist matrix and $\rho$
+\eqref{eq:GenLeibniz}, it has the following expression in terms of the twist matrix and $\rho$:
 \begin{equation}
@@
 \end{equation}
-Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=\UI_{\fl{M}}{}^{K}\UI_{\fl{N}}{}^{L}\partial_{K}U_{L}{}^{\fl{P}}$ and the trombone gauging
+Here, we defined the $\EE$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=\UI_{\fl{M}}{}^{K}\UI_{\fl{N}}{}^{L}\partial_{K}U_{L}{}^{\fl{P}}$ and the trombone gauging
 \begin{equation} \label{eq:Trombone}
@@
 The three-dimensional action follows from inserting the Ansätze~\eqref{eq:GSSansatz} in the ExFT action~\eqref{eq:ExFTaction}.
-The expressions of the kinetic and Chern-Simons terms result immediately from eq.~\eqref{eq:GSSexample}
+The expressions of the kinetic and Chern-Simons terms result immediately from eq.~\eqref{eq:GSSexample}:
 \begin{equation}
@@
 As a result, in that case, the bosonic $\En{9}$ ExFT \cite{Bossard:2018utw,Bossard:2021jix} provides the only currently accessible route for computing the gauged supergravity potential.}, but the potential is crucial for finding vacua of the three-dimensional theory and uplifting these in the later parts of this paper.
-
+In addition, we derive a necessary condition for the embedding tensor to arise from a compactification of higher-dimensional supergravity and illustrate it on an example.
+
+\subsection{Expression of the potential in terms of the embedding tensor}
 In order to derive the potential, we adopt the following strategy.
 We want $\mathscr{L}_{\rm int}$ \eqref{eq:ExFTLint} to reduce to the embedding tensor squared upon inserting the generalised Scherk-Schwarz Ans\"{a}tze \eqref{eq:GSSansatz}.
-However, as in higher dimensions, e.g.
-\cite{Berman:2012uy,Musaev:2013rq,Blair:2014zba}, this does not have to match identically, but only up to total derivative terms and terms which violate the section condition.
+However, as in higher dimensions, \textit{e.g.} \cite{Berman:2012uy,Musaev:2013rq,Blair:2014zba}, this does not have to match identically, but only up to total derivative terms and terms which violate the section condition.
 The possible boundary terms are
@@
 
-Now, we first insert the generalized Sherk-Schwarz Ansätze \eqref{eq:GSSansatz} into the expression of $\mathscr{L}_{\rm int}$ \eqref{eq:ExFTLint} with the additional total derivative \eqref{eq:BoundaryTermCombination}
+Now, we first insert the generalized Sherk-Schwarz Ansätze \eqref{eq:GSSansatz} into the expression of $\mathscr{L}_{\rm int}$~\eqref{eq:ExFTLint} with the additional total derivative \eqref{eq:BoundaryTermCombination}
 \begin{equation} \label{eq:Lintexpansion}
@@
 Secondly, knowing that the ${\cal N}=16$ potential must be quadratic in $X_{\fl{MN}}$, we consider the most general quadratic function in $X_{\fl{MN}}$ and develop it in \EE currents using eq.~\eqref{eq:symembeddingtensor}.
-Note that in higher dimensions, there exist only two quadratic combinations of the embedding tensor
-\begin{equation}
-	X_{\fl{M}\fl{N}}{}^{\fl{P}} X_{\fl{Q}\fl{P}}{}^{\fl{N}} \gM^{\fl{MQ}} \qquad \text{and} \qquad X_{\fl{M}\fl{N}}{}^{\fl{P}} X_{\fl{Q}\fl{R}}{}^{\fl{S}} \gM^{\fl{MQ}} \gM^{\fl{N}\fl{R}} \gM_{\fl{P}\fl{S}} \,.
+Note that in higher dimensions, there exist only two quadratic combinations of the embedding tensor:
+\begin{equation}
+	X_{\fl{M}\fl{N}}{}^{\fl{P}} X_{\fl{Q}\fl{P}}{}^{\fl{N}} \gM^{\fl{MQ}} \qquad \text{and} \qquad X_{\fl{M}\fl{N}}{}^{\fl{P}} X_{\fl{Q}\fl{R}}{}^{\fl{S}} \gM^{\fl{MQ}} \gM^{\fl{N}\fl{R}} \gM_{\fl{P}\fl{S}} \,,
+\end{equation}
+or equivalently
+\begin{equation}
+	X_{\fl{MN}}X_{\fl{PQ}}\,\M^{\fl{MP}}\eta^{\fl{NQ}} \qquad {\rm and} \qquad X_{\fl{MN}}X_{\fl{PQ}}\,\M^{\fl{MP}}\M^{\fl{NQ}}.
 \end{equation}
@@
 \end{equation}
-which can be expressed entirely in terms of $X_{\fl{M}\fl{N}}$ after tracing eq.~\eqref{eq:symembeddingtensor}
+which can be expressed entirely in terms of $X_{\fl{M}\fl{N}}$ after tracing eq.~\eqref{eq:symembeddingtensor}:
 \begin{equation}\label{eq:reltrX}
@@
 
+As mentioned above, eq.~\eqref{eq:reltrX} can be used to assess whether a given three-dimensional theory of embedding tensor $X_{\fl{MN}}$ has a higher-dimensional origin.
+Let us illustrate that on the ${\cal N}=(8,0)$ ${\rm AdS}_{3}$ vacuum with $\GL{6} \times \SO{2,2}$ gauging constructed in ref.~\cite{Deger:2019tem}.
+This solution has a compact gauging smaller than $\SO{9}$, thus escaping the no-go result of ref.~\cite{Galli:2022idq}.
+The embedding tensor of the solution is expressed by breaking $\EE$ as
+\begin{equation}
+	\begin{aligned}
+		\EE &\longrightarrow \SO{8,8}\\
+		\mathbf{248} &\longrightarrow \mathbf{120} \oplus \mathbf{128}\\
+		X^{\fl{M}} &\longrightarrow \left\{X^{[\fl{\sf IJ}]},X^{\fl{\sf A}}\right\},
+	\end{aligned}
+\end{equation}
+with $\fl{\sf I}$ and $\fl{\sf A}$ labels of the fundamental and spinorial representations of $\SO{8,8}$, respectively. Explicitly,
+\begin{equation}
+	\begin{aligned}
+		X_{\fl{\sf IJ},\fl{\sf KL}} &= \Theta_{\fl{\sf IJ},\fl{\sf KL}},\\
+		X_{\fl{\sf AB}} &= -2\,\theta\,\eta_{\fl{\sf AB}}+\frac{1}{24}\,\Gamma^{\fl{\sf IJ},\fl{\sf KL}}_{\fl{\sf AB}}\,\Theta_{\fl{\sf IJKL}},\\
+		X_{\fl{\sf IJ},\fl{\sf A}} &=0,
+	\end{aligned}
+\end{equation}
+where $\Gamma^{\fl{\sf IJKL}}_{\fl{\sf AB}}$ is the four-fold product of $\SO{8,8}$ $\Gamma$ matrices and $\eta_{\fl{\sf AB}}$ the $\mathbf{128}\otimes\mathbf{128}$ component of the Cartan-Killing metric.
+The tensor $\Theta_{\fl{\sf IJ},\fl{\sf KL}}$ is given by
+\begin{equation}
+	\Theta_{\fl{\sf IJ},\fl{\sf KL}}=\theta_{\fl{\sf IJKL}}+\frac12\big(\eta_{\fl{\sf K}[\fl{\sf I}}\theta_{\fl{\sf J}]\fl{\sf L}}-\eta_{\fl{\sf L}[\fl{\sf I}}\theta_{\fl{\sf J}]\fl{\sf K}}\big)+\theta\,\eta_{\fl{\sf K}[\fl{\sf I}}\eta_{\fl{\sf J}]\fl{\sf L}}\,,
+\end{equation}
+with $\theta_{\fl{\sf IJKL}}$ totally antisymmetric and $\theta_{\fl{\sf IJ}}$ symmetric, with non vanishing components
+\begin{align}
+  & \theta_{ij}=4\,\delta_{ij}\;,\quad \theta_{\alpha\beta}=-12\,\delta_{\alpha\beta}\;,\quad \theta_{r_{+}s_{+}}=-4\,\delta_{r_{+}s_{+}}\;,\quad \theta_{r_{-}s_{-}}=12\,\delta_{r_{-}s_{-}}\;,\nonumber\\
+  & \theta=-8\;,\quad \theta_{\alpha\beta r_{-}s_{-}} = -48\,\sigma_{\alpha\beta}\,\sigma_{r_{-}s_{-}}\;,\quad \theta_{ij r_{+}s_{+}} = 32\,\delta_{i[r_{+}}\,\delta_{s_{+}]j}\;,
+\end{align}
+where... \CE{(explain all notations...)} With this embedding, we get
+\begin{equation}
+	X_{\ov{MN}}\,X^{\ov{MN}} = \frac{55}{1922}\left(X_{\ov M}{}^{\ov M}\right)^2,
+\end{equation}
+thus violating the condition~\eqref{eq:reltrX} (the trombone gauging vanishes for the solution).
+Then, we deduce that the ${\cal N}=(8,0)$ solution of ref.~\cite{Deger:2019tem} with gauging $\GL{6} \times \SO{2,2}$ does not admit a higher-dimensional origin.
+This illustrate how the constraint~\eqref{eq:reltrX} can be used to determine if a given three-dimensional vacuum can be uplifted.
+
 \section{Adding fluxes to consistent truncations} \label{s:AddFlux}
@@
 
-This motivates the following question: Given a consistent truncation, i.e.
-$\cU_{\fl{M}}{}^M$, satisfying \eqref{eq:GenLeibniz}, when can we add a new flux component of string theory to the compactification to obtain a new consistent truncation?
+This motivates the following question: Given a consistent truncation, \textit{i.e.} $\cU_{\fl{M}}{}^M$, satisfying \eqref{eq:GenLeibniz}, when can we add a new flux component of string theory to the compactification to obtain a new consistent truncation?
 Adding a new flux component to the truncation is equivalent to twisting the generalised frame as follows \EM{Email DW and MP to ask who we should cite for this?}
@@
 \end{equation}
-where $F_{MN}{}^P$ is a tensor in the $\mathbf{1} \oplus \mathbf{248} \oplus \mathbf{3875}$ of $\EE$, i.e.
-the same representation as the embedding tensor, corresponding to the field strength of the potential $C$ in \eqref{eq:Twisting}.
+where $F_{MN}{}^P$ is a tensor in the $\mathbf{1} \oplus \mathbf{248} \oplus \mathbf{3875}$ of $\EE$, \textit{i.e.} the same representation as the embedding tensor, corresponding to the field strength of the potential $C$ in \eqref{eq:Twisting}.
 Using \eqref{eq:GenLeibniz}, we now have
@@
 \subsubsection{The $S^n$ twist matrix} \label{s:SLn}
-\EM{Move to appendix?!?!} \CE{(I think I would say yes)}\\
+\EM{Move to appendix?!?!} \CE{(I think I would say yes. Work here.)}\\
 Since we will use it throughout this paper, let us construct the $\SL{4} \simeq \SO{3,3}$ twist matrix that describes the consistent truncation on $S^3$.
@@
 
-We use an $\SL{n+1}$ ExFT, like in \cite{Lee:2014mla}, which encodes an $n$-dimensional metric and volume-form flux, i.e.
-Freund-Rubin compactifications, and thus gives a natural description of $S^n$ compactifications.
+We use an $\SL{n+1}$ ExFT, like in \cite{Lee:2014mla}, which encodes an $n$-dimensional metric and volume-form flux, \textit{i.e.} Freund-Rubin compactifications, and thus gives a natural description of $S^n$ compactifications.
 The $\SL{n+1}$ ExFT formally has coordinates in the antisymmetric representation of $\SL{n+1}$, $y^{IJ} = - y^{JI}$, with $I = 1, \ldots, n+1$, and similarly, generalised vector fields transform in the antisymmetric representation of $\SL{n+1}$.
@@
 We are interested in the maximal solutions of the section condition \eqref{eq:SLnSC} which preserve a $\SL{n} \subset \SL{n+1}$ subgroup.
-Under this decomposition $\SL{n+1} \rightarrow \SL{n}$ with $V^I = \left( V^i,\, V^0 \right)$, where $i = 1, \ldots, n$, we solve the section condition by having physical coordinates $y^{0i}$ on the $n$-dimensional manifold $M$, i.e.
-$\partial_{ij} = 0$ for all fields with only $\partial_{0i} = \partial_i \neq 0$.
+Under this decomposition $\SL{n+1} \rightarrow \SL{n}$ with $V^I = \left( V^i,\, V^0 \right)$, where $i = 1, \ldots, n$, we solve the section condition by having physical coordinates $y^{0i}$ on the $n$-dimensional manifold $M$, \textit{i.e.} $\partial_{ij} = 0$ for all fields with only $\partial_{0i} = \partial_i \neq 0$.
 Correspondingly, the generalised tangent bundle, whose sections are in the antisymmetric representation of $\SL{n+1}$ and carry weight $\frac{n-3}{n+1}$, decomposes as
@@
 Finally, we can also connect the above with the $\SL{n+1}$ Ansatz construction of \cite{Hohm:2014qga}.
-We do this by evaluating \eqref{eq:SLnFrame} and \eqref{eq:rho} on the northern hemisphere $Y^I = \left( y^i,\, \sqrt{1-y^i y_i}\right)$, $i = 1, \ldots, n$ and using the gauge choice for the potential $A$
+We do this by evaluating \eqref{eq:rho} and \eqref{eq:SLnFrame} on the northern hemisphere $Y^I = \left( y^i,\, \sqrt{1-y^i y_i}\right)$, $i = 1, \ldots, n$ and using the gauge choice for the potential $A$
 \begin{equation}
@@
 \end{equation}
-with $v = y^i\, y^i$ and $\epsilon_{i_1 \ldots i_{n-1}j}$ the volume form on $S^n$. With the above choices, we precisely recover the $\SL{n+1}$ twist matrix of \cite{Hohm:2014qga}, i.e.
+with $v = y^i\, y^i$ and $\epsilon_{i_1 \ldots i_{n-1}j}$ the volume form on $S^n$. With the above choices, we precisely recover the $\SL{n+1}$ twist matrix of \cite{Hohm:2014qga}, \textit{i.e.}
 \begin{equation} \label{eq:SLnTwist}
@@
 We denote by $U_A{}^{\ov{A}}$ the $\SO{3,3}$ twist matrix corresponding to the $S^3$ truncation constructed in \cite{Lee:2014mla,Baguet:2015iou} and obtained from \eqref{eq:SLnFrame}, \eqref{eq:rho}, \eqref{eq:SLnTwist}.
-Then, we can add a 3-form potential by twisting with the $\SO{4,4}$ generator
+Then, we can add a 3-form potential by twisting with the $\SO{4,4}$ generator \CE{(Sure here?
+Check notes.)}
 \begin{equation} \label{eq:C2S3example}
@@
 \end{equation}
-With this embedding tensor, the potential~\eqref{eq:3dpotential} has a vacuum at the scalar origin when $\lambda=\pm 4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$.
+With this embedding tensor, the potential~\eqref{eq:3dpotential} has a vacuum at the scalar origin when $\lambda=\pm4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$.
 The sign changes the chirality of the Killing spinors and, therefore, without loss of generality, we will choose $\lambda = 4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$ from here onwards.
@@
 Since we only have one $\SL{8-p} \times \SL{p}$ singlet, this cannot be a $p$-form potential and, therefore, turning on new fluxes with legs on $S^1$ will not lead to consistent truncation for $S^{7-p} \times S^{p-1} \times S^1$, $p = 1,\, 2,\, 3$.
-This analysis also reveals why the $S^3\times S^3 \times S^1$ case is special: the $\mbf{133}$ contains a 4 form of $\SL{8}$, i.e.
-the $\mathbf{70}$, which naturally contains the relevant singlets under $\SL{4}\times \SL{4}$.
+This analysis also reveals why the $S^3\times S^3 \times S^1$ case is special: the $\mbf{133}$ contains a 4 form of $\SL{8}$, \textit{i.e.} the $\mathbf{70}$, which naturally contains the relevant singlets under $\SL{4}\times \SL{4}$.
 
@@
 Additionally, there is a $\U{1}_F$ symmetry due to the $S^1$ factor in \eqref{eq:AdS3}.
-The spectrum organizes into multiplets of ${\cal G}$, made out of products of long representations $[\ell,\ts{\ell}]$ of $D^{1}(2,1;\alpha)$ (see app.~\ref{app:d21a} for a review of the representations of $D^{1}(2,1;\alpha)$), and carrying a charge under the $\U{1}_F$.
+The spectrum organizes into multiplets of ${\cal G}$, made out of products of long representations $[\ell,\ts{\ell}]$ of $D^{1}(2,1;\alpha)$ (see app.~\ref{app:d21a} for a review of the representations of $D^{1}(2,1;\alpha)$), and carrying a charge $n$ under the $\U{1}_F$.
 Explicitly, the spectrum is~\cite{Eberhardt:2017fsi}
@@
 where we denoted the generators according to the decomposition~\eqref{eq:248decompoinSL8}.
-The $(\chi_{i},\ts{\chi}_{i},\zeta_{i},\ts{\zeta}_{i})$ deformations excite the $(\mathbf{6},\mathbf{1})_{2}$ and $(\mathbf{1},\mathbf{6})_{2}$ generators in the branching~\eqref{eq:56inSL4SL4}.
-Note that changing the sign in some terms in \eqref{eq:FullDeformation}, e.g.
-changing the factor with $\Omega$ to
+The $(\chi_{i},\ts{\chi}_{i},\zeta_{i},\ts{\zeta}_{i})$ deformations excite the $(\mathbf{6},\mathbf{1})_{\mathbf{2}}$ and $(\mathbf{1},\mathbf{6})_{\mathbf{2}}$ generators in the branching~\eqref{eq:56inSL4SL4}.
+Note that changing the sign in some terms in \eqref{eq:FullDeformation}, \textit{e.g.} changing the factor with $\Omega$ to
 \begin{equation}
@@
 SUSY enhancement points are then given by combinations of the parameters that yield $\Delta = \nicefrac32$.
-This can either happen by leaving some modes with $\Delta=\nicefrac{3}{2}$ invariant, or where some other, originally massive gravitini outside the consistent truncation, i.e.
-with conformal dimension given by \eqref{eq:confdims3s3s1} with $n \neq 0$, obtain $\Delta = \nicefrac32$.
+This can either happen by leaving some modes with $\Delta=\nicefrac{3}{2}$ invariant, or where some other, originally massive gravitini outside the consistent truncation, \textit{i.e.} with conformal dimension given by \eqref{eq:confdims3s3s1} with $n \neq 0$, obtain $\Delta = \nicefrac32$.
 Here we will focus on the supersymmetry enhancement within the 3-dimensional truncation and will discuss the higher KK modes in section \ref{s:Compact}.
@@
 			\chi_{1}=\chi_{2}= 0,\\
-			\ts{\chi}_{1}=-\,\ts{\chi}_{2}=\sqrt{1-e^{2\omega}},\\
+			\ts{\chi}_{1}=-\,\ts{\chi}_{2}=\ts{\chi}=\sqrt{1-e^{2\omega}},\\
 			\psi = -\,\omega,
@@
 For generic values of $\chi_i$, $\ts{\chi}_i$, the AdS$_3$ vacuum will be completely non-supersymmetric.
-However, it is easy to see from inspection of the spectrum \eqref{eq:confdims3s3s1} and \eqref{eq:confdimshiftchi} that the spectrum is bounded from below by the masses of the 3-dimensional gauged supergravity modes at the ${\cal N}=(4,4)$ supersymmetric origin, i.e.
-where $\chi_i = \ts{\chi}_i = n = \ell = \ts{\ell} = 0$.
+However, it is easy to see from inspection of the spectrum \eqref{eq:confdims3s3s1} and \eqref{eq:confdimshiftchi} that the spectrum is bounded from below by the masses of the 3-dimensional gauged supergravity modes at the ${\cal N}=(4,4)$ supersymmetric origin, \textit{i.e.} where $\chi_i = \ts{\chi}_i = n = \ell = \ts{\ell} = 0$.
 Therefore, these non-supersymmetric AdS$_3$ vacua are perturbatively stable within IIB supergravity and, similarly to \cite{Giambrone:2021wsm} suggest that there may be a dual non-supersymmetric conformal manifold if there are no instabilities beyond supergravity.
@@
 This does not rule out all potential sources of instabilities.
-For example, the non-SUSY vacua may suffer from non-perturbative instabilities triggered by brane nucleation \cite{Ooguri:2016pdq,Bomans:2021ara} or non-vanishing $\beta$-functions of marginal multi-trace operators \cite{Witten:2001ua}.
+For example, the non-SUSY vacua may suffer from non-perturbative instabilities triggered by brane nucleation \cite{Ooguri:2016pdq,Bomans:2021ara} or non-vanishing $\beta$-functions of marginal multi-trace operators~\cite{Witten:2001ua}.
 However, our non-SUSY vacua here may have further protection against such instabilities due to their continuous limits to the SUSY vacua, just as they have against perturbative higher-derivative corrections.
@@
 \end{equation}
-We can also provide an expression for $H_3$ in the simplified case where $\Omega=\tilde\Omega=0$. It is convenient to first define some forms.
+We can also provide an expression for $H_3$ in the simplified case where $\Omega=\tilde\Omega=0$. It is convenient to first define some forms. \CE{(Work on this.)}
 \begin{equation}\label{eq:forms}
 	\begin{split}
-		Z(\theta,u,v,w)&=2+2e^{2\psi}(u^2\sin \theta^2+v^2\cos \theta^2+w^2)\\
-		\gamma&=4\sin\tilde\theta\cos\tilde \theta(\tilde{\zeta}_1^2-\tilde{\zeta}_2 ^2)\left(\zeta_2\cos \theta ^2\d \phi _1+\zeta _1\sin\theta ^2\d\phi _2\right)\\
-		\kappa_{ij}&=2\sin \theta \cos \theta Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_i)\zeta_j\d\phi_i\\
-		\omega_{ij} &=2\sin\tilde\theta \cos\tilde\theta Z(\theta,\zeta_1,\zeta_2,\tilde\zeta _i)\d \tilde \phi _i\wedge \left [(\zeta _1\tilde \zeta _j + \tilde \zeta _i \zeta _2)\cos \theta ^2 \d \phi_1+ (\zeta _1\tilde \zeta _i + \tilde \zeta _j \zeta _2)\sin \theta ^2 \d \phi_2\right]\\
-		\Theta&=(\zeta _1^2-\zeta_2 ^2)(\tilde{\zeta}_1 ^2-\tilde \zeta _2^2)\sin\tilde\theta \cos \tilde\theta \sin (2 \theta) ^2\d\tilde \theta\wedge\d \phi _1\wedge\d   \phi _2
+		Z(\theta,u,v,w)&=2+2e^{2\psi}(u^2\sin^2(\theta)+v^2\cos^2(\theta)+w^2)\\
+		\gamma&=4\sin(\tilde\theta)\cos(\tilde \theta)(\tilde{\zeta}_1^2-\tilde{\zeta}_2 ^2)\left(\zeta_2\cos^2(\theta)\d \phi _1+\zeta _1\sin^2(\theta)\d\phi _2\right)\\
+		\kappa_{ij}&=2\sin (\theta) \cos (\theta) Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_i)\zeta_j\d\phi_i\\
+		\omega_{ij} &=2\sin(\tilde\theta) \cos(\tilde\theta) Z(\theta,\zeta_1,\zeta_2,\tilde\zeta _i)\d \tilde \phi _i\wedge \left [(\zeta _1\tilde \zeta _j + \tilde \zeta _i \zeta _2)\cos^2 (\theta) \d \phi_1+ (\zeta _1\tilde \zeta _i + \tilde \zeta _j \zeta _2)\sin^2(\theta)  \d \phi_2\right]\\
+		\Theta&=(\zeta _1^2-\zeta_2 ^2)(\tilde{\zeta}_1 ^2-\tilde \zeta _2^2)\sin(\tilde\theta) \cos (\tilde\theta) \sin (2 \theta) ^2\d\tilde \theta\wedge\d \phi _1\wedge\d   \phi _2
 	\end{split}
@@
 \end{equation}
-In terms of the objects in \eqref{eq:forms} and \eqref{eq:omegagamma} we can write 
+In terms of the objects in \eqref{eq:forms} and \eqref{eq:omegagamma} we can write \CE{(Add AdS legs?)}
 \begin{equation}\label{eq:defH3}
 	\begin{split}
-		H_3=&\Delta^2\alpha^2\sin\theta \cos \theta Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_1) Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_2)\d \theta\wedge\d\phi_1\wedge\d\phi _2\\
-		&+\Delta^2\sin\tilde\theta \cos \tilde\theta Z(\theta,\zeta_1,\zeta_2,\tilde{\zeta}_1) Z( \theta,\zeta_1,\zeta_2,\tilde{\zeta}_2)\d \tilde\theta\wedge\d\tilde{\phi}_1\wedge\d\tilde{\phi} _2\\
+		H_(3)=&\Delta^2\alpha^2\sin(\theta) \cos (\theta) Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_1) Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_2)\d \theta\wedge\d\phi_1\wedge\d\phi _2\\
+		&+\Delta^2\sin(\tilde\theta) \cos (\tilde\theta) Z(\theta,\zeta_1,\zeta_2,\tilde{\zeta}_1) Z( \theta,\zeta_1,\zeta_2,\tilde{\zeta}_2)\d \tilde\theta\wedge\d\tilde{\phi}_1\wedge\d\tilde{\phi} _2\\
 		&+e^{2\psi}\alpha\Delta^2\left(\omega\wedge\d \tilde\theta+\tilde\omega\wedge\d \theta\right)+e^{4\psi}\Delta^2\alpha ^2\left(\Theta +\frac 1{\alpha^2}\tilde \Theta \right)\\
@@
 \begin{equation}
-	\tilde\gamma=4\sin\theta\cos\theta(\zeta_1^2-\zeta_2 ^2)\left(\tilde{\zeta}_2\cos\tilde \theta ^2\d \tilde \phi _1+\tilde{\zeta} _1\sin\tilde\theta ^2\d\tilde\phi _2\right).
+	\tilde\gamma=4\sin(\theta)\cos(\theta)(\zeta_1^2-\zeta_2 ^2)\left(\tilde{\zeta}_2\cos^2(\tilde \theta)\d \tilde \phi _1+\tilde{\zeta} _1\sin^2(\tilde\theta)\d\tilde\phi _2\right).
 \end{equation} 
@@
 \begin{equation}
-	\zeta_{1}=\pm\zeta_{2},\quad \ts{\zeta}_{1}=\mp\ts{\zeta}_{2}\,\quad\Omega=\ts{\Omega}=0,
-\end{equation}
-the solution~\eqref{eq:metriczeta} reproduces eq.~\eqref{eq:chipsi} for
+	\zeta_{1}=\pm\zeta_{2},\quad \ts{\zeta}_{1}=\mp\ts{\zeta}_{2},\quad\Omega=\ts{\Omega}=0,
+\end{equation}
+the solution~\eqref{eq:metriczeta} reproduces eq.~\eqref{eq:chipsi} for \CE{(Double check.)}
 \begin{equation}
@@
 The subset of these deformations corresponding to the limit~\eqref{eq:limittoT4} was analysed in the half-maximal theory in ref.~\cite{Eloy:2021fhc}.
-Again, within 3-dimensional ${\cal N}=8$ supergravity, this deformation is non-compact, and remains non-compact even after uplifting to 6-dimensional supergravity on $S^3$, with no periodicity in $\chi$ observed in the KK spectrum of the 6-dimensional solution \cite{Eloy:2021fhc}.
+Again, within 3-dimensional ${\cal N}=8$ supergravity, this deformation is non-compact, and remains non-compact even after uplifting to 6-dimensional supergravity on $S^3$, with no periodicity in $\ts{\chi}$ observed in the KK spectrum of the 6-dimensional solution \cite{Eloy:2021fhc}.
 
@@
 Indeed, in this case, after the transformation \eqref{eq:STransformChi}, strings wound around $S^1$ will become light, and one would expect them to replace the KK modes that have become heavy, realising the T-duality on $S^1$.
-This suggests that in the full IIB string theory, the moduli space of each $T^2$ fibration with complex structure \eqref{eq:T2CStructure} should be identified under the M\"{o}bius group $\SL{2,\mathbb{Z}}$, which has a natural action on the metric of this 5-parameter submanifold of moduli space \eqref{eq:Zam7Param}.
+This suggests that in the full IIB string theory, the moduli space of each $T^2$ fibration with complex structure \eqref{eq:T2CStructure} should be identified under the M\"{o}bius group $\SL{2,\mathbb{Z}}$, which has a natural action on the metric of this 5-parameter submanifold of moduli space~\eqref{eq:Zam7Param}.
 Note that this is quite different from the AdS$_4 \times S^5 \times S^1$ ``S-fold'' vacua \cite{Giambrone:2021zvp,Giambrone:2021wsm}, which do not have a $S^1$ rescaling modulus and, therefore, do not carry the natural action of $\SL{2,\mathbb{Z}}$ on each complex structure modulus that we find here.
@@
 Nonetheless, we used the generalised Scherk-Schwarz Ansatz of $\EE$ ExFT \cite{Galli:2022idq} to obtain the potential in terms of the embedding tensor, for all gauged supergravities that can be uplifted to maximal 10-/11-dimensional supergravity.
-This condition of being able to uplift imposes additional quadratic constraints on the embedding tensor \eqref{eq:reltrX}, beyond the usual quadratic constraints of gauged supergravity.
-This can be used to rule out the higher-dimensional origin of some 3-dimensional ${\cal N}=16$ gauged supergravities.
+This condition of being able to uplift imposes additional quadratic constraints on the embedding tensor~\eqref{eq:reltrX}, beyond the usual quadratic constraints of gauged supergravity.
+This can be used to rule out the higher-dimensional origin of some 3-dimensional ${\cal N}=16$ gauged supergravities, as we illustrated on one ${\cal N}=(8,0)$ ${\rm AdS}_{3}$ vacuum of ref.~\cite{Deger:2019tem}.
 \EM{Mention if we actually use this.}
@@
 The corresponding moduli are analogous to the  ``flat deformations'' that arise in the AdS$_4 \times S^5 \times S^1$ vacuum \cite{Guarino:2020gfe,Guarino:2021hrc,Giambrone:2021zvp,Giambrone:2021wsm}.
-I.e.
-they correspond to local diffeomorphisms mixing angles on the $S^3$'s with the $S^1$, but which are not globally well-defined, much like complex structure deformations of $T^2$, allowing us to compute the full Kaluza-Klein spectrum of these deformed AdS$_3$ vacua.
+\textit{i.e.} they correspond to local diffeomorphisms mixing angles on the $S^3$'s with the $S^1$, but which are not globally well-defined, much like complex structure deformations of $T^2$, allowing us to compute the full Kaluza-Klein spectrum of these deformed AdS$_3$ vacua.
 Generic ``flat deformations'' of this type break all supersymmetries but are still perturbatively stable.
@@
 \section*{Acknowledgements}
-We are grateful to \EM{add others} Nikolay Bobev, Adolfo Guarino, Yolanda Lozano, Niall Macpherson and Colin Sterckx for useful discussions and correspondence.
+We are grateful to \EM{add others} Nikolay Bobev, Adolfo Guarino, Gabriel Larios, Yolanda Lozano, Niall Macpherson and Colin Sterckx for useful discussions and correspondence.
 CE is supported by the FWO-Vlaanderen through the project G006119N and by the Vrije Universiteit Brussel through the Strategic Research Program ``High-Energy Physics''.
@@
 \begin{equation}
-	{\rm SU}(1\vert1)\times{\rm SU}(2)\times\ts{{\rm SU}(2)}
+	{\rm SU}(1,1)\times{\rm SU}(2)\times\ts{{\rm SU}(2)}
 \end{equation}
 as its even part.
-Its multiplets are labelled by the spins $\ell$ and $\ts{\ell}$ of each ${\rm SU}(2)$ factor and the eigenvalue $h$ of the $\mathfrak{su}(1\vert1)\simeq\mathfrak{sl}(2,\mathbb{R})$ generator.
+Its multiplets are labelled by the spins $\ell$ and $\ts{\ell}$ of each ${\rm SU}(2)$ factor and the eigenvalue $h$ of the $\mathfrak{su}(1,1)\simeq\mathfrak{sl}(2,\mathbb{R})$ generator.
 Generic short multiplets $[\ell,\ts{\ell}]_{\rm s}$ are given by~\cite{deBoer:1999gea,Eberhardt:2017fsi}

### 2023-06-20 Draft_3dH3.tex
Moved section 4.2 to an appendix, changed some typo in the text, added Berg and Samtleben in the conclusions.

@@
 Not only does this mean that there are also heterotic versions of these vacua (preserving ${\cal N}=(4,0)$ supersymmetry), but also that they can be readily studied via the string worldsheet CFT \cite{Maldacena:2000hw,Eberhardt:2018ouy,Eberhardt:2019niq,Eberhardt:2019ywk}.
-\EM{Cut?} Moreover, the string sigma model in these vacua is also integrable \cite{}.
+%\EM{Cut?} Moreover, the string sigma model in these vacua is also integrable \cite{}.
 Finally, the AdS$_3$/CFT$_2$ correspondence has seen much progress recently, with many new holographic duals being established \cite{}.
@@
 As a by-product, we find a constraint that must be obeyed by the embedding tensor of any 3-dimensional gauged supergravity that can be uplifted to 10-/11-dimensional supergravity.
-As we show, this allows to prove the lack of a higher-dimensional origin of some 3-dimensional gaugings, as we illustrate on an example.
+This allows to prove the lack of a higher-dimensional origin of some 3-dimensional gaugings, as we illustrate on an example.
 \EM{update}
@@
 Using this truncation, we study the moduli space of the AdS$_3$ vacua in section \ref{s:Moduli}, before concluding in section \ref{s:Conclusions}.
+We end the paper by an example in appendix~\ref{app:rulingoutgauging} of how to check if a three-dimensional supergravity can be uplifted, and a discussion of the $D^{1}(2,1;\alpha)$ supermultiplets in appendix~\ref{app:d21a}.
 
@@
 As a result, in that case, the bosonic $\En{9}$ ExFT \cite{Bossard:2018utw,Bossard:2021jix} provides the only currently accessible route for computing the gauged supergravity potential.}, but the potential is crucial for finding vacua of the three-dimensional theory and uplifting these in the later parts of this paper.
-In addition, we derive a necessary condition for the embedding tensor to arise from a compactification of higher-dimensional supergravity and illustrate it on an example.
-
-\subsection{Expression of the potential in terms of the embedding tensor}
+
+% In addition, we derive a necessary condition for the embedding tensor to arise from a compactification of higher-dimensional supergravity and illustrate it on an example.
+% \subsection{Expression of the potential in terms of the embedding tensor}
+
 In order to derive the potential, we adopt the following strategy.
@@
 \end{equation}
-Thus, \eqref{eq:reltrX} is a constraint on the embedding tensor of three-dimensional supergravity which must be satisfied in order for it to have an uplift to 10-/11-dimensional supergravity.
+Thus, \eqref{eq:reltrX} is a constraint on the embedding tensor of three-dimensional supergravity which must be satisfied in order for it to have an uplift to 10-/11-dimensional supergravity (see appendix~\ref{app:rulingoutgauging} for an example).
 Note that this constraint is not implied by the quadratic constraint.
@@
 
-\subsection{Ruling out gaugings}
-\EM{Let's check the $\GL{6} \times \SO{2,2}$ gauging (half-maximal embedded in maximal)....}
-
-As mentioned above, eq.~\eqref{eq:reltrX} can be used to assess whether a given three-dimensional theory of embedding tensor $X_{\fl{MN}}$ has a higher-dimensional origin.
-Let us illustrate that on the ${\cal N}=(8,0)$ ${\rm AdS}_{3}$ vacuum with $\GL{6} \times \SO{2,2}$ gauging constructed in ref.~\cite{Deger:2019tem}.
-This solution has a compact gauging smaller than $\SO{9}$, thus escaping the no-go result of ref.~\cite{Galli:2022idq}.
-The embedding tensor of the solution is expressed by breaking $\EE$ as
-\begin{equation}
-	\begin{aligned}
-		\EE &\longrightarrow \SO{8,8}\\
-		\mathbf{248} &\longrightarrow \mathbf{120} \oplus \mathbf{128}\\
-		X^{\fl{M}} &\longrightarrow \left\{X^{[\fl{\sf IJ}]},X^{\fl{\sf A}}\right\},
-	\end{aligned}
-\end{equation}
-with $\fl{\sf I}$ and $\fl{\sf A}$ labels of the fundamental and spinorial representations of $\SO{8,8}$, respectively. Explicitly,
-\begin{equation}
-	\begin{aligned}
-		X_{\fl{\sf IJ},\fl{\sf KL}} &= \Theta_{\fl{\sf IJ},\fl{\sf KL}},\\
-		X_{\fl{\sf AB}} &= -2\,\theta\,\eta_{\fl{\sf AB}}+\frac{1}{24}\,\Gamma^{\fl{\sf IJ},\fl{\sf KL}}_{\fl{\sf AB}}\,\Theta_{\fl{\sf IJKL}},\\
-		X_{\fl{\sf IJ},\fl{\sf A}} &=0,
-	\end{aligned}
-\end{equation}
-where $\Gamma^{\fl{\sf IJKL}}_{\fl{\sf AB}}$ is the four-fold product of $\SO{8,8}$ $\Gamma$ matrices and $\eta_{\fl{\sf AB}}$ the $\mathbf{128}\otimes\mathbf{128}$ component of the Cartan-Killing metric.
-The tensor $\Theta_{\fl{\sf IJ},\fl{\sf KL}}$ is given by
-\begin{equation}
-	\Theta_{\fl{\sf IJ},\fl{\sf KL}}=\theta_{\fl{\sf IJKL}}+\frac12\big(\eta_{\fl{\sf K}[\fl{\sf I}}\theta_{\fl{\sf J}]\fl{\sf L}}-\eta_{\fl{\sf L}[\fl{\sf I}}\theta_{\fl{\sf J}]\fl{\sf K}}\big)+\theta\,\eta_{\fl{\sf K}[\fl{\sf I}}\eta_{\fl{\sf J}]\fl{\sf L}}\,,
-\end{equation}
-with $\theta_{\fl{\sf IJKL}}$ totally antisymmetric and $\theta_{\fl{\sf IJ}}$ symmetric, with non vanishing components
-\begin{align}
-  & \theta_{ij}=4\,\delta_{ij}\;,\quad \theta_{\alpha\beta}=-12\,\delta_{\alpha\beta}\;,\quad \theta_{r_{+}s_{+}}=-4\,\delta_{r_{+}s_{+}}\;,\quad \theta_{r_{-}s_{-}}=12\,\delta_{r_{-}s_{-}}\;,\nonumber\\
-  & \theta=-8\;,\quad \theta_{\alpha\beta r_{-}s_{-}} = -48\,\sigma_{\alpha\beta}\,\sigma_{r_{-}s_{-}}\;,\quad \theta_{ij r_{+}s_{+}} = 32\,\delta_{i[r_{+}}\,\delta_{s_{+}]j}\;,
-\end{align}
-where... \CE{(explain all notations...)} With this embedding, we get
-\begin{equation}
-	X_{\ov{MN}}\,X^{\ov{MN}} = \frac{55}{1922}\left(X_{\ov M}{}^{\ov M}\right)^2,
-\end{equation}
-thus violating the condition~\eqref{eq:reltrX} (the trombone gauging vanishes for the solution).
-Then, we deduce that the ${\cal N}=(8,0)$ solution of ref.~\cite{Deger:2019tem} with gauging $\GL{6} \times \SO{2,2}$ does not admit a higher-dimensional origin.
-This illustrate how the constraint~\eqref{eq:reltrX} can be used to determine if a given three-dimensional vacuum can be uplifted.
-
 \section{Adding fluxes to consistent truncations} \label{s:AddFlux}
@@
 This motivates the following question: Given a consistent truncation, \textit{i.e.} $\cU_{\fl{M}}{}^M$, satisfying \eqref{eq:GenLeibniz}, when can we add a new flux component of string theory to the compactification to obtain a new consistent truncation?
-Adding a new flux component to the truncation is equivalent to twisting the generalised frame as follows \EM{Email DW and MP to ask who we should cite for this?}
+Adding a new flux component to the truncation is equivalent to twisting the generalised frame as follows %\EM{Email DW and MP to ask who we should cite for this?}
 \begin{equation} \label{eq:Twisting}
@@
 \subsubsection{The $S^n$ twist matrix} \label{s:SLn}
-\EM{Move to appendix?!?!} \CE{(I think I would say yes. Work here.)}\\
+\EM{Move to appendix?!?!} \CE{(I think I would say yes.)}\\
 Since we will use it throughout this paper, let us construct the $\SL{4} \simeq \SO{3,3}$ twist matrix that describes the consistent truncation on $S^3$.
@@
 We denote by $U_A{}^{\ov{A}}$ the $\SO{3,3}$ twist matrix corresponding to the $S^3$ truncation constructed in \cite{Lee:2014mla,Baguet:2015iou} and obtained from \eqref{eq:SLnFrame}, \eqref{eq:rho}, \eqref{eq:SLnTwist}.
-Then, we can add a 3-form potential by twisting with the $\SO{4,4}$ generator \CE{(Sure here?
-Check notes.)}
+Then, we can add a 3-form potential by twisting with the $\SO{4,4}$ generator \CE{(Sure here?)}
 \begin{equation} \label{eq:C2S3example}
-	(e^C)^{MN} = C_A \left( t^A \right)^{MN} \,,
+	(e^C)^{MN} = \eta^{MN} + C_A \left( t^A \right)^{MN} \,,
 \end{equation}
@@
 \begin{equation}
-	\zeta_{1}=\pm\zeta_{2},\quad \ts{\zeta}_{1}=\mp\ts{\zeta}_{2},\quad\Omega=\ts{\Omega}=0,
-\end{equation}
-the solution~\eqref{eq:metriczeta} reproduces eq.~\eqref{eq:chipsi} for \CE{(Double check.)}
+	\zeta_{1}=\pm\zeta_{2},\quad \ts{\zeta}_{1}=\mp\ts{\zeta}_{2},\quad\psi=\Omega=\ts{\Omega}=0,
+\end{equation}
+the solution~\eqref{eq:metriczeta} reproduces eq.~\eqref{eq:chipsi} for
 \begin{equation}
@@
 We constructed our consistent truncation by doing a $S^1$ reduction of the truncation of IIB on $S^3 \times S^3$ \cite{Inverso:2016eet}, and turning on an additional $H_7$ flux on $S^3 \times S^3 \times S^1$, which is necessary to obtain an AdS$_3$ vacuum.
-We also show that it is not possible to turn on such an additional flux for the other ``dyonic'' consistent truncations on $S^6$, $S^5 \times S^1$, $S^4 \times S^2$ \cite{Guarino:2015jca,Inverso:2016eet} reduced on $S^1$, whilst maintining a consistent truncation to ${\cal N}=16$ gauged supergravity.
+We also show that it is not possible to turn on such an additional flux for the other ``dyonic'' consistent truncations on $S^6$, $S^5 \times S^1$, $S^4 \times S^2$ \cite{Guarino:2015jca,Inverso:2016eet} reduced on $S^1$, whilst maintaining a consistent truncation to ${\cal N}=16$ gauged supergravity.
 
@@
 This condition of being able to uplift imposes additional quadratic constraints on the embedding tensor~\eqref{eq:reltrX}, beyond the usual quadratic constraints of gauged supergravity.
-This can be used to rule out the higher-dimensional origin of some 3-dimensional ${\cal N}=16$ gauged supergravities, as we illustrated on one ${\cal N}=(8,0)$ ${\rm AdS}_{3}$ vacuum of ref.~\cite{Deger:2019tem}.
+This can be used to rule out the higher-dimensional origin of some 3-dimensional ${\cal N}=16$ gauged supergravities, as we illustrated in appendix~\ref{app:rulingoutgauging} on one ${\cal N}=(8,0)$ ${\rm AdS}_{3}$ vacuum of ref.~\cite{Deger:2019tem}.
 \EM{Mention if we actually use this.}
@@
 The non-perturbative stability of the perturbatively stable non-supersymmetric AdS$_3$ vacua we found also deserves further study.
-Finally, similar ``flat deformations'' arise in any string compactification involving an $S^1$, in particular AdS$_3 \times S^3 \times T^4$.
+Thirdly, similar ``flat deformations'' arise in any string compactification involving an $S^1$, in particular AdS$_3 \times S^3 \times T^4$.
 It would be interesting to understand universal features of these deformations and their CFT duals.
+Finally, we would like to use the tools developed here to study RG flows between solutions of three-dimensional supergravity, or equivalently between fixed points of a two-dimensional conformal field theory.
+Note however that this cannot be applied to the RG flow of ref.~\cite{Berg:2001ty}: their solution cannot be described using \EE exceptional field theory as reproducing their embedding tensor would require breaking the section constraint.
 We leave these questions for future work.
@@
 \appendix
+
+\section{Ruling out gaugings} \label{app:rulingoutgauging}
+% \EM{Let's check the $\GL{6} \times \SO{2,2}$ gauging (half-maximal embedded in maximal)....}
+
+As mentioned in sec.~\ref{s:Potential}, eq.~\eqref{eq:reltrX} can be used to assess whether a given three-dimensional theory of embedding tensor $X_{\fl{MN}}$ has a higher-dimensional origin.
+Let us illustrate that on the ${\cal N}=(8,0)$ ${\rm AdS}_{3}$ vacuum with $\GL{6} \times \SO{2,2}$ gauging constructed in ref.~\cite{Deger:2019tem}.
+This solution has a compact gauging smaller than $\SO{9}$, thus escaping the no-go result of ref.~\cite{Galli:2022idq}.
+The embedding tensor of the solution is expressed by breaking $\EE$ as
+\begin{equation}
+	\begin{aligned}
+		\EE &\longrightarrow \SO{8,8}\\
+		\mathbf{248} &\longrightarrow \mathbf{120} \oplus \mathbf{128}\\
+		X^{\fl{M}} &\longrightarrow \left\{X^{[\fl{\sf IJ}]},X^{\fl{\sf A}}\right\},
+	\end{aligned}
+\end{equation}
+with $\fl{\sf I}$ and $\fl{\sf A}$ labels of the fundamental and spinorial representations of $\SO{8,8}$, respectively. Explicitly,
+\begin{equation}
+	\begin{aligned}
+		X_{\fl{\sf IJ},\fl{\sf KL}} &= \Theta_{\fl{\sf IJ},\fl{\sf KL}},\\
+		X_{\fl{\sf AB}} &= -2\,\theta\,\eta_{\fl{\sf AB}}+\frac{1}{24}\,\Gamma^{\fl{\sf IJ},\fl{\sf KL}}_{\fl{\sf AB}}\,\Theta_{\fl{\sf IJKL}},\\
+		X_{\fl{\sf IJ},\fl{\sf A}} &=0,
+	\end{aligned}
+\end{equation}
+where $\Gamma^{\fl{\sf IJKL}}_{\fl{\sf AB}}$ is the four-fold product of $\SO{8,8}$ $\Gamma$ matrices and $\eta_{\fl{\sf AB}}$ the $\mathbf{128}\otimes\mathbf{128}$ component of the Cartan-Killing metric, or equivalently the $\SO{8,8}$ charge conjugation matrix.
+The tensor $\Theta_{\fl{\sf IJ},\fl{\sf KL}}$ is given by
+\begin{equation}
+	\Theta_{\fl{\sf IJ},\fl{\sf KL}}=\theta_{\fl{\sf IJKL}}+\frac12\big(\eta_{\fl{\sf K}[\fl{\sf I}}\theta_{\fl{\sf J}]\fl{\sf L}}-\eta_{\fl{\sf L}[\fl{\sf I}}\theta_{\fl{\sf J}]\fl{\sf K}}\big)+\theta\,\eta_{\fl{\sf K}[\fl{\sf I}}\eta_{\fl{\sf J}]\fl{\sf L}}\,,
+\end{equation}
+with $\theta_{\fl{\sf IJKL}}$ totally antisymmetric and $\theta_{\fl{\sf IJ}}$ symmetric. They have the following non-vanishing components:
+\begin{align}
+  & \theta_{ij}=\delta_{ij}\;,\quad \theta_{\alpha\beta}=-3\,\delta_{\alpha\beta}\;,\quad \theta_{r_{+}s_{+}}=-\delta_{r_{+}s_{+}}\;,\quad \theta_{r_{-}s_{-}}=3\,\delta_{r_{-}s_{-}}\;,\nonumber\\
+  & \theta=-1\;,\quad \theta_{\alpha\beta r_{-}s_{-}} = -3\,\epsilon_{\alpha\beta}\,\epsilon_{r_{-}s_{-}}\;,\quad \theta_{ij r_{+}s_{+}} = 2\,\delta_{i[r_{+}}\,\delta_{s_{+}]j}\;,
+\end{align}
+% \begin{align}
+%   & \theta_{ij}=4\,\delta_{ij}\;,\quad \theta_{\alpha\beta}=-12\,\delta_{\alpha\beta}\;,\quad \theta_{r_{+}s_{+}}=-4\,\delta_{r_{+}s_{+}}\;,\quad \theta_{r_{-}s_{-}}=12\,\delta_{r_{-}s_{-}}\;,\nonumber\\
+%   & \theta=-8\;,\quad \theta_{\alpha\beta r_{-}s_{-}} = -48\,\epsilon_{\alpha\beta}\,\epsilon_{r_{-}s_{-}}\;,\quad \theta_{ij r_{+}s_{+}} = 32\,\delta_{i[r_{+}}\,\delta_{s_{+}]j}\;,
+% \end{align}
+where we split the indices according to
+\begin{equation}
+	\begin{aligned}
+		\SO{8,8} & \longrightarrow \SO{8}\times\SO{8} \longrightarrow \SO{6}\times\SO{2}\times\SO{6}\times\SO{2} \\
+		X^{\fl{\sf I}} & \ \tikz{\draw[arrows={->[scale=1.1]}] (0,0) -- (3.55
+	,0);}\ \left\{X^{i},\,X^{\alpha},\,X^{r_{+}},\,X^{r_{-}}\right\},
+	\end{aligned}
+\end{equation}
+and defined the matrix
+\begin{equation}
+	 \epsilon = \begin{pmatrix}
+                0 & 1\\
+                -1 & 0
+              \end{pmatrix}.
+\end{equation}
+With this embedding, we get
+\begin{equation}
+	X_{\ov{MN}}\,X^{\ov{MN}} = \frac{55}{1922}\left(X_{\ov M}{}^{\ov M}\right)^2,
+\end{equation}
+thus violating the condition~\eqref{eq:reltrX} (the trombone gauging vanishes for the solution).
+Then, we deduce that the ${\cal N}=(8,0)$ solution of ref.~\cite{Deger:2019tem} with gauging $\GL{6} \times \SO{2,2}$ does not admit a higher-dimensional origin as constructed with \EE exceptional field theory.
+This illustrate how the constraint~\eqref{eq:reltrX} can be used to determine if a given three-dimensional vacuum can be uplifted.
 

### 2023-06-20 Draft_3dH3.tex
Sl(n) in appendix, and 4pi in periodicities.

@@
 Using this truncation, we study the moduli space of the AdS$_3$ vacua in section \ref{s:Moduli}, before concluding in section \ref{s:Conclusions}.
-We end the paper by an example in appendix~\ref{app:rulingoutgauging} of how to check if a three-dimensional supergravity can be uplifted, and a discussion of the $D^{1}(2,1;\alpha)$ supermultiplets in appendix~\ref{app:d21a}.
+We end the paper by an example in appendix~\ref{app:rulingoutgauging} of how to check if a three-dimensional supergravity can be uplifted, a review of the construction of consistent truncations on $S^{3}$ in appendix~\ref{s:SLn} and a discussion of the $D^{1}(2,1;\alpha)$ supermultiplets in appendix~\ref{app:d21a}.
 
@@
 
-\subsubsection{The $S^n$ twist matrix} \label{s:SLn}
-\EM{Move to appendix?!?!} \CE{(I think I would say yes.)}\\
-Since we will use it throughout this paper, let us construct the $\SL{4} \simeq \SO{3,3}$ twist matrix that describes the consistent truncation on $S^3$.
-This can be viewed as a special case of a family of consistent truncations on $S^n$ \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou}.
-Here, we give a slightly different, but equivalent, form of this construction.
-
-We use an $\SL{n+1}$ ExFT, like in \cite{Lee:2014mla}, which encodes an $n$-dimensional metric and volume-form flux, \textit{i.e.} Freund-Rubin compactifications, and thus gives a natural description of $S^n$ compactifications.
-The $\SL{n+1}$ ExFT formally has coordinates in the antisymmetric representation of $\SL{n+1}$, $y^{IJ} = - y^{JI}$, with $I = 1, \ldots, n+1$, and similarly, generalised vector fields transform in the antisymmetric representation of $\SL{n+1}$.
-The generalised Lie derivative on a generalised tensor in the fundamental $V^I$ of weight $\lambda$ is given by
-\begin{equation} \label{eq:SLnGenLie}
-	\gL_\Lambda V^I = \frac12 \Lambda^{JK} \partial_{JK} V^{I} - V^J \partial_{JK} \Lambda^{IK} + \left( \frac{\lambda}{2} + \frac{1}{n+1} \right) V^I \partial_{JK} \Lambda^{JK} \,,
-\end{equation}
-and similarly for other generalised tensors. Closure of the generalised Lie derivative \eqref{eq:SLnGenLie} requires the section condition
-\begin{equation} \label{eq:SLnSC}
-	\partial_{[IJ} \otimes \partial_{KL]} = 0 \,,
-\end{equation}
-which restricts the dependence of all fields to a subset of physical coordinates.
-
-We are interested in the maximal solutions of the section condition \eqref{eq:SLnSC} which preserve a $\SL{n} \subset \SL{n+1}$ subgroup.
-Under this decomposition $\SL{n+1} \rightarrow \SL{n}$ with $V^I = \left( V^i,\, V^0 \right)$, where $i = 1, \ldots, n$, we solve the section condition by having physical coordinates $y^{0i}$ on the $n$-dimensional manifold $M$, \textit{i.e.} $\partial_{ij} = 0$ for all fields with only $\partial_{0i} = \partial_i \neq 0$.
-Correspondingly, the generalised tangent bundle, whose sections are in the antisymmetric representation of $\SL{n+1}$ and carry weight $\frac{n-3}{n+1}$, decomposes as
-\begin{equation} \label{eq:SLnE}
-	E = TM \oplus \Lambda^{n-2} T^*M \,,
-\end{equation}
-Note that for the case of interest to us, $n=3$, \eqref{eq:SLnE} reduces to
-\begin{equation}
-	E = TM \oplus T^*M \,,
-\end{equation}
-and its fibres transform in the $\mathbf{6}$ of $\SL{4} \simeq \SO{3,3}$.
-It is convenient to also introduce the generalised bundle with fibres in the anti-fundamental of $\SL{n+1}$, which is, similarly, given by
-\begin{equation}
-	N = T^*M \oplus \Lambda^{n} T^*M \,.
-\end{equation}
-Sections of $N$ are generalised tensors transforming in the anti-fundamental of $\SL{n+1}$ and carrying weight $\frac{2}{n+1}$.
-For $V, V' \in \Gamma(E)$ and $W \in \Gamma(N)$, the generalised Lie derivative \eqref{eq:SLnGenLie} reduces to
-\begin{equation}
-	\begin{split}
-		\gL_{V} V' &= [v, v'] + L_{v} \omega'_{(n-2)} - \imath_{v'} d\omega_{(n-2)} \,, \\
-		\gL_{V} W &= L_v \omega_{(1)} + L_v \omega_{(n)} + \omega_{(1)} \wedge d\omega_{(n-2)} \,,
-	\end{split}
-\end{equation}
-where we write $V = v + \omega_{(n-2)}$, $V' = v' + \omega'_{(n-2)}$ and $W = \omega_{(1)} + \omega_{(n)}$ as a formal of vectors and $p$-forms, and $L$ denotes the ordinary Lie derivative and $[v,v']$ the ordinary Lie bracket between vector fields $v$ and $v'$.
-
-We can now describe the $S^n$ consistent truncation using the $\SL{n+1}$ ExFT above.
-Let $Y^I$, $I = 1, \ldots, n+1$ be the embedding coordinates of $S^{n} \subset \mathbb{R}^{n+1}$, such that $Y^I\, Y_I = 1$.
-On $S^n$, we can define a parallelisation of $N$ using the generalised frame
-\begin{equation}\label{eq:SnFrame}
-	\cU^{\fl{I}} = dY^{\fl{I}} + Y^{\fl{I}}\, vol_{S^n} - dY^{\fl{I}} \wedge A \,,
-\end{equation}
-where $A$ is an $(n-1)$-potential with field strength $dA = (n-1) vol_{S^n}$, and
-\begin{equation}
-	vol_{S^n} = \frac{1}{n!}\epsilon_{I_1 I_2 \ldots I_{n+1}} Y^{I_1}\, dY^{I_2} \wedge \ldots \wedge dY^{I_{n+1}} \,,
-\end{equation}
-is the volume form on $S^n$.
-The frame in \eqref{eq:SnFrame} has the important property that the $n+1$ generalised tensors are nowhere vanishing since $dY^I = 0$ only when $Y^I = 1$.
-Therefore, \eqref{eq:SnFrame} provides a generalised parallelisation of $S^n$ in the $\SL{n+1}$ ExFT.
-
-In a local basis, \eqref{eq:SnFrame} gives us a $\GL{n+1}$ matrix, $\cU_I{}^{\fl{I}}$, whose determinant allows us to define the scalar density
-\begin{equation} \label{eq:rho}
-	\rho = \left(\det \cU_I{}^{\fl{I}}\right)^{-1/2} = \left(\det \mathring{g}\right)^{-1/2} \,,
-\end{equation}
-with $\mathring{g}$ the round metric on $S^n$. Using \eqref{eq:SnFrame} and \eqref{eq:rho} we can define the $\SL{n}$ twist matrix
-\begin{equation} \label{eq:SLnFrame}
-	U_I{}^{\fl{I}} = \rho^{2/(n+1)}\, \cU_I{}^{\fl{I}} \,,
-\end{equation}
-and hence a generalised frame for $E$ or a generalised bundle in any other rep of $\SL{n+1}$.
-For example, in the generalised tangent bundle \eqref{eq:SLnE}, we have the generalised frame $\cU_{\fl{I}\fl{J}}{}^{IJ} = \left(\det \mathring{g}\right)^{1/2} \cU_{[\fl{I}}{}^{I} \cU_{\fl{J}]}{}^J$, with components given by
-\begin{equation} \label{eq:SLnGenFrame}
-	2\, \cU_{\fl{I}\fl{J}} = v_{\fl{I}\fl{J}} + \star dY_{\fl{I}\fl{J}} + \imath_{v_{\fl{I}\fl{J}}} A \,,
-\end{equation}
-where $v_{\fl{I}\fl{J}}$ are the $\SO{n+1}$ Killing vectors of the round $S^n$, matching precisely the $\SL{n+1}$ parallelisations constructed in \cite{Lee:2014mla}.
-
-Using \eqref{eq:SLnGenLie}, we can easily check that the generalised frame  \eqref{eq:SLnGenFrame}, \eqref{eq:SLnTwist} defines a generalised Leibniz parallelisation.
-In particular, using $dA = (n-1) vol_{S^n}$, we obtain the embedding tensor
-\begin{equation}
-	\gL_{\cU_{\fl{I}\fl{J}}} \cU^{\fl{K}} = - X_{\fl{I}\fl{J}\fl{L}}{}^{\fl{K}}\, \cU^{\fl{L}} \,,
-\end{equation}
-with
-\begin{equation} \label{eq:SLnEmbeddingTensor}
-	X_{\fl{I}\fl{J},\fl{L}}{}^{\fl{K}} = - \delta_{\fl{L}[\fl{I}} \delta_{\fl{J}]}^{\fl{K}} \,.
-\end{equation}
-
-Finally, we can also connect the above with the $\SL{n+1}$ Ansatz construction of \cite{Hohm:2014qga}.
-We do this by evaluating \eqref{eq:rho} and \eqref{eq:SLnFrame} on the northern hemisphere $Y^I = \left( y^i,\, \sqrt{1-y^i y_i}\right)$, $i = 1, \ldots, n$ and using the gauge choice for the potential $A$
-\begin{equation}
-	A_{i_1 \ldots i_{n-1}} = \epsilon_{i_1 \ldots i_{n-1}j}\, y^j (1 + K(v)) \,,
-\end{equation}
-with $v = y^i\, y^i$ and $\epsilon_{i_1 \ldots i_{n-1}j}$ the volume form on $S^n$. With the above choices, we precisely recover the $\SL{n+1}$ twist matrix of \cite{Hohm:2014qga}, \textit{i.e.}
-\begin{equation} \label{eq:SLnTwist}
-	\UI_{\fl{I}}{}^I = \begin{pmatrix}
-		\left(1-v\right)^{-1/(n+1)} \left( \delta_i{}^j + y_i\, y^j K(v) \right) & y_i \left(1-v\right)^{(n-1)/(2(n+1))} \\
-		y^j \left(1-v\right)^{(n-1)/(2(n+1))} K(v) & \left(1-v\right)^{\tfrac{n}{n+1}}
-	\end{pmatrix} \,.
-\end{equation}
-
-\subsubsection{Adding flux}
-To demonstrate our methodology, we will now show how the parameter $\lambda$ introduced in \cite{Eloy:2021fhc} can be obtained by the twisting procedure described above.
+The construction of the the $\SL{4} \simeq \SO{3,3}$ twist matrix describing the consistent truncation on $S^3$ is detailed in appendix~\ref{s:SLn}.
+To demonstrate our methodology, we will now show how the parameter $\lambda$ introduced in \cite{Eloy:2021fhc} can be obtained by the twisting procedure described in appendix~\ref{s:SLn}.
 Thus, we want to consider the $\SO{3,3} \subset \SO{4,4}$ twist matrix corresponding to $S^3$ \eqref{eq:SLnTwist} and add a 3-form flux via a $\SO{4,4}$ twist.
@@
 
-In the above cases, it is easy to see from \eqref{eq:confdimshiftchi} that the spectrum  is invariant under $\chi_i \rightarrow \chi_i + 2\pi k_i\,\alpha$, $\ts{\chi}_i \rightarrow \ts{\chi}_i + 2\pi \ts{k}_i$, for $k_i$, $\ts{k}_i \in \mathbb{Z}$, with the SUSY enhancements also occurring if the relations \eqref{eq:N2}, \eqref{eq:N4Large}, \eqref{eq:N4Small} or \eqref{eq:N6} are satisfied up to integer shifts.
+In the above cases, it is easy to see from \eqref{eq:confdimshiftchi} that the spectrum  is invariant under $\chi_i \rightarrow \chi_i + 4\pi k_i\,\alpha$, $\ts{\chi}_i \rightarrow \ts{\chi}_i + 4\pi \ts{k}_i$, for $k_i$, $\ts{k}_i \in \mathbb{Z}$, with the SUSY enhancements also occurring if the relations \eqref{eq:N2}, \eqref{eq:N4Large}, \eqref{eq:N4Small} or \eqref{eq:N6} are satisfied up to integer shifts.
 We will return to this point below in section \ref{s:Compact}, when discussing compactness of the moduli space.
@@
 	\begin{split}
-		\chi_i &\rightarrow \chi_i + 2\pi\alpha\, k_i\,, \\
-		\ts{\chi}_i &\rightarrow \ts{\chi}_i + 2\pi \ts{k}_i \,,
+		\chi_i &\rightarrow \chi_i + 4\pi\alpha\, k_i\,, \\
+		\ts{\chi}_i &\rightarrow \ts{\chi}_i + 4\pi \ts{k}_i \,,
 	\end{split}
@@
 Under this identification, the shifts \eqref{eq:ShiftSymmetries} correspond to $T$-transformations of the tori, which belong to the modular group $\SL{2,\mathbb{Z}}$, just as for AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
+\CE{(Need to change here given $4\pi$ in \eqref{eq:ShiftSymmetries}?)}
 
@@
 Finally, we would like to use the tools developed here to study RG flows between solutions of three-dimensional supergravity, or equivalently between fixed points of a two-dimensional conformal field theory.
-Note however that this cannot be applied to the RG flow of ref.~\cite{Berg:2001ty}: their solution cannot be described using \EE exceptional field theory as reproducing their embedding tensor would require breaking the section constraint.
+Note however that this cannot be applied to the RG flow of ref.~\cite{Berg:2001ty}: their solution cannot be described using the generalized Scherk-Schwarz Ansatz of \EE exceptional field theory as reproducing their embedding tensor would require breaking the section constraint.
 We leave these questions for future work.
@@
 
+\section{The $S^n$ twist matrix} \label{s:SLn}
+Let us construct the $\SL{4} \simeq \SO{3,3}$ twist matrix that describes the consistent truncation on $S^3$.
+This can be viewed as a special case of a family of consistent truncations on $S^n$ \cite{Lee:2014mla,Hohm:2014qga,Baguet:2015iou}.
+Here, we give a slightly different, but equivalent, form of this construction.
+
+We use an $\SL{n+1}$ ExFT, like in \cite{Lee:2014mla}, which encodes an $n$-dimensional metric and volume-form flux, \textit{i.e.} Freund-Rubin compactifications, and thus gives a natural description of $S^n$ compactifications.
+The $\SL{n+1}$ ExFT formally has coordinates in the antisymmetric representation of $\SL{n+1}$, $y^{IJ} = - y^{JI}$, with $I = 1, \ldots, n+1$, and similarly, generalised vector fields transform in the antisymmetric representation of $\SL{n+1}$.
+The generalised Lie derivative on a generalised tensor in the fundamental $V^I$ of weight $\lambda$ is given by
+\begin{equation} \label{eq:SLnGenLie}
+	\gL_\Lambda V^I = \frac12 \Lambda^{JK} \partial_{JK} V^{I} - V^J \partial_{JK} \Lambda^{IK} + \left( \frac{\lambda}{2} + \frac{1}{n+1} \right) V^I \partial_{JK} \Lambda^{JK} \,,
+\end{equation}
+and similarly for other generalised tensors. Closure of the generalised Lie derivative \eqref{eq:SLnGenLie} requires the section condition
+\begin{equation} \label{eq:SLnSC}
+	\partial_{[IJ} \otimes \partial_{KL]} = 0 \,,
+\end{equation}
+which restricts the dependence of all fields to a subset of physical coordinates.
+
+We are interested in the maximal solutions of the section condition \eqref{eq:SLnSC} which preserve a $\SL{n} \subset \SL{n+1}$ subgroup.
+Under this decomposition $\SL{n+1} \rightarrow \SL{n}$ with $V^I = \left( V^i,\, V^0 \right)$, where $i = 1, \ldots, n$, we solve the section condition by having physical coordinates $y^{0i}$ on the $n$-dimensional manifold $M$, \textit{i.e.} $\partial_{ij} = 0$ for all fields with only $\partial_{0i} = \partial_i \neq 0$.
+Correspondingly, the generalised tangent bundle, whose sections are in the antisymmetric representation of $\SL{n+1}$ and carry weight $\frac{n-3}{n+1}$, decomposes as
+\begin{equation} \label{eq:SLnE}
+	E = TM \oplus \Lambda^{n-2} T^*M \,,
+\end{equation}
+Note that for the case of interest to us, $n=3$, \eqref{eq:SLnE} reduces to
+\begin{equation}
+	E = TM \oplus T^*M \,,
+\end{equation}
+and its fibres transform in the $\mathbf{6}$ of $\SL{4} \simeq \SO{3,3}$.
+It is convenient to also introduce the generalised bundle with fibres in the anti-fundamental of $\SL{n+1}$, which is, similarly, given by
+\begin{equation}
+	N = T^*M \oplus \Lambda^{n} T^*M \,.
+\end{equation}
+Sections of $N$ are generalised tensors transforming in the anti-fundamental of $\SL{n+1}$ and carrying weight $\frac{2}{n+1}$.
+For $V, V' \in \Gamma(E)$ and $W \in \Gamma(N)$, the generalised Lie derivative \eqref{eq:SLnGenLie} reduces to
+\begin{equation}
+	\begin{split}
+		\gL_{V} V' &= [v, v'] + L_{v} \omega'_{(n-2)} - \imath_{v'} d\omega_{(n-2)} \,, \\
+		\gL_{V} W &= L_v \omega_{(1)} + L_v \omega_{(n)} + \omega_{(1)} \wedge d\omega_{(n-2)} \,,
+	\end{split}
+\end{equation}
+where we write $V = v + \omega_{(n-2)}$, $V' = v' + \omega'_{(n-2)}$ and $W = \omega_{(1)} + \omega_{(n)}$ as a formal of vectors and $p$-forms, and $L$ denotes the ordinary Lie derivative and $[v,v']$ the ordinary Lie bracket between vector fields $v$ and $v'$.
+
+We can now describe the $S^n$ consistent truncation using the $\SL{n+1}$ ExFT above.
+Let $Y^I$, $I = 1, \ldots, n+1$ be the embedding coordinates of $S^{n} \subset \mathbb{R}^{n+1}$, such that $Y^I\, Y_I = 1$.
+On $S^n$, we can define a parallelisation of $N$ using the generalised frame
+\begin{equation}\label{eq:SnFrame}
+	\cU^{\fl{I}} = dY^{\fl{I}} + Y^{\fl{I}}\, vol_{S^n} - dY^{\fl{I}} \wedge A \,,
+\end{equation}
+where $A$ is an $(n-1)$-potential with field strength $dA = (n-1) vol_{S^n}$, and
+\begin{equation}
+	vol_{S^n} = \frac{1}{n!}\epsilon_{I_1 I_2 \ldots I_{n+1}} Y^{I_1}\, dY^{I_2} \wedge \ldots \wedge dY^{I_{n+1}} \,,
+\end{equation}
+is the volume form on $S^n$.
+The frame in \eqref{eq:SnFrame} has the important property that the $n+1$ generalised tensors are nowhere vanishing since $dY^I = 0$ only when $Y^I = 1$.
+Therefore, \eqref{eq:SnFrame} provides a generalised parallelisation of $S^n$ in the $\SL{n+1}$ ExFT.
+
+In a local basis, \eqref{eq:SnFrame} gives us a $\GL{n+1}$ matrix, $\cU_I{}^{\fl{I}}$, whose determinant allows us to define the scalar density
+\begin{equation} \label{eq:rho}
+	\rho = \left(\det \cU_I{}^{\fl{I}}\right)^{-1/2} = \left(\det \mathring{g}\right)^{-1/2} \,,
+\end{equation}
+with $\mathring{g}$ the round metric on $S^n$. Using \eqref{eq:SnFrame} and \eqref{eq:rho} we can define the $\SL{n}$ twist matrix
+\begin{equation} \label{eq:SLnFrame}
+	U_I{}^{\fl{I}} = \rho^{2/(n+1)}\, \cU_I{}^{\fl{I}} \,,
+\end{equation}
+and hence a generalised frame for $E$ or a generalised bundle in any other rep of $\SL{n+1}$.
+For example, in the generalised tangent bundle \eqref{eq:SLnE}, we have the generalised frame $\cU_{\fl{I}\fl{J}}{}^{IJ} = \left(\det \mathring{g}\right)^{1/2} \cU_{[\fl{I}}{}^{I} \cU_{\fl{J}]}{}^J$, with components given by
+\begin{equation} \label{eq:SLnGenFrame}
+	2\, \cU_{\fl{I}\fl{J}} = v_{\fl{I}\fl{J}} + \star dY_{\fl{I}\fl{J}} + \imath_{v_{\fl{I}\fl{J}}} A \,,
+\end{equation}
+where $v_{\fl{I}\fl{J}}$ are the $\SO{n+1}$ Killing vectors of the round $S^n$, matching precisely the $\SL{n+1}$ parallelisations constructed in \cite{Lee:2014mla}.
+
+Using \eqref{eq:SLnGenLie}, we can easily check that the generalised frame  \eqref{eq:SLnGenFrame}, \eqref{eq:SLnTwist} defines a generalised Leibniz parallelisation.
+In particular, using $dA = (n-1) vol_{S^n}$, we obtain the embedding tensor
+\begin{equation}
+	\gL_{\cU_{\fl{I}\fl{J}}} \cU^{\fl{K}} = - X_{\fl{I}\fl{J}\fl{L}}{}^{\fl{K}}\, \cU^{\fl{L}} \,,
+\end{equation}
+with
+\begin{equation} \label{eq:SLnEmbeddingTensor}
+	X_{\fl{I}\fl{J},\fl{L}}{}^{\fl{K}} = - \delta_{\fl{L}[\fl{I}} \delta_{\fl{J}]}^{\fl{K}} \,.
+\end{equation}
+
+Finally, we can also connect the above with the $\SL{n+1}$ Ansatz construction of \cite{Hohm:2014qga}.
+We do this by evaluating \eqref{eq:rho} and \eqref{eq:SLnFrame} on the northern hemisphere $Y^I = \left( y^i,\, \sqrt{1-y^i y_i}\right)$, $i = 1, \ldots, n$ and using the gauge choice for the potential $A$
+\begin{equation}
+	A_{i_1 \ldots i_{n-1}} = \epsilon_{i_1 \ldots i_{n-1}j}\, y^j (1 + K(v)) \,,
+\end{equation}
+with $v = y^i\, y^i$ and $\epsilon_{i_1 \ldots i_{n-1}j}$ the volume form on $S^n$. With the above choices, we precisely recover the $\SL{n+1}$ twist matrix of \cite{Hohm:2014qga}, \textit{i.e.}
+\begin{equation} \label{eq:SLnTwist}
+	\UI_{\fl{I}}{}^I = \begin{pmatrix}
+		\left(1-v\right)^{-1/(n+1)} \left( \delta_i{}^j + y_i\, y^j K(v) \right) & y_i \left(1-v\right)^{(n-1)/(2(n+1))} \\
+		y^j \left(1-v\right)^{(n-1)/(2(n+1))} K(v) & \left(1-v\right)^{\tfrac{n}{n+1}}
+	\end{pmatrix} \,.
+\end{equation}
+
 \section{Representations of \texorpdfstring{$D^{1}(2,1;\alpha)$}{D(2,1,a)}} \label{app:d21a}

### 2023-06-20 Draft_3dH3.tex
Modifications by Emanuel and Michele.

@@
 
-\EM{To do:
-\begin{itemize}
-	\item Periodicity $4\pi$ or $2\pi$
-	\item Mention lack of higher-dimensional origin for Berg and Samtleben
-	\item Comment earlier on uplift of 6d gSUGRA
-	\item Add references to introduction
-	%\item Complex geometry of moduli space?
-	%\item Compare with classification known in literature, \textit{e.g.} in IIA (and IIB -- Jerome's story)
-	\item Email DW and MP to ask who we should cite for \eqref{eq:Twisting}
-\end{itemize}
-}
-
 \section{Introduction}
@@
 Not only does this mean that there are also heterotic versions of these vacua (preserving ${\cal N}=(4,0)$ supersymmetry), but also that they can be readily studied via the string worldsheet CFT \cite{Maldacena:2000hw,Eberhardt:2018ouy,Eberhardt:2019niq,Eberhardt:2019ywk}.
-%\EM{Cut?} Moreover, the string sigma model in these vacua is also integrable \cite{}.
-Finally, the AdS$_3$/CFT$_2$ correspondence has seen much progress recently, with many new holographic duals being established \cite{}.
 
@@
 As a by-product, we find a constraint that must be obeyed by the embedding tensor of any 3-dimensional gauged supergravity that can be uplifted to 10-/11-dimensional supergravity.
-This allows to prove the lack of a higher-dimensional origin of some 3-dimensional gaugings, as we illustrate on an example.
-\EM{update}
+This allows to prove the lack of a higher-dimensional origin of some 3-dimensional gaugings, as we illustrate for an example.
+\EM{HERE}
 
@@
 Using this truncation, we study the moduli space of the AdS$_3$ vacua in section \ref{s:Moduli}, before concluding in section \ref{s:Conclusions}.
-We end the paper by an example in appendix~\ref{app:rulingoutgauging} of how to check if a three-dimensional supergravity can be uplifted, a review of the construction of consistent truncations on $S^{3}$ in appendix~\ref{s:SLn} and a discussion of the $D^{1}(2,1;\alpha)$ supermultiplets in appendix~\ref{app:d21a}.
+We end the paper by an example in appendix~\ref{app:rulingoutgauging} of how to rule out a higher-dimensional origin for a three-dimensional supergravity \EM{HERE}, a review of the construction of consistent truncations on $S^{3}$ in appendix~\ref{s:SLn} and a discussion of the $D^{1}(2,1;\alpha)$ supermultiplets in appendix~\ref{app:d21a}.
 
@@
 	\begin{split}
-		\xi_{\fl{M}} %&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\fl{M}}{}^{N} \\
+		\xi_{\fl{M}} 
 		&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1} - \rho^{-1}\, \Gamma_{\ov{N}\ov{M}}{}^{\ov{N}} \,.
@@
 As a result, in that case, the bosonic $\En{9}$ ExFT \cite{Bossard:2018utw,Bossard:2021jix} provides the only currently accessible route for computing the gauged supergravity potential.}, but the potential is crucial for finding vacua of the three-dimensional theory and uplifting these in the later parts of this paper.
-
-% In addition, we derive a necessary condition for the embedding tensor to arise from a compactification of higher-dimensional supergravity and illustrate it on an example.
-% \subsection{Expression of the potential in terms of the embedding tensor}
 
@@
 		-V &= X_{\fl{MN}}X_{\fl{PQ}}\left(\alpha\,\M^{\fl{MP}}\M^{\fl{NQ}}+\beta\,\M^{\fl{MP}}\eta^{\fl{NQ}}+\delta\,\eta^{\fl{MP}}\eta^{\fl{NQ}}
-		%+\gamma\,\eta^{\fl{MN}}\eta^{\fl{PQ}}
 		\right) \\
@@
 		&\ \quad +2\,\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma^{\fl{K}}{}_{\fl{N}}+\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\,\Gamma_{\fl{N}}{}^{\fl{K}}+\left(-12\,\alpha+2\,\delta
-		%-(62)^2\,\gamma
 		\right)\,\Gamma_{\fl{MN}}\,\Gamma^{\fl{MN}}\\
@@
 \begin{equation}
-	\alpha = \frac{1}{28}\,,\quad \beta = \frac{1}{2}\,, \quad \delta=\frac{13}{28}\,, \quad a=1 \,. %, \quad \gamma=0.
-\end{equation}
-%\CE{Freedom for $\delta$ and $\gamma$: $2\delta-(62)^2\gamma=\rho^{2}(1/2+3/7)$.}
-%\EM{MG and EM are confused about this -- we need to chat all together}
-
-%\CE{Some formula used to derive the previous equations:
-%\begin{equation}
-%	\begin{aligned}
-%		\M^{\fl{MP}}\M^{\fl{NQ}}f_{\fl{PQ}}{}^{\fl{K}}&=-f^{\fl{MN}}{}_{\fl{L}}\,\M^{\fl{LK}},\\
-%		{\rm Ad\ invariance:}\quad 2\,\Gamma_{\fl{K}[\fl{M}}{}^{\fl{L}}\,f_{\fl{N}]\fl{L}}{}^{\fl{P}}&= -f_{\fl{MN}}{}^{\fl{L}}\,\Gamma_{\fl{KL}}{}^{\fl{P}}\,,\\
-%		{\rm No\ trombone:}\quad \UI_{\fl{M}}{}^{M}\partial_{M}\ln(\rho)&= -\frac{1}{2}\,\Gamma_{\fl{KM}}{}^{\fl{K}},\\
-%		{\rm Eq.~\eqref{eq:sectionconstraints}}\ \implies \ f^{\fl{K}}{}_{\fl{MP}}f^{\fl{PL}}{}_{\fl{N}}\,\partial_{\fl{K}}\otimes\partial_{\fl{L}} &= 2\,\partial_{(\fl{M}}\otimes\partial_{\fl{N})}\,.
-%	\end{aligned}
-%\end{equation}
-%}
-
-% Consider a twist matrix $U_{\bar M}{}^{M}$ and a scale factor $\rho$. A consistent truncation requires that the objects
-% \begin{equation} \label{eq:DoubleU}
-% 	\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}}) \,, \qquad \Sigma_{\fl{M}\,M} = \frac{1}{60} \rho^{-1} f_{\fl{M}}{}^{\fl{N}\fl{P}}\, U_{\fl{N}\,P} \partial_M U_{\fl{P}}{}^{P} \,, \qquad \cU_{\fl{M}}{}^M = \rho^{-1} U_{\fl{M}}{}^M \,,
-% \end{equation}
-% satisfy the differential condition
-% \begin{equation} \label{eq:GenLeibniz}
-% 	\gL_{\ff{U}_{\fl{M}}} {\cU}_{\fl{N}}{}^M = X_{\fl{M}\fl{N}}{}^{\fl{P}}\, \cU_{\fl{P}}{}^M \,,
-% \end{equation}
+	\alpha = \frac{1}{28}\,,\quad \beta = \frac{1}{2}\,, \quad \delta=\frac{13}{28}\,, \quad a=1 \,. 
+\end{equation}
 
@@
 \end{equation}
-with the potential%\footnote{To obtain this potential, one has to add the total derivative $-\partial_{M}\left(\sqrt{\vert g\vert}\,\partial_{N}\M^{MN}+(4/3)\,\M^{MN}\partial_{N}\sqrt{\vert g\vert}\right)$ to $\sqrt{\vert g\vert}\,\mathscr{L}_{\rm int}$.}
+with the potential
 \begin{equation} \label{eq:3dpotential}
@@
 As in higher dimensions, $X_{\ov{M}\ov{N}}$ obtained from \eqref{eq:GenLeibniz} automatically satisfies the linear constraint of the 3-dimensional maximal gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv}, and the section condition implies the quadratic constraints for $X_{\ov{M}\ov{N}}$.
-
-%\subsection{Relating $\tr( X^2)$ and $(\tr X) ^2$ using $\xi$}
-%One can square eq.~\eqref{eq:symembeddingtensor} to derive an expression for $X_{\ov{MN}}X^{\ov{MN}}$ in terms of the current $\Gamma$, we find 
-%\begin{equation}\label{eq:XXwitheta}
-%	X_{\ov{MN}}X^{\ov{MN}}=21\rho^{-2}\Gamma_{\ov{MN}}\Gamma^{\ov{NM}}+19\rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\right)^2.
-%\end{equation}
-%Similarly, squaring the trombone tensor $\xi$ gives 
-%\begin{equation}\label{eq:xixiwitheta}
-%	\xi_{\ov M}\xi^{\ov M}=\rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\Gamma_{\ov N}{}^{\ov N}+\Gamma_{\ov{MN}}\Gamma^{\ov{NM}}\right),
-%\end{equation}
-%we can then deduce
-%\begin{equation}
-%	X_{\ov{MN}}X^{\ov{MN}}=21	\xi_{\ov M}\xi^{\ov M}-2\rho^{-2}\left(\Gamma_{\ov M}{}^{\ov M}\right)^2
-%\end{equation}
-%which can be expressed entirely in terms of $X$ after tracing eq.~\eqref{eq:symembeddingtensor}:
-%\begin{equation}\label{eq:reltrX}
-%		X_{\ov{MN}}X^{\ov{MN}}=21	\xi_{\ov M}\xi^{\ov M}-\frac1{1922}\left(X_{\ov M}{}^{\ov M}\right)^2. 
-%\end{equation}
-%Whenever $\xi=0$, eq.~\eqref{eq:reltrX} is a constraint on the embedding tensor of the resulting three dimensional supergravity which does not arise from the quadratic constraint.
-To see this, simply observe that the theory with $\En{8}$ gauging constructed in \MG{REFERENCE}, has $X_{\ov{MN}}=\eta_{\ov{MN}}$, violating~\eqref{eq:reltrX}.
-\\
-%Since we used the Scherk-Schwarz Ansatz in the calculation, we deduce that this must in fact be a condition satisfied by any theory that comes from type II or 11 dimensional supergravity.
-For example \MG{$\SO{4}\times \SO{4}$ gauging ...}
 
@@
 This motivates the following question: Given a consistent truncation, \textit{i.e.} $\cU_{\fl{M}}{}^M$, satisfying \eqref{eq:GenLeibniz}, when can we add a new flux component of string theory to the compactification to obtain a new consistent truncation?
-Adding a new flux component to the truncation is equivalent to twisting the generalised frame as follows %\EM{Email DW and MP to ask who we should cite for this?}
+Adding a new flux component to the truncation is equivalent to twisting the generalised frame as follows
 \begin{equation} \label{eq:Twisting}
@@
 We denote by $U_A{}^{\ov{A}}$ the $\SO{3,3}$ twist matrix corresponding to the $S^3$ truncation constructed in \cite{Lee:2014mla,Baguet:2015iou} and obtained from \eqref{eq:SLnFrame}, \eqref{eq:rho}, \eqref{eq:SLnTwist}.
-Then, we can add a 3-form potential by twisting with the $\SO{4,4}$ generator \CE{(Sure here?)}
+Then, we can add a 3-form potential by twisting with the $\SO{4,4}$ generator
 \begin{equation} \label{eq:C2S3example}
@@
 explicitly using \eqref{eq:C2S3example} and setting $C^i = \rho^{-1}\,\lambda\, \xi^i$, with $\nabla_i \xi^i = 1$, in the notation of \cite{Eloy:2021fhc}, we obtain precisely the twist matrix used in \cite{Eloy:2021fhc} for the consistent truncation of 6-dimensional ${\cal N}=(1,1)$ supergravity on $S^3$ with $H_3$ flux.
-%\EM{Give precise form of $C^i$ such that we recover $\lambda$?}
-
-%\EM{Spell out this as an example of the method}\\
-%In fact, the consistent truncation of AdS$_3 \times S^3$ constructed in \cite{Eloy:2021fhc} can be understood exactly as arising in this way: it utilises the generalised parallelisability of $S^3$ with $U_M{}^A \in \SL{4} \simeq \SO{3,3}$ twist matrices but then adds a volume flux to the $S^3$ which is a singlet of $\SL{4}$ to obtain a new twist matrix via \eqref{eq:Twisting} which lives in $\SO{4,4}$.
-\EM{Should mention that this is a subsector of the $\SO{4,8}$ setup there?}
 We will now follow this same procedure in the next section to obtain the consistent truncation of IIB supergravity on $S^3 \times S^3 \times S^1$ with 7-form flux.
@@
 As explained in \cite{Galli:2022idq}, we can construct a consistent truncation on $M \times S^1$ to 3-dimensional gauged supergravity by embedding a consistent truncation on $M$ to 4-dimensional supergravity, characterised by an $\En{7}$ twist matrix and $\En{7}$ scalar density $\sigma$, as well as
-%as follows. The $\EE$ twist matrix is parameterised by the $\En{7}$ twist matrix describing the consistent truncation on $M$ and 
 the $\SL{2}$ twist matrix given by
@@
 \subsubsection{Adding flux} \label{s:AddFluxS3S3S1}
-%We now wish to add a 7-form flux to the $S^3 \times S^3 \times S^1$ truncation constructed above.
+
 To add a 7-form flux to the above truncation, we need to determine whether the 7-form flux is stabilised by the twist matrix on $S^3 \times S^3 \times S^1$ constructed in section \ref{s:S3S3S1}.
-Thus, we need to understand
-%the group theory underlying the consistent truncation on $S^3 \times S^3$ \cite{Inverso:2016eet}.
-The $\En{7}$ twist matrix describing this truncation is constructed from two $\SL{4}$ twist matrices, one for each $S^3$ similar to \ref{s:S3Flux}, via the decomposition
-%\begin{equation}
-%	\En{7} \rightarrow \SL{8} \rightarrow \SL{4} \times \SL{4} \times \mathbb{R}^+ \,,
-%\end{equation}
-%under which the fundamental of $\En{7}$ branches as
-%\begin{equation}
-%	\mathbf{56} \rightarrow \mathbf{28} \oplus \overline{\mathbf{28}} \rightarrow \left[ \mathbf{\left(6,1\right)_2} \oplus \mathbf{\left(1,6\right)_{-2}} \oplus \mathbf{\left(4,4\right)_0} \right] \oplus \left[ \mathbf{\left(6,1\right)_{-2}} \oplus \mathbf{\left(1,6\right)_{2}} \oplus \mathbf{\left(\overline{4},\overline{4}\right)_0} \right] \,,
-%\end{equation}
-%where the first square brackets denote the branching of the $\mathbf{28}$ under $\SL{4} \times \SL{4} \times \mathbb{R}^+$ and the second square brackets that of the $\mathbf{\overline{28}}$.
-%We want to see if 
-whether IIB supergravity admits a 7-form field strength that is a singlet under the two $\SL{4}$ groups in \eqref{eq:SL4Embedding}.
+Thus, we need to understand whether IIB supergravity admits a 7-form field strength that is a singlet under the two $\SL{4}$ groups in \eqref{eq:SL4Embedding}.
 To answer this question, we pick a gauge where the 6-form potential lives entirely in $S^3 \times S^3$ but depends on the $S^1$ coordinate, $z$.
@@
 
-% \EM{Give embedding tensor components wrt the 3-d basis used for the moduli}\\
-% \EM{Vacuum condition for $\lambda$}\\
-% \EM{SUSY AdS$_3$ vacuum in 10-d}
-
-%, which transform under the subgroup $\SL{6} \times \SL{2} \times \mathbb{R}^+_{IIB} \subset \En{7}$ as $\mathbf{\left(1,2\right)_{6}} \subset \mathbf{133}$
-
-%\EM{Describe how $C_6{}^\alpha$ sits in here}
-
 \section{Moduli of \texorpdfstring{AdS$_3 \times S^3 \times S^3 \times S^1$}{AdS3xS3xS3xS1}} \label{s:Moduli}
@@
 
-% \paragraph{S-fold like deformations} Scalar spectrum:
-% \begin{equation}
-% 	\begin{aligned}
-% 		(m_{(0)}\ell_{\rm AdS})^2:	\quad 
-% 		&8\ [1],\quad \frac{4\,\chi_{1}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{4\,\chi_{2}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{(\chi_{1}+\chi_{2})^{2}}{1+\alpha^{2}}\ [4], \quad \frac{(\chi_{1}-\chi_{2})^{2}}{1+\alpha^{2}}\ [4],	\\
-% 		&\frac{4\,\alpha^{2}\ts{\chi}_{1}^{2}}{1+\alpha^{2}}\ [2], \quad \frac{4\,\alpha^{2}\ts{\chi}_{2}^{2}}{1+\alpha^{2}}\ [2], \quad \alpha^{2} \frac{(\ts{\chi}_{1}+\ts{\chi}_{2})^{2}}{1+\alpha^{2}}\ [4], \quad \alpha^{2} \frac{(\ts{\chi}_{1}-\ts{\chi}_{2})^{2}}{1+\alpha^{2}}\ [4],	\\
-% 		& \frac{\left(\chi_{1} + \chi_{2} \pm \alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2})\right)^{2}}{1+\alpha^{2}}\ [2+2], \quad \frac{\left(\chi_{1} - \chi_{2} \pm \alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2})\right)^{2}}{1+\alpha^{2}}\ [2+2],\\
-% 		&1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-% 		&1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-% 		&1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-% 		&1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{1}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-% 		&1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-% 		&1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{1}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-% 		&1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}-\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2], \\
-% 		&1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}} \pm 2\,\sqrt{1+\frac{\left(\chi_{2}+\alpha\,\ts{\chi}_{2}\right)^{2}}{1+\alpha^{2}}}\ [2+2].
-% 	\end{aligned}
-% \end{equation}
-
 \subsection{Moduli in 10 dimensions}
@@
 Therefore, here we will instead focus on a few interesting subsets of deformations.
-
-%In all cases, the internal seven form flux is unaffected by the deformations, i.e. $H_{(3)}\vert_{AdS_3}$ remains unchanged, so that we will not give it explicitly below.
 
@@
 	\begin{split}
-		\left(\pm1,\pm1;0,0\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(%2\pi n +
+		\left(\pm1,\pm1;0,0\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(
 		\chi_{1}+\chi_{2}+\alpha\,\big(\ts{\chi}_{1}-\ts{\chi}_{2}\big)\right)^{2}}{4\, e^{2\psi}\, (1+\alpha^{2})}}\,, \\
-		\left(\pm1,\mp1;0,0\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(%2\pi n +
+		\left(\pm1,\mp1;0,0\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(
 		\chi_{1}+\chi_{2}-\alpha\,\big(\ts{\chi}_{1}-\ts{\chi}_{2}\big)\right)^{2}}{4\, e^{2\psi}\, (1+\alpha^{2})}}\,, \\
-		\left(0,0;\pm1,\pm1\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(%2\pi n +
+		\left(0,0;\pm1,\pm1\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(
 		\chi_{1}-\chi_{2}+\alpha\,\big(\ts{\chi}_{1}+\ts{\chi}_{2}\big)\right)^{2}}{4\, e^{2\psi}\, (1+\alpha^{2})}}\,, \\
-		\left(0,0;\pm1,\mp1\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(%2\pi n + 
+		\left(0,0;\pm1,\mp1\right):\quad \Delta=\frac{1}{2}+\sqrt{1 + \frac{\left(
 		\chi_{1}-\chi_{2} - \alpha\,\big(\ts{\chi}_{1}+\ts{\chi}_{2}\big)\right)^{2}}{4\, e^{2\psi}\, (1+\alpha^{2})}}\,.
@@
 	\begin{equation} \label{eq:N2}
-		\chi_{2} = \chi_{1} \pm\alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2})% + 2\pi k 
-		\quad {\rm or}\quad \chi_{2} = -\chi_{1} \pm\alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2})% + 2\pi k \,, \qquad k \in \mathbb{Z}
+		\chi_{2} = \chi_{1} \pm\alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2})
+		\quad {\rm or}\quad \chi_{2} = -\chi_{1} \pm\alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2}) \mathbb{Z}
 		\,,
@@
 		\begin{cases}
-			\chi_{2} = \chi_{1}\,,\\% + 2\pi k\,,\\
-			\ts{\chi}_{2} = -\ts{\chi}_{1}\,,% + 2\pi l / \alpha \,,
+			\chi_{2} = \chi_{1}\,,\\
+			\ts{\chi}_{2} = -\ts{\chi}_{1}\,,
 		\end{cases}
@@
 		\begin{cases}
-			\chi_{2} = - \chi_{1}\,,\\% + 2\pi k\,,\\
-			\ts{\chi}_{2} = \ts{\chi}_{1}\,,% + 2\pi l / \alpha \,,
-		\end{cases}% \qquad k, l \in \mathbb{Z} \,,
+			\chi_{2} = - \chi_{1}\,,\\
+			\ts{\chi}_{2} = \ts{\chi}_{1}\,,
+		\end{cases}
 	\end{equation}
@@
 		\begin{cases}
-			\ts{\chi}_{1} = \pm \chi_{1}/\alpha\,,\\% + 2\pi k \,,\\
-			\ts{\chi}_{2} = \mp \chi_{2}/\alpha\,,% + 2\pi l\,,
+			\ts{\chi}_{1} = \pm \chi_{1}/\alpha\,,\\
+			\ts{\chi}_{2} = \mp \chi_{2}/\alpha\,,
 		\end{cases}
@@
 		\begin{cases}
-			\ts{\chi}_{1} = \pm \chi_{2}/\alpha\,,\\% + 2\pi k\,,\\
-			\ts{\chi}_{2} = \mp \chi_{1}/\alpha\,,% + 2\pi l\,,
-		\end{cases}% \qquad k, l \in \mathbb{Z} \,,
+			\ts{\chi}_{1} = \pm \chi_{2}/\alpha\,,\\
+			\ts{\chi}_{2} = \mp \chi_{1}/\alpha\,,
+		\end{cases}
 	\end{equation}
@@
 		\begin{cases}
-			\chi_{2} = \chi_{1}\,,\\% + 2\pi k\,,\\
-			\ts{\chi}_{1} = %\left(
-			\pm \chi_{1}% + 2 \pi l \right)
+			\chi_{2} = \chi_{1}\,,\\
+			\ts{\chi}_{1} = 
+			\pm \chi_{1}
 			/\alpha\,,\\
-			\ts{\chi}_{2} = %\left(
-			\mp \chi_{1}% + 2 \pi m \right)
+			\ts{\chi}_{2} = 
+			\mp \chi_{1}
 			/\alpha\,,
@@
 		\begin{cases}
-			\chi_{2} = -\chi_{1}\,,\\% + 2\pi k\,,\\
-			\ts{\chi}_{1} = %\left(
-			\pm \chi_{1}% + 2 \pi l\right) 
+			\chi_{2} = -\chi_{1}\,,\\
+			\ts{\chi}_{1} = 
+			\pm \chi_{1}
 			/\alpha\,,\\
-			\ts{\chi}_{2} = %\left(
-			\mp \chi_{1}% + 2\pi m \right)
+			\ts{\chi}_{2} = 
+			\mp \chi_{1}
 			/\alpha\,,
-		\end{cases}% \qquad k, l, m \in \mathbb{Z} \,,
+		\end{cases}
 	\end{equation}
@@
 
-% \paragraph{\boldmath $(\zeta,\ts{\zeta},\psi)$}
-% Again with spherical coordinates:
-% \begin{equation}
-% 	\begin{split}
-% 		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) -\Delta\,\d z^{2}\\
-% 		&+ \alpha^{2}\Big[\d\theta^{2} + \Delta\left(\cos^{2}(\theta)\,\d\phi_{1}^{2}+\sin^{2}(\theta)\,\d\phi_{2}^{2}\right)\Big]+\d\ts{\theta}^{2} + \Delta\left(\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}^{2}+\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}^{2}\right)\\
-% 		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
-% 		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
-% 		&-2\,\alpha\,\Delta\,e^{2\psi}\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
-% 		&+\Delta\,e^{2\psi}\,\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\\
-% 		&+\Delta\,e^{2\psi}\,\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2},
-% 	\end{split}
-% \end{equation}
-% with the warp factor
-% \begin{equation}
-% 	\Delta^{-1} = 1+e^{2\psi}\left(\zeta_{1}^{2}\sin^{2}(\theta)+\zeta_{2}^{2}\cos^{2}(\theta)+\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})+\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})\right)\,.
-% \end{equation}
-
-% \paragraph{\boldmath $(\zeta,\ts{\zeta},\Omega,\ts{\Omega})$}
-% Again with spherical coordinates:
-% \begin{equation}
-% 	\begin{split}
-% 		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) -\Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\,\d z^{2}\\
-% 		&+ \alpha^{2}\Big[\d\theta^{2} + \Delta\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big(e^{\Omega}\cos^{2}(\theta)\,\d\phi_{1}^{2}+\sin^{2}(\theta)\,\d\phi_{2}^{2}\Big)\Big]\\
-% 		&+\d\ts{\theta}^{2} + \Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}^{2}+e^{\ts{\Omega}}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}^{2}\Big)\\
-% 		&+\Delta\,e^{\Omega}\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,e^{\ts{\Omega}}\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
-% 		&+\Delta\,e^{\Omega+\ts{\Omega}}\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
-% 		&-2\,\alpha\,\Delta\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+e^{\Omega}\,\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(e^{\ts{\Omega}}\,\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
-% 		&+\Delta\,\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big[\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+e^{\Omega}\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\Big]\\
-% 		&+\Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big[e^{\ts{\Omega}}\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2}\Big],
-% 	\end{split}
-% \end{equation}
-% with the warp factor
-% \begin{equation}
-% 	\begin{aligned}
-% 	\Delta^{-1} &= \Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\\
-% 	&+\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\\
-% 	&+\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right).
-% 	\end{aligned}
-% \end{equation}
-
 \paragraph{\boldmath $(\zeta,\ts{\zeta},\Omega,\ts{\Omega},\psi)$}
@@
 \end{equation}
-We can also provide an expression for $H_3$ in the simplified case where $\Omega=\tilde\Omega=0$. It is convenient to first define some forms. \CE{(Work on this.)}
+We can also provide an expression for $H_3$, and we will do so here in the simplified case where $\Omega=\tilde\Omega=0$ \EM{HERE}.
+It is convenient to first define some forms.
+We will denote by $\star$ and $\star_0$ the hodge star operators on the deformed and undeformed $S^3$'s respectively.
+\CE{(Work on this.)}
 \begin{equation}\label{eq:forms}
 	\begin{split}
-		Z(\theta,u,v,w)&=2+2e^{2\psi}(u^2\sin^2(\theta)+v^2\cos^2(\theta)+w^2)\\
-		\gamma&=4\sin(\tilde\theta)\cos(\tilde \theta)(\tilde{\zeta}_1^2-\tilde{\zeta}_2 ^2)\left(\zeta_2\cos^2(\theta)\d \phi _1+\zeta _1\sin^2(\theta)\d\phi _2\right)\\
-		\kappa_{ij}&=2\sin (\theta) \cos (\theta) Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_i)\zeta_j\d\phi_i\\
-		\omega_{ij} &=2\sin(\tilde\theta) \cos(\tilde\theta) Z(\theta,\zeta_1,\zeta_2,\tilde\zeta _i)\d \tilde \phi _i\wedge \left [(\zeta _1\tilde \zeta _j + \tilde \zeta _i \zeta _2)\cos^2 (\theta) \d \phi_1+ (\zeta _1\tilde \zeta _i + \tilde \zeta _j \zeta _2)\sin^2(\theta)  \d \phi_2\right]\\
-		\Theta&=(\zeta _1^2-\zeta_2 ^2)(\tilde{\zeta}_1 ^2-\tilde \zeta _2^2)\sin(\tilde\theta) \cos (\tilde\theta) \sin (2 \theta) ^2\d\tilde \theta\wedge\d \phi _1\wedge\d   \phi _2
+		Z(\theta,u,v,w)&=2+2e^{2\psi}(u^2\sin \theta^2+v^2\cos \theta^2+w^2)\\
+		\gamma&=4\sin\tilde\theta\cos\tilde \theta(\tilde{\zeta}_1^2-\tilde{\zeta}_2 ^2)\left(\zeta_2\cos \theta ^2\d \phi _1+\zeta _1\sin\theta ^2\d\phi _2\right)\\
+		\sigma&=2\left(	Z(\tilde\theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_2)\zeta_1\cos \theta ^2\d \phi _1+\zeta _2\sin\theta ^2Z(\tilde\theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_1)\d\phi _2\right)\\
+		\omega_{ij} &=2\sin\tilde\theta \cos\tilde\theta Z(\theta,\zeta_1,\zeta_2,\tilde\zeta _i)\d \tilde \phi _i\wedge \left [(\zeta _1\tilde \zeta _j + \tilde \zeta _i \zeta _2)\cos \theta ^2 \d \phi_1+ (\zeta _1\tilde \zeta _i + \tilde \zeta _j \zeta _2)\sin \theta ^2 \d \phi_2\right]\\
+		\Theta&=(\zeta _1^2-\zeta_2 ^2)(\tilde{\zeta}_1 ^2-\tilde \zeta _2^2)\sin(2\tilde\theta ) \sin (2 \theta)\d\tilde \theta\wedge(\star_0\d\theta)
 	\end{split}
@@
 \begin{equation}\label{eq:omegagamma}
-	\kappa = \epsilon^{ij}\kappa_{ij},\quad \omega=\epsilon^{ij}\omega _{ij}.
+ \omega=\epsilon^{ij}\omega _{ij}.
 \end{equation}
@@
 	\begin{split}
-		H_(3)=&\Delta^2\alpha^2\sin(\theta) \cos (\theta) Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_1) Z(\tilde \theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_2)\d \theta\wedge\d\phi_1\wedge\d\phi _2\\
-		&+\Delta^2\sin(\tilde\theta) \cos (\tilde\theta) Z(\theta,\zeta_1,\zeta_2,\tilde{\zeta}_1) Z( \theta,\zeta_1,\zeta_2,\tilde{\zeta}_2)\d \tilde\theta\wedge\d\tilde{\phi}_1\wedge\d\tilde{\phi} _2\\
-		&+e^{2\psi}\alpha\Delta^2\left(\omega\wedge\d \tilde\theta+\tilde\omega\wedge\d \theta\right)+e^{4\psi}\Delta^2\alpha ^2\left(\Theta +\frac 1{\alpha^2}\tilde \Theta \right)\\
-		&+\Delta^2e^{2\psi}\alpha\left(\d \theta\wedge \kappa +\frac 1{\alpha}\d \tilde \theta \wedge \tilde \kappa\right)\wedge\d\psi+e^{4\psi}\alpha\Delta^2\left(\d\tilde \theta \wedge \gamma +\frac 1{\alpha}\d \theta\wedge\tilde\gamma\right)\wedge\d\psi.
+		H_3=&\frac1 \alpha(\star_0 vol_{S^3})vol_{S^3}+(\tilde{\star}_0vol_{\tilde{S^3}})vol_{\tilde{S}^3}\\
+		&+e^{2\psi}\alpha\Delta^2\left(\omega\wedge\d \tilde\theta+\tilde\omega\wedge\d \theta\right)
+		+e^{4\psi}\Delta^2\alpha \left(\Theta +\frac 1{\alpha}\tilde \Theta \right)\\
+		&+\Delta^2e^{2\psi}\left(\star_0\sigma+\tilde{\star}_0\tilde\sigma \right)\wedge\d\psi
+		-e^{4\psi}\alpha\Delta^2\left(\d\tilde \theta \wedge \gamma +\frac 1{\alpha}\d \theta\wedge\tilde\gamma\right)\wedge\d\psi.
 	\end{split}
@@
 \end{equation}
-%\CE{(Expression of $H$?)}
 
@@
 with ${\cal N}=(4,0)$ (or $(0,4)$) and symmetry enhancement to ${\rm SO}(4)\times{\rm U}(1)^{2}$. There seems to be no other points with (super)-symmetry enhancement in the scalar manifold.
-
-%
-%\paragraph{SUSY deformation}
-%
-%%In Hopf coordinates:
-%%\begin{equation}
-%%	\begin{split}
-%%		ds^2 &= \alpha^2 \left[ ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
-%%		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{\CE{-}(1-e^{2\omega})} d\psi \,, \\
-%%		d\sigma &= vol_{\mathbb{CP}^1} \,.
-%%	\end{split}
-%%\end{equation}
-%
-%It is convenient to use the Hopf fibration to describe this, we denote by $\phi$ the coordinate on the $S^1$ fibre and by $\xi$ the homogeneous coordinate on $\mathbb{CP}^1$.
-The round metric on $S^3$ then reads
-%\begin{equation}
-%	g= \mathrm{d}s^2_{\mathbb{CP}^1} + (\sigma + \mathrm{d}\phi)^2
-%\end{equation}
-%where 
-%\begin{equation}
-%	\begin{split}
-%		\mathrm{d}s^2_{\mathbb{CP}^1} &= \frac1{(1+|\xi|^2)^2}\mathrm{d}\xi\,\mathrm{ d}\ov{\xi}\\
-%		\sigma&=\frac{i}{2(1+|\xi|^2)}(\xi \mathrm{d} \ov{\xi}-\ov{\xi}\mathrm{d}\xi)\\ 
-%		vol_{S^3}&=vol_{\mathbb{CP}^1}\wedge \mathrm{d}\psi .
-%	\end{split}
-%\end{equation}
-%The deformation does not affect $S_+^3$, but it mixes the $S^1$ factor in the internal space with the Hopf fibre of $S_-^3$. It is parametrised by a real number $\Omega$, such that the metric reads
-%\begin{equation}
-%	\begin{split}
-%		\mathrm{d}s^2 &= \alpha^2(\mathrm{d}s^2_{\mathbb{CP}^1}+\kappa^2) + \mathrm{d}s^2_{S_+^3} + e^{-4\Omega}\mathrm{d}\psi^2\\
-%		\kappa &= \mathrm{d}\phi + \sigma - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi.
-%	\end{split}
-%\end{equation}
-% The three form flux gets changed according to the prescription $\d\phi \rightarrow \d\phi -  \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d \psi$ and we find:
-%\begin{equation}
-%	H_{(3)}=\alpha^2vol_{\mathbb{CP}^1}\wedge (\d\phi - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi) + vol_{S_+^3}.
-%\end{equation}
-%
-%%
-%%In spherical coordinates:
-%%\begin{equation}
-%%	\begin{aligned}
-%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+\alpha^{2}\,\d s^2\left(S^{3}_{-}\right) +e^{-2\omega}\,\d\psi^{2}\\
-%%		&\quad+2\,\alpha\,e^{-2\omega}\,\sqrt{-1+e^{2\omega}}\left(-\cos^{2}(\theta)\,\d\varphi_{1}+\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi\\[5pt]
-%%		&= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+e^{-4\omega}\,\d\psi^{2}\\
-%%		&\quad+\alpha^{2}\bigg[\d \theta^2+\cos^{2}(\theta)\left(\d\varphi_{1}-\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}+\sin^{2}(\theta)\left(\d\varphi_{2}+\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}\bigg] ,\\[5pt]
-%%		\d s^2\left(S^{3}_{-}\right) &= \d\theta^{2}+\cos^{2}(\theta)\,\d\varphi_{1}^{2}+\sin^{2}(\theta)\,\d\varphi_{2}^{2}.
-%%	\end{aligned}
-%%\end{equation}
-%
-%\paragraph{Non-SUSY deformation}
-%Here we study a more general deformation depending on three parameters $\Omega$, $\zeta_{1,8}$ and $\zeta_{2,3}$.
-It is convenient to write down the uplift in terms of the Hopf coordinates on $S_-^3$, while again $S_+^3$ is not deformed.\\
-%\noindent For the metric we find
-%%\begin{equation}
-%%	\begin{aligned}
-%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-%%		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
-%%		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
-%%		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2}.\\[5pt]
-%%		\Delta^{-1} &= 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
-%%	\end{aligned}
-%%\end{equation}
-%\begin{equation}
-%	\begin{aligned}
-%		\d s^{2} &= \ell_{\rm AdS}^{2} \,\d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-%		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
-%		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
-%		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2},
-%	\end{aligned}
-%\end{equation}
-%where $\Delta$ is the warp factor
-%\begin{equation}
-%		\Delta^{-1} = 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
-%\end{equation}
-%The three-form flux is 
-%\begin{equation}
-%	H_{(3)}=vol_{S_-^3}+\alpha ^2\sin(\theta)\cos (\theta)(2+e^{2\Omega}\zeta^2_{1,8})(2e^{2\Omega}+\zeta_{2,3}^2)\Delta^2\mathrm{d}\theta\wedge\kappa_1\wedge\kappa_2,
-%\end{equation}
-%with the two one forms $\kappa_{1,2}$ defined by 
-%\begin{equation}
-%\begin{split}
-%		\kappa_1&=\mathrm{d}\phi_1-\frac{\zeta_{2,3}}{\alpha(2e^{2\Omega}+\zeta_{2,3}^2)}\mathrm{d}\psi \\
-%	\kappa_2&=\mathrm{d}\phi_2+ \frac{\zeta_{1,8}}{\alpha(2+e^{2\Omega}\zeta_{1,8}^2)}\mathrm{d}\psi.
-%\end{split}
-%\end{equation}
-%Note that setting $...$ recovers the supersymmetric deformation described earlier.
-%%In Hopf coordinates:
-%% \begin{equation}
-%% \begin{split}
-%% ds^2 &= \alpha^2 \left[ d\alpha_1^2 +  ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
-%% \kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
-%% d\sigma &= vol_{\mathbb{CP}^1} \,.
-%% \end{split}
-%% \end{equation}
-%% \begin{equation}
-%% 	\begin{aligned}
-%% 		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-%% 		&\quad + \Delta\,\alpha^{2}\bigg[\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm I}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm R}^{2}\Big)\,\d z_{\rm R}^{2}\\
-%% 		&\qquad\ \  + \frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm R}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm I}^{2}\Big)\,\d z_{\rm I}^{2}\\
-%% 		&\qquad\ \  + 2\,\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(-\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(2+\vert z\vert^{2}\right)+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d z_{\rm R}\d z_{\rm I}\\
-%% 		&\qquad\ \  +2\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\,\vert z\vert^{2}+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d\theta^{2}\bigg]\\
-%% 		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
-%% 		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
-%% 		\Delta^{-1} &= 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
-%% 	\end{aligned}
-%% \end{equation}
-%
-%%%%%
-%
-%%\begin{equation}
-%%	\begin{aligned}
-%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
-%%		&\quad + \frac{\alpha^{2}}{1+\gamma\,\vert z\vert^{2}}\bigg[\Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm I}^{2}\right)+\left(\gamma-1\right)\,z_{\rm R}^{2}\Big)\,\frac{\d z_{\rm R}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
-%%		&\qquad + \Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm R}^{2}\right)+\left(\gamma-1\right)\,z_{\rm I}^{2}\Big)\,\frac{\d z_{\rm I}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}} - 2\,\Big(1+\vert z\vert^{2}-\left(\gamma-1\right)\Big)\,\frac{\d z_{\rm R}\d z_{\rm I}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
-%%		&\qquad+2\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\left(\gamma+\vert z\vert^{2}\right)\d\theta^{2}\bigg]\\
-%%		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
-%%		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
-%%		\gamma &= \frac{2\,e^{2\Omega}+\zeta_{2,3}^{2}}{2+e^{2\Omega}\zeta_{1,8}^{2}},\qquad \Delta^{-1} = 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
-%%	\end{aligned}
-%%\end{equation}
 
@@
 
-%One interesting aspect that we observe is that the invariance of the KK spectrum under the shifts requires the inclusion of the $S^1$ direction.
-A subset of the $\chi_i$, $\ts{\chi}_i$ moduli, corresponding to the SUSY line $\chi_1 = \chi_2 = \chi$, $\ts{\chi}_i = 0$, was analysed in the half-maximal theory in \cite{Eloy:2021fhc}.
-The deformation $\chi$ is both non-compact in the 3-dimensional half-maximal gauged supergravity and in its 6-dimensional uplift, with no periodicity in $\chi$ observed in the KK spectrum of the 6-dimensional solution \cite{Eloy:2021fhc}.
-However, as we have shown, the full uplift to 10 dimensions compactifies the moduli space, thanks to the $S^1$ direction, which is often ignored in holographic applications \EM{Maybe forget this last sentence
-
 The compactification of the moduli space in 10 dimensions can also be understood geometrically.
@@
 Under this identification, the shifts \eqref{eq:ShiftSymmetries} correspond to $T$-transformations of the tori, which belong to the modular group $\SL{2,\mathbb{Z}}$, just as for AdS$_4 \times S^5 \times S^1$ \cite{Giambrone:2021zvp,Giambrone:2021wsm}.
-\CE{(Need to change here given $4\pi$ in \eqref{eq:ShiftSymmetries}?)}
+In fact, \eqref{eq:T2CStructure} only shows how the bosonic fields transform and thus suggests that the periodicities are $2\pi\alpha$ and $2\pi$.
+However, this is wrong: as the KK spectrum \eqref{eq:confdimshiftchi} shows, the fermions require double that periodicity, i.e.
+$4\pi\alpha$ and $4\pi$ as in \eqref{eq:ShiftSymmetries}.
+\EM{HERE}
 
@@
 This can be used to rule out the higher-dimensional origin of some 3-dimensional ${\cal N}=16$ gauged supergravities, as we illustrated in appendix~\ref{app:rulingoutgauging} on one ${\cal N}=(8,0)$ ${\rm AdS}_{3}$ vacuum of ref.~\cite{Deger:2019tem}.
-\EM{Mention if we actually use this.}
 
@@
 It would be interesting to understand universal features of these deformations and their CFT duals.
-Finally, we would like to use the tools developed here to study RG flows between solutions of three-dimensional supergravity, or equivalently between fixed points of a two-dimensional conformal field theory.
-Note however that this cannot be applied to the RG flow of ref.~\cite{Berg:2001ty}: their solution cannot be described using the generalized Scherk-Schwarz Ansatz of \EE exceptional field theory as reproducing their embedding tensor would require breaking the section constraint.
+Finally, we would like to use the tools developed here to study RG flows between solutions of three-dimensional supergravity, or equivalently between two-dimensional conformal field theories.
+Note however that this cannot be applied to the RG flow of ref.~\cite{Berg:2001ty}: their solution cannot be described using the generalized Scherk-Schwarz Ansatz of \EE or $\SO{8,8}$ exceptional field theory \EM{HERE} as reproducing their embedding tensor would require breaking the section constraint.
 We leave these questions for future work.
@@
 \section*{Acknowledgements}
-We are grateful to \EM{add others} Nikolay Bobev, Adolfo Guarino, Gabriel Larios, Yolanda Lozano, Niall Macpherson and Colin Sterckx for useful discussions and correspondence.
+We are grateful to Nikolay Bobev, Adolfo Guarino, Gabriel Larios, Yolanda Lozano, Niall Macpherson, Michela Petrini, Colin Sterckx and Dan Waldram for useful discussions and correspondence \EM{HERE}.
 CE is supported by the FWO-Vlaanderen through the project G006119N and by the Vrije Universiteit Brussel through the Strategic Research Program ``High-Energy Physics''.
@@
 \section{Ruling out gaugings} \label{app:rulingoutgauging}
-% \EM{Let's check the $\GL{6} \times \SO{2,2}$ gauging (half-maximal embedded in maximal)....}
-
-As mentioned in sec.~\ref{s:Potential}, eq.~\eqref{eq:reltrX} can be used to assess whether a given three-dimensional theory of embedding tensor $X_{\fl{MN}}$ has a higher-dimensional origin.
+\EM{Why do we refer to uplifting the solution here, rather than the theory?}
+
+As mentioned in section~\ref{s:Potential}, eq.~\eqref{eq:reltrX} can be used to assess whether a given three-dimensional theory of embedding tensor $X_{\fl{MN}}$ has a higher-dimensional origin \EM{HERE}.
 Let us illustrate that on the ${\cal N}=(8,0)$ ${\rm AdS}_{3}$ vacuum with $\GL{6} \times \SO{2,2}$ gauging constructed in ref.~\cite{Deger:2019tem}.
@@
 		\mathbf{248} &\longrightarrow \mathbf{120} \oplus \mathbf{128}\\
-		X^{\fl{M}} &\longrightarrow \left\{X^{[\fl{\sf IJ}]},X^{\fl{\sf A}}\right\},
+		X^{\fl{M}} &\longrightarrow \left\{X^{[\fl{\sf IJ}]},X^{\fl{\sf A}}\right\}\,,
 	\end{aligned}
@@
 	\begin{aligned}
-		X_{\fl{\sf IJ},\fl{\sf KL}} &= \Theta_{\fl{\sf IJ},\fl{\sf KL}},\\
-		X_{\fl{\sf AB}} &= -2\,\theta\,\eta_{\fl{\sf AB}}+\frac{1}{24}\,\Gamma^{\fl{\sf IJ},\fl{\sf KL}}_{\fl{\sf AB}}\,\Theta_{\fl{\sf IJKL}},\\
-		X_{\fl{\sf IJ},\fl{\sf A}} &=0,
+		X_{\fl{\sf IJ},\fl{\sf KL}} &= \Theta_{\fl{\sf IJ},\fl{\sf KL}}\,,\\
+		X_{\fl{\sf AB}} &= -2\,\theta\,\eta_{\fl{\sf AB}}+\frac{1}{24}\,\Gamma^{\fl{\sf IJ},\fl{\sf KL}}_{\fl{\sf AB}}\,\Theta_{\fl{\sf IJKL}}\,,\\
+		X_{\fl{\sf IJ},\fl{\sf A}} &=0\,,
 	\end{aligned}
@@
 \begin{align}
-  & \theta_{ij}=\delta_{ij}\;,\quad \theta_{\alpha\beta}=-3\,\delta_{\alpha\beta}\;,\quad \theta_{r_{+}s_{+}}=-\delta_{r_{+}s_{+}}\;,\quad \theta_{r_{-}s_{-}}=3\,\delta_{r_{-}s_{-}}\;,\nonumber\\
-  & \theta=-1\;,\quad \theta_{\alpha\beta r_{-}s_{-}} = -3\,\epsilon_{\alpha\beta}\,\epsilon_{r_{-}s_{-}}\;,\quad \theta_{ij r_{+}s_{+}} = 2\,\delta_{i[r_{+}}\,\delta_{s_{+}]j}\;,
+  & \theta_{ij}=\delta_{ij}\,,\quad \theta_{\alpha\beta}=-3\,\delta_{\alpha\beta}\,,\quad \theta_{r_{+}s_{+}}=-\delta_{r_{+}s_{+}}\,,\quad \theta_{r_{-}s_{-}}=3\,\delta_{r_{-}s_{-}}\,,\nonumber\\
+  & \theta=-1\,,\quad \theta_{\alpha\beta r_{-}s_{-}} = -3\,\epsilon_{\alpha\beta}\,\epsilon_{r_{-}s_{-}}\,,\quad \theta_{ij r_{+}s_{+}} = 2\,\delta_{i[r_{+}}\,\delta_{s_{+}]j}\,,
 \end{align}
-% \begin{align}
-%   & \theta_{ij}=4\,\delta_{ij}\;,\quad \theta_{\alpha\beta}=-12\,\delta_{\alpha\beta}\;,\quad \theta_{r_{+}s_{+}}=-4\,\delta_{r_{+}s_{+}}\;,\quad \theta_{r_{-}s_{-}}=12\,\delta_{r_{-}s_{-}}\;,\nonumber\\
-%   & \theta=-8\;,\quad \theta_{\alpha\beta r_{-}s_{-}} = -48\,\epsilon_{\alpha\beta}\,\epsilon_{r_{-}s_{-}}\;,\quad \theta_{ij r_{+}s_{+}} = 32\,\delta_{i[r_{+}}\,\delta_{s_{+}]j}\;,
-% \end{align}
+
 where we split the indices according to
@@
 		X^{\fl{\sf I}} & \ \tikz{\draw[arrows={->[scale=1.1]}] (0,0) -- (3.55
-	,0);}\ \left\{X^{i},\,X^{\alpha},\,X^{r_{+}},\,X^{r_{-}}\right\},
+	,0);}\ \left\{X^{i},\,X^{\alpha},\,X^{r_{+}},\,X^{r_{-}}\right\}\,,
 	\end{aligned}
@@
                 -1 & 0
-              \end{pmatrix}.
+              \end{pmatrix}\,.
 \end{equation}
@@
 \begin{equation}
-	X_{\ov{MN}}\,X^{\ov{MN}} = \frac{55}{1922}\left(X_{\ov M}{}^{\ov M}\right)^2,
-\end{equation}
-thus violating the condition~\eqref{eq:reltrX} (the trombone gauging vanishes for the solution).
+	X_{\ov{MN}}\,X^{\ov{MN}} = \frac{55}{1922}\left(X_{\ov M}{}^{\ov M}\right)^2\,,
+\end{equation}
+thus violating the condition~\eqref{eq:reltrX} (the trombone gauging vanishes for the truncation) \EM{HERE}.
 Then, we deduce that the ${\cal N}=(8,0)$ solution of ref.~\cite{Deger:2019tem} with gauging $\GL{6} \times \SO{2,2}$ does not admit a higher-dimensional origin as constructed with \EE exceptional field theory.
-This illustrate how the constraint~\eqref{eq:reltrX} can be used to determine if a given three-dimensional vacuum can be uplifted.
+This illustrates how the constraint~\eqref{eq:reltrX} can be used to determine if a given three-dimensional gauged supergravity can be uplifted.
+\EM{HERE}
 

### 2023-06-20 Draft_3dH3.tex
Corrections done with Michele and other possibility for H3.

@@
 This allows to prove the lack of a higher-dimensional origin of some 3-dimensional gaugings, as we illustrate for an example.
-\EM{HERE}
 
@@
 Using this truncation, we study the moduli space of the AdS$_3$ vacua in section \ref{s:Moduli}, before concluding in section \ref{s:Conclusions}.
-We end the paper by an example in appendix~\ref{app:rulingoutgauging} of how to rule out a higher-dimensional origin for a three-dimensional supergravity \EM{HERE}, a review of the construction of consistent truncations on $S^{3}$ in appendix~\ref{s:SLn} and a discussion of the $D^{1}(2,1;\alpha)$ supermultiplets in appendix~\ref{app:d21a}.
+We end the paper by an example in appendix~\ref{app:rulingoutgauging} of how to rule out a higher-dimensional origin for a three-dimensional supergravity, a review of the construction of consistent truncations on $S^{3}$ in appendix~\ref{s:SLn} and a discussion of the $D^{1}(2,1;\alpha)$ supermultiplets in appendix~\ref{app:d21a}.
 
@@
 \end{equation}
-We can also provide an expression for $H_3$, and we will do so here in the simplified case where $\Omega=\tilde\Omega=0$ \EM{HERE}.
+We can also provide an expression for $H_{(3)}$, and we will do so here in the simplified case where $\Omega=\tilde\Omega=0$.
 It is convenient to first define some forms.
 We will denote by $\star$ and $\star_0$ the hodge star operators on the deformed and undeformed $S^3$'s respectively.
-\CE{(Work on this.)}
 \begin{equation}\label{eq:forms}
@@
 \end{equation}
-In terms of the objects in \eqref{eq:forms} and \eqref{eq:omegagamma} we can write \CE{(Add AdS legs?)}
+In terms of the objects in \eqref{eq:forms} and \eqref{eq:omegagamma} we can write
 \begin{equation}\label{eq:defH3}
 	\begin{split}
-		H_3=&\frac1 \alpha(\star_0 vol_{S^3})vol_{S^3}+(\tilde{\star}_0vol_{\tilde{S^3}})vol_{\tilde{S}^3}\\
+		H_{(3)}=&2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})+\frac1 \alpha(\star_0 {\rm Vol}(S^3)){\rm Vol}(S^3)+(\tilde{\star}_0{\rm Vol}(\tilde{S^3})){\rm Vol}(\tilde{S}^3)\\
 		&+e^{2\psi}\alpha\Delta^2\left(\omega\wedge\d \tilde\theta+\tilde\omega\wedge\d \theta\right)
 		+e^{4\psi}\Delta^2\alpha \left(\Theta +\frac 1{\alpha}\tilde \Theta \right)\\
-		&+\Delta^2e^{2\psi}\left(\star_0\sigma+\tilde{\star}_0\tilde\sigma \right)\wedge\d\psi
-		-e^{4\psi}\alpha\Delta^2\left(\d\tilde \theta \wedge \gamma +\frac 1{\alpha}\d \theta\wedge\tilde\gamma\right)\wedge\d\psi.
+		&+\Delta^2e^{2\psi}\left(\star_0\sigma+\tilde{\star}_0\tilde\sigma \right)\wedge\d z
+		-e^{4\psi}\alpha\Delta^2\left(\d\tilde \theta \wedge \gamma +\frac 1{\alpha}\d \theta\wedge\tilde\gamma\right)\wedge\d z.
 	\end{split}
@@
 \end{equation}
+
+\CE{Other possibility:
+\begin{equation}
+  \begin{aligned}
+    H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})\\
+    & + 2\,\Delta^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge \bigg[\Phi_{1}\wedge\Phi_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+\zeta_{2}\ts{\zeta}_{1}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{1}-\Phi_{2}\wedge\ts{\varphi}_{2}\Big)\\
+    &\qquad+ \left(\zeta_{1}\ts{\zeta}_{1}+\zeta_{2}\ts{\zeta}_{2}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{2}-\Phi_{2}\wedge\ts{\varphi}_{1}\Big)+\Big(\zeta_{1}^{2}-\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\ts{\varphi}_{1}\wedge\ts{\varphi}_{2}\\
+    &\qquad-e^{2\psi}\,\Big(\zeta_{1}^{2}-\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{2}\,\ts{\varphi}_{1}+\ts{\zeta}_{1}\,\ts{\varphi}_{2}\Big)\wedge\d z+e^{2\psi}\,\Big(\zeta_{2}\,\Phi_{1}-\zeta_{1}\,\Phi_{2}\Big)\wedge\d z\bigg]\\
+    & + 2\,\Delta^{2}\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge \bigg[\ts{\Phi}_{1}\wedge\ts{\Phi}_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+\zeta_{2}\ts{\zeta}_{1}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{1}-\ts{\Phi}_{2}\wedge\varphi_{2}\Big)\\
+    &\qquad+ \left(\zeta_{1}\ts{\zeta}_{1}+\zeta_{2}\ts{\zeta}_{2}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{2}-\ts{\Phi}_{2}\wedge\varphi_{1}\Big)+\Big(\zeta_{1}^{2}-\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\varphi_{1}\wedge\varphi_{2}\\
+    &\qquad-e^{2\psi}\,\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\Big(\zeta_{2}\,\varphi_{1}+\zeta_{1}\,\varphi_{2}\Big)\wedge\d z+e^{2\psi}\,\Big(\ts{\zeta}_{2}\,\ts{\Phi}_{1}-\ts{\zeta}_{1}\,\ts{\Phi}_{2}\Big)\wedge\d z\bigg],
+  \end{aligned}
+\end{equation}
+where
+\begin{equation}
+  \begin{aligned}
+    \Phi_{i} &= \alpha\,\Big(1+e^{2\psi}\left(\cos^{2}(\ts{\theta})\,\ts{\zeta}_{2}^{2}+\sin^{2}(\ts{\theta})\,\ts{\zeta}_{1}^{2}+\zeta_{i}\right)\Big)\,\d\phi_{i},\\
+    \ts{\Phi}_{i} &= \Big(1+e^{2\psi}\left(\cos^{2}(\theta)\,\zeta_{2}^{2}+\sin^{2}(\theta)\,\zeta_{1}^{2}+\ts{\zeta}_{i}\right)\Big)\,\d\ts{\phi}_{i},\\
+    \varphi_{1} &= \alpha\,e^{2\psi}\cos^{2}(\theta)\,\d\phi_{1},\qquad
+    \varphi_{2} = \alpha\,e^{2\psi}\sin^{2}(\theta)\,\d\phi_{2},\\
+    \ts{\varphi}_{1} &= e^{2\psi}\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1},\qquad\ \ \,
+    \ts{\varphi}_{2} = e^{2\psi}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}.
+  \end{aligned}
+\end{equation}}
 
@@
 In fact, \eqref{eq:T2CStructure} only shows how the bosonic fields transform and thus suggests that the periodicities are $2\pi\alpha$ and $2\pi$.
-However, this is wrong: as the KK spectrum \eqref{eq:confdimshiftchi} shows, the fermions require double that periodicity, i.e.
-$4\pi\alpha$ and $4\pi$ as in \eqref{eq:ShiftSymmetries}.
-\EM{HERE}
+However, this is wrong: as the KK spectrum \eqref{eq:confdimshiftchi} shows, the fermions require double that periodicity, \textit{i.e.} $4\pi\alpha$ and $4\pi$ as in \eqref{eq:ShiftSymmetries}.
 
@@
 Finally, we would like to use the tools developed here to study RG flows between solutions of three-dimensional supergravity, or equivalently between two-dimensional conformal field theories.
-Note however that this cannot be applied to the RG flow of ref.~\cite{Berg:2001ty}: their solution cannot be described using the generalized Scherk-Schwarz Ansatz of \EE or $\SO{8,8}$ exceptional field theory \EM{HERE} as reproducing their embedding tensor would require breaking the section constraint.
+Note however that this cannot be applied to the RG flow of ref.~\cite{Berg:2001ty}: their theory cannot be described using the generalized Scherk-Schwarz Ansatz of \EE or $\SO{8,8}$ exceptional field theory as reproducing their embedding tensor would require breaking the section constraint.
 We leave these questions for future work.
@@
 \section*{Acknowledgements}
-We are grateful to Nikolay Bobev, Adolfo Guarino, Gabriel Larios, Yolanda Lozano, Niall Macpherson, Michela Petrini, Colin Sterckx and Dan Waldram for useful discussions and correspondence \EM{HERE}.
+We are grateful to Nikolay Bobev, Adolfo Guarino, Gabriel Larios, Yolanda Lozano, Niall Macpherson, Michela Petrini, Colin Sterckx and Dan Waldram for useful discussions and correspondence.
 CE is supported by the FWO-Vlaanderen through the project G006119N and by the Vrije Universiteit Brussel through the Strategic Research Program ``High-Energy Physics''.
@@
 \section{Ruling out gaugings} \label{app:rulingoutgauging}
-\EM{Why do we refer to uplifting the solution here, rather than the theory?}
-
-As mentioned in section~\ref{s:Potential}, eq.~\eqref{eq:reltrX} can be used to assess whether a given three-dimensional theory of embedding tensor $X_{\fl{MN}}$ has a higher-dimensional origin \EM{HERE}.
+As mentioned in section~\ref{s:Potential}, eq.~\eqref{eq:reltrX} can be used to assess whether a given three-dimensional theory of embedding tensor $X_{\fl{MN}}$ has a higher-dimensional origin.
 Let us illustrate that on the ${\cal N}=(8,0)$ ${\rm AdS}_{3}$ vacuum with $\GL{6} \times \SO{2,2}$ gauging constructed in ref.~\cite{Deger:2019tem}.
-This solution has a compact gauging smaller than $\SO{9}$, thus escaping the no-go result of ref.~\cite{Galli:2022idq}.
-The embedding tensor of the solution is expressed by breaking $\EE$ as
+This theory has a compact gauging smaller than $\SO{9}$, thus escaping the no-go result of ref.~\cite{Galli:2022idq}.
+The embedding tensor of the theory is expressed by breaking $\EE$ as
 \begin{equation}
@@
 \end{align}
-
 where we split the indices according to
@@
 \end{equation}
-thus violating the condition~\eqref{eq:reltrX} (the trombone gauging vanishes for the truncation) \EM{HERE}.
-Then, we deduce that the ${\cal N}=(8,0)$ solution of ref.~\cite{Deger:2019tem} with gauging $\GL{6} \times \SO{2,2}$ does not admit a higher-dimensional origin as constructed with \EE exceptional field theory.
+thus violating the condition~\eqref{eq:reltrX} (the trombone gauging vanishes for the truncation).
+Then, we deduce that the ${\cal N}=(8,0)$ theory of ref.~\cite{Deger:2019tem} with gauging $\GL{6} \times \SO{2,2}$ does not admit a higher-dimensional origin as constructed with \EE exceptional field theory.
 This illustrates how the constraint~\eqref{eq:reltrX} can be used to determine if a given three-dimensional gauged supergravity can be uplifted.
-\EM{HERE}
 

### 2023-06-20 Draft_3dH3.tex
Change in hyperref.
Solving issues with hyperref and arXiv.

@@
 %\usepackage{isomath}
-\usepackage{latexsym,amssymb}
-\usepackage{amsmath,amssymb,amsthm}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{xcolor}
 \usepackage{hyperref}
+\definecolor{darkorange}{RGB}{166, 88, 0}
+\hypersetup{colorlinks=true,
+        pdfstartview=FitV,
+        linkcolor= darkorange,% mydarkorange,
+        citecolor= darkorange, %mydarkorange,
+        urlcolor= gray!60!black,
+        hypertexnames=false,
+        linktoc=page}
 %\usepackage{fontenc}
@@
 %\usepackage{lmodern}
-\usepackage{xcolor}
 \usepackage{mathtools}
@@
 
-%  PDF specials
-%\newif\ifpdf
-\usepackage{ifpdf}
-\ifx\pdfoutput\undefined
-\pdffalse
-\usepackage{cite}
-\else
-\pdfoutput=1
-\pdftrue
-%\usepackage[pdftex]{hyperref}
-\pdfcompresslevel=9
-\fi
+% %  PDF specials
+% %\newif\ifpdf
+% \usepackage{ifpdf}
+% \ifx\pdfoutput\undefined
+% \pdffalse
+% \usepackage{cite}
+% \else
+% \pdfoutput=1
+% \pdftrue
+% %\usepackage[pdftex]{hyperref}
+% \pdfcompresslevel=9
+% \fi
 \DeclareFontFamily{OMS}{rsfs}{\skewchar\font'60}
@@
 \end{equation}
-
 Two short multiplets can combine into a long multiplets $[\ell,\ts{\ell}]$ as follows:

### 2023-06-21 Draft_3dH3.tex
Changes by Emanuel.
Choose of the second formulation for H3 with zeta and psi, and added H3 with zeta, psi and Omega.

@@
 \end{equation}
-We can also provide an expression for $H_{(3)}$, and we will do so here in the simplified case where $\Omega=\tilde\Omega=0$.
-It is convenient to first define some forms.
-We will denote by $\star$ and $\star_0$ the hodge star operators on the deformed and undeformed $S^3$'s respectively.
-\begin{equation}\label{eq:forms}
-	\begin{split}
-		Z(\theta,u,v,w)&=2+2e^{2\psi}(u^2\sin \theta^2+v^2\cos \theta^2+w^2)\\
-		\gamma&=4\sin\tilde\theta\cos\tilde \theta(\tilde{\zeta}_1^2-\tilde{\zeta}_2 ^2)\left(\zeta_2\cos \theta ^2\d \phi _1+\zeta _1\sin\theta ^2\d\phi _2\right)\\
-		\sigma&=2\left(	Z(\tilde\theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_2)\zeta_1\cos \theta ^2\d \phi _1+\zeta _2\sin\theta ^2Z(\tilde\theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_1)\d\phi _2\right)\\
-		\omega_{ij} &=2\sin\tilde\theta \cos\tilde\theta Z(\theta,\zeta_1,\zeta_2,\tilde\zeta _i)\d \tilde \phi _i\wedge \left [(\zeta _1\tilde \zeta _j + \tilde \zeta _i \zeta _2)\cos \theta ^2 \d \phi_1+ (\zeta _1\tilde \zeta _i + \tilde \zeta _j \zeta _2)\sin \theta ^2 \d \phi_2\right]\\
-		\Theta&=(\zeta _1^2-\zeta_2 ^2)(\tilde{\zeta}_1 ^2-\tilde \zeta _2^2)\sin(2\tilde\theta ) \sin (2 \theta)\d\tilde \theta\wedge(\star_0\d\theta)
-	\end{split}
-\end{equation}
-where we take $i,j\in\{1,2\}$ and they are not summed over. It is further useful to introduce (now sum over repeated $i,j$ as usual)
-\begin{equation}\label{eq:omegagamma}
- \omega=\epsilon^{ij}\omega _{ij}.
-\end{equation}
-In terms of the objects in \eqref{eq:forms} and \eqref{eq:omegagamma} we can write
-\begin{equation}\label{eq:defH3}
-	\begin{split}
-		H_{(3)}=&2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})+\frac1 \alpha(\star_0 {\rm Vol}(S^3)){\rm Vol}(S^3)+(\tilde{\star}_0{\rm Vol}(\tilde{S^3})){\rm Vol}(\tilde{S}^3)\\
-		&+e^{2\psi}\alpha\Delta^2\left(\omega\wedge\d \tilde\theta+\tilde\omega\wedge\d \theta\right)
-		+e^{4\psi}\Delta^2\alpha \left(\Theta +\frac 1{\alpha}\tilde \Theta \right)\\
-		&+\Delta^2e^{2\psi}\left(\star_0\sigma+\tilde{\star}_0\tilde\sigma \right)\wedge\d z
-		-e^{4\psi}\alpha\Delta^2\left(\d\tilde \theta \wedge \gamma +\frac 1{\alpha}\d \theta\wedge\tilde\gamma\right)\wedge\d z.
-	\end{split}
-\end{equation}
-Note that in equation \eqref{eq:defH3} all forms with a tilde correspond to the analogues of \eqref{eq:forms} and \eqref{eq:omegagamma} where every variable and form is ``conjugated" as $x\mapsto\tilde x$, $\tilde x\mapsto x$.
-For example
-\begin{equation}
-	\tilde\gamma=4\sin(\theta)\cos(\theta)(\zeta_1^2-\zeta_2 ^2)\left(\tilde{\zeta}_2\cos^2(\tilde \theta)\d \tilde \phi _1+\tilde{\zeta} _1\sin^2(\tilde\theta)\d\tilde\phi _2\right).
-\end{equation}
-
-\CE{Other possibility:
+We can also provide an expression for $H_{(3)}$, and we will do so here in the simplified case where $\Omega=\tilde\Omega=0$. It is convenient to first define some forms:
+\begin{equation}
+  \begin{aligned}
+    \Phi_{i} &= \alpha\,\Big(1+e^{2\psi}\left(\cos^{2}(\ts{\theta})\,\ts{\zeta}_{2}^{2}+\sin^{2}(\ts{\theta})\,\ts{\zeta}_{1}^{2}+\zeta_{i}^{2}\right)\Big)\,\d\phi_{i},\\
+    \ts{\Phi}_{i} &= \Big(1+e^{2\psi}\left(\cos^{2}(\theta)\,\zeta_{2}^{2}+\sin^{2}(\theta)\,\zeta_{1}^{2}+\ts{\zeta}_{i}^{2}\right)\Big)\,\d\ts{\phi}_{i},\\
+    \varphi_{1} &= \alpha\,e^{2\psi}\cos^{2}(\theta)\,\d\phi_{1},\qquad
+    \varphi_{2} = \alpha\,e^{2\psi}\sin^{2}(\theta)\,\d\phi_{2},\\
+    \ts{\varphi}_{1} &= e^{2\psi}\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1},\qquad\ \ \,
+    \ts{\varphi}_{2} = e^{2\psi}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}.
+  \end{aligned}
+\end{equation}
+In terms of these forms, we get
 \begin{equation}
@@
     &\qquad+ \left(\zeta_{1}\ts{\zeta}_{1}+\zeta_{2}\ts{\zeta}_{2}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{2}-\ts{\Phi}_{2}\wedge\varphi_{1}\Big)+\Big(\zeta_{1}^{2}-\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\varphi_{1}\wedge\varphi_{2}\\
-    &\qquad-e^{2\psi}\,\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\Big(\zeta_{2}\,\varphi_{1}+\zeta_{1}\,\varphi_{2}\Big)\wedge\d z+e^{2\psi}\,\Big(\ts{\zeta}_{2}\,\ts{\Phi}_{1}-\ts{\zeta}_{1}\,\ts{\Phi}_{2}\Big)\wedge\d z\bigg],
-  \end{aligned}
-\end{equation}
-where
-\begin{equation}
-  \begin{aligned}
-    \Phi_{i} &= \alpha\,\Big(1+e^{2\psi}\left(\cos^{2}(\ts{\theta})\,\ts{\zeta}_{2}^{2}+\sin^{2}(\ts{\theta})\,\ts{\zeta}_{1}^{2}+\zeta_{i}\right)\Big)\,\d\phi_{i},\\
-    \ts{\Phi}_{i} &= \Big(1+e^{2\psi}\left(\cos^{2}(\theta)\,\zeta_{2}^{2}+\sin^{2}(\theta)\,\zeta_{1}^{2}+\ts{\zeta}_{i}\right)\Big)\,\d\ts{\phi}_{i},\\
-    \varphi_{1} &= \alpha\,e^{2\psi}\cos^{2}(\theta)\,\d\phi_{1},\qquad
+    &\qquad-e^{2\psi}\,\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\Big(\zeta_{2}\,\varphi_{1}+\zeta_{1}\,\varphi_{2}\Big)\wedge\d z+e^{2\psi}\,\Big(\ts{\zeta}_{2}\,\ts{\Phi}_{1}-\ts{\zeta}_{1}\,\ts{\Phi}_{2}\Big)\wedge\d z\bigg].
+  \end{aligned}
+\end{equation}
+
+% We will denote by $\star$ and $\star_0$ the hodge star operators on the deformed and undeformed $S^3$'s respectively.
+% \begin{equation}\label{eq:forms}
+% 	\begin{split}
+% 		Z(\theta,u,v,w)&=2+2e^{2\psi}(u^2\sin \theta^2+v^2\cos \theta^2+w^2) \,, \\
+% 		\gamma&=4\sin\tilde\theta\cos\tilde \theta(\tilde{\zeta}_1^2-\tilde{\zeta}_2 ^2)\left(\zeta_2\cos \theta ^2\d \phi _1+\zeta _1\sin\theta ^2\d\phi _2\right) \,, \\
+% 		\sigma&=2\left(	Z(\tilde\theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_2)\zeta_1\cos \theta ^2\d \phi _1+\zeta _2\sin\theta ^2Z(\tilde\theta,\tilde{\zeta}_1,\tilde{\zeta}_2,\zeta_1)\d\phi _2\right) \,, \\
+% 		\omega_{ij} &=2\sin\tilde\theta \cos\tilde\theta Z(\theta,\zeta_1,\zeta_2,\tilde\zeta _i)\d \tilde \phi _i\wedge \left [(\zeta _1\tilde \zeta _j + \tilde \zeta _i \zeta _2)\cos \theta ^2 \d \phi_1+ (\zeta _1\tilde \zeta _i + \tilde \zeta _j \zeta _2)\sin \theta ^2 \d \phi_2\right] \,, \\
+% 		\Theta&=(\zeta _1^2-\zeta_2 ^2)(\tilde{\zeta}_1 ^2-\tilde \zeta _2^2)\sin(2\tilde\theta ) \sin (2 \theta)\d\tilde \theta\wedge(\star_0\d\theta) \,,
+% 	\end{split}
+% \end{equation}
+% where we take $i,j\in\{1,2\}$ and they are not summed over. It is further useful to introduce (now sum over repeated $i,j$ as usual)
+% \begin{equation}\label{eq:omegagamma}
+%  \omega=\epsilon^{ij}\omega _{ij}.
+% \end{equation}
+% In terms of the objects in \eqref{eq:forms} and \eqref{eq:omegagamma} we can write
+% \begin{equation}\label{eq:defH3}
+% 	\begin{split}
+% 		H_{(3)}=&2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})+\frac1 \alpha(\star_0 {\rm Vol}(S^3)){\rm Vol}(S^3)+(\tilde{\star}_0{\rm Vol}(\tilde{S^3})){\rm Vol}(\tilde{S}^3)\\
+% 		&+e^{2\psi}\alpha\Delta^2\left(\omega\wedge\d \tilde\theta+\tilde\omega\wedge\d \theta\right)
+% 		+e^{4\psi}\Delta^2\alpha \left(\Theta +\frac 1{\alpha}\tilde \Theta \right)\\
+% 		&+\Delta^2e^{2\psi}\left(\star_0\sigma+\tilde{\star}_0\tilde\sigma \right)\wedge\d z
+% 		-e^{4\psi}\alpha\Delta^2\left(\d\tilde \theta \wedge \gamma +\frac 1{\alpha}\d \theta\wedge\tilde\gamma\right)\wedge\d z \,.
+% 	\end{split}
+% \end{equation}
+% Note that in equation \eqref{eq:defH3} all forms with a tilde correspond to the analogues of \eqref{eq:forms} and \eqref{eq:omegagamma} where every variable and form is ``conjugated" as $x\mapsto\tilde x$, $\tilde x\mapsto x$.
+For example
+% \begin{equation}
+% 	\tilde\gamma=4\sin(\theta)\cos(\theta)(\zeta_1^2-\zeta_2 ^2)\left(\tilde{\zeta}_2\cos^2(\tilde \theta)\d \tilde \phi _1+\tilde{\zeta} _1\sin^2(\tilde\theta)\d\tilde\phi _2\right) \,.
+% \end{equation}
+
+\CE{With $\Omega$ and $\ts{\Omega}$:
+\begin{equation}
+  \begin{aligned}
+    \Phi_{1} &= \alpha\,\Big(\big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\big)\big(e^{\Omega}+e^{2\psi}\,\zeta_{1}^{2}\big)+e^{2\psi+\Omega}\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\Big)\,\d\phi_{1},\\
+    \Phi_{2} &= \alpha\,\Big(\big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\big)\big(1+e^{2\psi+\Omega}\,\zeta_{2}^{2}\big)+e^{2\psi}\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\Big)\,\d\phi_{2},\\
+    \ts{\Phi}_{1} &= \Big(\big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\big)\big(1+e^{2\psi+\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\big)+e^{2\psi}\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right)\Big)\,\d\ts{\phi}_{1},\\
+    \ts{\Phi}_{2} &= \Big(\big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\big)\big(e^{\ts{\Omega}}+e^{2\psi}\,\ts{\zeta}_{2}^{2}\big)+e^{2\psi+\ts{\Omega}}\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right)\Big)\,\d\ts{\phi}_{2},\\
+    \varphi_{1} &= \alpha\,e^{2\psi}\cos^{2}(\theta)\,\d\phi_{1},\qquad\qquad\qquad
     \varphi_{2} = \alpha\,e^{2\psi}\sin^{2}(\theta)\,\d\phi_{2},\\
-    \ts{\varphi}_{1} &= e^{2\psi}\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1},\qquad\ \ \,
+    \ts{\varphi}_{1} &= e^{2\psi}\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1},\qquad\qquad\qquad\ \ \,
     \ts{\varphi}_{2} = e^{2\psi}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}.
+  \end{aligned}
+\end{equation}
+and
+\begin{equation}
+  \begin{aligned}
+    H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})\\
+    & + 2\,\Delta^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge \bigg[\Phi_{1}\wedge\Phi_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+e^{\Omega+\ts{\Omega}}\zeta_{2}\ts{\zeta}_{1}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{1}-\Phi_{2}\wedge\ts{\varphi}_{2}\Big)\\
+    &\quad+ \left(e^{\ts{\Omega}}\zeta_{1}\ts{\zeta}_{1}+e^{\Omega}\zeta_{2}\ts{\zeta}_{2}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{2}-\Phi_{2}\wedge\ts{\varphi}_{1}\Big)+\Big(\zeta_{1}^{2}-e^{2\Omega}\zeta_{2}^{2}\Big)\Big(e^{2\ts{\Omega}}\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\ts{\varphi}_{1}\wedge\ts{\varphi}_{2}\\
+    &\quad+e^{2\psi}\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\bigg(\Big(e^{\Omega}\zeta_{2}\,\Phi_{1}-\zeta_{1}\,\Phi_{2}\Big)-\Big(\zeta_{1}^{2}-e^{2\Omega}\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{2}\,\ts{\varphi}_{1}+e^{\ts{\Omega}}\ts{\zeta}_{1}\,\ts{\varphi}_{2}\Big)\bigg)\wedge\d z\bigg]\\
+    & + 2\,\Delta^{2}\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge \bigg[\ts{\Phi}_{1}\wedge\ts{\Phi}_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+e^{\Omega+\ts{\Omega}}\zeta_{2}\ts{\zeta}_{1}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{1}-\ts{\Phi}_{2}\wedge\varphi_{2}\Big)\\
+    &\quad+ \left(e^{\ts{\Omega}}\zeta_{1}\ts{\zeta}_{1}+e^{\Omega}\zeta_{2}\ts{\zeta}_{2}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{2}-\ts{\Phi}_{2}\wedge\varphi_{1}\Big)+\Big(\zeta_{1}^{2}-e^{2\Omega}\zeta_{2}^{2}\Big)\Big(e^{2\ts{\Omega}}\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\varphi_{1}\wedge\varphi_{2}\\
+    &\quad+e^{2\psi}\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\bigg(\Big(\ts{\zeta}_{2}\,\ts{\Phi}_{1}-e^{\ts{\Omega}}\ts{\zeta}_{1}\,\ts{\Phi}_{2}\Big)-\Big(e^{2\ts{\Omega}}\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\Big(e^{\Omega}\zeta_{2}\,\varphi_{1}+\zeta_{1}\,\varphi_{2}\Big)\bigg)\wedge\d z\bigg].
   \end{aligned}

### 2023-06-21 Draft_3dH3.tex
Version sent to arXiv. Corrected some typos, removed the H3 with zeta but no Omega.

@@
 Here and in the following, \EE indices are raised and lowered by the Cartan-Killing metric $\eta_{MN}$.
-The section constraints~\eqref{eq:sectionconstraints} ensure that the fields depends only on the 7- or 8-dimensional physical internal coordinates embeded in $Y^{M}$.
+The section constraints~\eqref{eq:sectionconstraints} ensure that the fields depends only on the 7- or 8-dimensional physical internal coordinates embedded in $Y^{M}$.
 
@@
 \end{equation}
-with $g_{\mu\nu}$ the 3-dimensinal external metric, $\M_{MN}$ the generalized metric parametrizing the coset space $\EE/\SO{16}$ and the gauge fields $A_{\mu}{}^{M}$ and $B_{\mu\,M}$.
+with $g_{\mu\nu}$ the 3-dimensional external metric, $\M_{MN}$ the generalized metric parametrizing the coset space $\EE/\SO{16}$ and the gauge fields $A_{\mu}{}^{M}$ and $B_{\mu\,M}$.
 It is a gauge theory, invariant under the generalized Lie derivative of parameters $\Upsilon=(\Lambda^{M},\Sigma_{M})$, whose action on a vector $V^{M}$ of weight $\lambda$ is given by
@@
 \end{equation}
-The embedding tensor is most nicely expressed once projected on the adjoint representation
+The embedding tensor is most nicely expressed once projected on the adjoint representation:
 \begin{equation} \label{eq:symembeddingtensor}
@@
 \end{equation}
-
 However, the case of the potential term $\mathscr{L}_{\rm int}$, leading to a potential $V$ for the three-dimensional scalars $\M_{\fl{MN}}$, is more subtle.
@@
 \end{equation}
-or equivalently
+or equivalently with eq.~\eqref{eq:symembeddingtensor}
 \begin{equation}
@@
 The construction of the the $\SL{4} \simeq \SO{3,3}$ twist matrix describing the consistent truncation on $S^3$ is detailed in appendix~\ref{s:SLn}.
-To demonstrate our methodology, we will now show how the parameter $\lambda$ introduced in \cite{Eloy:2021fhc} can be obtained by the twisting procedure described in appendix~\ref{s:SLn}.
+To demonstrate our methodology, we will now show how the parameter $\lambda$ introduced in \cite{Eloy:2021fhc} can be obtained by the twisting procedure described above.
 Thus, we want to consider the $\SO{3,3} \subset \SO{4,4}$ twist matrix corresponding to $S^3$ \eqref{eq:SLnTwist} and add a 3-form flux via a $\SO{4,4}$ twist.
@@
 Decomposing with respect to the geometric $\SL{3} \times \mathbb{R}^+$ of the $S^3$,  the coordinates on $S^3$ live in the $Y^A = \left( y^i,\, y_i \right)$, $i = 1, 2, 3$, while $C_A = \left( C_i,\, C^i \right)$ naturally contains a 2-form $C^i$.
-The field strength $H_3 = \partial^A C_A = \partial_i C^i$ is a singlet of $\SO{3,3}$ and thus we see that $\rho^{-1} F_{\ov{M}\ov{N}}{}^{\ov{P}}$ in \eqref{eq:FlatF} is constant and we obtain a consistent truncation with a new 3-form flux.
+The field strength $H_{(3)} = \partial^A C_A = \partial_i C^i$ is a singlet of $\SO{3,3}$ and thus we see that $\rho^{-1} F_{\ov{M}\ov{N}}{}^{\ov{P}}$ in \eqref{eq:FlatF} is constant and we obtain a consistent truncation with a new 3-form flux.
 Evaluating the twist matrix
@@
 \end{equation}
-This solution of the section condition defines the ``geometric'' $\SL{3}_1 \times \RO \subset \SL{4}_1$ and $\SL{3}_2 \times \RT \subset \SL{4}_2$ subgroups, that will play an important role when adding flux in section \ref{s:AddFluxS3S3S1}.
-
-We can now use one copy of the $\SL{4}$ frame \eqref{eq:SLnFrame} for each $\SL{4}$ subgroup of \eqref{eq:SL4Embedding} to construct a generalised parallelisation for the full $\En{7}$ ExFT, with an embedding tensor via \eqref{eq:GenLeibniz} given as in \eqref{eq:SLnEmbeddingTensor} embedded in $\En{7}$ as follows.
+This solution of the section condition defines the ``geometric'' $\SL{3}_1 \times \RO \subset \SL{4}_1$ and $\SL{3}_2 \times \RT \subset \SL{4}_2$ subgroups, that will play an important role when adding flux in section~\ref{s:AddFluxS3S3S1}.
+
+We can now use one copy of the $\SL{4}$ frame \eqref{eq:SLnFrame} for each $\SL{4}$ subgroup of \eqref{eq:SL4Embedding} to construct a generalised parallelisation for the full $\En{7}$ ExFT, with an embedding tensor via \eqref{eq:GenLeibniz} given as in~\eqref{eq:SLnEmbeddingTensor} embedded in $\En{7}$ as follows.
 Under $\En{7} \rightarrow \SL{8}$, the embedding tensor representation branches as
@@
 These 4-dimensional truncations arise from compactifications of 10-dimensional supergravity on $S^6$, $S^5\times S^1$, $S^4\times S^2$, with the 10-d theory corresponding to (massive) IIA/IIB when the spheres have even/odd dimensions, respectively.
-The corresponding twist matrices for $S^6$, $S^5\times S^1$, $S^4\times S^2$ belong to $\SL{8-p} \times \SL{p}$, with $p = 1,\, 2,\, 3$ for the respective cases, and are constructed as in section \ref{s:SLn}.
+The corresponding twist matrices for $S^6$, $S^5\times S^1$, $S^4\times S^2$ belong to $\SL{8-p} \times \SL{p}$, with $p = 1,\, 2,\, 3$ for the respective cases, and are constructed as in appendix \ref{s:SLn}.
 
@@
 However, this $\mathbb{R}^+$ generator cannot correspond to a form potential.
-If it did, there would also have be a corresponding compact generator in the same representation (with possibly different $\mathbb{R}^+$ chargse), just as in \eqref{eq:133DecompSL4SL4}, associated to the ``dual'' potential.
+If it did, there would also have been a corresponding compact generator in the same representation (with possibly different $\mathbb{R}^+$ chargse), just as in \eqref{eq:133DecompSL4SL4}, associated to the ``dual'' potential.
 Since we only have one $\SL{8-p} \times \SL{p}$ singlet, this cannot be a $p$-form potential and, therefore, turning on new fluxes with legs on $S^1$ will not lead to consistent truncation for $S^{7-p} \times S^{p-1} \times S^1$, $p = 1,\, 2,\, 3$.
-This analysis also reveals why the $S^3\times S^3 \times S^1$ case is special: the $\mbf{133}$ contains a 4 form of $\SL{8}$, \textit{i.e.} the $\mathbf{70}$, which naturally contains the relevant singlets under $\SL{4}\times \SL{4}$.
+This analysis also reveals why the $S^3\times S^3 \times S^1$ case is special: the $\mbf{133}$ contains a 4-form of $\SL{8}$, \textit{i.e.} the $\mathbf{70}$, which naturally contains the relevant singlets under $\SL{4}\times \SL{4}$.
 
@@
 Additionally, there is a $\U{1}_F$ symmetry due to the $S^1$ factor in \eqref{eq:AdS3}.
-The spectrum organizes into multiplets of ${\cal G}$, made out of products of long representations $[\ell,\ts{\ell}]$ of $D^{1}(2,1;\alpha)$ (see app.~\ref{app:d21a} for a review of the representations of $D^{1}(2,1;\alpha)$), and carrying a charge $n$ under the $\U{1}_F$.
+The spectrum organizes into multiplets of ${\cal G}$, made out of products of long representations $[\ell,\ts{\ell}]$ of $D^{1}(2,1;\alpha)$ (see appendix~\ref{app:d21a} for a review of the representations of $D^{1}(2,1;\alpha)$), and carrying a charge $n$ under the $\U{1}_F$.
 Explicitly, the spectrum is~\cite{Eberhardt:2017fsi}
@@
 \begin{equation}
-	\big(\nicefrac{1}{2},\nicefrac{1}{2};0,0\big) \quad {\rm and} \quad \big(0,0;\nicefrac{1}{2},\nicefrac{1}{2}\big)\,.
+	\big(\nicefrac{1}{2},\nicefrac{1}{2};0,0\big) \quad {\rm and} \quad \big(0,0;\nicefrac{1}{2},\nicefrac{1}{2}\big)\,,
 \end{equation}
@@
 		\chi_{2} = \chi_{1} \pm\alpha\,(\ts{\chi}_{1}+\ts{\chi}_{2})
-		\quad {\rm or}\quad \chi_{2} = -\chi_{1} \pm\alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2}) \mathbb{Z}
+		\quad {\rm or}\quad \chi_{2} = -\chi_{1} \pm\alpha\,(\ts{\chi}_{1}-\ts{\chi}_{2})
 		\,,
@@
 \paragraph{\boldmath $(\zeta,\ts{\zeta},\Omega,\ts{\Omega},\psi)$}
-Again in Hopf coordinates:
+Restricting to the parameters $(\zeta_i, \ts{\zeta}_i, \Omega, \ts{\Omega}, \psi)$, $i = 1,2$, and using again Hopf coordinates, the metric is
 \begin{equation} \label{eq:metriczeta}
@@
 \end{equation}
-We can also provide an expression for $H_{(3)}$, and we will do so here in the simplified case where $\Omega=\tilde\Omega=0$. It is convenient to first define some forms:
+To provide an expression for $H_{(3)}$ it is convenient to first define some forms:
 \begin{equation}
   \begin{aligned}
-    \Phi_{i} &= \alpha\,\Big(1+e^{2\psi}\left(\cos^{2}(\ts{\theta})\,\ts{\zeta}_{2}^{2}+\sin^{2}(\ts{\theta})\,\ts{\zeta}_{1}^{2}+\zeta_{i}^{2}\right)\Big)\,\d\phi_{i},\\
-    \ts{\Phi}_{i} &= \Big(1+e^{2\psi}\left(\cos^{2}(\theta)\,\zeta_{2}^{2}+\sin^{2}(\theta)\,\zeta_{1}^{2}+\ts{\zeta}_{i}^{2}\right)\Big)\,\d\ts{\phi}_{i},\\
-    \varphi_{1} &= \alpha\,e^{2\psi}\cos^{2}(\theta)\,\d\phi_{1},\qquad
+    \Phi_{1} &= \alpha\,\Big(\big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\big)\big(e^{\Omega}+e^{2\psi}\,\zeta_{1}^{2}\big)+e^{2\psi+\Omega}\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\Big)\,\d\phi_{1},\\
+    \Phi_{2} &= \alpha\,\Big(\big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\big)\big(1+e^{2\psi+\Omega}\,\zeta_{2}^{2}\big)+e^{2\psi}\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\Big)\,\d\phi_{2},\\
+    \ts{\Phi}_{1} &= \Big(\big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\big)\big(1+e^{2\psi+\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\big)+e^{2\psi}\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right)\Big)\,\d\ts{\phi}_{1},\\
+    \ts{\Phi}_{2} &= \Big(\big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\big)\big(e^{\ts{\Omega}}+e^{2\psi}\,\ts{\zeta}_{2}^{2}\big)+e^{2\psi+\ts{\Omega}}\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right)\Big)\,\d\ts{\phi}_{2},\\
+    \varphi_{1} &= \alpha\,e^{2\psi}\cos^{2}(\theta)\,\d\phi_{1},\qquad\qquad\qquad
     \varphi_{2} = \alpha\,e^{2\psi}\sin^{2}(\theta)\,\d\phi_{2},\\
-    \ts{\varphi}_{1} &= e^{2\psi}\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1},\qquad\ \ \,
+    \ts{\varphi}_{1} &= e^{2\psi}\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1},\qquad\qquad\qquad\ \ \,
     \ts{\varphi}_{2} = e^{2\psi}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}.
@@
     H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})\\
-    & + 2\,\Delta^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge \bigg[\Phi_{1}\wedge\Phi_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+\zeta_{2}\ts{\zeta}_{1}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{1}-\Phi_{2}\wedge\ts{\varphi}_{2}\Big)\\
-    &\qquad+ \left(\zeta_{1}\ts{\zeta}_{1}+\zeta_{2}\ts{\zeta}_{2}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{2}-\Phi_{2}\wedge\ts{\varphi}_{1}\Big)+\Big(\zeta_{1}^{2}-\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\ts{\varphi}_{1}\wedge\ts{\varphi}_{2}\\
-    &\qquad-e^{2\psi}\,\Big(\zeta_{1}^{2}-\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{2}\,\ts{\varphi}_{1}+\ts{\zeta}_{1}\,\ts{\varphi}_{2}\Big)\wedge\d z+e^{2\psi}\,\Big(\zeta_{2}\,\Phi_{1}-\zeta_{1}\,\Phi_{2}\Big)\wedge\d z\bigg]\\
-    & + 2\,\Delta^{2}\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge \bigg[\ts{\Phi}_{1}\wedge\ts{\Phi}_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+\zeta_{2}\ts{\zeta}_{1}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{1}-\ts{\Phi}_{2}\wedge\varphi_{2}\Big)\\
-    &\qquad+ \left(\zeta_{1}\ts{\zeta}_{1}+\zeta_{2}\ts{\zeta}_{2}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{2}-\ts{\Phi}_{2}\wedge\varphi_{1}\Big)+\Big(\zeta_{1}^{2}-\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\varphi_{1}\wedge\varphi_{2}\\
-    &\qquad-e^{2\psi}\,\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\Big(\zeta_{2}\,\varphi_{1}+\zeta_{1}\,\varphi_{2}\Big)\wedge\d z+e^{2\psi}\,\Big(\ts{\zeta}_{2}\,\ts{\Phi}_{1}-\ts{\zeta}_{1}\,\ts{\Phi}_{2}\Big)\wedge\d z\bigg].
+    & + 2\,\Delta^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge \bigg[\Phi_{1}\wedge\Phi_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+e^{\Omega+\ts{\Omega}}\zeta_{2}\ts{\zeta}_{1}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{1}-\Phi_{2}\wedge\ts{\varphi}_{2}\Big)\\
+    &\quad+ \left(e^{\ts{\Omega}}\zeta_{1}\ts{\zeta}_{1}+e^{\Omega}\zeta_{2}\ts{\zeta}_{2}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{2}-\Phi_{2}\wedge\ts{\varphi}_{1}\Big)+\Big(\zeta_{1}^{2}-e^{2\Omega}\zeta_{2}^{2}\Big)\Big(e^{2\ts{\Omega}}\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\ts{\varphi}_{1}\wedge\ts{\varphi}_{2}\\
+    &\quad+e^{2\psi}\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\bigg(\Big(e^{\Omega}\zeta_{2}\,\Phi_{1}-\zeta_{1}\,\Phi_{2}\Big)-\Big(\zeta_{1}^{2}-e^{2\Omega}\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{2}\,\ts{\varphi}_{1}+e^{\ts{\Omega}}\ts{\zeta}_{1}\,\ts{\varphi}_{2}\Big)\bigg)\wedge\d z\bigg]\\
+    & + 2\,\Delta^{2}\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge \bigg[\ts{\Phi}_{1}\wedge\ts{\Phi}_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+e^{\Omega+\ts{\Omega}}\zeta_{2}\ts{\zeta}_{1}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{1}-\ts{\Phi}_{2}\wedge\varphi_{2}\Big)\\
+    &\quad+ \left(e^{\ts{\Omega}}\zeta_{1}\ts{\zeta}_{1}+e^{\Omega}\zeta_{2}\ts{\zeta}_{2}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{2}-\ts{\Phi}_{2}\wedge\varphi_{1}\Big)+\Big(\zeta_{1}^{2}-e^{2\Omega}\zeta_{2}^{2}\Big)\Big(e^{2\ts{\Omega}}\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\varphi_{1}\wedge\varphi_{2}\\
+    &\quad+e^{2\psi}\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\bigg(\Big(\ts{\zeta}_{2}\,\ts{\Phi}_{1}-e^{\ts{\Omega}}\ts{\zeta}_{1}\,\ts{\Phi}_{2}\Big)-\Big(e^{2\ts{\Omega}}\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\Big(e^{\Omega}\zeta_{2}\,\varphi_{1}+\zeta_{1}\,\varphi_{2}\Big)\bigg)\wedge\d z\bigg].
   \end{aligned}
 \end{equation}
-
+% \begin{equation}
+%   \begin{aligned}
+%     \Phi_{i} &= \alpha\,\Big(1+e^{2\psi}\left(\cos^{2}(\ts{\theta})\,\ts{\zeta}_{2}^{2}+\sin^{2}(\ts{\theta})\,\ts{\zeta}_{1}^{2}+\zeta_{i}^{2}\right)\Big)\,\d\phi_{i},\\
+%     \ts{\Phi}_{i} &= \Big(1+e^{2\psi}\left(\cos^{2}(\theta)\,\zeta_{2}^{2}+\sin^{2}(\theta)\,\zeta_{1}^{2}+\ts{\zeta}_{i}^{2}\right)\Big)\,\d\ts{\phi}_{i},\\
+%     \varphi_{1} &= \alpha\,e^{2\psi}\cos^{2}(\theta)\,\d\phi_{1},\qquad
+%     \varphi_{2} = \alpha\,e^{2\psi}\sin^{2}(\theta)\,\d\phi_{2},\\
+%     \ts{\varphi}_{1} &= e^{2\psi}\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1},\qquad\ \ \,
+%     \ts{\varphi}_{2} = e^{2\psi}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}.
+%   \end{aligned}
+% \end{equation}
+% In terms of these forms, we get
+% \begin{equation}
+%   \begin{aligned}
+%     H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})\\
+%     & + 2\,\Delta^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge \bigg[\Phi_{1}\wedge\Phi_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+\zeta_{2}\ts{\zeta}_{1}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{1}-\Phi_{2}\wedge\ts{\varphi}_{2}\Big)\\
+%     &\qquad+ \left(\zeta_{1}\ts{\zeta}_{1}+\zeta_{2}\ts{\zeta}_{2}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{2}-\Phi_{2}\wedge\ts{\varphi}_{1}\Big)+\Big(\zeta_{1}^{2}-\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\ts{\varphi}_{1}\wedge\ts{\varphi}_{2}\\
+%     &\qquad-e^{2\psi}\,\Big(\zeta_{1}^{2}-\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{2}\,\ts{\varphi}_{1}+\ts{\zeta}_{1}\,\ts{\varphi}_{2}\Big)\wedge\d z+e^{2\psi}\,\Big(\zeta_{2}\,\Phi_{1}-\zeta_{1}\,\Phi_{2}\Big)\wedge\d z\bigg]\\
+%     & + 2\,\Delta^{2}\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge \bigg[\ts{\Phi}_{1}\wedge\ts{\Phi}_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+\zeta_{2}\ts{\zeta}_{1}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{1}-\ts{\Phi}_{2}\wedge\varphi_{2}\Big)\\
+%     &\qquad+ \left(\zeta_{1}\ts{\zeta}_{1}+\zeta_{2}\ts{\zeta}_{2}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{2}-\ts{\Phi}_{2}\wedge\varphi_{1}\Big)+\Big(\zeta_{1}^{2}-\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\varphi_{1}\wedge\varphi_{2}\\
+%     &\qquad-e^{2\psi}\,\Big(\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\Big(\zeta_{2}\,\varphi_{1}+\zeta_{1}\,\varphi_{2}\Big)\wedge\d z+e^{2\psi}\,\Big(\ts{\zeta}_{2}\,\ts{\Phi}_{1}-\ts{\zeta}_{1}\,\ts{\Phi}_{2}\Big)\wedge\d z\bigg].
+%   \end{aligned}
+% \end{equation}
+%
 % We will denote by $\star$ and $\star_0$ the hodge star operators on the deformed and undeformed $S^3$'s respectively.
@@
 % \end{equation} 
-
-\CE{With $\Omega$ and $\ts{\Omega}$:
-\begin{equation}
-  \begin{aligned}
-    \Phi_{1} &= \alpha\,\Big(\big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\big)\big(e^{\Omega}+e^{2\psi}\,\zeta_{1}^{2}\big)+e^{2\psi+\Omega}\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\Big)\,\d\phi_{1},\\
-    \Phi_{2} &= \alpha\,\Big(\big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\big)\big(1+e^{2\psi+\Omega}\,\zeta_{2}^{2}\big)+e^{2\psi}\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\Big)\,\d\phi_{2},\\
-    \ts{\Phi}_{1} &= \Big(\big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\big)\big(1+e^{2\psi+\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\big)+e^{2\psi}\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right)\Big)\,\d\ts{\phi}_{1},\\
-    \ts{\Phi}_{2} &= \Big(\big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\big)\big(e^{\ts{\Omega}}+e^{2\psi}\,\ts{\zeta}_{2}^{2}\big)+e^{2\psi+\ts{\Omega}}\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right)\Big)\,\d\ts{\phi}_{2},\\
-    \varphi_{1} &= \alpha\,e^{2\psi}\cos^{2}(\theta)\,\d\phi_{1},\qquad\qquad\qquad
-    \varphi_{2} = \alpha\,e^{2\psi}\sin^{2}(\theta)\,\d\phi_{2},\\
-    \ts{\varphi}_{1} &= e^{2\psi}\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1},\qquad\qquad\qquad\ \ \,
-    \ts{\varphi}_{2} = e^{2\psi}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}.
-  \end{aligned}
-\end{equation}
-and
-\begin{equation}
-  \begin{aligned}
-    H_{(3)} &= 2\,\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})\\
-    & + 2\,\Delta^{2}\cos(\theta)\sin(\theta)\,\d\theta\wedge \bigg[\Phi_{1}\wedge\Phi_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+e^{\Omega+\ts{\Omega}}\zeta_{2}\ts{\zeta}_{1}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{1}-\Phi_{2}\wedge\ts{\varphi}_{2}\Big)\\
-    &\quad+ \left(e^{\ts{\Omega}}\zeta_{1}\ts{\zeta}_{1}+e^{\Omega}\zeta_{2}\ts{\zeta}_{2}\right)\Big(\Phi_{1}\wedge\ts{\varphi}_{2}-\Phi_{2}\wedge\ts{\varphi}_{1}\Big)+\Big(\zeta_{1}^{2}-e^{2\Omega}\zeta_{2}^{2}\Big)\Big(e^{2\ts{\Omega}}\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\ts{\varphi}_{1}\wedge\ts{\varphi}_{2}\\
-    &\quad+e^{2\psi}\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\bigg(\Big(e^{\Omega}\zeta_{2}\,\Phi_{1}-\zeta_{1}\,\Phi_{2}\Big)-\Big(\zeta_{1}^{2}-e^{2\Omega}\zeta_{2}^{2}\Big)\Big(\ts{\zeta}_{2}\,\ts{\varphi}_{1}+e^{\ts{\Omega}}\ts{\zeta}_{1}\,\ts{\varphi}_{2}\Big)\bigg)\wedge\d z\bigg]\\
-    & + 2\,\Delta^{2}\cos(\ts{\theta})\sin(\ts{\theta})\,\d\ts{\theta}\wedge \bigg[\ts{\Phi}_{1}\wedge\ts{\Phi}_{2} + \left(\zeta_{1}\ts{\zeta}_{2}+e^{\Omega+\ts{\Omega}}\zeta_{2}\ts{\zeta}_{1}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{1}-\ts{\Phi}_{2}\wedge\varphi_{2}\Big)\\
-    &\quad+ \left(e^{\ts{\Omega}}\zeta_{1}\ts{\zeta}_{1}+e^{\Omega}\zeta_{2}\ts{\zeta}_{2}\right)\Big(\ts{\Phi}_{1}\wedge\varphi_{2}-\ts{\Phi}_{2}\wedge\varphi_{1}\Big)+\Big(\zeta_{1}^{2}-e^{2\Omega}\zeta_{2}^{2}\Big)\Big(e^{2\ts{\Omega}}\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\,\varphi_{1}\wedge\varphi_{2}\\
-    &\quad+e^{2\psi}\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\bigg(\Big(\ts{\zeta}_{2}\,\ts{\Phi}_{1}-e^{\ts{\Omega}}\ts{\zeta}_{1}\,\ts{\Phi}_{2}\Big)-\Big(e^{2\ts{\Omega}}\ts{\zeta}_{1}^{2}-\ts{\zeta}_{2}^{2}\Big)\Big(e^{\Omega}\zeta_{2}\,\varphi_{1}+\zeta_{1}\,\varphi_{2}\Big)\bigg)\wedge\d z\bigg].
-  \end{aligned}
-\end{equation}}
-
 Finally, the metric parametrising this moduli space is:
@@
 Even though the vacuum breaks half of the supersymmetries, we are able to construct a consistent truncation to 3-dimensional maximal gauged supergravity, providing an uplift to the ${\cal N}=16$ gauged supergravity proposed in \cite{Hohm:2005ui} for the 3-dimensional description of this AdS$_3$ vacuum.
-We constructed our consistent truncation by doing a $S^1$ reduction of the truncation of IIB on $S^3 \times S^3$ \cite{Inverso:2016eet}, and turning on an additional $H_7$ flux on $S^3 \times S^3 \times S^1$, which is necessary to obtain an AdS$_3$ vacuum.
+We constructed our consistent truncation by doing a $S^1$ reduction of the truncation of IIB on $S^3 \times S^3$ \cite{Inverso:2016eet}, and turning on an additional $H_{(7)}$ flux on $S^3 \times S^3 \times S^1$, which is necessary to obtain an AdS$_3$ vacuum.
 We also show that it is not possible to turn on such an additional flux for the other ``dyonic'' consistent truncations on $S^6$, $S^5 \times S^1$, $S^4 \times S^2$ \cite{Guarino:2015jca,Inverso:2016eet} reduced on $S^1$, whilst maintaining a consistent truncation to ${\cal N}=16$ gauged supergravity.
